### 2015-07-17 draft/fs_qa.tex
revised-17/07/2015

\documentclass[11pt]{iopart}
\usepackage[english]{babel}
\pdfoutput=1
%\usepackage{amsmath}
\usepackage{wasysym}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{sidecap}
\usepackage{bm}% bold math

\usepackage[colorlinks,bookmarks=false,citecolor=blue,linkcolor=red,urlcolor=blue]{hyperref}

%\usepackage{cite}

%
% WARNING !!!!
% 
% iopart.cls definition of \tableofcontents overwrites the
% short title printed every page. 
% The following redefinition of \tableofcontents fixes the
% the problem.

\catcode`@=11 % If we need private TeX macros
\renewcommand\tableofcontents{%
  \section*{\contentsname}%
  \@starttoc{toc}%
}
\catcode`@=12% '@' is no more a character
\newcommand{\bra}[1]{\langle\left.{#1}\right|}
\newcommand{\ket}[1]{\left|{#1}\right.\rangle}

\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\u{\uparrow}
\def\d{\downarrow}
\def\nm{\newmoon}
\def\fm{\fullmoon}
\def\T{\rule{0pt}{.6cm}}
\def\B{\rule[-.4cm]{0pt}{0pt}}

\begin{document}

\setlength{\parindent}{0pt}

\title{Finite-size study of the Quench Action approach in integrable spin 
chains}

\author{Vincenzo Alba$^1$, Pasquale Calabrese$^1$}
\address{$^1$ International School for Advanced Studies (SISSA),
Via Bonomea 265, 34136, Trieste, Italy,
INFN, Sezione di Trieste}

\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

fdasfa
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%% INTRODUCTION %%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{intro}

%%%%%% NEEL OVERLAP
\section{Overlap with the Neel state}

Let us consider a generic $n$-string state
%
\begin{equation}
\lambda_{n;\alpha}^{a}=\lambda_{n;\alpha}+\frac{i}{2}(n+1-2a)+i\delta_{n;\alpha}^{a}
\quad\textrm{with}\, a=1,\dots, n.
\end{equation}
%
We denote the generic parity invariant eigenstate as $|\{\pm\lambda_j\}_{j=1}^m,n_\infty\rangle$, 
where $m$ is the number of rapidity pairs, $N_{\infty}$ is the number of infinite rapidities, 
with $M=L/2=N_\infty+2m$, and $n_\infty\equiv N_\infty/L$ is the infinite rapidities density.

The overlap with the Neel state $|\Psi_0\rangle$ reads 
%
\begin{equation}
\label{neel-ov}
\frac{\langle\Psi_0|\{\pm\lambda_j\}_{j=1}^m,n_\infty\rangle}{|||\{\lambda_j\}_{j=1}^m,n_\infty\rangle||}=
\frac{\sqrt{2}N_{\infty}!}{\sqrt{(2N_\infty)!}}\left[\prod_{j=1}^m\frac{\sqrt{\lambda_j^2+1/4}}{4\lambda_j}
\right]\sqrt{\frac{\textrm{det}_m(G^+)}{\textrm{det}_m(G^-)}}
\end{equation}
%
where 
%
\begin{equation}
\label{G-pm}
G^{\pm}_{jk}=\delta_{jk}\left(NK_{1/2}(\lambda_j)-\sum\limits_{l=1}^mK_1^+(\lambda_j,\lambda_l)\right)
+K_{1}^{\pm}(\lambda_j,\lambda_k),\quad\,j,k=1,\dots,m
\end{equation}
%
and 
%
\begin{equation}
\label{K-1}
K_1^\pm(\lambda,\mu)=K_1(\lambda-\mu)\pm K_1(\lambda+\mu)
\end{equation}
%
and 
%
\begin{equation}
\label{K-alpha}
K_\alpha(\lambda)\equiv\frac{2\alpha}{\lambda^2+\alpha^2}
\end{equation}
%

%%%%%% REDUCED NEEL OVERLAP
\subsection{Reduced Neel overlap}

In the case of perfect strings the matrices $G^{\pm}_{jk}$ become ill-defined. Precisely, 
$K_{1}^+(\lambda,\mu)$ diverges if $\lambda$ and $\mu$ are successive members of 
the same string, i.e., $|\lambda-\mu|=i$.

It is possible to rewrite~\eref{neel-ov} in terms of the string centers $\lambda_{n;\alpha}$ only. 
Here we restrict ourselves to rapidity configurations with no zero-momentum strings.

It is convenient to split the indices $i,j$ of $G^\pm_{ij}$ as $i=(n,\alpha)$ $j=(m,\beta)$, 
with $n,m$ being the length of the strings and $\alpha,\beta$ labelling the string centers.

The result reads 
%
\begin{equation}
\fl \frac{1}{2}G^+_{(n,\alpha)(m,\beta)}=\left\{\begin{array}{cc}
L\theta_n'(\lambda_{n;\alpha})
-\sum\limits_{(\ell,\gamma)\ne(n,\alpha)}(\Theta'_{n,\ell}
(\lambda_{n;\alpha}-\lambda_{\ell;\gamma})+\Theta'_{n,\ell}
(\lambda_{n;\alpha}+\lambda_{\ell;\gamma})) & \textrm{if}\,(n,\alpha)= (m,\beta)\\
\Theta'_{n,m}
(\lambda_{n;\alpha}-\lambda_{m;\beta})+\Theta'_{n,m}
(\lambda_{n;\alpha}+\lambda_{m;\beta}) & \textrm{if}\,(n,\alpha)\ne(m,\beta)
\end{array}\right.
\end{equation}
%
Here $\theta_n'(x)\equiv d/dx\theta_n(x)$ and $\Theta'(x)\equiv d/dx\Theta(x)$.

For $G^-_{ij}$ one obtains

\begin{equation}
\fl\frac{1}{2}G^-_{(n,\alpha)(m,\beta)}=\left\{\begin{array}{cc}
(L-1)\theta'_n(\lambda_{n;\alpha})-2\sum\limits_{k=1}^{n-1}\theta'_k(\lambda_{n;\alpha})
-\sum\limits_{(\ell,\gamma)\ne(n,\alpha)}(\Theta'_{n,\ell}
(\lambda_{n;\alpha}-\lambda_{\ell;\gamma})+\Theta'_{n,l}
(\lambda_{n;\alpha}+\lambda_{\ell;\gamma})) & \quad\textrm{if}\,(n,\alpha)= (m,\beta)\\
\Theta'_{n,m}
(\lambda_{n;\alpha}-\lambda_{m;\beta})-\Theta'_{n,m}
(\lambda_{n;\alpha}+\lambda_{m;\beta})) & \quad\textrm{if}\,(n,\alpha)\ne(m,\beta)
\end{array}\right.
\end{equation}
%
Finally, the multiplicative prefactor in~\eref{neel-ov} for the generic $n$-string 
can be rewritten as 
%
\begin{equation}
\prod\limits_{a=1}^n\frac{\sqrt{(\lambda^a_{n;\alpha})^2+1/4}}{4\lambda^a_{n;\alpha}}=
\frac{1}{4^n}\left(\frac{\sqrt{n^2+\lambda^2_{n;\alpha}}}{\lambda_{n;\alpha}}
\prod\limits_{k=0}^{\lceil n/2\rceil-1}\frac{(2k)^2+\lambda^2_{n;\alpha}}{(2k+1)^2+
\lambda^2_{n;\alpha}}\right)^{{\mathcal P}},
\end{equation}
%
with ${\mathcal P}=+$ and ${\mathcal P}=-$ for even and odd strings, respectively.

\begin{table}[h]
\scriptsize
\centering
Bethe states with nonzero N\'eel overlap ($N=12$)\\[1ex]
\begin{tabular}{rrrrr}
String content & $2I^+_n$ & E & $|\langle \{\lambda\}| \Psi_0 \rangle|^2$ & here \\[0.3em]
\toprule
6 inf & - & $0$ & $0.002164502165$ & $0.002164502165$ \\
\midrule
2 one, 4 inf &$1_1 $ & $-3.918985947229$ & $0.096183409244$ & $0.096183409244237$ \\
 &$3_1 $ & $-3.309721467891$ & $0.011288497947$ &  $0.0112884979464673$\\
 &$5_1 $ & $-2.284629676547$ & $0.004542580506$ &  $0.0045425805061850$\\
 &$7_1 $ & $-1.169169973996$ & $0.002752622983$ &  $0.0027526229835876$\\
 &$9_1 $ & $-0.317492934338$ & $0.002116006203$ &  $0.0021160062026402$\\
\midrule
4 one, 2 inf &$1_1 3_1 $ & $-7.070529325964$ & $0.310133033838$ &$ 0.554809782804$ \\
  &$1_1 5_1 $ & $-5.847128730477$ & $0.129277023687$ \\
  &$ 1_1 7_1$ & $-4.570746557876$ & $0.085992436024$ \\
  &$ 3_1 5_1$ & $-5.153853093221$ & $0.015256395523$ \\
  &$3_1 7_1 $ & $-3.916336243695$ & $0.010091113504$ \\
  &$5_1 7_1 $ & $-2.817696043731$ & $0.004059780228$ \\
  \midrule
2 two, 2 inf &$1_2 $ & $-1.905667167442$ & $0.001207238321$ & $0.005468702625$\\
  &$3_2 $ & $-1.368837200825$ & $0.002340453815$ \\
  &$5_2 $ & $-0.681173793635$ & $0.001921010489$ \\
    \midrule
1 one, 1 three, 2 inf &$0_1 0_3 $ & $-2.668031843135$ & $0.034959609810$ & $0.034959609810$ \\
    \midrule
6 one &$1_1 3_1 5_1 $ & $-8.387390917445$ & $0.153412152966$ & $0.153412152966$ \\
  \midrule
2 two, 2 one &$1_1 1_2 $ & $-5.401838225870$ & $0.040162686361$ & $0.046134750850$ \\
  &$3_1 1_2 $ & $-4.613929948329$ & $0.004636541934$ \\
  &$5_1 1_2 $ & $-3.147465758841$ & $0.001335522556$ \\
    \midrule
1 three, 3 one &$0_1 2_1 0_3$ & $-6.340207488736$ & $0.052743525774$ & $0.078910020729$ \\
  &$0_1 4_1 0_3$ & $-5.203653009936$ & $0.015022005621$ \\
  &$0_1 6_1 0_3$ & $-3.788693957250$ & $0.011144489334$ \\
      \midrule
1 five, 1 one &$0_1 0_5$ & $-2.444293750583$ & $0.005887902992$ & $0.005887902992$ \\
      \midrule
2 three &$1_3$ & $-1.111855930538$ & $0.001342476001$ & $0.001342476001$ \\
      \midrule
1 two, 1 four &$0_2 0_4$ & $-1.560671012472$ & $0.000026982174$ & $0.000026982174$ \\
  \bottomrule
 \end{tabular}
\caption{All Bethe states for $N=12$ with nonzero overlap with the zero-momentum N\'eel state. The 
overlap squares add up to $1$ up to the precision in which the Bethe equations were solved. The 
$2I^+_n$ in the second column give the positive $n$-string quantum numbers of the parity-invariant 
Bethe states.}
\label{table:RV:sumruleN12}
\end{table}

%##################################################################
\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\textwidth]{./draft_figs/L20_BT_check}
\end{center}
\caption{ The squared overlap $|\langle\Psi_0|\{\lambda\}\rangle|^2$ between the the 
 Neel state $|\Psi_0\rangle$ and the eigenstates $|\{\lambda\}\rangle$ of the $XXX$ 
 chain with $L=22$ sites. Only non-zero overlaps are shown. In all the panels the 
 $x$-axis shows the eigenstate energy density $E/L$. The circles are the exact 
 diagonalization results for all the non-zero overlaps. The crosses are the Bethe 
 ansatz results obtained using the Bethe-Gaudin-Takahashi equations. The missing 
 crosses correspond to eigenstates containing zero-momentum strings. (a) Overview 
 of all the non-zero overlaps. (b)(c)(d) The same overlaps as in (a) zooming in 
 the regions $[0,0.2]$, $[0,0.020]$, and $[0,4\cdot 10^{-5}]$. The discrepancies 
 between the ED and the Bethe ansatz results are attributed to the string deviations. 
}
\label{fig1-BGT-check}
\end{figure}
%##################################################################

%##################################################################
\begin{figure}[t]
\begin{center}
\includegraphics[width=.6\textwidth]{./draft_figs/Neel_over}
\end{center}
\caption{ The overlap sum rule $\sum_{\{\lambda\}}|\langle\{\lambda\}|\Psi_0\rangle|^2$, 
 with $|\Psi_0\rangle$ the Neel state and $|\{\lambda\}\rangle$ the eigenstates  of the 
 $XXX$ spin chain, plotted versus $1/L$, with $L$ the chain length. The circles are 
 Bethe ansatz results for chains up to $L=36$. Only the eigenstates with no zero-momentum 
 strings are considered in the sum. The dash-dotted line is a fit to $A/L^{1/2}+B/L$, with 
 $A,B$ fitting parameters. Inset: The same data as in the main Figure plotted versus 
 $1/L^{1/2}$.
}
\label{fig2-neel-sr}
\end{figure}
%##################################################################

%##################################################################
\begin{figure}[t]
\begin{center}
\includegraphics[width=.6\textwidth]{./draft_figs/Dimer_over}
\end{center}
\caption{ The overlap sum rule $\sum_{\{\lambda\}}|\langle\{\lambda\}|\Psi_0\rangle|^2$, 
 with $|\Psi_0\rangle$ the Majumdar-Ghosh state and $|\{\lambda\}\rangle$ the eigenstates  
 of the $XXX$ spin chain, plotted versus $1/L$, with $L$ the chain length. The circles are 
 Bethe ansatz results for chains up to $L=32$. Only the eigenstates with no zero-momentum 
 strings are considered in the sum. The dash-dotted line is a fit to $A/L^{1/2}+B/L$, with 
 $A,B$ fitting parameters. Inset: The same data as in the main Figure plotted versus 
 $1/L^{1/2}$.
}
\label{fig3-dimer-sr}
\end{figure}
%##################################################################

%##################################################################
\begin{figure}[t]
\begin{center}
\includegraphics[width=.75\textwidth]{./draft_figs/Neel_over_ener}
\end{center}
\caption{ The overlap between the Neel state and the eigenstates of the 
 $XXX$ chain as a function of the eigenstate energy. (a) The squared 
 overlap $|\langle\{\lambda\}|Neel\rangle|^2$ plotted versus the 
 eigenstates energy density $E/L$. The data are Bethe ansatz results 
 for chains of length $L=22,26,32,36$ (different symbols). (b) Same as 
 in (a) plotting on the $y$-axis the combination $-2\log(|\langle\{
 \lambda\}|Neel\rangle|)/L$. 
}
\label{fig4-neel-ener}
\end{figure}
%##################################################################

%%%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{thebibliography}{99}

%\end{thebibliography}

\end{document}

### 2015-07-17 old_notes/check.tex
revised-17/07/2015

\documentclass[12pt,a4paper,final]{iopart} 
\usepackage{graphicx}
%\pdfoutput=1
\usepackage{amsfonts, dsfont}

\usepackage{leftidx}
\usepackage{cite}
\usepackage{booktabs}

\usepackage{verbatim}
\usepackage{color}
\usepackage[colorlinks,bookmarks=false,citecolor=blue,
linkcolor=red,urlcolor=blue]{hyperref}
\usepackage{times}

%%%%%%%%%%%%%   useful shortcuts %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{table}[h]
\scriptsize
\centering
Bethe states with nonzero M-G overlap ($L=12$)\\[1ex]
\begin{tabular}{rrrr}
String content & Energy (ED) & $|\langle \{\lambda\}| \Psi_0 \rangle|^2$ (ED) & $|\langle \{\lambda\}| \Psi_0 \rangle|^2$ (B-T) \\[0.3em]
\toprule
$1_1 3_1 5_1$ & $-8.38739$  & $0.716616$     &  $0.7166157692239$\\
              & $-6.34021$  & $0.205891$     &  \\
$5_1 1_2$     & $-5.40184$  & $0.0556247$    & $0.05403336654338$\\
              & $-5.20365$  & $0.0388322$    & \\
$3_1 1_2$     & $-4.61393$  & $0.00568743$   & $0.005582983043235$\\
              & $-3.78869$  & $0.00601941$   & \\
$1_1 1_2$     & $-3.14747$  & $0.00210748$   & $0.0021070869333835$\\
              & $-2.44429$  & $0.000129601$  & \\
              & $-1.56067$  & $0.000330573$  & \\
$1_3$         & $-1.11186$  & $0.0000117278$ & $0.000012785579923275$\\
\bottomrule
\end{tabular}
\caption{All Bethe states for $L=12$ with nonzero overlap with the zero-momentum 
 M-G state. The first column show the string content of the eigenstate. The second 
 and third columns show the exact diagonalization resutls for the energy and the 
 overlap, respectively. The last colum is the overlap obtained in the Bethe ansatz 
 approach using the Bethe-Takahashi equations.
}
\label{table:RV:sumruleN12}
\end{table}

\begin{table}[h]
\scriptsize
\centering
Bethe states with nonzero M-G overlap ($L=16$)\\[1ex]
\begin{tabular}{rrrr}
String content & Energy (ED) & $|\langle \{\lambda\}| \Psi_0 \rangle|^2$ (ED) & $|\langle \{\lambda\}| \Psi_0 \rangle|^2$ (B-T) \\[0.3em]
\toprule
$7_1 5_1 3_1 1_1$ & $-11.1423$ & $0.517742$         & $0.5177418283152$\\
& $-9.59129$ & $0.244845$         &\\
$7_1 5_1 1_2$ & $-8.81424$ & $0.0727096$        & $0.07100180464371$\\
& $-8.56579$ & $0.082852$         &\\
$7_1 3_1 1_2$ & $-7.96995$ & $0.0232953$        & $0.02300602650371$\\
& $-7.89112$  & $0.0181713$        &\\
$7_1 1_1 1_2$ & $-7.51522$ & $0.00245007$       & $0.002427999643379$\\
& $-7.41983$ & $0.0192443$        &\\
$5_1 3_1 1_2$ & $-6.80829$ & $0.012519$         & $0.012518660407092$\\
& $-6.78357$ & $0.00398018$       &\\
$5_1 1_1 1_2$ & $-6.3398$  &  $0.00135119$      & $0.0013511980854654$\\
& $-6.25276$ & $0.000721952$      &\\
& $-5.86683$ & $0.00112415$       &\\
& $-5.69103$ & $0.000141052$      &\\
& $-5.50802$ & $0.00373666$       &\\
$3_1 1_2$ & $-5.45276$ & $0.000466819$      & $0.0004668223478716$\\
& $-5.06385$ & $0.000380056$      & $0.000166548883431$\\
& $-4.86668$ & $0.0000395855$     &\\
& $-4.64743$ & $0.000014786$      & $0.000016403668846624$\\
& $-4.49059$ & $0.00155894$       &\\
& $-4.25924$ & $0.000109932$      &\\
& $-3.93068$ & $4.12108e-6$       & $4.6283550855711e-6$\\
& $-3.92645$ & $0.0000102752$     &\\
& $-3.77995$ & $0.0000732808$     &\\
& $-3.259$   & $0.0000348879$     &\\
& $-3.12751$ & $0.0000739906$     & $0.00007017294942524$\\
& $-3.04176$ & $1.62543e-6$       &\\
& $-3.00072$ & $1.4684e-6$        & $1.6374806913113e-6$\\
& $-2.32465$ & $2.01172e-8$       &\\
& $-2.26529$ & $7.53377e-6$       &\\
& $-2.02465$ & $5.8028e-7$        & $5.722094498217e-7$\\
& $-1.38078$ & $2.17607e-7$       &\\
& $-1.11438$ & $1.825e-7$         &\\
& $-0.844856$& $1.84715e-9$       & $2.4957509639475e-9$\\
\bottomrule
\end{tabular}
\caption{All Bethe states for $L=12$ with nonzero overlap with the zero-momentum 
 M-G state. The first column show the string content of the eigenstate. The second 
 and third columns show the exact diagonalization resutls for the energy and the 
 overlap, respectively. The last colum is the overlap obtained in the Bethe ansatz 
 approach using the Bethe-Takahashi equations.
}
\label{table:RV:sumruleN12}
\end{table}

\end{document}

### 2015-07-17 draft/compile.sh

@@ -1,0 +1,1 @@
+pdflatex Neel_v1.tex

### 2015-07-23 draft/fs_qa.tex
rev

@@
 
+We show that it is possible to numerically simulate the Quench Action approach 
+combining Monte Carlo methods and Bethe ansatz techniques.
+
+We focus on the situation in which the pre-quench initial state is the Neel 
+state or the Majumdar-Ghosh state.
+
+We investigate the importance of the zero-momentum strings in the Quench Action.
+
+Without zero-momentum strings the overlap saturation rules are not valid, 
+i.e., in finite size systems the vast majority of the eigenstates contain 
+zero momentum strings.
+
+The details on the eigenstates counting depend on the pre-quench initial state.
+
+However, we show that one can restrict to the set of non-zero momentum strings. 
+The fact that one neglects zero-momentum strings gives rise only to scaling 
+corrections.
+
+We also investigate the validity of the Bethe-Takahashi approximation for the 
+calculation of the overlap.
+
+%%%%%%%%%%%%%%%%%%%%%%% BETHE ANSATZ APPROACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The Heisenberg spin chain}
+\label{xxx-chain}
+
+Here we consdier the spin-$\frac{1}{2}$ isotropic Heisenberg chain ($XXX$ chain). 
+The $XXX$ chain with $L$ sites is defined by the Hamiltonian 
+%
+\begin{equation}
+\label{xxx-ham}
+{\mathcal H}\equiv J\sum\limits_{i=1}^L\left[\frac{1}{2}(S_i^+S^-_{i+1} 
++S_i^{-}S_{i+1}^+)+S_i^zS_{i+1}^z\right],  
+\end{equation}
+%
+where $S^{\pm}_i\equiv (\sigma_i^x\pm i\sigma_i^y)/2$ are spin operators acting on the 
+site $i$, $S_i^z\equiv\sigma_i^z/2$, and $\sigma^{x,y,z}_i$ the Pauli matrices. We fix 
+$J=1$ and use periodic boundary conditions, identifying sites $L+1$ and $1$. The total 
+magnetization $S_{T}^z\equiv\sum_iS_i^z=L/2-M$, with $M$ number of down spins (particles), 
+commutes with~\eref{xxx-ham}, and it is here used to label its eigenstates.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Bethe equations and wavefunctions}
+\label{bethe_equations}
+
+The generic eigenstate of~\eref{xxx-ham} in the sector with $M$ particles can be written as 
+%
+\begin{equation}
+\label{ba_eig}
+|\Psi_M\rangle=\sum\limits_{1\le x_1<x_2<\dots<x_M\le L}A_M(x_1,x_2,
+\dots,x_M)|x_1,x_2,\dots,x_M\rangle,
+\end{equation}
+%
+where the sum is over the positions $\{x_i\}$ of the particles, and $A_M(x_1,
+x_2,\dots,x_M)$ is the eigenstate amplitude corresponding to particles 
+at positions $x_1,x_2,\dots, x_M$. $A_M(x_1,x_2,\dots, x_M)$ is given as 
+%
+\begin{equation}
+\label{ba_amp}
+A_M(x_1,x_2,\dots,x_M)\equiv\sum\limits_{{\mathcal P}\in S_M}\exp\Big[i
+\sum\limits_{j=1}^Mk_{{\mathcal P}_j}x_j+i\sum\limits_{i<j}\theta_{{
+\mathcal P}_i{\mathcal P}_j}\Big].
+\end{equation}
+%
+Here the outermost sum is over the permutations $S_M$ 
+of the so-called quasi-momenta $\{k_1,k_2,\dots,k_M\}$. The two-particle 
+scattering phases $\theta_{m,n}$ are defined as 
+%
+\begin{equation}
+\label{s_phases}
+\theta_{m,n}\equiv \frac{1}{2i}\log\Big[-\frac{e^{ik_m+ik_n}-2e^{ik_m}+1}
+{e^{ik_m+ik_n}-2e^{ik_n}+1}\Big].
+\end{equation}
+%
+The energy associated to the eigenstate~\eref{ba_eig} is  
+%
+\begin{equation}
+\label{ba_ener}
+E=\sum\limits_{\alpha=1}^M(\cos(k_\alpha)-1).
+\end{equation}
+%
+The quasi-momenta $\{k_\alpha\}$ are obtained by solving the so-called 
+Bethe equations  
+%
+\begin{equation}
+\label{ba_eq}
+e^{ik_\alpha L}=\prod\limits^M_{\beta\ne\alpha}\Big[-\frac{1-2e^{
+ik_\alpha}-e^{ik_\alpha+ik_\beta}}{1-2e^{ik_\beta}-e^{ik_\alpha+
+ik_\beta}}\Big].
+\end{equation}
+%
+It is useful to  introduce the rapidities $\{\lambda_\alpha\}$ as 
+%
+\begin{equation}
+\label{rap}
+k_\alpha=\pi-2\arctan(\lambda_\alpha)\quad\mbox{mod}\, 2\pi.
+\end{equation}
+%
+Taking the logarithm on both sides in~\eref{ba_eq}, and using~\eref{rap}, 
+one obtains the Bethe equations in logarithmic form as 
+%
+\begin{equation}
+\label{ba_eq_log}
+\arctan(\lambda_\alpha)=\frac{\pi}{L}J_\alpha+\frac{1}{L}\sum\limits_{
+\beta\ne\alpha}\arctan\Big(\frac{\lambda_\alpha-\lambda_\beta}{2}\Big),
+\end{equation}
+%
+where $-L/2<J_\alpha\le L/2$ are the so-called Bethe quantum numbers. The 
+$J_\alpha$ are half-integers and integers for $L-M$ even and odd.
+
+These solutions of the Bethe equations~\eref{ba_eq} form particular ``string'' patterns 
+in the complex plane, in the limit of large chains $L\to\infty$(string hypothesis)~\cite{
+bethe-1931,taka-book}. Specifically, rapidities forming a ``string'' of length $1\le 
+n\le M$ (that we defined here as $n$-string) are parametrized as 
+%
+\begin{equation}
+\label{str_hyp}
+\lambda^{j}_{n;\gamma}=\lambda_{n;\gamma}-i(n-1-2j)+i\delta_{n;\gamma}^j,\qquad 
+j=0,1,\dots, n-1, 
+\end{equation}
+%
+where $\lambda_{n;\gamma}$ is the real part of the string (string center), 
+and $\gamma$ labels strings with different centers, while $j$ labels the different 
+components of the string. In~\eref{str_hyp} $\delta_{n;\gamma}^j$ are the string 
+deviations, which typically vanish exponentially in the thermodynamic limit.
+
+Notice that pure real rapidities are strings of unit length ($1$-strings).
+
+\subsection{Bethe-Takahashi equations.}
+
+The string centers $\lambda_{n;\gamma}$ in~\eref{str_hyp} are obtained by solving the 
+so-called Bethe-Takahashi equations
+%
+\begin{equation}
+\label{bt_eq}
+2L\theta_n(\lambda_{n;\gamma})=2\pi I_{n;\gamma}+\sum\limits_{(m,
+\beta)\ne(n,\gamma)}\Theta_{m,n}(\lambda_{n;\gamma}-\lambda_{m;\beta}), 
+\end{equation}
+%
+where the generalized scattering phases $\Theta_{m,n}$ read 
+%
+\begin{eqnarray}
+\nonumber\fl\Theta_{m,n}(x)\equiv\left\{\begin{array}{cc}
+\theta_{|n-m|}(x)+\!\!\!\!\!\sum
+\limits_{r=1}^{(n+m-|n-m|-1)/2}\!\!\!\!\!2\theta_{|n-m|+2r}(x)
++\theta_{n+m}(x) & \quad\mbox{if}
+\quad n\ne m\\\fl\sum\limits_{r=1}^{n-1}2\theta_{2r}(x)+
+\theta_{2n}(x) & \quad\mbox{if}\quad n=m
+\end{array}\right.
+\end{eqnarray}
+%
+and $\theta_\alpha(x)\equiv 2\arctan(x/\alpha)$. Here $I_{n;\gamma}$ are the 
+Bethe-Takahashi quantum numbers associated with $\lambda_{n;\gamma}$.
+
+Each $M$-particle eigenstate can be characterized by its ``string content'' ${
+\mathcal S}\equiv\{s_1,\dots,s_M\}$, with $s_n$ the number of $n$-strings.
+
+It can be shown that $I_{n;\gamma}$  are integers or half-integers for $L-s_n$ 
+odd and even, respectively.
+
+Clearly, the constraint $\sum_{\alpha=1}^{M}\alpha s_\alpha=M$ 
+has to be satisfied. The upper bound for the Bethe-Takahashi quantum numbers 
+can be derived as   
+%
+\begin{equation}
+|I_{n;\gamma}|\le I^{(MAX)}_{n}\equiv\frac{1}{2}(L-1-\sum
+\limits_{m=1}^Mt_{m,n}s_m),
+\label{bt_qn_bound}
+\end{equation}
+%
+where $t_{m,n}\equiv 2\mbox{min}(n,m)-\delta_{m,n}$.
+
 %%%%%% NEEL OVERLAP
@@
 
-Let us consider a generic $n$-string state
-%
-\begin{equation}
-\lambda_{n;\alpha}^{a}=\lambda_{n;\alpha}+\frac{i}{2}(n+1-2a)+i\delta_{n;\alpha}^{a}
-\quad\textrm{with}\, a=1,\dots, n.
-\end{equation}
-%
-We denote the generic parity invariant eigenstate as $|\{\pm\lambda_j\}_{j=1}^m,n_\infty\rangle$, 
-where $m$ is the number of rapidity pairs, $N_{\infty}$ is the number of infinite rapidities, 
-with $M=L/2=N_\infty+2m$, and $n_\infty\equiv N_\infty/L$ is the infinite rapidities density.
+Here we restrict to the parity-invariant eigenstates. These are the only 
+eigenstates with non-zero overlap with the Neel state. Parity-invariant 
+eigenstates contain only pairs of rapidities with opposite sign.
 
-The overlap with the Neel state $|\Psi_0\rangle$ reads 
+We denote the generic parity invariant eigenstate as $|\{\pm\lambda_j\}_{j=1}^m,
+n_\infty\rangle$, where $m$ is the number of rapidity pairs, $N_{\infty}$ is the 
+number of infinite rapidities, with $M=L/2=N_\infty+2m$, and $n_\infty\equiv 
+N_\infty/L$ is the density of infinite rapidities.
+
+The overlap with the Neel state $|N\rangle$ reads 
 %
@@
 \label{neel-ov}
-\frac{\langle\Psi_0|\{\pm\lambda_j\}_{j=1}^m,n_\infty\rangle}{|||\{\lambda_j\}_{j=1}^m,n_\infty\rangle||}=
-\frac{\sqrt{2}N_{\infty}!}{\sqrt{(2N_\infty)!}}\left[\prod_{j=1}^m\frac{\sqrt{\lambda_j^2+1/4}}{4\lambda_j}
-\right]\sqrt{\frac{\textrm{det}_m(G^+)}{\textrm{det}_m(G^-)}}
+\frac{\langle N|\{\pm\lambda_j\}_{j=1}^m,n_\infty\rangle}{|||\{\lambda_j\}_{j=1}^m,
+n_\infty\rangle||}=\frac{\sqrt{2}N_{\infty}!}{\sqrt{(2N_\infty)!}}\left[\prod_{j=1}^m
+\frac{\sqrt{\lambda_j^2+1}}{4\lambda_j}\right]\sqrt{\frac{\textrm{det}_m(G^+)}{
+\textrm{det}_m(G^-)}}
 \end{equation}
@@
 \label{G-pm}
-G^{\pm}_{jk}=\delta_{jk}\left(NK_{1/2}(\lambda_j)-\sum\limits_{l=1}^mK_1^+(\lambda_j,\lambda_l)\right)
-+K_{1}^{\pm}(\lambda_j,\lambda_k),\quad\,j,k=1,\dots,m
+G^{\pm}_{jk}=\delta_{jk}\Big(NK_{1/2}(\lambda_j)-\sum\limits_{l=1}^mK_1^+(\lambda_j,
+\lambda_l)\Big)+K_{1}^{\pm}(\lambda_j,\lambda_k),\quad\,j,k=1,\dots,m
 \end{equation}
@@
 \label{K-alpha}
-K_\alpha(\lambda)\equiv\frac{2\alpha}{\lambda^2+\alpha^2}
+K_\alpha(\lambda)\equiv\frac{8\alpha}{\lambda^2+4\alpha^2}
 \end{equation}
@@
 
-In the case of perfect strings the matrices $G^{\pm}_{jk}$ become ill-defined. Precisely, 
-$K_{1}^+(\lambda,\mu)$ diverges if $\lambda$ and $\mu$ are successive members of 
-the same string, i.e., $|\lambda-\mu|=i$.
+Here we consider the overlap formula for the Neel state~\eref{neel-ov} in the 
+limit $L\to\infty$, assuming that the rapidities form perfect strings.
 
-It is possible to rewrite~\eref{neel-ov} in terms of the string centers $\lambda_{n;\alpha}$ only. 
-Here we restrict ourselves to rapidity configurations with no zero-momentum strings.
+In the case of perfect strings the matrices $G^{\pm}_{jk}$ become ill-defined. 
+Precisely, $K_{1}^\pm(\lambda,\mu)$ diverges if $\lambda$ and $\mu$ are successive 
+members of the same string, i.e., $|\lambda-\mu|=2i$.
 
-It is convenient to split the indices $i,j$ of $G^\pm_{ij}$ as $i=(n,\alpha)$ $j=(m,\beta)$, 
-with $n,m$ being the length of the strings and $\alpha,\beta$ labelling the string centers.
+It is possible to rewrite~\eref{neel-ov} in terms of the string centers 
+$\lambda_{n;\alpha}$ only. Here we restrict ourselves to rapidity configurations 
+with no zero-momentum strings. Our results are not valid for zero-rapidity 
+strings. These would require the knowledge of the precise form of the string 
+deviations, i.e., the dependence of the string deviations on $L$, as it has 
+been pointed out in Ref.~\cite{calabrese-2014}.
+
+It is convenient to split the indices $i,j$ of $G^\pm_{ij}$ as $i=(n,\alpha)$ 
+$j=(m,\beta)$, with $n,m$ being the length of the strings and $\alpha,\beta$ 
+labelling the string centers.
 
@@
 %
-Here $\theta_n'(x)\equiv d/dx\theta_n(x)$ and $\Theta'(x)\equiv d/dx\Theta(x)$.
+Here $\theta_n'(x)\equiv d/dx \theta_n(x)=2n/(n^2+x^2)$ and $\Theta'(x)\equiv d/dx
+\Theta(x)$.
 
@@
 \begin{equation}
-\prod\limits_{a=1}^n\frac{\sqrt{(\lambda^a_{n;\alpha})^2+1/4}}{4\lambda^a_{n;\alpha}}=
+\prod\limits_{a=1}^n\frac{\sqrt{(\lambda^a_{n;\alpha})^2+1}}{4\lambda^a_{n;\alpha}}=
 \frac{1}{4^n}\left(\frac{\sqrt{n^2+\lambda^2_{n;\alpha}}}{\lambda_{n;\alpha}}
@@
 with ${\mathcal P}=+$ and ${\mathcal P}=-$ for even and odd strings, respectively.
+
+%%%%%% REDUCED MG overlap 
+\section{Overlap with the Majumdar-Ghosh state}
+
+The overlap between the generic eigenstate of the $XXX$ chain and the Majumdar-Ghosh 
+state is obtained fro the overlap with the Neel state as 
+%
+\begin{equation}
+\label{ov-MG}
+\langle MG|\{\lambda_j\}_{j=1}^M\rangle=\prod\limits_{j=1}^M\frac{1}{\sqrt{2}}
+\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)\langle N|\{\lambda_j\}_{j=1}^M\rangle
+\end{equation}
+%
+The mutliplicative factor in~\eref{ov-MG}, using the string hypothesis for the generic 
+$n$-string is rewritten as 
+%
+%\begin{equation}
+%\prod\limits_{j=1}^M\frac{1}{\sqrt{2}}
+%\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)=2^n\lambda_{n;\gamma}^2(\lambda_{n;
+%\gamma}^2+n^2)\prod\limits_{k=0}^{n/2}\frac{1}{(\lambda_{n;\gamma}^2+(2k)^2)^2}
+%\end{equation}
+%
+\begin{equation}
+\prod\limits_{j=1}^M\frac{1}{\sqrt{2}}
+\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)=2^n\prod\limits_{k=0}^{\lfloor 
+n/2\rfloor}\frac{1}{[\lambda_{n;\gamma}^2+(2k+(1-(-1)^n)/2)^2]^2}
+\end{equation}
+%
+
+%##################################################################
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=.9\textwidth]{./draft_figs/L20_BT_check}
+\end{center}
+\caption{ The squared overlap $|\langle\Psi_0|\{\lambda\}\rangle|^2$ between the the 
+ Neel state $|\Psi_0\rangle$ and the eigenstates $|\{\lambda\}\rangle$ of the $XXX$ 
+ chain with $L=22$ sites. Only non-zero overlaps are shown. In all the panels the 
+ $x$-axis shows the eigenstate energy density $E/L$. The circles are the exact 
+ diagonalization results for all the non-zero overlaps. The crosses are the Bethe 
+ ansatz results obtained using the Bethe-Gaudin-Takahashi equations. The missing 
+ crosses correspond to eigenstates containing zero-momentum strings. (a) Overview 
+ of all the non-zero overlaps. (b)(c)(d) The same overlaps as in (a) zooming in 
+ the regions $[0,0.2]$, $[0,0.020]$, and $[0,4\cdot 10^{-5}]$. The discrepancies 
+ between the ED and the Bethe ansatz results are attributed to the string deviations. 
+}
+\label{fig1-BGT-check}
+\end{figure}
+%##################################################################
+
+%##################################################################
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=.9\textwidth]{./draft_figs/Neel}
+\end{center}
+\caption{ Overlap sum rules for the Neel state. (a) The overlap sum rule 
+ $\sum_{\{\lambda\}}|\langle\{\lambda\}|N\rangle|^2=1$, with $|N\rangle$ 
+ the Neel state and $|\{\lambda\}\rangle$ the eigenstates  of the $XXX$ 
+ spin chain. The $x$-axis shows $1/L$, with $L$ the chain length. The 
+ circles are Bethe ansatz results for chains up to $L=36$. The results 
+ are obtained via a full scanning of the chain Hilbert space. Only the 
+ eigenstates with no zero-momentum strings are considered. The dash-dotted 
+ line is a fit to $A/L^{1/2}+B/L$, with $A,B$ fitting parameters. Inset: 
+ The same data as in the main Figure plotted versus $1/L^{1/2}$. (b) 
+ The same as in (a) for the sum rule $\sum_{\{\lambda\}}|\langle\{
+ \lambda\}|N\rangle|^2e(\{\lambda\})=1/2$, with $e(\{\lambda\})$  the 
+ eigenstates energy density. 
+}
+\label{fig2-neel-sr}
+\end{figure}
+%##################################################################
+
+%##################################################################
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=.9\textwidth]{./draft_figs/Dimer}
+\end{center}
+\caption{ Overlap sum rules for the Majumdar-Ghosh (MG) state. (a) The 
+ overlap sum rule $\sum_{\{\lambda\}}|\langle\{\lambda\}|MG\rangle|^2=1$, 
+ with $|MG\rangle$ the Majumdar-Ghosh state and $|\{\lambda\}\rangle$ 
+ the eigenstates  of the $XXX$ spin chain. The $x$-axis shows $1/L$, 
+ with $L$ the chain length. The circles are Bethe ansatz results for 
+ chains up to $L=36$. The results are obtained via a full scanning of 
+ the chain Hilbert space. Only the eigenstates with no zero-momentum 
+ strings are considered. The dash-dotted line is a fit to $A/L+B/L^2$, 
+ with $A,B$ fitting parameters. (b) The same as in (a) for the sum 
+ rule $\sum_{\{\lambda\}}|\langle\{\lambda\}|MG\rangle|^2e(\{\lambda\})=
+ 2/3$, with $e(\{\lambda\})$  the eigenstates energy density. 
+}
+\label{fig3-dimer-sr}
+\end{figure}
+%##################################################################
+
+%##################################################################
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=.75\textwidth]{./draft_figs/Neel_over_ener}
+\end{center}
+\caption{ The overlap between the Neel state and the eigenstates of the 
+ $XXX$ chain as a function of the eigenstate energy. (a) The squared 
+ overlap $|\langle\{\lambda\}|Neel\rangle|^2$ plotted versus the 
+ eigenstates energy density $E/L$. The data are Bethe ansatz results 
+ for chains of length $L=22,26,32,36$ (different symbols). (b) Same as 
+ in (a) plotting on the $y$-axis the combination $-2\log(|\langle\{
+ \lambda\}|Neel\rangle|)/L$. 
+}
+\label{fig4-neel-ener}
+\end{figure}
+%##################################################################
+
+%##################################################################
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=.9\textwidth]{./draft_figs/QAMC_Obs_Neel}
+\end{center}
+\caption{ The overlap between the Neel state and the eigenstates of the 
+ $XXX$ chain as a function of the eigenstate energy. (a) The squared 
+ overlap $|\langle\{\lambda\}|Neel\rangle|^2$ plotted versus the 
+ eigenstates energy density $E/L$. The data are Bethe ansatz results 
+ for chains of length $L=22,26,32,36$ (different symbols). (b) Same as 
+ in (a) plotting on the $y$-axis the combination $-2\log(|\langle\{
+ \lambda\}|Neel\rangle|)/L$. 
+}
+\label{fig4-neel-ener}
+\end{figure}
+%##################################################################
+
+%%%%%%
+\subsection{Counting of eigenstates with non-zero Neel overlap}
+
+We numerically checked that the number of states with non-zero overlap 
+with the Neel state is given as 
+%
+\begin{equation}
+Z_N=2^{\frac{L}{2}-1}+\frac{1}{2}B\left(\frac{L}{2},
+\frac{L}{4}\right)+1,
+\end{equation}
+%
+with $B(x,y)$ denoting the binomial coefficient. The contribution $1$ 
+accounts for the ferromagnetic state. Here 
+we assumed that $L$ is divisible by four. Here $Z_N$ is be obtained 
+as the total number of parity-invariant Bethe-Gaudin-Takahashi quantum 
+numbers.
+
+After excluding the zero-momentum strings the total number of states 
+with non-zero overlap with the Neel state is 
+%
+\begin{equation}
+\label{neel-ov-count}
+Z'_{N}=B\left(\frac{L}{2},\frac{L}{4}\right)
+\end{equation}
+%
+Importantly, the fraction of eigenstates corresponding to non-zero momentum 
+strings is vanishing in the thermodynamic limit as 
+%
+\begin{equation}
+\frac{Z_N'}{Z_N}\propto\frac{4}{\sqrt{\pi L}}.
+\end{equation}
+%
+%%%%% PROOF
+\subsection{Proof of~\eref{neel-ov-count}}
+
+Here we prove~\eref{neel-ov-count}. The proof follows very closely the one of the 
+completeness of the Bethe ansatz eigenstates {\bf cita qualcosa}. The proof is 
+based on the counting of all the possible parity-invariant quantum number configurations.
+
+Given a generic $M$-particle eigenstate of the $XXX$ chain, due to parity invariance, 
+if one excludes the zero-momentum strings only the $n$-strings with length $n\le M/2$ 
+can contribute.
+
+Thus, we denote the string content ${\mathcal S_{PI}}$ of a generic parity-invariant 
+with no zero-momentum string eigenstate as ${\mathcal S}_{PI}\equiv\{s_1,\dots,s_{M/2}\}$.
+Clearly one has the constraint $\sum_k ks_k=M/2$. We also restrict ourselves for simplicity 
+to $L$ divisible by four.
+
+The number of available parity-invariant quantum numbers ${\mathcal N}_n$ in the $n$-string 
+sector is given as  
+%
+\begin{equation}
+{\mathcal N}_n(L,{\mathcal S}_{PI})=\frac{L}{2}-\sum_{m=1}^{M/2}t_{nm}s_m.
+\end{equation}
+%
+Thus, the number of parity-invariant quantum number configurations ${\mathcal N}(L,{\mathcal 
+S}_{PI})$ compatible with string content ${\mathcal S}_{PI}$ is obtained by choosing in 
+all the possible ways the quantum numbers as  
+%
+\begin{equation}
+{\mathcal N}(L,{\mathcal S}_{PI})=\prod_{k=1}^{M/2} B({\mathcal N}_k,s_k).
+\end{equation}
+%
+It is useful to focus on the situation with fixed number of particles $0\le\ell\le M/2$ 
+and number $1\le q\le M/2$ of independent strings. The total number of eigenstates 
+${\mathcal N}''(L,\ell,q)$ is obtained as  
+%
+\begin{equation}
+\label{eq}
+{\mathcal N}''(L,\ell,q)=\sum\limits_{\{s_k\}\,s.t\, \sum k s_k=\ell, \sum s_k=q}{\mathcal N}(L,
+{\mathcal S}_{PI}).
+\end{equation}
+%
+where the sum is over all possible string contents $\{s_k\}$ compatible with the constraints 
+$\sum_k s_k=q$ and $\sum_k k s_k=\ell$.
+
+The idea is now to derive a recursive relation for ${\mathcal N}''(L,\ell,q)$. 
+It is useful to consider the shifted string content ${\mathcal S}'_{PI}$ as  
+%
+\begin{equation}
+{\mathcal S}'_{PI}\equiv \{s_{m+1}\}\quad\textrm{with}\, s_m\in{\mathcal S}_{PI}.
+\end{equation}
+%
+Observing that 
+%
+\begin{equation}
+t_{ij}=t_{i-1,j-1}+2,
+\end{equation}
+%
+one can write for $n>1$ that 
+%
+%\begin{eqnarray}
+%{\mathcal N}_n(L,{\mathcal S}_{PI})=\Big\lceil\frac{L}{2}-\frac{1}{2}\Big\rceil-t_{n,1}s_1-
+%\sum\limits_{m>1}t_{nm}s_m=\\
+%\Big\lceil\frac{L}{2}-\frac{1}{2}\Big\rceil-2s_1-
+%\sum\limits_{m>1}(t_{n-1,m-1}+2)s_m=\\
+%\Big\lceil\frac{L}{2}-\frac{1}{2}\Big\rceil-2q-
+%\sum\limits_{m}t_{n-1,m}s'_m.
+%\end{eqnarray}
+%
+%This means
+%
+\begin{equation}
+{\mathcal N}_n(L,{\mathcal S}_{PI})={\mathcal N}_{n-1}(L-4q,{\mathcal S}'_{PI}),
+\end{equation}
+%
+which implies
+%
+\begin{equation}
+Z(L,{\mathcal S})=B(Z_1(L,{\mathcal S}),s_1)Z(L-4q,{\mathcal S}').
+\end{equation}
+%
+Substituting in~\eref{eq} one obtains
+%
+\begin{equation}
+Z(L,\ell,q)=\sum_{s=0}^{q-1}B\Big(\Big\lceil\frac{L}{2}-\frac{1}{2}\Big
+\rceil-2q+s,s\Big)Z(L-4q,\ell-q,q-s),
+\end{equation}
+%
+i.e.,
+%
+\begin{equation}
+Z(L,\ell,q)=\sum_{s=0}^{q-1}B\Big(\frac{L}{2}-2q+s,s\Big)Z(L-4q,\ell-q,q-s).
+\end{equation}
+%
+The initial condition $Z(L,1,1)$ reads 
+%
+\begin{equation}
+Z(L,1,1)=\frac{L}{2}-1
+\end{equation}
+%
+One can show that this leads to 
+%
+\begin{equation}
+Z(L,\ell,q)=\frac{L/2-2\ell+1}{L/2-\ell+1}B(L/2-\ell+1,q)B(\ell-1,q-1).
+\end{equation}
+%
+By summing over $q=1,\dots,\ell$ one obtains 
+%
+\begin{equation}
+\sum\limits_{q=1}^\ell Z(L,\ell,q)=B(L/2,\ell)-B(L/2,\ell-1).
+\end{equation}
+%
+Summing over $\ell$ one obtains~\eref{neel-ov-count}.
 
@@
 
-%##################################################################
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=.9\textwidth]{./draft_figs/L20_BT_check}
-\end{center}
-\caption{ The squared overlap $|\langle\Psi_0|\{\lambda\}\rangle|^2$ between the the 
- Neel state $|\Psi_0\rangle$ and the eigenstates $|\{\lambda\}\rangle$ of the $XXX$ 
- chain with $L=22$ sites. Only non-zero overlaps are shown. In all the panels the 
- $x$-axis shows the eigenstate energy density $E/L$. The circles are the exact 
- diagonalization results for all the non-zero overlaps. The crosses are the Bethe 
- ansatz results obtained using the Bethe-Gaudin-Takahashi equations. The missing 
- crosses correspond to eigenstates containing zero-momentum strings. (a) Overview 
- of all the non-zero overlaps. (b)(c)(d) The same overlaps as in (a) zooming in 
- the regions $[0,0.2]$, $[0,0.020]$, and $[0,4\cdot 10^{-5}]$. The discrepancies 
- between the ED and the Bethe ansatz results are attributed to the string deviations. 
+\begin{table}[h]
+\scriptsize
+\centering
+Bethe states with nonzero M-G overlap ($L=12$)\\[1ex]
+\begin{tabular}{rrrr}
+String content & Energy (ED) & $|\langle \{\lambda\}| \Psi_0 \rangle|^2$ (ED) & $|\langle \{\lambda\}| \Psi_0 \rangle|^2$ (B-T) \\[0.3em]
+\toprule
+$1_1 3_1 5_1$ & $-8.38739$  & $0.716616$     &  $0.7166157692239$\\
+              & $-6.34021$  & $0.205891$     &  \\
+$5_1 1_2$     & $-5.40184$  & $0.0556247$    & $0.05403336654338$\\
+              & $-5.20365$  & $0.0388322$    & \\
+$3_1 1_2$     & $-4.61393$  & $0.00568743$   & $0.005582983043235$\\
+              & $-3.78869$  & $0.00601941$   & \\
+$1_1 1_2$     & $-3.14747$  & $0.00210748$   & $0.0021070869333835$\\
+              & $-2.44429$  & $0.000129601$  & \\
+              & $-1.56067$  & $0.000330573$  & \\
+$1_3$         & $-1.11186$  & $0.0000117278$ & $0.000012785579923275$\\
+\bottomrule
+\end{tabular}
+\caption{All Bethe states for $L=12$ with nonzero overlap with the zero-momentum 
+ M-G state. The first column show the string content of the eigenstate. The second 
+ and third columns show the exact diagonalization resutls for the energy and the 
+ overlap, respectively. The last colum is the overlap obtained in the Bethe ansatz 
+ approach using the Bethe-Takahashi equations.
 }
-\label{fig1-BGT-check}
-\end{figure}
-%##################################################################
+\label{table:RV:sumruleN12}
+\end{table}
 
-%##################################################################
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=.6\textwidth]{./draft_figs/Neel_over}
-\end{center}
-\caption{ The overlap sum rule $\sum_{\{\lambda\}}|\langle\{\lambda\}|\Psi_0\rangle|^2$, 
- with $|\Psi_0\rangle$ the Neel state and $|\{\lambda\}\rangle$ the eigenstates  of the 
- $XXX$ spin chain, plotted versus $1/L$, with $L$ the chain length. The circles are 
- Bethe ansatz results for chains up to $L=36$. Only the eigenstates with no zero-momentum 
- strings are considered in the sum. The dash-dotted line is a fit to $A/L^{1/2}+B/L$, with 
- $A,B$ fitting parameters. Inset: The same data as in the main Figure plotted versus 
- $1/L^{1/2}$.
+\begin{table}[h]
+\scriptsize
+\centering
+Bethe states with nonzero M-G overlap ($L=16$)\\[1ex]
+\begin{tabular}{rrrr}
+String content & Energy (ED) & $|\langle \{\lambda\}| \Psi_0 \rangle|^2$ (ED) & $|\langle \{\lambda\}| \Psi_0 \rangle|^2$ (B-T) \\[0.3em]
+\toprule
+$7_1 5_1 3_1 1_1$ & $-11.1423$ & $0.517742$         & $0.5177418283152$\\
+& $-9.59129$ & $0.244845$         &\\
+$7_1 5_1 1_2$ & $-8.81424$ & $0.0727096$        & $0.07100180464371$\\
+& $-8.56579$ & $0.082852$         &\\
+$7_1 3_1 1_2$ & $-7.96995$ & $0.0232953$        & $0.02300602650371$\\
+& $-7.89112$  & $0.0181713$        &\\
+$7_1 1_1 1_2$ & $-7.51522$ & $0.00245007$       & $0.002427999643379$\\
+& $-7.41983$ & $0.0192443$        &\\
+$5_1 3_1 1_2$ & $-6.80829$ & $0.012519$         & $0.012518660407092$\\
+& $-6.78357$ & $0.00398018$       &\\
+$5_1 1_1 1_2$ & $-6.3398$  &  $0.00135119$      & $0.0013511980854654$\\
+& $-6.25276$ & $0.000721952$      &\\
+& $-5.86683$ & $0.00112415$       &\\
+& $-5.69103$ & $0.000141052$      &\\
+& $-5.50802$ & $0.00373666$       &\\
+$3_1 1_2$ & $-5.45276$ & $0.000466819$      & $0.0004668223478716$\\
+& $-5.06385$ & $0.000380056$      & $0.000166548883431$\\
+& $-4.86668$ & $0.0000395855$     &\\
+& $-4.64743$ & $0.000014786$      & $0.000016403668846624$\\
+& $-4.49059$ & $0.00155894$       &\\
+& $-4.25924$ & $0.000109932$      &\\
+& $-3.93068$ & $4.12108e-6$       & $4.6283550855711e-6$\\
+& $-3.92645$ & $0.0000102752$     &\\
+& $-3.77995$ & $0.0000732808$     &\\
+& $-3.259$   & $0.0000348879$     &\\
+& $-3.12751$ & $0.0000739906$     & $0.00007017294942524$\\
+& $-3.04176$ & $1.62543e-6$       &\\
+& $-3.00072$ & $1.4684e-6$        & $1.6374806913113e-6$\\
+& $-2.32465$ & $2.01172e-8$       &\\
+& $-2.26529$ & $7.53377e-6$       &\\
+& $-2.02465$ & $5.8028e-7$        & $5.722094498217e-7$\\
+& $-1.38078$ & $2.17607e-7$       &\\
+& $-1.11438$ & $1.825e-7$         &\\
+& $-0.844856$& $1.84715e-9$       & $2.4957509639475e-9$\\
+\bottomrule
+\end{tabular}
+\caption{All Bethe states for $L=12$ with nonzero overlap with the zero-momentum 
+ M-G state. The first column show the string content of the eigenstate. The second 
+ and third columns show the exact diagonalization resutls for the energy and the 
+ overlap, respectively. The last colum is the overlap obtained in the Bethe ansatz 
+ approach using the Bethe-Takahashi equations.
 }
-\label{fig2-neel-sr}
-\end{figure}
-%##################################################################
-
-%##################################################################
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=.6\textwidth]{./draft_figs/Dimer_over}
-\end{center}
-\caption{ The overlap sum rule $\sum_{\{\lambda\}}|\langle\{\lambda\}|\Psi_0\rangle|^2$, 
- with $|\Psi_0\rangle$ the Majumdar-Ghosh state and $|\{\lambda\}\rangle$ the eigenstates  
- of the $XXX$ spin chain, plotted versus $1/L$, with $L$ the chain length. The circles are 
- Bethe ansatz results for chains up to $L=32$. Only the eigenstates with no zero-momentum 
- strings are considered in the sum. The dash-dotted line is a fit to $A/L^{1/2}+B/L$, with 
- $A,B$ fitting parameters. Inset: The same data as in the main Figure plotted versus 
- $1/L^{1/2}$.
-}
-\label{fig3-dimer-sr}
-\end{figure}
-%##################################################################
-
-%##################################################################
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=.75\textwidth]{./draft_figs/Neel_over_ener}
-\end{center}
-\caption{ The overlap between the Neel state and the eigenstates of the 
- $XXX$ chain as a function of the eigenstate energy. (a) The squared 
- overlap $|\langle\{\lambda\}|Neel\rangle|^2$ plotted versus the 
- eigenstates energy density $E/L$. The data are Bethe ansatz results 
- for chains of length $L=22,26,32,36$ (different symbols). (b) Same as 
- in (a) plotting on the $y$-axis the combination $-2\log(|\langle\{
- \lambda\}|Neel\rangle|)/L$. 
-}
-\label{fig4-neel-ener}
-\end{figure}
-%##################################################################
+\label{table:RV:sumruleN12}
+\end{table}
 
@@
 
-%\begin{thebibliography}{99}
+\begin{thebibliography}{99}
 
-%\end{thebibliography}
+\bibitem{calabrese-2014}
+P.~Calabrese and P.~Le Doussal, J.\ Stat.\ Mech.\ (2014) P05004.
+
+\end{thebibliography}
 

### 2015-07-31 draft/fs_qa.tex
fin

@@
 \begin{equation}
+\label{Neel-count}
 Z_N=2^{\frac{L}{2}-1}+\frac{1}{2}B\left(\frac{L}{2},
@@
 Summing over $\ell$ one obtains~\eref{neel-ov-count}.
+
+%%%%%%%%%%%%%
+\subsection{Proof of non-zero Neel overlap counting}
+
+Here we prove~\eref{Neel-count}.
+
+Let us consider the string configurations as before in which all the particle are 
+distributed in at most $M/2$-strings, as ${\mathcal S}_{PI}=\{s_1,s_2,\dots,s_{M/2}\}$. 
+Now we have $\sum_k ks_k=M$.
+
+The number of available parity-invariant quantum numbers ${\mathcal N}_n$ in the 
+$n$-string sector is now given as 
+%
+\begin{equation}
+{\mathcal N}_n(L,{\mathcal S}_{PI})=\frac{L}{2}-\frac{1}{2}\sum_{m=1}^{M/2}t_{nm}s_m.
+\end{equation}
+%
 

### 2015-09-01 draft/fs_qa_v1.tex
revised-01/09/2015

\documentclass[11pt]{iopart}
\usepackage[english]{babel}
\pdfoutput=1
%\usepackage{amsmath}
\usepackage{wasysym}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{sidecap}
\usepackage{bm}% bold math
\usepackage{tikz}

\usepackage[colorlinks,bookmarks=false,citecolor=blue,linkcolor=red,urlcolor=blue]{hyperref}

\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}

%\usepackage{cite}

%
% WARNING !!!!
% 
% iopart.cls definition of \tableofcontents overwrites the
% short title printed every page. 
% The following redefinition of \tableofcontents fixes the
% the problem.

\catcode`@=11 % If we need private TeX macros
\renewcommand\tableofcontents{%
  \section*{\contentsname}%
  \@starttoc{toc}%
}
\catcode`@=12% '@' is no more a character
\newcommand{\bra}[1]{\langle\left.{#1}\right|}
\newcommand{\ket}[1]{\left|{#1}\right.\rangle}

\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\u{\uparrow}
\def\d{\downarrow}
\def\nm{\newmoon}
\def\fm{\fullmoon}
\def\T{\rule{0pt}{.6cm}}
\def\B{\rule[-.4cm]{0pt}{0pt}}

\begin{document}

\setlength{\parindent}{0pt}

\title{The Quench-Action method in integrable spin chains: A Monte Carlo 
approach}

\author{Vincenzo Alba$^1$, Pasquale Calabrese$^1$}
\address{$^1$ International School for Advanced Studies (SISSA),
Via Bonomea 265, 34136, Trieste, Italy,
INFN, Sezione di Trieste}

\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

fdasfa
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%% INTRODUCTION %%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{intro}

We show that it is possible to numerically simulate the Quench Action approach 
combining Monte Carlo methods and Bethe ansatz techniques.

We focus on the situation in which the pre-quench initial state is the Neel 
state or the Majumdar-Ghosh state.

We investigate the importance of the zero-momentum strings in the Quench Action.

Without zero-momentum strings the overlap saturation rules are not valid, 
i.e., in finite size systems the vast majority of the eigenstates contain 
zero momentum strings.

The details on the eigenstates counting depend on the pre-quench initial state.

However, we show that one can restrict to the set of non-zero momentum strings. 
The fact that one neglects zero-momentum strings gives rise only to scaling 
corrections.

We also investigate the validity of the Bethe-Takahashi approximation for the 
calculation of the overlap.

%%%%%%%%%%%%%%%%%%%%%%% BETHE ANSATZ APPROACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Heisenberg spin chain}
\label{xxx-chain}

Here we consdier the spin-$\frac{1}{2}$ isotropic Heisenberg chain ($XXX$ chain). 
The $XXX$ chain with $L$ sites is defined by the Hamiltonian 
%
\begin{equation}
\label{xxx-ham}
{\mathcal H}\equiv J\sum\limits_{i=1}^L\left[\frac{1}{2}(S_i^+S^-_{i+1} 
+S_i^{-}S_{i+1}^+)+S_i^zS_{i+1}^z\right],  
\end{equation}
%
where $S^{\pm}_i\equiv (\sigma_i^x\pm i\sigma_i^y)/2$ are spin operators acting on the 
site $i$, $S_i^z\equiv\sigma_i^z/2$, and $\sigma^{x,y,z}_i$ the Pauli matrices. We fix 
$J=1$ and use periodic boundary conditions, identifying sites $L+1$ and $1$. The total 
magnetization $S_{T}^z\equiv\sum_iS_i^z=L/2-M$, with $M$ number of down spins (particles), 
commutes with~\eref{xxx-ham}, and it is here used to label its eigenstates.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Bethe equations and wavefunctions}
\label{bethe_equations}

The generic eigenstate of~\eref{xxx-ham} in the sector with $M$ particles can be written as 
%
\begin{equation}
\label{ba_eig}
|\Psi_M\rangle=\sum\limits_{1\le x_1<x_2<\dots<x_M\le L}A_M(x_1,x_2,
\dots,x_M)|x_1,x_2,\dots,x_M\rangle,
\end{equation}
%
where the sum is over the positions $\{x_i\}$ of the particles, and $A_M(x_1,
x_2,\dots,x_M)$ is the eigenstate amplitude corresponding to particles 
at positions $x_1,x_2,\dots, x_M$. $A_M(x_1,x_2,\dots, x_M)$ is given as 
%
\begin{equation}
\label{ba_amp}
A_M(x_1,x_2,\dots,x_M)\equiv\sum\limits_{{\mathcal P}\in S_M}\exp\Big[i
\sum\limits_{j=1}^Mk_{{\mathcal P}_j}x_j+i\sum\limits_{i<j}\theta_{{
\mathcal P}_i{\mathcal P}_j}\Big].
\end{equation}
%
Here the outermost sum is over the permutations $S_M$ 
of the so-called quasi-momenta $\{k_1,k_2,\dots,k_M\}$. The two-particle 
scattering phases $\theta_{m,n}$ are defined as 
%
\begin{equation}
\label{s_phases}
\theta_{m,n}\equiv \frac{1}{2i}\log\Big[-\frac{e^{ik_m+ik_n}-2e^{ik_m}+1}
{e^{ik_m+ik_n}-2e^{ik_n}+1}\Big].
\end{equation}
%
The energy associated to the eigenstate~\eref{ba_eig} is  
%
\begin{equation}
\label{ba_ener}
E=\sum\limits_{\alpha=1}^M(\cos(k_\alpha)-1).
\end{equation}
%
The quasi-momenta $\{k_\alpha\}$ are obtained by solving the so-called 
Bethe equations  
%
\begin{equation}
\label{ba_eq}
e^{ik_\alpha L}=\prod\limits^M_{\beta\ne\alpha}\Big[-\frac{1-2e^{
ik_\alpha}-e^{ik_\alpha+ik_\beta}}{1-2e^{ik_\beta}-e^{ik_\alpha+
ik_\beta}}\Big].
\end{equation}
%
It is useful to  introduce the rapidities $\{\lambda_\alpha\}$ as 
%
\begin{equation}
\label{rap}
k_\alpha=\pi-2\arctan(\lambda_\alpha)\quad\mbox{mod}\, 2\pi.
\end{equation}
%
Taking the logarithm on both sides in~\eref{ba_eq}, and using~\eref{rap}, 
one obtains the Bethe equations in logarithmic form as 
%
\begin{equation}
\label{ba_eq_log}
\arctan(\lambda_\alpha)=\frac{\pi}{L}J_\alpha+\frac{1}{L}\sum\limits_{
\beta\ne\alpha}\arctan\Big(\frac{\lambda_\alpha-\lambda_\beta}{2}\Big),
\end{equation}
%
where $-L/2<J_\alpha\le L/2$ are the so-called Bethe quantum numbers. The 
$J_\alpha$ are half-integers and integers for $L-M$ even and odd.

These solutions of the Bethe equations~\eref{ba_eq} form particular ``string'' patterns 
in the complex plane, in the limit of large chains $L\to\infty$(string hypothesis)~\cite{
bethe-1931,taka-book}. Specifically, rapidities forming a ``string'' of length $1\le 
n\le M$ (that we defined here as $n$-string) are parametrized as 
%
\begin{equation}
\label{str_hyp}
\lambda^{j}_{n;\gamma}=\lambda_{n;\gamma}-i(n-1-2j)+i\delta_{n;\gamma}^j,\qquad 
j=0,1,\dots, n-1, 
\end{equation}
%
where $\lambda_{n;\gamma}$ is the real part of the string (string center), 
and $\gamma$ labels strings with different centers, while $j$ labels the different 
components of the string. In~\eref{str_hyp} $\delta_{n;\gamma}^j$ are the string 
deviations, which typically vanish exponentially in the thermodynamic limit.

Notice that pure real rapidities are strings of unit length ($1$-strings).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Bethe-Takahashi equations}

The string centers $\lambda_{n;\gamma}$ in~\eref{str_hyp} are obtained by solving the 
so-called Bethe-Takahashi equations
%
\begin{equation}
\label{bt_eq}
2L\theta_n(\lambda_{n;\gamma})=2\pi I_{n;\gamma}+\sum\limits_{(m,
\beta)\ne(n,\gamma)}\Theta_{m,n}(\lambda_{n;\gamma}-\lambda_{m;\beta}), 
\end{equation}
%
where the generalized scattering phases $\Theta_{m,n}$ read 
%
\begin{eqnarray}
\nonumber\fl\Theta_{m,n}(x)\equiv\left\{\begin{array}{cc}
\theta_{|n-m|}(x)+\!\!\!\!\!\sum
\limits_{r=1}^{(n+m-|n-m|-1)/2}\!\!\!\!\!2\theta_{|n-m|+2r}(x)
+\theta_{n+m}(x) & \quad\mbox{if}
\quad n\ne m\\\fl\sum\limits_{r=1}^{n-1}2\theta_{2r}(x)+
\theta_{2n}(x) & \quad\mbox{if}\quad n=m
\end{array}\right.
\end{eqnarray}
%
and $\theta_\alpha(x)\equiv 2\arctan(x/\alpha)$. Here $I_{n;\gamma}$ are the 
Bethe-Takahashi quantum numbers associated with $\lambda_{n;\gamma}$.

Each $M$-particle eigenstate can be characterized by its ``string content'' ${
\mathcal S}\equiv\{s_1,\dots,s_M\}$, with $s_n$ the number of $n$-strings.

It can be shown that $I_{n;\gamma}$  are integers or half-integers for $L-s_n$ 
odd and even, respectively.

Clearly, the constraint $\sum_{\alpha=1}^{M}\alpha s_\alpha=M$ 
has to be satisfied. The upper bound for the Bethe-Takahashi quantum numbers 
can be derived as   
%
\begin{equation}
|I_{n;\gamma}|\le I^{(MAX)}_{n}\equiv\frac{1}{2}(L-1-\sum
\limits_{m=1}^Mt_{m,n}s_m),
\label{bt_qn_bound}
\end{equation}
%
where $t_{m,n}\equiv 2\mbox{min}(n,m)-\delta_{m,n}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overlap with the Neel state}

Here we restrict to the parity-invariant eigenstates. These are the only 
eigenstates with non-zero overlap with the Neel state. Parity-invariant 
eigenstates contain only pairs of rapidities with opposite sign.

We denote the generic parity invariant eigenstate as $|\{\pm\lambda_j\}_{j=1}^m,
n_\infty\rangle$, where $m$ is the number of rapidity pairs, $N_{\infty}$ is the 
number of infinite rapidities, with $M=L/2=N_\infty+2m$, and $n_\infty\equiv 
N_\infty/L$ is the density of infinite rapidities.

The overlap with the Neel state $|N\rangle$ reads 
%
\begin{equation}
\label{neel-ov}
\frac{\langle N|\{\pm\lambda_j\}_{j=1}^m,n_\infty\rangle}{|||\{\lambda_j\}_{j=1}^m,
n_\infty\rangle||}=\frac{\sqrt{2}N_{\infty}!}{\sqrt{(2N_\infty)!}}\left[\prod_{j=1}^m
\frac{\sqrt{\lambda_j^2+1}}{4\lambda_j}\right]\sqrt{\frac{\textrm{det}_m(G^+)}{
\textrm{det}_m(G^-)}}
\end{equation}
%
where 
%
\begin{equation}
\label{G-pm}
G^{\pm}_{jk}=\delta_{jk}\Big(NK_{1/2}(\lambda_j)-\sum\limits_{l=1}^mK_1^+(\lambda_j,
\lambda_l)\Big)+K_{1}^{\pm}(\lambda_j,\lambda_k),\quad\,j,k=1,\dots,m
\end{equation}
%
and 
%
\begin{equation}
\label{K-1}
K_1^\pm(\lambda,\mu)=K_1(\lambda-\mu)\pm K_1(\lambda+\mu)
\end{equation}
%
and 
%
\begin{equation}
\label{K-alpha}
K_\alpha(\lambda)\equiv\frac{8\alpha}{\lambda^2+4\alpha^2}
\end{equation}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reduced Neel overlap}

Here we consider the overlap formula for the Neel state~\eref{neel-ov} in the 
limit $L\to\infty$, assuming that the rapidities form perfect strings.

In the case of perfect strings the matrices $G^{\pm}_{jk}$ become ill-defined. 
Precisely, $K_{1}^\pm(\lambda,\mu)$ diverges if $\lambda$ and $\mu$ are successive 
members of the same string, i.e., $|\lambda-\mu|=2i$.

It is possible to rewrite~\eref{neel-ov} in terms of the string centers 
$\lambda_{n;\alpha}$ only. Here we restrict ourselves to rapidity configurations 
with no zero-momentum strings. Our results are not valid for zero-rapidity 
strings. These would require the knowledge of the precise form of the string 
deviations, i.e., the dependence of the string deviations on $L$, as it has 
been pointed out in Ref.~\cite{calabrese-2014}.

It is convenient to split the indices $i,j$ of $G^\pm_{ij}$ as $i=(n,\alpha)$ 
$j=(m,\beta)$, with $n,m$ being the length of the strings and $\alpha,\beta$ 
labelling the string centers.

The result reads 
%
\begin{equation}
\fl \frac{1}{2}G^+_{(n,\alpha)(m,\beta)}=\left\{\begin{array}{cc}
L\theta_n'(\lambda_{n;\alpha}) -\sum\limits_{(\ell,\gamma)\ne(n,\alpha)}\Big[\Theta'_{n,\ell}
(\lambda_{n;\alpha}-\lambda_{\ell;\gamma}) & \quad\textrm{if}\,(n,\alpha)=(m,\beta) \\
+\Theta'_{n,\ell}(\lambda_{n;\alpha}+\lambda_{\ell;\gamma})\Big] & \\ \\
\Theta'_{n,m}
(\lambda_{n;\alpha}-\lambda_{m;\beta})+\Theta'_{n,m}
(\lambda_{n;\alpha}+\lambda_{m;\beta}) & \quad\textrm{if}\,(n,\alpha)\ne(m,\beta)
\end{array}\right.
\end{equation}
%
Here $\theta_n'(x)\equiv d\theta_n(x)/dx=2n/(n^2+x^2)$ and $\Theta'(x)\equiv d\Theta(x)/dx$.

For $G^-_{ij}$ one obtains

\begin{equation}
\fl\frac{1}{2}G^-_{(n,\alpha)(m,\beta)}=\left\{\begin{array}{cc}
\fl(L-1)\theta'_n(\lambda_{n;\alpha})-2\sum\limits_{k=1}^{n-1}\theta'_k(\lambda_{n;\alpha})
& \textrm{if}\,(n,\alpha)= (m,\beta)\\
-\hspace{-.5cm}\sum\limits_{(\ell,\gamma)\ne(n,\alpha)}\Big[\Theta'_{n,\ell}
(\lambda_{n;\alpha}-\lambda_{\ell;\gamma})+\Theta'_{n,\ell}
(\lambda_{n;\alpha}+\lambda_{\ell;\gamma})\Big] \\\\
\Theta'_{n,m}
(\lambda_{n;\alpha}-\lambda_{m;\beta})-\Theta'_{n,m}
(\lambda_{n;\alpha}+\lambda_{m;\beta})) & \textrm{if}\,(n,\alpha)\ne(m,\beta)
\end{array}\right.
\end{equation}
%
Finally, the multiplicative prefactor in~\eref{neel-ov} for the generic $n$-string 
can be rewritten as 
%
\begin{equation}
\prod\limits_{a=1}^n\frac{\sqrt{(\lambda^a_{n;\alpha})^2+1}}{4\lambda^a_{n;\alpha}}=
\frac{1}{4^n}\left(\frac{\sqrt{n^2+\lambda^2_{n;\alpha}}}{\lambda_{n;\alpha}}
\prod\limits_{k=0}^{\lceil n/2\rceil-1}\frac{(2k)^2+\lambda^2_{n;\alpha}}{(2k+1)^2+
\lambda^2_{n;\alpha}}\right)^{{\mathcal P}},
\end{equation}
%
with ${\mathcal P}=+$ and ${\mathcal P}=-$ for even and odd strings, respectively.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overlap with the Majumdar-Ghosh state}

The overlap between the generic eigenstate of the $XXX$ chain and the Majumdar-Ghosh 
state is obtained fro the overlap with the Neel state as 
%
\begin{equation}
\label{mg-ov}
\langle MG|\{\lambda_j\}_{j=1}^M\rangle=\prod\limits_{j=1}^M\frac{1}{\sqrt{2}}
\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)\langle N|\{\lambda_j\}_{j=1}^M\rangle
\end{equation}
%
The mutliplicative factor in~\eref{ov-MG}, using the string hypothesis for the generic 
$n$-string is rewritten as 
%
\begin{equation}
\prod\limits_{j=1}^M\frac{1}{\sqrt{2}}
\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)=2^n\prod\limits_{k=0}^{\lfloor 
n/2\rfloor}\frac{1}{[\lambda_{n;\gamma}^2+(2k+(1-(-1)^n)/2)^2]^2}
\end{equation}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overlap sum rules: the role of the zero-momentum strings}
\label{ov-sum-rules}

In this section we investigate the role of the zero-momentum strings. We focus on 
conserved quantities sum rules. Specifically, given a generic conserved quantity 
(charge) $\hat Q$ we consider the trivial identity  
%
\begin{equation}
\label{sum}
Q_0\equiv\langle\Psi_0|\hat Q|\Psi_0\rangle=\sum\limits_{\lambda}|\langle\lambda|
\Psi_0\rangle|^2Q_\lambda, 
\end{equation}
%
where $Q_0$ is the charge expectation values over the initial state $|\Psi_0
\rangle$, $|\lambda\rangle$ denotes the generic eigenstate of the $XXX$ chain, 
and $Q_\lambda$ is the charge eigenvalue over the eigenstate.

Here we restrict ourselves to the cases with $\hat Q=\mathbb{I}$ and $\hat 
Q={\mathcal H}$, considering both the case with $|\Psi\rangle=|N\rangle$ and 
$|\Psi_0\rangle=|MG\rangle$.

%##################################################################
\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\textwidth]{./draft_figs/Neel}
\end{center}
\caption{ Overlap sum rules for the Neel state. (a) The overlap sum rule 
 $\sum_{\lambda}|\langle\lambda|N\rangle|^2=1$, with $|N\rangle$ 
 the Neel state and $|\lambda\rangle$ the eigenstates  of the $XXX$ 
 spin chain. The $x$-axis shows $1/L$, with $L$ the chain length. The 
 circles are Bethe ansatz results for chains up to $L=36$. The results 
 are obtained via a full scanning of the chain Hilbert space. Only the 
 eigenstates with no zero-momentum strings are considered. The dash-dotted 
 line is a fit to $A/L^{1/2}+B/L$, with $A,B$ fitting parameters. Inset: 
 The same data as in the main Figure plotted versus $1/L^{1/2}$. (b) 
 The same as in (a) for the sum rule $\sum_{\lambda}|\langle
 \lambda|N\rangle|^2e(\lambda)=1/2$, with $e(\lambda)$  the 
 eigenstates energy density. 
}
\label{fig2-neel-sr}
\end{figure}
%##################################################################

%##################################################################
\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\textwidth]{./draft_figs/Dimer}
\end{center}
\caption{ Overlap sum rules for the Majumdar-Ghosh (MG) state. (a) The 
 overlap sum rule $\sum_{\lambda}|\langle\lambda|MG\rangle|^2=1$, 
 with $|MG\rangle$ the Majumdar-Ghosh state and $|\lambda\rangle$ 
 the eigenstates  of the $XXX$ spin chain. The $x$-axis shows $1/L$, 
 with $L$ the chain length. The circles are Bethe ansatz results for 
 chains up to $L=36$. The results are obtained via a full scanning of 
 the chain Hilbert space. Only the eigenstates with no zero-momentum 
 strings are considered. The dash-dotted line is a fit to $A/L+B/L^2$, 
 with $A,B$ fitting parameters. (b) The same as in (a) for the sum 
 rule $\sum_{\lambda}|\langle\lambda|MG\rangle|^2e(\lambda)=
 2/3$, with $e(\lambda)\equiv E/L$  the eigenstates energy density. 
}
\label{fig3-dimer-sr}
\end{figure}
%##################################################################

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Validity of the string hypothesis for overlap calculations}
\label{string-ov}

Here we discuss the validity of the string hypothesis when calculating the 
overlaps between the eigenstates of the $XXX$ chain and the N\'eel state. 
Here we focus on the Heisenberg chain with $L=20$ sites. 
Figure~\ref{fig1-BGT-check} plots the squared overlaps $|\langle\lambda|
N\rangle|^2$ between the N\'eel state and the eigenstates of the chain. 
The overlaps are plotted against the eigenstate energy density $E/L
\in[-\log(2),0]$. The circles are exact diagonalization results for all 
the chain eigenstates ($382$ eigenstates), whereas the crosses denote the 
overlaps calculated using formula~\eref{neel-ov}, and the 
Bethe-Gaudin-Takahashi equations. Note that only the eigenstates with 
no zero-momentum strings are shown ($252$ eigenstates) in the Figure. 
Panel (a) in the Figure is an overview of all the results. Panels (b)-(d) 
correspond to zooming to the smaller overlap values $|\langle N|\lambda
\rangle|\lesssim 0.02$, $|\langle N|\lambda\rangle|\lesssim 0.002$, and 
$|\langle N|\lambda\rangle|\lesssim 10^{-5}$.

Clearly, the overlaps decay rapidly upon increasing the energy density. 
This is expected since the $XXX$ Hamiltonian expectation value over 
the N\'eel state is $\langle N|{H}|N\rangle=-1/2$. Importantly, the 
agreement between the exact diagonalization results and the results 
obtained using the BGT equations~\eref{ba_eq} is excellent, confirming 
the validity of the string hypothesis.

%##################################################################
\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\textwidth]{./draft_figs/L20_BT_check}
\end{center}
\caption{ The squared overlap $|\langle N|\lambda\rangle|^2$ between the the 
 Neel state $|N\rangle$ and the eigenstates $|\lambda\rangle$ of the $XXX$ 
 chain with $L=20$ sites. Only non-zero overlaps are shown. In all the panels the 
 $x$-axis shows the eigenstate energy density $E/L$. The circles are the exact 
 diagonalization results for all the non-zero overlaps. The crosses are the Bethe 
 ansatz results obtained using the Bethe-Gaudin-Takahashi equations. The missing 
 crosses correspond to eigenstates containing zero-momentum strings. (a) Overview 
 of all the non-zero overlaps. (b)(c)(d) The same overlaps as in (a) zooming in 
 the regions $[0,0.2]$, $[0,0.020]$, and $[0,4\cdot 10^{-5}]$. The discrepancies 
 between the ED and the Bethe ansatz results are attributed to the string 
 deviations. 
}
\label{fig1-BGT-check}
\end{figure}
%##################################################################

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Monte Carlo implementation of the Quench-Action approach}

For the finite-size Heisenberg spin chain the Quench-Action expectation 
values can be obtained by sampling the eigenstates of the chain using 
Monte Carlo. One starts with an eigenstate of the $XXX$ chain with 
$N_{\infty}$ infinite rapidities and $M\equiv L/2-N_\infty$ finite ones. 
The state is identified by a parity-invariant Bethe quantum number 
configuration ${\mathcal C}$ and by the corresponding parity-invariant 
rapidities $\{\lambda\}$ as $|\lambda\rangle$. The string content 
associated with the finite rapidities is denoted as ${\mathcal S}$. The Monte 
Carlo procedure consists of four steps as follows: 
%
\begin{enumerate}
\item[\circled{1}] Choose a new number of finite rapidities $M'$ with 
probability
%
\begin{equation}
\label{PM}
{\mathcal P}(M')=\frac{\widetilde Z'_{Neel}(L,M')}{\widetilde{Z}_{Neel}(L)}. 
\end{equation}
%
\item[\circled{2}] Choose a new a new string content ${\mathcal S}'\equiv
\{s_1',\dots,s_{M'}'\}$ with probability ${\mathcal P}'(M',{\mathcal S}')$
%
\begin{equation}
\label{PS}
{\mathcal P}'(M',{\mathcal S}')=\frac{1}{\widetilde Z'_{Neel}(L,M')}
\prod_{n=1}^{M'}B\Big(\frac{L}{2}-\frac{1}{2}\sum\limits_{m=1}^{M'}t_{nm}
s'_m,s'_n\Big).
\end{equation}
%
\item[\circled{3}] Generate a new parity-invariant quantum number configuration 
${\mathcal C}'$ compatible with the ${\mathcal  S}'$ obtained in step $\circled{2}$. 
Solve the corresponding BGT equations~\eref{bt_eq}, finding a new eigenstate 
$|\lambda'\rangle$. 
\item[\circled{4}] Calculate the overlap $\langle\lambda'|N\rangle$ between the 
new eigenstate and the N\'eel state and accept the eigenstate with the Metropolis 
probability 
%
\begin{equation}
\label{metropolis}
{\mathcal P}''_{\lambda\to\lambda'}=\textrm{Min}\Big\{1,\exp\Big(-
2\Re({\mathcal E}'-{\mathcal E})\Big)\Big\}, 
\end{equation}
%
where ${\mathcal E}'\equiv-\log\langle\lambda'|N\rangle$, and similarly for 
${\mathcal E}$. 
\end{enumerate}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Monte Carlo Quench-Action approach: Numerical results}
\label{MCQA-nr}

The validity of the Monte Carlo approach for simulating the Quench-Action results 
is demonstrated in Figure~\ref{fig5-neel-sum-rules}. The Figure focuses on the 
N\'eel sum rules for the conserved charges $Q_2$ and $Q_4$. Specifically, 
panel (a) shows the sum rule $\langle Q_2\rangle/L=1/2$ (energy conservation). 
%
\begin{equation}
\langle N|\hat Q_n|N\rangle=\sum\limits_{\lambda}|\langle N|\lambda\rangle|^2
Q_n
\end{equation}
%

%##################################################################
\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\textwidth]{./draft_figs/QAMC_Obs_Neel}
\end{center}
\caption{The overlap sum rules for the Neel state: Numerical results 
 obtained using the Hilbert space Monte Carlo sampling approach. (a) 
 The energy sum rule $\langle N|Q_2|N\rangle/L=-1/2$, with $Q_2/L$ 
 the Hamiltonian density. We plot $\sum_{\lambda}|\langle\lambda|
 N\rangle|^2Q_2(\lambda)/L=1/2$, with $|\lambda\rangle$ the 
 eigenstates of the $XXX$ chain, versus the inverse chain length $1/L$. 
 The symbols are Monte Carlo data obtained by sampling the eigenstates 
 of the $XXX$ chain. The dash-dotted line is the expected result. The 
 dashed line is a fit to the behavior $-1/2+A/L+B/L^2$, with $A,B$ 
 fitting parameters. (b) The energy fluctuations sum rule $\sigma^2(Q_2)/
 L\equiv(\langle N|Q_2^2|N\rangle-\langle N|Q_2|N\rangle^2)/L=1/4$. The 
 horizontal line is the expected result. (c)(d) Same as in (a)(b) for 
 the charge $Q_4$ and its fluctuations. 
}
\label{fig5-neel-sum-rules}
\end{figure}
%##################################################################

%##################################################################
\begin{figure}[t]
\begin{center}
\includegraphics[width=.8\textwidth]{./draft_figs/Neel_rho}
\end{center}
\caption{ The steady-state root densities $\rho_1(x)$ (panel (a)) and 
 $\rho_2(x)$ (panel (b)), plotted versus the root $x$. The histograms 
 are Monte Carlo data for the Heisenberg chain with $L=56$ sites and 
 $\sim 10^7$ Monte Carlo steps. The $y$-axis is divided by $10^6$ for 
 convenience. The continuous lines are the analytical Quench-Action 
 results in the thermodynamic limit. 
}
\label{fig6-neel-roots}
\end{figure}
%##################################################################

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Counting of eigenstates with non-zero Neel overlap}

We numerically checked that the number of states with non-zero overlap 
with the Neel state is given as 
%
\begin{equation}
\label{Neel-count}
Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\left(\frac{L}{2},
\frac{L}{4}\right)+1,
\end{equation}
%
with $B(x,y)$ denoting the binomial coefficient. The contribution $1$ 
accounts for the ferromagnetic state. Here 
we assumed that $L$ is divisible by four. Here $Z_N$ is be obtained 
as the total number of parity-invariant Bethe-Gaudin-Takahashi quantum 
numbers.

After excluding the zero-momentum strings the total number of states 
with non-zero overlap with the Neel state is 
%
\begin{equation}
\label{neel-ov-count}
\widetilde {Z}_{Neel}=\Big(\frac{L}{2},\frac{L}{4}\Big)
\end{equation}
%
Importantly, the fraction of eigenstates corresponding to non-zero momentum 
strings is vanishing in the thermodynamic limit as 
%
\begin{equation}
\frac{\widetilde Z_{Neel}}{Z_{Neel}}\propto\frac{4}{\sqrt{\pi L}}.
\end{equation}
%

\appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Eigenstates with nonzero N\'eel overlap: eigenstates counting and 
string content}
\label{app-1}

Here we prove that the total number of eigenstates with N\'eel nozero overlap 
$Z_{Neel}(L)$for a chain of length $L$ is given as 
%
\begin{equation}
\label{N-count}
Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1. 
\end{equation}
%
For simplicity here we restrict ourselves to the situation with $L$ divisible by 
four. The strategy to prove~\eref{N-count} is to count all the possible parity-invariant 
BGT quantum numbers configurations. Let us consider the sector with fixed number of 
particles $M$, and a generic string content ${\mathcal S}=\{s_1,s_2,\dots,s_{M}\}$. 
Here $s_n$ is the number of $n$-strings, and one has the constraint $\sum_k ks_k=M$.

It is straightforward to check that total number of parity-invariant quantum number 
pairs ${\mathcal N}_n(L,{\mathcal S})$ in the $n$-string sector is given as 
%
\begin{equation}
\label{NnLS}
{\mathcal N}_n(L,{\mathcal S})=\Big\lfloor\frac{L}{2}-\frac{1}{2}
\sum_{m=1}^{M}t_{nm}s_m\Big\rfloor.
\end{equation}
%
where $t_{nm}\equiv 2\textrm{Min}(n,m)-\delta_{n,m}$. The number of parity-invariant 
quantum number configurations (i.e., eigenstates) ${\mathcal N}(L,{\mathcal S})$ 
compatible with string content ${\mathcal S}$ is obtained by choosing in all the 
possible ways the parity-invariant quantum number pairs independently in each 
$n$-string sector, which implies that    
%
\begin{equation}
\label{NLS}
{\mathcal N}(L,{\mathcal S})=\prod_{m=1}^{M} B\left({\mathcal N}_m,\left\lfloor
\frac{s_m}{2}\right\rfloor\right).
\end{equation}
%
Here the product is because each string sector is treated independently, while the 
factor $1/2$ in $s_m/2$ is because since all quantum numbers are organized in pairs, 
only half of the quantum numbers have to be specified. Note that in each $n$-string 
sector only one zero momentum (i.e., zero quantum number) string is allowed, due to 
the Pauli principle. Moreover, $s_m$ is odd (even) only if the zero momentum string 
is (not) present. The floor function $\lfloor\cdot\rfloor$ in~\eref{NLS} reflects 
that the quantum number of zero-momentum strings is fixed.

We now consider the string configurations with particle number $0\le\ell\le M$ and 
fixed number of strings $1\le q\le M/2$. Note that the maximul allowed string length 
is $M/2$ beacause of parity invariance. Note also that in determining $q$ strings of 
different length are treated equally. Clearly, one has that $\sum_m s_m=q$. 
For a given fixed pair $\ell,q$ the total number of quantum number configurations 
is given as 
%
\begin{equation}
\label{NLlq}
{\mathcal N}'(L,\ell,q)=\sum\limits_{\{\{s_m\}\,:\, \sum m s_m=\ell, \sum s_m=q\}}
{\mathcal N}(L,{\mathcal S}),
\end{equation}
%
where the sum is over the content $\{s_m\}_{m=1}^M$ compatible with the constraints 
$\sum_m s_m=q$ and $\sum_m m s_m=\ell$. The strategy is to write a recursive relation 
for ${\mathcal N}'(L,\ell,q)$. To this purpose it is useful to consider the shifted 
string content ${\mathcal S}'$ defined as  
%
\begin{equation}
{\mathcal S}'\equiv \{s_{m+1}\}\quad\textrm{with}\, s_m\in{\mathcal S},\,\forall m.
\end{equation}
%
Using the definition of $t_{ij}$, it is straightforward to derive that  
%
\begin{equation}
t_{ij}=t_{i-1,j-1}+2,
\end{equation}
%
which implies that ${\mathcal N}_n(L,{\mathcal S})$ (see~\eref{NnLS}) satisfies the 
recursive equation 
%
\begin{equation}
{\mathcal N}_n(L,{\mathcal S})={\mathcal N}_{n-1}(L-2q,{\mathcal S}'). 
\end{equation}
%
After substituting in~\eref{NLS} one obtains 
%
\begin{equation}
\label{NLSr}
{\mathcal N}(L,{\mathcal S})=B\Big({\mathcal N}_1(L,{\mathcal S}),\Big\lfloor \frac{s_1}{2}
\Big\rfloor\Big){\mathcal N}(L-2q,{\mathcal S}'). 
\end{equation}
%
Finally, after substituting~\eref{NLSr} in~\eref{NLlq}, one obtains a recursive relation 
for ${\mathcal N}'(L,\ell,q)$ as 
%
\begin{equation}
\label{NpLlq}
{\mathcal N}'(L,\ell,q)=\sum_{s=0}^{q-1}B\Big(\frac{L}{2}-q+\Big\lfloor\frac{s}{2}\Big\rfloor,
\left\lfloor\frac{s}{2}\right\rfloor\Big){\mathcal N}'\left(L-2q,\ell-q,
q-s\right), 
\end{equation}
%
with the constraint that when $\ell=q$ one has 
%
\begin{equation}
{\mathcal N}'(L,q,q)=B\Big(\Big\lfloor\frac{L-q}{2}\Big\rfloor,\Big\lfloor\frac{q}{2} 
\Big\rfloor\Big).
\end{equation}
%
This is obtained by observing that if $\ell=q$ only $1$-strings are allowed and~\eref{NnLS} 
gives ${\mathcal N}_n(L,{\mathcal S})=\lfloor (L-q)/2\rfloor$.

It is straightforward to check that for even $q$ the ansatz 
%
\begin{equation}
{\mathcal N}'(L,\ell,q)=\frac{q}{\ell}B\Big(\frac{L-\ell}{2},\frac{q}{2}\Big)
B\Big(\frac{\ell}{2},\frac{q}{2}\Big),
\end{equation}
% 
satisfies~\eref{NpLlq}. For odd $q$ the solution of~\eref{NpLlq} is 
%
\begin{equation}
{\mathcal N}'(L,\ell,q)=\frac{\ell-q+1}{\ell}B\Big(\frac{L-\ell}{2},\frac{q-1}{2}
\Big)B\Big(\frac{\ell}{2},\frac{q-1}{2}\Big).
\end{equation}
%
The number of eigenstates in the sector with $\ell$ particles with nonzero 
N\'eel overlap $Z'_{Neel}(L,\ell)$ are obtained by summing over all possible values 
of $q$ as 
%
\begin{equation}
\label{sum1}
Z'_{Neel}(L,\ell)=\sum\limits_{q=1}^\ell {\mathcal N}'(L,\ell,q).
\end{equation}
%
It is convenient to split the summation in~\eref{sum1} considering odd values of $q$ 
and even $q$ separately. For odd $q$ one obtains 
%
\begin{equation}
\sum\limits_{k=0}^{\ell/2-1} {\mathcal N}'(L,\ell,2k+1)=B\Big(\frac{L}{2}-1,
\frac{\ell}{2}-1\Big),
\end{equation}
%
while for even $q$ one has 
%
\begin{equation}
\sum\limits_{k=0}^{\ell/2} {\mathcal N}'(L,\ell,2k)=B\Big(\frac{L}{2}-1,
\frac{\ell}{2}\Big). 
\end{equation}
%
Putting everything together one obtains 
%
\begin{equation}
\label{N-count-p}
Z'_{Neel}(L,\ell)=B\Big(\frac{L}{2}-1,
\frac{\ell}{2}-1\Big)+B\Big(\frac{L}{2}-1,
\frac{\ell}{2}\Big). 
\end{equation}
%
The total number of eigenstates with nonzero N\'eel overlap $Z_{Neel}(L)$ 
(cf.~\eref{N-count}) is obtained from~\eref{N-count-p} by summing over 
the allowed values of $\ell=2k$ with $k=0,1,\dots,\ell/2$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Excluding the zero-momentum strings}
\label{app-2}

Here we demonstrate that the total number of eigenstates with nonzero N\'eel overlap, 
which do not contain zero-momentum strings, $\widetilde Z_{Neel}(L)$ is given as 
%
\begin{equation}
\widetilde Z_{Neel}(L)=B\Big(\frac{L}{2},\frac{L}{4}\Big). 
\end{equation}
%
Given a generic $M$-particle eigenstate of the $XXX$ chain, due to parity invariance, 
if one excludes the zero-momentum strings only $n$-strings with length $n\le M/2$ 
are allowed. Similarly, the string content is of the form $\widetilde{\mathcal S}
\equiv\{\tilde s_1,\dots,\tilde s_{M/2}\}$, i.e., $\tilde s_m=0$ $\forall m>M/2$.
Note that due to parity invariance and to the exclusion of the zero-momentum strings 
one has that $\tilde s_m$ is always an even integer. Clearly one has $\sum_{m=1}^{M/2}
m \tilde s_m=M$.

The total number of parity-invariant quantum numbers $\widetilde{\mathcal N}_n$ in the $n$-string 
sector is given as  
%
\begin{equation}
\widetilde{\mathcal N}_n(L,\widetilde{\mathcal S})=\frac{L}{2}-\frac{1}{2}
\sum_{m=1}^{M/2}t_{nm}\tilde s_m.
\end{equation}
%
The proof now proceeds as in~\ref{app-1}. One can define the total number of eigenstates 
with nonzero N\'eel overla in the sector with $\ell$ particles and $q$ different strings as 
$\widetilde{\mathcal N}'(L,\ell,q)$. Note that due to parity invariance and the exclusion of 
zero-momentum strings, $q$ must be even. It is straigtforward to show that $\widetilde
{\mathcal N}'(L,\ell,q)$ obeys the recursive relation
%
\begin{equation}
\label{NpLlq-1}
\widetilde{\mathcal N}'(L,\ell,q)=\sum_{s=0}^{q/2-1}B\Big(\frac{L}{2}-q+s,s\Big)\widetilde
{\mathcal N}'\Big(L-2q,\frac{\ell-q}{2},\frac{q}{2}-s\Big),
\end{equation}
% 
with the constraint
%
\begin{equation}
\widetilde{\mathcal N}'(L,1,1)=\frac{L}{2}-1. 
\end{equation}
%
It is straightforward to check that the solution of~\eref{NpLlq-1} is given as 
%
\begin{equation}
\widetilde{\mathcal N}'(L,\ell,q)=\frac{L-2\ell+2}{L-\ell+2}B\Big(\frac{L-\ell}{2}+1,q\Big)
B\Big(\frac{\ell}{2}-1,\frac{q}{2}-1\Big).
\end{equation}
%
After summing over the allowed values of $q=2k$ with $k=1,2,\dots,\ell/2$ one obtains 
the total number of eigenstaets with nonzero N\'eel overlap at fixed number of 
particles $\ell$ $\widetilde Z_{Neel}'(L,\ell)$ as 
%
\begin{equation}
\widetilde Z_{Neel}'(L,\ell)=B\Big(\frac{L}{2},\frac{\ell}{2}\Big)-
B\Big(\frac{L}{2},\frac{\ell}{2}-1\Big).
\end{equation}
%
Summing over $\ell$ one obtains~\eref{neel-ov-count}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Exact N\'eel and Majumdar-Ghosh overlaps for a small Heisenberg chain} 
\label{app-L12}

In this section we provide exact diagonalization results for the overlap of both the 
N\'eel state and the Majumdar-Ghosh (MG) state with all the eigenstates of the Heisenberg 
spin chain with $L=12$ sites. We also provide the corresponding results obtained 
using the string hypothesis and the overlap formulas~\eref{neel-ov} and~\eref{mg-ov}, 
restricting ourselves to eigenstates with no zero-momentum strings.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{N\'eel overlap}
\label{app-neel}

The overlaps between all the eigenstates of the Heisenberg spin chain and the N\'eel 
state are reported in Table~\ref{table:neel}. The first column in the Table shows 
the string content ${\mathcal S}\equiv\{s_1,\dots,s_M\}$, with $M$ being the number 
of finite rapidities. The number of infinite rapidities $N_{\infty}=L/2-M$ is also 
reported. Note that eigenstates containing infinite rapidities correspond to 
different $S_z$ eigenvalue. The second column shows 
$2I_n^+$, with $I_n$ the Bethe-Gaudin-Takahashi quantum number identifying the 
BGT rapidity of the $n$-string. Due to the parity invariance only the positive 
quantum numbers are reported. The total number of independent strings, i.e., 
$q\equiv\sum_js_j$, is reported in the third column. The fourth column is the 
eigenstate's energy eigenvalue $E$. The last two columns show the squared N\'eel 
overlaps and the corresponding result obtained using the Bethe-Gaudin-Takahashi 
equations, respectively. In the last column only the case with no zero-momentum 
strings is considered. The deviations from the exact diagonalization results (digits 
with different colors) have to be attributed to the string hypothesis. Notice that  
the overlap between the N\'eel state and the $S_z=0$ eigenstate in the sector with 
maximal total spin $S=L/2$ (first column in Table~\ref{table:neel}), is given 
analytically as $2/B(L,L/2)$, with $B(x,y)$ the Newton binomial.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
\scriptsize
\centering
Bethe states with nonzero N\'eel overlap ($L=12$)\\[1ex]
\begin{tabular}{rrrrrr}
\toprule
String content & $2I^+_n$ & $q$ & E & $|\langle\lambda|N\rangle|^2$ (exact) & $|\langle
\lambda|N\rangle|^2$ (BGT) \\[0.3em]
\toprule
6 inf & - & - & $0$ & $0.002164502165$ & $0.002164502165$\\
\midrule
\{2,0\}\, 4 inf &$1_1$ & $2$ & $-3.918985947229$ & $0.096183409244$ & $0.096183409244$\\
 &$3_1 $ & & $-3.309721467891$ & $0.011288497947$ &             $0.011288497947$\\
 &$5_1 $ & & $-2.284629676547$ & $0.004542580506$ &             $0.004542580506$\\
 &$7_1 $ & & $-1.169169973996$ & $0.002752622983$ &             $0.002752622983$\\
 &$9_1 $ & & $-0.317492934338$ & $0.002116006203$ &             $0.002116006203$\\
\midrule
\{4,0,0,0\}\, 2 inf &$1_1 3_1 $ & $4$ & $-7.070529325964$ & $0.310133033838$ &$0.310133033838$\\
  &$1_1 5_1 $ & & $-5.847128730477$ & $0.129277023687$ &           $0.129277023687$\\
  &$ 1_1 7_1$ & & $-4.570746557876$ & $0.085992436024$ &           $0.085992436024$\\
  &$ 3_1 5_1$ & & $-5.153853093221$ & $0.015256395523$ &           $0.015256395523$\\
  &$3_1 7_1 $ & & $-3.916336243695$ & $0.010091113504$ &           $0.010091113504$\\
  &$5_1 7_1 $ & & $-2.817696043731$ & $0.004059780228$ &           $0.004059780228$\\
\midrule
\{0,2,0,0\}\, 2 inf &$1_2 $ & $2$ & $-1.905667167442$ & $0.001207238321$ & $0.0012072{\color{red}45406}$\\
  &$3_2 $ & & $-1.368837200825$ & $0.002340453815$ &            $0.0023{\color{red}25724713}$\\
  &$5_2 $ & & $-0.681173793635$ & $0.001921010489$ &            $0.0019{\color{red}39001396}$\\
\midrule
\{1,0,1,0\}\, 2 inf &$0_1 0_3$ & $2$ & $-2.668031843135$ & $0.034959609810$ & -\\
\midrule
\{6,0,0,0,0,0\}\, 0 inf &$1_1 3_1 5_1$ & $6$ & $-8.387390917445$ & $0.153412152966$ & $0.153412152966$\\
\midrule
\{2,2,0,0,0,0\}\, 0 inf &$1_1 1_2$ & $4$ & $-5.401838225870$ & $0.040162686361$ & $0.04{\color{red}1042488913}$\\  
&$3_1 1_2 $ & & $-4.613929948329$ & $0.004636541934$ & $0.004{\color{red}730512604}$\\
  &$5_1 1_2 $ &  & $-3.147465758841$ & $0.001335522556$ & $0.00133{\color{red}7334035}$\\
\midrule
\{3,0,1,0,0,0\}\, 0 inf &$0_1 2_1 0_3$ & $4$ & $-6.340207488736$ & $0.052743525774$ & -\\
  &$0_1 4_1 0_3$ & & $-5.203653009936$ & $0.015022005621$ & - \\
  &$0_1 6_1 0_3$ & & $-3.788693957250$ & $0.011144489334$ & - \\
\midrule
\{1,0,0,0,1,0\}\, 0 inf &$0_1 0_5$ & $2$ & $-2.444293750583$ & $0.005887902992$ & - \\
\midrule
\{0,0,2,0,0,0\}\, 0 inf &$1_3$ & $2$ & $-1.111855930538$ & $0.001342476001$ & $0.0013{\color{red}84980817}$ \\
\midrule
\{0,1,0,1,0,0\}\, 0 inf &$0_2 0_4$ & $2$ &  $-1.560671012472$ & $0.000026982174$ & - \\
\bottomrule
\end{tabular}
\caption{All Bethe states for $L=12$ having nonzero overlap with the zero-momentum N\'eel state. 
 The first column shows the string content of the Bethe states, including the number of infinite 
 rapidities. The second and third column show $2I_n^+$, with $I_n^+$ the BGT quantum numbers 
 identifying the different states, and the number $q$ of independent strings. In the second 
 column only the positive BGT numbers are shown. The fourth column is the Bethe state eigenenergy. 
 Finally, the last two columns show the exact overlap with the N\'eel state and the approximate 
 result obatained using the BGT equations. In the last column Bethe states containing zero-momentum 
 strings are excluded. Deviations from the exact result (digits with different colors) are 
 attributed to the string hypothesis. 
}
\label{table:neel}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Majumdar-Ghosh overlap}
\label{app-mg}
The overlap between the Heisenberg chain eigenstates with the Majumdar-Ghosh state are shown in 
Table~\ref{table:mg}. The conventions on the representation of the eigenstates is the same as in 
Table~\ref{table:neel}. Note that in contrast with the N\'eel state, only the eigenstates with 
zero total spin $S=0$ have non zero overlap, i.e., no eigenstates with infinite rapidities are 
present, which reflect that the Majumdar-Ghosh state is unvariant under $SU(2)$ rotations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
\scriptsize
\centering
Bethe states with nonzero N\'eel overlap ($L=12$)\\[1ex]
\begin{tabular}{rrrrrr}
\toprule
String content & $2I^+_n$ & $q$ & E & $|\langle\lambda|MG\rangle|^2$ (exact) & $|\langle\lambda|MG\rangle|^2$ (BGT) \\[0.3em]
\toprule
\{6,0,0,0,0,0\} &$1_1 3_1 5_1$ & $6$ & $-8.387390917445$ & $0.716615769224$ & $0.716615769224$\\
\midrule
\{2,2,0,0,0,0\} &$1_1 1_2$ & $4$ & $-5.401838225870$ & $0.055624700196$ & $0.05{\color{red}4033366543}$\\  
&$3_1 1_2 $ & & $-4.613929948329$ & $0.005687428810$ & $0.005{\color{red}582983043}$\\
&$5_1 1_2 $ &  & $-3.147465758841$ & $0.002107475934$ & $0.002107{\color{red}086933}$\\
\midrule
\{3,0,1,0,0,0\} &$0_1 2_1 0_3$ & $4$ & $-6.340207488736$ & $0.205891158647$ & -\\
  &$0_1 4_1 0_3$ & & $-5.203653009936$ & $0.038832154450$ & - \\
  &$0_1 6_1 0_3$ & & $-3.788693957250$ & $0.006019410923$ & - \\
\midrule
\{1,0,0,0,1,0\} &$0_1 0_5$ & $2$ & $-2.444293750583$ & $0.000129601311$ & - \\
\midrule
\{0,0,2,0,0,0\} &$1_3$ & $2$ & $-1.111855930538$ & $0.000011727787$ & $0.00001{\color{red}2785580}$\\
\midrule
\{0,1,0,1,0,0\} &$0_2 0_4$ & $2$ &  $-1.560671012472$ & $0.000330572718$ & - \\
\bottomrule
\end{tabular}
\caption{All Bethe states for $L=12$ having nonzero overlap with the zero-momentum Majumdar-Ghosh (MG) 
 state. The first column shows the string content of the Bethe states. The second and third column show 
 $2I_n^+$, with $I_n^+$ the BGT quantum numbers identifying the different states, and the number $q$ 
 of independent strings. In the second column only the positive BGT numbers are shown. Note that, in 
 contrast to Table~\ref{table:neel} no states with infinite rapidities are present. The fourth column 
 is the Bethe state eigenenergy. Finally, the last two columns show the exact overlap with the MG state 
 and the approximate result obatained using the BGT equations. In the last column Bethe states containing 
 zero-momentum strings are excluded. Deviations from the exact result (digits with different colors) 
 are attributed to the string hypothesis. 
}
\label{table:mg}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}

\bibitem{calabrese-2014}
P.~Calabrese and P.~Le Doussal, J.\ Stat.\ Mech.\ (2014) P05004.

\bibitem{alba-2015}
V.~Alba, arXiv:1507.06994.

\end{thebibliography}

\end{document}

### 2015-09-10 draft/fs_qa_v1.tex
revised 10/09/2015

@@
 \usepackage{tikz}
+%\usepackage[backend=bibtex]{biblatex}
 
@@
 
-\author{Vincenzo Alba$^1$, Pasquale Calabrese$^1$}
-\address{$^1$ International School for Advanced Studies (SISSA),
-Via Bonomea 265, 34136, Trieste, Italy,
-INFN, Sezione di Trieste}
+\author{Authors}
+%\address{$^1$ International School for Advanced Studies (SISSA),
+%Via Bonomea 265, 34136, Trieste, Italy,
+%INFN, Sezione di Trieste}
 
@@
 calculation of the overlap.
+
+In the thermodynamic limit it is natural to assume that the steady-state expectation 
+values are obtained using the so-called diagonal ensemble, which is defined as 
+%
+\begin{equation}
+\label{d-ensemble}
+\langle{\mathcal O}\rangle=\sum\limits_{\alpha}|\langle\Psi_0|\alpha\rangle|^2
+\langle\alpha|{\mathcal O}|\alpha\rangle. 
+\end{equation}
+%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Bethe-Takahashi equations}
+\subsection{Bethe-Gaudin-Takahashi (BGT) equations}
 
@@
 
+In the thermodynamic limit the BGT equations become a set of coupled integral 
+equations given as 
+%
+\begin{equation}
+\label{bgt-th}
+a_n(\lambda)=\rho_n(\lambda)+\rho^h_n(\lambda)+\sum_m(T_{n,m}*\rho_m)
+(\lambda),
+\end{equation}
+%
+where 
+%
+\begin{equation}
+(T_{n,m}*\rho_m)(\lambda)\equiv\int_{-\infty}^{+\infty}T_{n,m}(\lambda-\lambda')
+\rho_{m}(\lambda'). 
+\end{equation}
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The conserved charges}
+
+The $XXX$ chain exhibits an extensive number of local conserved charges $Q_n$. 
+These are defined as 
+%
+\begin{equation}
+\label{Q-def}
+\left.Q_{j+1}\equiv\frac{i}{(j-1)!}\frac{d^j}{dy^j}\log\tau
+(y)\right|_{y=i},
+\end{equation}
+%
+where $y$ is a spectral parameter and $\tau(y)$ is the eigenvalue of the 
+so-called transfer matrix in the Algebraic Bethe Ansatz framework. The 
+analytic expression of $\tau(y)$ for a given eigenstate identified by 
+a set of rapidities $\{\lambda_\alpha\}$ is given as 
+%
+\begin{equation}
+\label{tau}
+\tau(y)\equiv\Big(\frac{y+i}{2}\Big)^L\prod\limits_\alpha\frac{y-\lambda_\alpha-2i}
+{y-\lambda_\alpha}+\Big(\frac{y-i}{2}\Big)^L\prod\limits_\alpha\frac{y-\lambda_\alpha
++2i}{y-\lambda_\alpha}.
+\end{equation}
+%
+Using the string hypothesis and~\eref{Q-def} and~\eref{tau}, one obtains tha for 
+a generic $n$-string with string center $\lambda$ the first few charges have the 
+simple expressions
+%
+\begin{eqnarray}
+Q_2=-\frac{2n}{\lambda^2+n^2}\\
+Q_3=-\frac{4n\lambda}{(\lambda^2+n^2)^2}\\
+Q_4=\frac{2n(n^2-3\lambda^2)}{(n^2+\lambda^2)^3}\\
+Q_5=\frac{8n\lambda(n^2-\lambda^2)}{(n^2+\lambda^2)^4}\\
+Q_6=-\frac{2n(5\lambda^4-10n^2\lambda^2+n^4)}{(n^2+\lambda^2)^5}
+\end{eqnarray}
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{N\'eel expectation values}
+\label{Q-Neel}
+
+The expectation values of the $XXX$ chain conserved charges over the N\'eel 
+state are given as
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+Here we focus on the overlap with the zero-momentum N\'eel state $|N\rangle$, 
+defined as 
+%
+\begin{equation}
+\label{neel}
+|N\rangle\equiv\frac{1}{\sqrt{2}}\Big(|\uparrow\downarrow\rangle^{\otimes L/2}
++|\downarrow\uparrow\rangle^{\otimes L/2}\Big).
+\end{equation}
+%
 Here we restrict to the parity-invariant eigenstates. These are the only 
@@
 
+The Majumdar-Ghosh state $|MG\rangle$ is defined as 
+%
+\begin{equation}
+|MG\rangle\equiv \Big(\frac{|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle}
+{\sqrt{2}}\Big)^{\otimes L/2}
+\end{equation}
+%
 The overlap between the generic eigenstate of the $XXX$ chain and the Majumdar-Ghosh 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Quench Action method}
+\label{quench-action}
+
+For integrable models the Quench-Action approach allows to extract exactly both 
+the steady state after the quench and the relaxation dynamics to the steady state.
+
+In the thermodynamic limit the sum over the model eigenstates is recast into 
+a functional integral over the so-called root distributions $\pmb{\rho}\equiv
+\{\rho_n(\lambda)\}_{n=1}^\infty$ as
+%
+\begin{equation}
+\label{eig-sum}
+\sum\limits_{\alpha}\rightarrow\int{\mathcal D}\pmb{\rho}e^{S_{YY}(\pmb{\rho})}. 
+\end{equation}
+%
+Here ${\mathcal D}\pmb{\rho}\equiv\prod_{n=1}^\infty{\mathcal D}\rho_n(\lambda)$, 
+$\rho_n(\lambda)$ denote the distribution of the $n$-strings BGT roots, and 
+$S_{YY}(\pmb{\rho})$ is the Yang-Yang entropy, which counts the number of 
+Bethe states leading to the same $\pmb{\rho}$ in the thermodynamic limit. 
+Formally, $\rho_n(\lambda)$  are defined as $\rho_n(\lambda)\equiv\lim_{L\to
+\infty}(\lambda_{n;\gamma+1}-\lambda_{n;\gamma})^{-1}$.
+
+Using~\eref{eig-sum} the diagonal ensemble~\eref{d-ensemble} becomes 
+%
+\begin{equation}
+\label{qa-d-ensemble}
+\fl
+\quad\langle{\mathcal O}\rangle=\int{\mathcal D}\pmb{\rho}(\lambda)
+\exp\Big(2\Re\log\langle\Psi_0|\pmb{\rho}(\lambda)\rangle 
++S_{YY}(\pmb{\rho})\Big)\langle\pmb{\rho}(\lambda)|{\mathcal O}|\pmb{\rho}
+(\lambda)\rangle
+\end{equation}
+%
+Note that in~\eref{qa-d-ensemble} it is assumed that in the thermodynamic limit 
+the eigenstate expectation values $\langle\alpha|{\mathcal O}|\alpha\rangle$ 
+become smooth functionals  $\langle\pmb{\rho}(\lambda)|{\mathcal O}|\pmb{\rho}
+(\lambda)\rangle$ of the root distributions $\pmb{\rho}$.
+
+Similarly, in~\eref{qa-d-ensemble} $\langle\Psi_0|\pmb{\rho}(\lambda)\rangle$ 
+denotes the Bethe states overlap density with the prequench state $\Psi_0$.
+
+The strategy is to evaluate the functional integral in~\eref{qa-d-ensemble} 
+using the saddle point approximation.
+
+One has then to minimize the functional ${\mathcal S}(\pmb{\rho})$ defined 
+as 
+%
+\begin{equation}
+L{\mathcal S}(\pmb{\rho})\equiv 2\Re\log\langle\pmb{\rho}|\Psi_0
+\rangle+S_{YY}(\pmb{\rho}(\lambda)). 
+\end{equation}
+% 
+under the constraint that the BGT equations hold. For the quench with initial 
+state the N\'eel state the resulting saddle point root distributions 
+$\rho_n^*(\lambda)$ can be obtained analytically. The first few root distributions 
+are given as 
+%
+\begin{eqnarray}
+\label{rho_sp}
+\fl\quad\rho^*_1(\lambda)=\frac{8(4+\lambda^2)}{\pi(19+3\lambda^2)(1+6\lambda^2+
+\lambda^4)}\\
+\fl\quad\rho_2^*(\lambda)=\frac{8\lambda^2(9+\lambda^2)(4+3\lambda^2)}{\pi(2+\lambda^2)
+(16+14\lambda^2+\lambda^4)(256+132\lambda^2+9\lambda^4)}\\
+\fl\quad\rho_3^*=\frac{8(1+\lambda^2)^2(5+\lambda^2)(16+\lambda^2)(21+\lambda^2)}
+{\pi(19+3\lambda^2)(9+624\lambda^2+262\lambda^4+32\lambda^6+\lambda^8)
+(509+5\lambda^2(26+\lambda^2))}.
+\end{eqnarray}
+%
+
+%##################################################################
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=.9\textwidth]{./draft_figs/Neel_overlaps}
+\end{center}
+\caption{ 
+}
+\label{fig0}
+\end{figure}
+%##################################################################
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Overlap sum rules: the role of the zero-momentum strings}
 \label{ov-sum-rules}
-
-In this section we investigate the role of the zero-momentum strings. We focus on 
-conserved quantities sum rules. Specifically, given a generic conserved quantity 
-(charge) $\hat Q$ we consider the trivial identity  
-%
-\begin{equation}
-\label{sum}
-Q_0\equiv\langle\Psi_0|\hat Q|\Psi_0\rangle=\sum\limits_{\lambda}|\langle\lambda|
-\Psi_0\rangle|^2Q_\lambda, 
-\end{equation}
-%
-where $Q_0$ is the charge expectation values over the initial state $|\Psi_0
-\rangle$, $|\lambda\rangle$ denotes the generic eigenstate of the $XXX$ chain, 
-and $Q_\lambda$ is the charge eigenvalue over the eigenstate.
-
-Here we restrict ourselves to the cases with $\hat Q=\mathbb{I}$ and $\hat 
-Q={\mathcal H}$, considering both the case with $|\Psi\rangle=|N\rangle$ and 
-$|\Psi_0\rangle=|MG\rangle$.
 
@@
 \end{center}
-\caption{ Overlap sum rules for the Neel state. (a) The overlap sum rule 
- $\sum_{\lambda}|\langle\lambda|N\rangle|^2=1$, with $|N\rangle$ 
- the Neel state and $|\lambda\rangle$ the eigenstates  of the $XXX$ 
- spin chain. The $x$-axis shows $1/L$, with $L$ the chain length. The 
- circles are Bethe ansatz results for chains up to $L=36$. The results 
+\caption{ Overlap sum rules for the Neel state: The role of the zero-momentum 
+ strings. (a) The overlap sum rule $\sum_{\lambda}|\langle\lambda|N\rangle|^2=1$, 
+ with $|N\rangle$ the Neel state and $|\lambda\rangle$ the eigenstates  of 
+ the $XXX$ spin chain. The $x$-axis shows $1/L$, with $L$ the chain length. 
+ The circles are Bethe ansatz results for chains up to $L=36$. The results 
  are obtained via a full scanning of the chain Hilbert space. Only the 
@@
 %##################################################################
+
+In this section we investigate the role of the zero-momentum strings. We focus on 
+conserved quantities sum rules. Specifically, given a generic conserved quantity 
+(charge) $\hat Q$ we consider the trivial identity  
+%
+\begin{equation}
+\label{sum}
+Q_0\equiv\langle\Psi_0|\hat Q|\Psi_0\rangle=\sum\limits_{\lambda}|\langle\lambda|
+\Psi_0\rangle|^2Q_\lambda, 
+\end{equation}
+%
+where $Q_0$ is the charge expectation values over the initial state $|\Psi_0
+\rangle$, $|\lambda\rangle$ denotes the generic eigenstate of the $XXX$ chain, 
+and $Q_\lambda$ is the charge eigenvalue over the eigenstate.
+
+Here we restrict ourselves to the cases with $\hat Q=\mathbb{I}$ and $\hat 
+Q={\mathcal H}$, considering both the case with $|\Psi\rangle=|N\rangle$ and 
+$|\Psi_0\rangle=|MG\rangle$.
+
+For the N\'eel state, for any finite $L$ Eq.~\eref{sum} gives $Q_0=1,-1/2$ for 
+$\hat{Q}=\mathbb{I}$ and $\hat Q={\mathcal H}$, respectively.
+
+Figure~\ref{fig2-neel-sr} plots the numerical results obtained via a full 
+scanning of the Hilbert space of the Heisenberg chain.
+
+Precisely, the numerical data are obtained by generating all the possible string 
+contents ${\mathcal S}$ compatible with the parity-invariance constraint
+
+Panel (a) and (b) in the 
+Figure plots the sum rule~\eref{sum} for $\hat Q=\mathbb{I}$ and $\hat Q={\mathcal 
+H}$, respectively. The circles are obtained considering all the eigenstates of the 
+Heisenberg spin chain with $L$ sites, excluding eigenstates containing 
+zero-momentum strings.
+
+The total number of eigenstates $\widetilde Z_{Neel}$ containing no zero-momentum 
+strings is given as 
+%
+\begin{equation}
+\label{ztilde}
+\widetilde Z_{Neel}=B\Big(\frac{L}{2},\frac{L}{4}\Big).
+\end{equation}
+%
+The proof of\eref{ztilde} is reported in~\ref{app-2}.
 
@@
 
+The largest chain size considered is $L=36$. The data are plotted versus $1/L$.
+
+Interestingly, both the sum rules (panels (a)(b)) are not saturated, as expected 
+since the eigenstates corresponding to zero-momentum strings are excluded in the 
+sum in the right-hand-side in~\eref{sum}.
+
+Interestingly, both sum rules exhibit vanishing behavior upon increasing the 
+chain size. The dash-dotted lines in the Figures are fits to the behavior 
+$A/L^{1/2}+B/L$, with $A,B$ fitting parameters, and perfectly describe the 
+behavior of the data.
+
+The vanishing behavior as $\propto 1/L^{1/2}$ of the sum rules reflects the vanishing 
+of the fraction of non-zero momentum string eigenstates in the thermodynamic limit ad 
+%
+\begin{equation}
+\label{beh}
+\frac{\widetilde Z_{Neel}}{Z_{Neel}}\propto\frac{4}{\sqrt{\pi L}}, 
+\end{equation}
+% 
+with $Z_{Neel}$ being the total number of eigenstates corresponding to parity 
+invariant BGT quantum numbers configurations.
+
+One should observe that the asymptotic, i.e., at large $L$, behavior~\eref{beh} 
+is not generic, meaning that different initial states $|\Psi_0\rangle$ might 
+give different behaviors.
+
+This is illustrated in Figure~\ref{fig3-dimer-sr}, focusing on the Majumdar-Ghosh 
+(MG) state. Panels (a) and (b) plot the sum rules with $\hat Q=\mathbb{I}$ and 
+$\hat Q={\mathcal H}$ (same as in Figure~\ref{fig2-neel-sr}). As for the N\'eel 
+state only eigenstates containing no zero-momentum strings are consdidered. 
+Note that their number $\widetilde Z_{MG}$ (see~\ref{app-2}) is now given as 
+%
+\begin{equation}
+\widetilde Z_{MG}=B\Big(\frac{L}{2},\frac{L}{4}\Big)-B\Big(\frac{L}{2},
+\frac{L}{4}-1\Big). 
+\end{equation}
+%
+Similar to Figure~\ref{fig2-neel-sr}, due to the exclusion of the zero-momentum 
+strings, the saturation rules exhibit vanishing behavior in the thermodynamic 
+limit. However, in contrast with the N\'eel case (see Figure~\ref{fig2-neel-sr}), 
+one has the behavior $Q_0\sim 1/L$, as confirmed by the fits (dash-dotted lines 
+in Figure~\ref{fig3-dimer-sr}).
+
+Similar to the N\'eel case this reflects the same vanishing behavior of the 
+eigenstates containing no zero-momentum strings $\widetilde Z_{MG}/Z_{MG}$ as 
+%
+\begin{equation}
+\frac{\widetilde Z_{MG}}{Z_{MG}}=\frac{4}{4+L}. 
+\end{equation}
+%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Monte Carlo implementation of the Quench-Action approach}
+\label{mcqa-sec}
 
@@
 %
-where ${\mathcal E}'\equiv-\log\langle\lambda'|N\rangle$, and similarly for 
-${\mathcal E}$. 
+where ${\mathcal E}'\equiv-\log\langle\lambda'|N\rangle$, similarly for 
+${\mathcal E}$, and $\Re$ denotes the real part. 
 \end{enumerate}
 %
+
+Afte some necessary thermalization steps the sequence $1-4$ generates eigenstates 
+of the $XXX$ chain distributed according to the Quench-Action probability 
+distribution.
+
+For a generic observable ${\mathcal O}$, its Quench-Action expectation value 
+$\langle{\mathcal O}\rangle_{QA}$ is obtained as the arithmetic average of the 
+expectation value over the eigenstates sampled in the Monte Carlo as 
+%
+\begin{equation}
+\langle{\mathcal O}\rangle_{QA}=\frac{1}{N_{mcs}}\sum\limits_{\lambda}
+\langle\lambda|{\mathcal O}|\lambda\rangle, 
+\end{equation}
+%
+with $N_{mcs}$ being the total number of Monte Carlo steps.
 
@@
 \label{MCQA-nr}
-
-The validity of the Monte Carlo approach for simulating the Quench-Action results 
-is demonstrated in Figure~\ref{fig5-neel-sum-rules}. The Figure focuses on the 
-N\'eel sum rules for the conserved charges $Q_2$ and $Q_4$. Specifically, 
-panel (a) shows the sum rule $\langle Q_2\rangle/L=1/2$ (energy conservation). 
-%
-\begin{equation}
-\langle N|\hat Q_n|N\rangle=\sum\limits_{\lambda}|\langle N|\lambda\rangle|^2
-Q_n
-\end{equation}
-%
 
@@
 }
-\label{fig5-neel-sum-rules}
+\label{fig5-neel-sr}
 \end{figure}
 %##################################################################
+
+In this section we numerically demonstrate that the only effect of neglecting 
+the zero-momentum strings are finite-size corrections.
+
+The validity of the Monte Carlo approach for simulating the Quench-Action 
+results is demonstrated in Figure~\ref{fig5-neel-sr}. The Figure focuses on 
+the N\'eel sum rules for the conserved charges $Q_2$ and $Q_4$. Specifically, 
+panel (a) shows the sum rules for $\hat Q=\hat Q_2$, $\hat Q=\hat Q_4$, 
+and the corresponding fluctuations $\sigma^2(Q_n)\equiv \langle N|\hat Q_n^2|
+N\rangle-\langle N|\hat Q_n|N\rangle^2$. 
+%
+\begin{equation}
+\langle N|\hat Q_n|N\rangle=\sum\limits_{\lambda}|\langle N|\lambda\rangle|^2
+Q_n.
+\end{equation}
+%
+Note that the N\'eel sum rule for the identity $\mathbb{I}$ is trivially satisfied, 
+and it corresponds to the normalization of the Monte Carlo probability. 
+Figure~\ref{fig5-neel-sr} (a) plots the N\'eel sum rule for the energy density $Q_2/L$. 
+The circles are Monte Carlo data obtained using the procedure outlined in~\ref{mcqa-sec} 
+for several Heisenberg spin chains. The largest chain simulated is for $L=56$ sites. 
+The data correspond to a simulation with $\sim 10^7$ Monte Carlo step (mcs). 
+The expected result $\langle N|\hat Q_2|N\rangle/L=-1/2$ is shown as dash-dotted 
+line.
+
+In stark contrast with Figure~\ref{fig2-neel-sr} and Figure~\ref{fig3-dimer-sr}, 
+while for small chains the sum rule is violated the data strongly suggest that 
+in the thermodynamic limit the sum rule saturates the expected theoretical 
+value.
+
+Furthermore, the data suggest the behavior $\propto 1/L$, as confirmed by the fit 
+to $-1/2+A/L+b/L^2$ (dashed line in the Figure), with $A,B$ fitting parameters.
+
+The same qualitative behavior is demonstrated in panel (b) for the energy 
+fluctuations. Interestingly, for $L=56$ the Monte Carlo result is compatible 
+within the error bar with the expected asymptotic one.
+
+Finally, panels (c)(d) show the same results as for (a)(b) for the conserved 
+charge $Q_4$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The Quench-Action root distributions}
+\label{MCQA-root}
 
@@
 \begin{center}
-\includegraphics[width=.8\textwidth]{./draft_figs/Neel_rho}
+\includegraphics[width=.95\textwidth]{./draft_figs/Neel_rho}
 \end{center}
-\caption{ The steady-state root densities $\rho_1(x)$ (panel (a)) and 
- $\rho_2(x)$ (panel (b)), plotted versus the root $x$. The histograms 
- are Monte Carlo data for the Heisenberg chain with $L=56$ sites and 
- $\sim 10^7$ Monte Carlo steps. The $y$-axis is divided by $10^6$ for 
- convenience. The continuous lines are the analytical Quench-Action 
- results in the thermodynamic limit. 
+\caption{ The Quench-Action steady state root ddistributions $\rho_1(x)$ 
+ and $\rho_2(x)$: Monte Carlos results. (a) The histograms of the $1$-string 
+ rapidities sampled in the Monte Carlo. The $x$-axis shows the $1$-string BGT 
+ root $\lambda$. The data are for a chain with $L=56$ sites and $N_{mcs}\sim 
+ 10^7$ Monte Carlo steps. The data are divided by a factor $10^6$ for plotting 
+ convenience. The width of the histogram bin is $\Delta\lambda\sim 0.07$. (b) 
+ The same as in (a) for the $2$-string roots sampled in the Monte Carlo. (b) 
+ The extracted $1$-string root distribution $\rho_1(\lambda)$ plotted versus 
+ $\lambda$ for two chains with $L=48$ and $L=56$ (diamond and circles, respectively). 
+ The full line is the Quench-Action analytic result in the thermodynamic limit. (d) 
+ The same as in (c) for the $2$-string root density $\rho_2(\lambda)$. In both 
+ (c)(d) the oscillations are finite-size effects, whereas the error bars 
+ show the statistical Monte Carlo error. 
 }
@@
 %##################################################################
+
+The BGT root distributions $\rho_n(\lambda)$ identifying the Quench-Action saddle 
+point can be extracted from the Monte Carlo simulation as shown in~\cite{alba-2015}.
+
+Figure~\ref{fig6-neel-roots} displays the first two root distributions 
+$\rho_1(\lambda)$ (panel (a)) and $\rho_2(\lambda)$ (panel (b)), plotted agains 
+the BGT root $\lambda$. The data are the histograms of the BGT roots sampled 
+in the Monte Carlo. The data are for a chain with $L=56$ sites and 
+$N_{mcs}\sim 10^7$ Monte Carlo steps. All the data are divided by a factor 
+$10^6$ for plotting convenience. The width of the histogram bins $\Delta\lambda$ 
+is $\Delta\lambda\approx0.02$ and $\Delta\lambda\approx0.001$ for $\rho_1(\lambda)$ 
+and $\rho_2(\lambda)$, respectively.
+
+The histogram fluctuations are due to $N_{mcs}$ being finite, and are expected 
+to vanish in the limit $N_{mcs}\to\infty$.
+
+The continuous lines is the expected analytic result in the thermodynamic limit.
+
+Clearly, $\rho_1(\lambda)$ is in good agreement with the Monte Carlo data in the 
+whole range $-2\le\lambda\le2$ considered. 
+On the other hand, larger deviations from the theoretical result are present 
+for $\rho_2(\lambda)$. These deviations are larger on the tails of the 
+distribution. This is expected since large $\lambda$ correspond to large 
+quasimomenta, which are more sensitive to the finite size of the chain.
 
@@
 
+Note that the total number $Z_{MG}$ of parity-invariant eigenstates having non 
+zero overlap with the Majumdar-Ghosh state is obtained from Eq~\eref{N-count-p} 
+replacing $\ell=L/2$, to obtain 
+%
+\begin{equation}
+\label{p-inv-mg}
+Z_{MG}=B\Big(\frac{L}{2}-1,\frac{L}{4}-1\Big)+B\Big(\frac{L}{2}-1,\frac{L}{4}
+\Big). 
+\end{equation}
+%
+Physically, this is due to the fact that the 
+Majumdar-Ghosh state is invariant under $SU(2)$ rotations, which implies 
+that only eigenstates with zero total spin $S=0$ can have non zero overlap.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The total number of parity-invariant quantum numbers $\widetilde{\mathcal N}_n$ in the $n$-string 
-sector is given as  
+The total number of parity-invariant quantum numbers $\widetilde{\mathcal N}_n$ in the 
+$n$-string sector is given as  
 %
@@
 \begin{equation}
+\label{neel-fi}
 \widetilde Z_{Neel}'(L,\ell)=B\Big(\frac{L}{2},\frac{\ell}{2}\Big)-
@@
 Summing over $\ell$ one obtains~\eref{neel-ov-count}.
+Similar to~\eref{p-inv-mg} the total number of eigenstates $\widetilde Z_{MG}$ 
+with no zero-momentum strings having non-zero overlap with the Majumdar-Ghosh 
+state is obtained from~\eref{neel-fi} replacing $\ell\to L/2$, to obtain 
+%
+\begin{equation}
+\label{mg-fi}
+\widetilde Z_{MG}=B\Big(\frac{L}{2},\frac{L}{4}\Big)-B\Big(\frac{L}{2},\frac{L}{4}-1
+\Big). 
+\end{equation}
+%
+Interestingly, using~\eref{p-inv-mg} and~\eref{mg-fi}, one obtains that the ratio 
+$\widetilde Z_{MG}/Z_{MG}$ is given as 
+%
+\begin{equation}
+\frac{\widetilde Z_{MG}}{Z_{MG}}=\frac{4}{4+L}. 
+\end{equation}
+%
 

### 2015-09-11 draft/fs_qa_v1.tex
final

@@
 \end{center}
-\caption{ 
+\caption{ N\'eel state overlaps in the Heisenberg spin chain. (a) 
+ The N\'eel state overlaps with the eigenstates of the Heisenberg 
+ spin chain: Squared overlaps $|\langle\lambda|N\rangle|^2$ plotted 
+ as a function of the eigenstates energy density $E/L$. Here $|\lambda
+ \rangle$ denotes the generic eigenstate of the Heisenberg spin chain. 
+ The data are for chains with length $26\le L\le 38$. The data are 
+ obtained from a full scanning of the chains Hilbert space. 
+ Eigenstates containing strings with zero-momentum components 
+ are escluded. The overlaps decay exponentially with the chain size. 
+ (b) Histograms of $-2\log|\langle\lambda|N\rangle|/L$. Different 
+ histograms are for different chain sizes. The histogram bin width 
+ is $\sim 2/L$. The $y$-axis is rescaled by a factor $10^5$ for 
+ convenience. Note the peaking of the histograms around 
+ $-2\log|\langle\lambda|N\rangle|\sim 0.5$ in the thermodynamic 
+ limit {\bf really??}. 
 }
-\label{fig0}
+\label{fig0:N-ov-overview}
 \end{figure}

### 2015-09-11 draft/fs_qa_v1.tex
fo
revised 11/09/2015

@@
 
-%%%%%%%%%%%%%%%%%%%%%%% BETHE ANSATZ APPROACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Heisenberg spin chain}
-\label{xxx-chain}
-
-Here we consdier the spin-$\frac{1}{2}$ isotropic Heisenberg chain ($XXX$ chain). 
-The $XXX$ chain with $L$ sites is defined by the Hamiltonian 
+%%%%%%%%%%%%%%%%%%%%%%% BETHE ANSATZ FOR THE XXX CHAIN %%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Bethe ansatz solution of the Heisenberg ($XXX$) spin chain}
+\label{sec:1}
+
+Here we review some Bethe ansatz results for the spin-$\frac{1}{2}$ Heisenberg 
+($XXX$) chain. Specifically, in
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The spin-$\frac{1}{2}$ Heisenberg chain}
+\label{sec:1.1}
+
+The spin-$\frac{1}{2}$ isotropic Heisenberg chain ($XXX$ chain) with $L$ sites 
+is defined by the Hamiltonian 
 %
@@
 \subsection{Bethe equations and wavefunctions}
-\label{bethe_equations}
-
-The generic eigenstate of~\eref{xxx-ham} in the sector with $M$ particles can be written as 
-%
-\begin{equation}
-\label{ba_eig}
+\label{sec:1.2}
+
+In the Bethe ansatz framework~\cite{bethe-1931,taka-book} the generic eigenstate 
+of~\eref{xxx-ham} (Bethe state) in the sector with $M$ particles can be written as 
+%
+\begin{equation}
+\label{ba-eig}
 |\Psi_M\rangle=\sum\limits_{1\le x_1<x_2<\dots<x_M\le L}A_M(x_1,x_2,
@@
 %
-where the sum is over the positions $\{x_i\}$ of the particles, and $A_M(x_1,
-x_2,\dots,x_M)$ is the eigenstate amplitude corresponding to particles 
-at positions $x_1,x_2,\dots, x_M$. $A_M(x_1,x_2,\dots, x_M)$ is given as 
+where the sum is over the positions $\{x_i\}_{i=1}^M$ of the particles, and $A_M(x_1,
+x_2,\dots,x_M)$ is the eigenstate amplitude corresponding to the particles 
+being at positions $x_1,x_2,\dots, x_M$. Here $A_M(x_1,x_2,\dots, x_M)$ is 
+given as 
 %
@@
 \label{ba_amp}
-A_M(x_1,x_2,\dots,x_M)\equiv\sum\limits_{{\mathcal P}\in S_M}\exp\Big[i
-\sum\limits_{j=1}^Mk_{{\mathcal P}_j}x_j+i\sum\limits_{i<j}\theta_{{
-\mathcal P}_i{\mathcal P}_j}\Big].
-\end{equation}
-%
-Here the outermost sum is over the permutations $S_M$ 
-of the so-called quasi-momenta $\{k_1,k_2,\dots,k_M\}$. The two-particle 
-scattering phases $\theta_{m,n}$ are defined as 
+A_M(x_1,x_2,\dots,x_M)\equiv\sum\limits_{\sigma\in S_M}\exp\Big[i
+\sum\limits_{j=1}^Mk_{\sigma_j}x_j+i\sum\limits_{i<j}\theta_{\sigma_i,\sigma_j}
+\Big], 
+\end{equation}
+%
+where the outermost summation is over the permutations $S_M$ of the so-called 
+quasi-momenta $\{k_\alpha\}_{\alpha=1}^M$. The two-particle scattering phases 
+$\theta_{\alpha,\beta}$ are defined as 
 %
@@
 \label{s_phases}
-\theta_{m,n}\equiv \frac{1}{2i}\log\Big[-\frac{e^{ik_m+ik_n}-2e^{ik_m}+1}
-{e^{ik_m+ik_n}-2e^{ik_n}+1}\Big].
-\end{equation}
-%
-The energy associated to the eigenstate~\eref{ba_eig} is  
+\theta_{\alpha,\beta}\equiv \frac{1}{2i}\log\Big[-\frac{e^{ik_\alpha+ik_\beta}-
+2e^{ik_\alpha}+1}{e^{ik_\alpha+ik_\beta}-2e^{ik_\beta}+1}\Big].
+\end{equation}
+%
+The eigenenergy associated to the eigenstate~\eref{ba-eig} is  
 %
@@
 %
-The quasi-momenta $\{k_\alpha\}$ are obtained by solving the so-called 
-Bethe equations  
-%
-\begin{equation}
-\label{ba_eq}
+The quasi-momenta $k_\alpha$ are obtained by solving the so-called Bethe 
+equations~\cite{bethe-1931}
+%
+\begin{equation}
+\label{ba-eq}
 e^{ik_\alpha L}=\prod\limits^M_{\beta\ne\alpha}\Big[-\frac{1-2e^{
@@
 %
-It is useful to  introduce the rapidities $\{\lambda_\alpha\}$ as 
+It is useful to  introduce the rapidities $\{\lambda_\alpha\}_{\alpha=1}^M$ as 
 %
@@
 %
-Taking the logarithm on both sides in~\eref{ba_eq}, and using~\eref{rap}, 
+Taking the logarithm on both sides in~\eref{ba-eq}, and using~\eref{rap}, 
 one obtains the Bethe equations in logarithmic form as 
@@
 \begin{equation}
-\label{ba_eq_log}
+\label{ba-eq-log}
 \arctan(\lambda_\alpha)=\frac{\pi}{L}J_\alpha+\frac{1}{L}\sum\limits_{
@@
 where $-L/2<J_\alpha\le L/2$ are the so-called Bethe quantum numbers. The 
-$J_\alpha$ are half-integers and integers for $L-M$ even and odd.
-
-These solutions of the Bethe equations~\eref{ba_eq} form particular ``string'' patterns 
-in the complex plane, in the limit of large chains $L\to\infty$(string hypothesis)~\cite{
-bethe-1931,taka-book}. Specifically, rapidities forming a ``string'' of length $1\le 
-n\le M$ (that we defined here as $n$-string) are parametrized as 
-%
-\begin{equation}
-\label{str_hyp}
+$J_\alpha$ are half-integers and integers for $L-M$ even and odd, 
+respectively.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{String hypothesis \& the Bethe-Gaudin-Takahashi (BGT) equations}
+\label{sec:1.3}
+
+In the thermodynamic limit $L\to\infty$ the solutions of the Bethe 
+equations~\eref{ba-eq} form particular ``string'' patterns in the complex plane, 
+(string hypothesis)~\cite{bethe-1931,taka-book}. Specifically, the rapidities 
+forming a ``string'' of length $1\le n\le M$ (that we defined here as 
+$n$-string) can be parametrized as 
+%
+\begin{equation}
+\label{str-hyp}
 \lambda^{j}_{n;\gamma}=\lambda_{n;\gamma}-i(n-1-2j)+i\delta_{n;\gamma}^j,\qquad 
@@
 %
-where $\lambda_{n;\gamma}$ is the real part of the string (string center), 
-and $\gamma$ labels strings with different centers, while $j$ labels the different 
-components of the string. In~\eref{str_hyp} $\delta_{n;\gamma}^j$ are the string 
-deviations, which typically vanish exponentially in the thermodynamic limit.
-
-Notice that pure real rapidities are strings of unit length ($1$-strings).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Bethe-Gaudin-Takahashi (BGT) equations}
-
-The string centers $\lambda_{n;\gamma}$ in~\eref{str_hyp} are obtained by solving the 
-so-called Bethe-Takahashi equations
-%
-\begin{equation}
-\label{bt_eq}
+with $\lambda_{n;\gamma}$ being the real part of the string (string center), 
+$\gamma$ labelling strings with different centers, and $j$ labelling the different 
+components of the string. In Eq.~\eref{str-hyp} $\delta_{n;\gamma}^j$ are the string 
+deviations, which typically, i.e., for most of the chain eigenstates, vanish 
+exponentially with $L$ in the thermodynamic limit. 
+Note that real rapidities correspond to strings of unit length ($1$-strings), i.e., 
+$n=1$ in Eq.~\eref{str-hyp}.
+
+The string centers $\lambda_{n;\gamma}$ are obtained by solving the so-called 
+Bethe-Gaudin-Takahashi equations
+%
+\begin{equation}
+\label{bgt-eq}
 2L\theta_n(\lambda_{n;\gamma})=2\pi I_{n;\gamma}+\sum\limits_{(m,
-\beta)\ne(n,\gamma)}\Theta_{m,n}(\lambda_{n;\gamma}-\lambda_{m;\beta}), 
-\end{equation}
-%
-where the generalized scattering phases $\Theta_{m,n}$ read 
+\beta)\ne(n,\gamma)}\Theta_{m,n}(\lambda_{n;\gamma}-\lambda_{m;\beta}).  
+\end{equation}
+%
+The generalized scattering phases $\Theta_{m,n}$ read 
 %
@@
 %
-and $\theta_\alpha(x)\equiv 2\arctan(x/\alpha)$. Here $I_{n;\gamma}$ are the 
+with $\theta_\alpha(x)\equiv 2\arctan(x/\alpha)$. Here $I_{n;\gamma}$ are the 
 Bethe-Takahashi quantum numbers associated with $\lambda_{n;\gamma}$. 
-
-Each $M$-particle eigenstate can be characterized by its ``string content'' ${
-\mathcal S}\equiv\{s_1,\dots,s_M\}$, with $s_n$ the number of $n$-strings.
-
-It can be shown that $I_{n;\gamma}$  are integers or half-integers for $L-s_n$ 
-odd and even, respectively.
-
-Clearly, the constraint $\sum_{\alpha=1}^{M}\alpha s_\alpha=M$ 
-has to be satisfied. The upper bound for the Bethe-Takahashi quantum numbers 
+The solutions of~\eref{bgt-eq}, and the Bethe states thereof, are naturally 
+classified according to their ``string content'' ${\mathcal S}\equiv\{s_n
+\}_{n=1}^M$, with $s_n$ the number of $n$-strings. Clearly, the constraint 
+$\sum_{n=1}^{M}n s_n=M$ has to be satisfied. It can be shown that 
+the BGT quantum numbers $I_{n;\gamma}$ associated with the $n$-strings are 
+integers and half-integers for $L-s_n$ odd and even, respectively.
+
+The upper bound for the Bethe-Takahashi quantum numbers 
 can be derived as   
@@
 \rho_{m}(\lambda'). 
+\end{equation}
+%
+The matrix $T_{n,m}(x)\equiv\Theta'(x)$ is given as 
+%
+\begin{eqnarray}
+\nonumber\fl T_{m,n}(x)\equiv\left\{\begin{array}{cc}
+a_{|n-m|}(x)+\!\!\!\!\!\sum
+\limits_{r=1}^{(n+m-|n-m|-1)/2}\!\!\!\!\!2a_{|n-m|+2r}(x)
++a_{n+m}(x) & \quad\mbox{if}
+\quad n\ne m\\\fl\sum\limits_{r=1}^{n-1}2a_{2r}(x)+
+a_{2n}(x) & \quad\mbox{if}\quad n=m
+\end{array}\right.
+\end{eqnarray}
+%
+with 
+%
+\begin{equation}
+a_n(x)\equiv\frac{1}{\pi}\frac{n}{x^2+n^2}. 
 \end{equation}
@@
 with ${\mathcal P}=+$ and ${\mathcal P}=-$ for even and odd strings, respectively.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Thermodynamic limit}
+
+In the thermodynamic limit the expression for the overlap~\eref{neel-ov} becomes 
+%
+\begin{equation}
+\label{neel-ov-th}
+\fl\lim_{L\to\infty}\left[\frac{\langle N|\{\pm\lambda_j\}_{j=1}^m,n_\infty
+\rangle}{|||\{\lambda_j\}_{j=1}^m,n_\infty\rangle||}\right]=\frac{L}{2}\Big(
+n_\infty\log(2)+\sum_{n=1}^\infty\int_0^\infty d\lambda\rho_n(\lambda)[g_n(\lambda)
++2n\log(4)]\Big), 
+\end{equation}
+%
+with 
+%
+\begin{eqnarray}
+g_n(\lambda)=\sum_{l=1}^{n-1}\Big[f_{n-1-2l}(\lambda)-f_{n-2l}(\lambda)\Big],\\
+f_n(\lambda)=\log\Big(\lambda^2+\frac{n^2}{4}\Big),\\
+n_\infty=1-2\sum_{m=1}^\infty m\int_{-\infty}^\infty d\lambda\rho_m(\lambda). 
+\end{eqnarray}
+%
+Note that~\eref{neel-ov-th} is extensive, subextensive contributions 
+are neglected. In particular, Eq.~\eref{neel-ov-th} that the ratio of 
+determinants $\det_m(G^+)/\det_m(G^-)$ does not contribute.
 
@@
  $-2\log|\langle\lambda|N\rangle|\sim 0.5$ in the thermodynamic 
- limit {\bf really??}. 
+ limit {\bf really??}. The dotted vertical line is the expected 
+ Quench-Action result in the thermodynamic limit.  
 }
@@
 
+\bibitem{bethe-1931}
+H.~Bethe, Zur Theorie der Metalle. I. Eigenwerte und Eigenfunktionen 
+der linearen Atomkette, Z.\ Phys.\ {\bf 71}, 205 (1931).
+
+\bibitem{taka-book}
+M.~Takahashi, {\it Thermodynamics of one-dimensional solvable models}, 
+Cambridge University Press, Cambridge, 1999.
+
 \end{thebibliography}

### 2015-09-13 draft/fs_qa_v1.tex
rev 13/09/2015

@@
 Here we review some Bethe ansatz results for the spin-$\frac{1}{2}$ Heisenberg 
-($XXX$) chain. Specifically, in
+($XXX$) chain. Specifically, in section~\ref{sec:1.1} we introduce the model. 
+Its eigenstates (Bethe states) and the Bethe equations are discussed in 
+section~\ref{sec:1.2}. Section~\ref{sec:1.3} focuses on the string hypothesis 
+and the so-called Bethe-Gaudin-Takahashi (BGT) equations. The form of the 
+BGT equations in the thermodynamic limit is discussed in section~\ref{sec:1.4}. 
+Finally, in section~\ref{sec:1.5} we provide some exact formulas for the 
+local conserved charges of the model.
 
@@
 \begin{equation}
-\label{ba_ener}
+\label{ba-ener}
 E=\sum\limits_{\alpha=1}^M(\cos(k_\alpha)-1). 
@@
 respectively.
+
+Finally, one should remark that $M$-particle eigenstates corresponding to 
+{\it finite} rapidities are eigenstates with maximum allowed magnetization 
+(highest-weight eigenstates) $S_T^z=L/2-M=S_T$, with $S_T$ the total spin. 
+Due to the $SU(2)$ invariance of~\eref{xxx-ham}, all the states in the same 
+$S_T$ multiplet and different $-S_T\le S_T^z\le S_T$ are eigenstates of the 
+$XXX$ chain with the same energy eigenvalue. These eigenstates (descendants) 
+are obtained by multiple applications of the total-spin lowering operator 
+$S_T^-\equiv\sum_iS_i^-$ on the highest-weight eigenstates. In the Bethe ansatz 
+framework the rapidities of a generic $M$-particle descendant eigenstate with 
+$S_T^T=L/2-M'$, with $M'<M$, are obtained by supplementing the $M$ rapidities 
+of the highest-weight state with $M'-M$  infinite rapidities. We anticipate 
+that descendant eigenstates have non-zero overlap with the zero-momentum 
+N\'eel state (cf. section~\ref{sec:2}).
 
@@
 integers and half-integers for $L-s_n$ odd and even, respectively. 
-
-The upper bound for the Bethe-Takahashi quantum numbers 
-can be derived as   
+An upper bound for the BGT quantum numbers can be derived as~\cite{taka-book} 
 %
@@
 %
-where $t_{m,n}\equiv 2\mbox{min}(n,m)-\delta_{m,n}$.
-
-In the thermodynamic limit the BGT equations become a set of coupled integral 
-equations given as 
+where $t_{m,n}\equiv 2\mbox{min}(n,m)-\delta_{m,n}$. Using the string hypothesis 
+Bethe states energy eigenvalue~\eref{ba-ener} becomes
+%
+\begin{equation}
+\label{ener-str}
+E=-\sum_{n,\gamma}\frac{2n}{\lambda_{n;\gamma}^2+n^2}. 
+\end{equation}
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Thermodynamic limit}
+\label{sec:1.4}
+
+In the thermodynamic limit $L\to\infty$ at fixed finite particle density $M/L$ 
+the solutions of the BGT equations~\eref{bgt-eq} become dense. One then defines 
+the BGT root distributions for the $n$-strings as $\pmb{\rho}\equiv\{\rho_n(
+\lambda)\}_{n=1}^\infty$, with $\rho_n(\lambda)\equiv\lim_{L\to\infty}[
+\lambda_{n;\gamma+1}-\lambda_{n;\gamma}]^{-1}$. Thus the  BGT 
+equations~\eref{bgt-eq} become an infinite set of coupled non-linear integral 
+equations for the $\rho_n(\lambda)$ as 
 %
@@
 %
-where 
+where $\rho_n^{h}$ are the hole-distributions, and the functions $a_n(\lambda)$ 
+are defined as 
+%
+\begin{equation}
+a_n(x)\equiv\frac{1}{\pi}\frac{n}{x^2+n^2}. 
+\end{equation}
+%
+In~\eref{bgt-th} $T_{n,m}*\rho_m$ denotes the convolution 
 %
@@
 (T_{n,m}*\rho_m)(\lambda)\equiv\int_{-\infty}^{+\infty}T_{n,m}(\lambda-\lambda')
-\rho_{m}(\lambda'). 
-\end{equation}
-%
-The matrix $T_{n,m}(x)\equiv\Theta'(x)$ is given as 
+\rho_{m}(\lambda'),
+\end{equation}
+%
+with the matrix $T_{n,m}(x)\equiv\Theta'(x)$ being dfined as 
 %
@@
 %
-with 
-%
-\begin{equation}
-a_n(x)\equiv\frac{1}{\pi}\frac{n}{x^2+n^2}. 
-\end{equation}
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The conserved charges}
-
-The $XXX$ chain exhibits an extensive number of local conserved charges $Q_n$. 
-These are defined as 
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The conserved charges}
+\label{sec:1.5}
+
+The $XXX$ chain exhibits an extensive number of mutually commuting local conserved 
+charges $Q_n$, with $n\in\mathbb{N}$, i.e., 
+%
+\begin{equation}
+[Q_n,{\mathcal H}]=0\quad\forall n\quad\textrm{and}\quad [Q_n,Q_m]=0\quad\forall n,m.
+\end{equation}
+%
+The eigenvalues $q_n$ of the conserved charges over the Bethe eigenstates 
+(cf.~\eref{ba-eig}) are given as 
 %
@@
 \label{Q-def}
-\left.Q_{j+1}\equiv\frac{i}{(j-1)!}\frac{d^j}{dy^j}\log\tau
+\left.q_{n+1}\equiv\frac{i}{(n-1)!}\frac{d^n}{dy^n}\log\tau
 (y)\right|_{y=i},
@@
 %
-where $y$ is a spectral parameter and $\tau(y)$ is the eigenvalue of the 
-so-called transfer matrix in the Algebraic Bethe Ansatz framework. The 
-analytic expression of $\tau(y)$ for a given eigenstate identified by 
-a set of rapidities $\{\lambda_\alpha\}$ is given as 
+where $y$ is a spectral parameter and $\tau(y)$ is the Bethe state eigenvalue of the 
+so-called transfer matrix in the Algebraic Bethe Ansatz framework~\cite{kor-book}. 
+The analytic expression for $\tau(y)$ in terms of the solutions 
+$\{\lambda_\alpha\}_{\alpha=1}^M$ of the Bethe equations~\eref{ba-eq} is given as 
 %
@@
 %
-Using the string hypothesis and~\eref{Q-def} and~\eref{tau}, one obtains tha for 
-a generic $n$-string with string center $\lambda$ the first few charges have the 
-simple expressions
+Interestingly, from~\eref{Q-def} one has that the second term in~\eref{tau} does not 
+contribute to $q_n$, at least for $n\le L-2$. 
+For a generic Bethe state $q_n$ is obtained by summing independently the contributions 
+of the BGT roots as 
+%
+\begin{equation}
+\label{qngnk}
+q_n=\sum_{k,\gamma}g_{n,k}(\lambda_{k;\gamma}).
+\end{equation}
+%
+Using the string hypothesis~\eref{str-hyp}, and~\eref{Q-def},~\eref{tau}, one obtains  
+the the first few functions $g_{n,k}$ in terms of the solutions of the BGT equations as 
 %
 \begin{eqnarray}
-Q_2=-\frac{2n}{\lambda^2+n^2}\\
-Q_3=-\frac{4n\lambda}{(\lambda^2+n^2)^2}\\
-Q_4=\frac{2n(n^2-3\lambda^2)}{(n^2+\lambda^2)^3}\\
-Q_5=\frac{8n\lambda(n^2-\lambda^2)}{(n^2+\lambda^2)^4}\\
-Q_6=-\frac{2n(5\lambda^4-10n^2\lambda^2+n^4)}{(n^2+\lambda^2)^5}
+\label{gnk}
+g_{3,k}=-\frac{4k\lambda_{k;\gamma}}{(\lambda_{k;\gamma}^2+k^2)^2}, &\quad  
+g_{4,k}=\frac{2k(k^2-3\lambda_{k;\gamma}^2)}{(k^2+\lambda_{k;\gamma}^2)^3}\\\nonumber 
+g_{5,k}=\frac{8k\lambda_{k;\gamma}(k^2-\lambda_{k;\gamma}^2)}{(k^2+
+\lambda_{k;\gamma}^2)^4}, & \quad
+g_{6,k}=-\frac{2k(5\lambda_{k;\gamma}^4-10k^2\lambda_{k;\gamma}^2+k^4)}{(k^2+
+\lambda_{k;\gamma}^2)^5}. 
 \end{eqnarray}
 %
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{N\'eel expectation values}
-\label{Q-Neel}
-
-The expectation values of the $XXX$ chain conserved charges over the N\'eel 
-state are given as
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overlap with the Neel state}
-
-Here we focus on the overlap with the zero-momentum N\'eel state $|N\rangle$, 
+Note that $q_2$ is the Bethe state energy eigenvalue and is given in~\eref{ener-str}. 
+It is also interesting to observe that $g_{n,k}$ (cf.~\eref{gnk}) is vanishing for 
+infinite BGT roots. This is expected to hold for the generic $g_{n,k}$, i.e., for any 
+$n$, and it is a consequence of the $SU(2)$ invariance of the conserved charges. Finally, 
+in the thermodynamic limit $L\to\infty$ from~\eref{qngnk} one has 
+%
+\begin{equation}
+q_n\to\sum_{k=1}^\infty\int_{-\infty}^{+\infty}d\lambda\rho_k(\lambda)g_{n,k}(\lambda), 
+\end{equation}
+%
+where the BGT root distributions $\rho_k(\lambda)$ are solutions of~\eref{bgt-th}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Overlap between the Bethe states and some initial states} 
+\label{sec:2}
+
+Here we detail the Bethe ansatz results for the overlap of the Bethe states (cf.~\eref{ba-eig}) 
+with the zero-momentum (one-site shift invariant) N\'eel state $|N\rangle$ and the 
+Majumdar-Ghosh (MG) $|MG\rangle$ state. We stard discussing the N\'eel state. This is 
 defined as 
@@
 \label{neel}
-|N\rangle\equiv\frac{1}{\sqrt{2}}\Big(|\uparrow\downarrow\rangle^{\otimes L/2}
-+|\downarrow\uparrow\rangle^{\otimes L/2}\Big).
-\end{equation}
-%
-Here we restrict to the parity-invariant eigenstates. These are the only 
-eigenstates with non-zero overlap with the Neel state. Parity-invariant 
-eigenstates contain only pairs of rapidities with opposite sign.
-
-We denote the generic parity invariant eigenstate as $|\{\pm\lambda_j\}_{j=1}^m,
-n_\infty\rangle$, where $m$ is the number of rapidity pairs, $N_{\infty}$ is the 
-number of infinite rapidities, with $M=L/2=N_\infty+2m$, and $n_\infty\equiv 
-N_\infty/L$ is the density of infinite rapidities.
-
-The overlap with the Neel state $|N\rangle$ reads 
+|N\rangle\equiv\frac{1}{\sqrt{2}}\big(|N_1\rangle
++|N_2\rangle\big), 
+\end{equation}
+%
+with $|N_1\rangle\equiv |\uparrow\downarrow\rangle^{\otimes L/2}$, and $|N_2\rangle\equiv 
+|\downarrow\uparrow\rangle^{\otimes L/2}$. Note that $|N_1\rangle=\hat T|N_2\rangle$, 
+with $\hat T$ the one-site shift operator.
+
+Due to the zero-momentum constraint, only parity-invariant Bethe states can have non-zero 
+N\'eel overlap~\cite{brockmann-2014}. Parity-invariant Bethe states contain only pairs of 
+solutions of the Bethe equations~\eref{ba-eq} with opposite sign.  Here we denote the generic 
+parity-invariant rapidity configuration as $|\{\pm\tilde\lambda_\alpha\}_{\alpha=1}^m,n_\infty
+\rangle$, i.e., considering only positive rapidities. Here $m$ is the number of rapidity pairs. 
+Since the N\'eel state is not invariant under $SU(2)$ rotations, eigenstates with 
+infinite rapidities can have non-zero N\'eel overlaps.
+Here the number of infinite rapidities is denoted as $N_{\infty}$. Note that one has $M=L/2=
+N_\infty+2m$. We denote as $n_\infty\equiv N_\infty/L$ the density of infinite rapidities. 
+Finally, the overlap between the Bethe states and the Neel state $|N\rangle$ 
+reads~\cite{brockmann-2014,pozsgay-2014} 
 %
@@
 \label{neel-ov}
-\frac{\langle N|\{\pm\lambda_j\}_{j=1}^m,n_\infty\rangle}{|||\{\lambda_j\}_{j=1}^m,
+\frac{\langle N|\{\pm\tilde\lambda_j\}_{j=1}^m,n_\infty\rangle}{|||\{\tilde\lambda_j\}_{j=1}^m,
 n_\infty\rangle||}=\frac{\sqrt{2}N_{\infty}!}{\sqrt{(2N_\infty)!}}\left[\prod_{j=1}^m
-\frac{\sqrt{\lambda_j^2+1}}{4\lambda_j}\right]\sqrt{\frac{\textrm{det}_m(G^+)}{
-\textrm{det}_m(G^-)}}
+\frac{\sqrt{\tilde\lambda_j^2+1}}{4\tilde\lambda_j}\right]\sqrt{\frac{\textrm{det}_m(G^+)}{
+\textrm{det}_m(G^-)}}.
+\end{equation}
+%
+The matrix $G^\pm$ is  defined as  
+%
+\begin{equation}
+\label{G-pm}
+\fl\quad G^{\pm}_{jk}=\delta_{jk}\Big(LK_{1/2}(\tilde\lambda_j)-\sum\limits_{l=1}^mK_1^+(
+\tilde\lambda_j,\tilde\lambda_l)\Big)+K_{1}^{\pm}(\tilde\lambda_j,\tilde\lambda_k),
+\quad\,j,k=1,\dots,m, 
 \end{equation}
@@
 \begin{equation}
-\label{G-pm}
-G^{\pm}_{jk}=\delta_{jk}\Big(NK_{1/2}(\lambda_j)-\sum\limits_{l=1}^mK_1^+(\lambda_j,
-\lambda_l)\Big)+K_{1}^{\pm}(\lambda_j,\lambda_k),\quad\,j,k=1,\dots,m
-\end{equation}
-%
-and 
-%
-\begin{equation}
-\label{K-1}
-K_1^\pm(\lambda,\mu)=K_1(\lambda-\mu)\pm K_1(\lambda+\mu)
-\end{equation}
-%
-and 
-%
-\begin{equation}
-\label{K-alpha}
-K_\alpha(\lambda)\equiv\frac{8\alpha}{\lambda^2+4\alpha^2}
-\end{equation}
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Reduced Neel overlap}
+\label{K}
+K_1^\pm(\lambda,\mu)=K_1(\lambda-\mu)\pm K_1(\lambda+\mu) \quad\textrm{with}\quad 
+K_\alpha(\lambda)\equiv\frac{8\alpha}{\lambda^2+4\alpha^2}. 
+\end{equation}
+%
+Note that our definitions of $K_{\alpha}(\lambda)$ differs from the one in 
+Ref.~\cite{brockmann-2014}, due to a factor $2$ in the definition of the 
+rapidities (see also~\eref{str-hyp}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The string hypothesis: Reduced overlap formulas}
 
 Here we consider the overlap formula for the Neel state~\eref{neel-ov} in the 
-limit $L\to\infty$, assuming that the rapidities form perfect strings.
-
-In the case of perfect strings the matrices $G^{\pm}_{jk}$ become ill-defined. 
-Precisely, $K_{1}^\pm(\lambda,\mu)$ diverges if $\lambda$ and $\mu$ are successive 
-members of the same string, i.e., $|\lambda-\mu|=2i$.
-
-It is possible to rewrite~\eref{neel-ov} in terms of the string centers 
-$\lambda_{n;\alpha}$ only. Here we restrict ourselves to rapidity configurations 
-with no zero-momentum strings. Our results are not valid for zero-rapidity 
-strings. These would require the knowledge of the precise form of the string 
-deviations, i.e., the dependence of the string deviations on $L$, as it has 
-been pointed out in Ref.~\cite{calabrese-2014}.
-
-It is convenient to split the indices $i,j$ of $G^\pm_{ij}$ as $i=(n,\alpha)$ 
-$j=(m,\beta)$, with $n,m$ being the length of the strings and $\alpha,\beta$ 
-labelling the string centers.
+limit $L\to\infty$, assuming that the rapidities form perfect strings, i.e., 
+$\delta_{n;\gamma}^j=0$ in~\eref{str-hyp}.  
+Then it is possible to rewrite~\eref{neel-ov} in terms of the string centers 
+$\tilde\lambda_{n;\alpha}$ only. Here we restrict ourselves to rapidity 
+configurations with no zero-momentum strings. Our results are not valid for 
+zero-rapidity strings.
+
+It is convenient to first split the indices $i,j$ of $G^\pm_{ij}$ as $i=(n,\gamma,i)$ 
+and $j=(m,\gamma',j)$, with $n,m$ being the length of the strings, $\gamma,\gamma'$ 
+labelling the corresponding string centers, and $i,j$ the components of the 
+two strings. 
+Using~\eref{G-pm} and~\eref{K}, one has that for two consecutive rapidities in the same 
+string, i.e., for $m=n,\gamma=\gamma',|i-j|=2$, the matrices $G^{\pm}_{jk}$ become 
+ill-defined in the thermodynamic limit. Precisely, since $K_{1}(\tilde\lambda_{n;\gamma}^i-
+\tilde\lambda_{n;\gamma}^{i+1})\sim 1/(\delta_{n;\gamma}^i-\delta_{n;\gamma}^{i+1})$, 
+$G_{ij}^\pm$ diverges in the thermodynamic limit. Importantly, as the same type of 
+divergence occur in both $G^+$ and $G^-$, their ratio (cf.~\eref{neel-ov}), and 
+the overlaps, are finite.
 
@@
 %
+
+These would require the knowledge of the precise form of the string 
+deviations, i.e., the dependence of the string deviations on $L$, as it has 
+been pointed out in Ref.~\cite{calabrese-2014}.
+
 Finally, the multiplicative prefactor in~\eref{neel-ov} for the generic $n$-string 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Validity of the string hypothesis for overlap calculations}
-\label{string-ov}
-
-Here we discuss the validity of the string hypothesis when calculating the 
-overlaps between the eigenstates of the $XXX$ chain and the N\'eel state. 
-Here we focus on the Heisenberg chain with $L=20$ sites. 
-Figure~\ref{fig1-BGT-check} plots the squared overlaps $|\langle\lambda|
-N\rangle|^2$ between the N\'eel state and the eigenstates of the chain. 
-The overlaps are plotted against the eigenstate energy density $E/L
-\in[-\log(2),0]$. The circles are exact diagonalization results for all 
-the chain eigenstates ($382$ eigenstates), whereas the crosses denote the 
-overlaps calculated using formula~\eref{neel-ov}, and the 
-Bethe-Gaudin-Takahashi equations. Note that only the eigenstates with 
-no zero-momentum strings are shown ($252$ eigenstates) in the Figure. 
-Panel (a) in the Figure is an overview of all the results. Panels (b)-(d) 
-correspond to zooming to the smaller overlap values $|\langle N|\lambda
-\rangle|\lesssim 0.02$, $|\langle N|\lambda\rangle|\lesssim 0.002$, and 
-$|\langle N|\lambda\rangle|\lesssim 10^{-5}$.
-
-Clearly, the overlaps decay rapidly upon increasing the energy density. 
-This is expected since the $XXX$ Hamiltonian expectation value over 
-the N\'eel state is $\langle N|{H}|N\rangle=-1/2$. Importantly, the 
-agreement between the exact diagonalization results and the results 
-obtained using the BGT equations~\eref{ba_eq} is excellent, confirming 
-the validity of the string hypothesis.
-
-%##################################################################
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=.9\textwidth]{./draft_figs/L20_BT_check}
-\end{center}
-\caption{ The squared overlap $|\langle N|\lambda\rangle|^2$ between the the 
- Neel state $|N\rangle$ and the eigenstates $|\lambda\rangle$ of the $XXX$ 
- chain with $L=20$ sites. Only non-zero overlaps are shown. In all the panels the 
- $x$-axis shows the eigenstate energy density $E/L$. The circles are the exact 
- diagonalization results for all the non-zero overlaps. The crosses are the Bethe 
- ansatz results obtained using the Bethe-Gaudin-Takahashi equations. The missing 
- crosses correspond to eigenstates containing zero-momentum strings. (a) Overview 
- of all the non-zero overlaps. (b)(c)(d) The same overlaps as in (a) zooming in 
- the regions $[0,0.2]$, $[0,0.020]$, and $[0,4\cdot 10^{-5}]$. The discrepancies 
- between the ED and the Bethe ansatz results are attributed to the string 
- deviations. 
-}
-\label{fig1-BGT-check}
-\end{figure}
-%##################################################################
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Monte Carlo implementation of the Quench-Action approach}
@@
 analytically as $2/B(L,L/2)$, with $B(x,y)$ the Newton binomial.
+
+Figure~\ref{fig1-BGT-check} plots the squared overlaps $|\langle\lambda|
+N\rangle|^2$ between the N\'eel state and the eigenstates of the chain. 
+The overlaps are plotted against the eigenstate energy density $E/L
+\in[-\log(2),0]$. The circles are exact diagonalization results for all 
+the chain eigenstates ($382$ eigenstates), whereas the crosses denote the 
+overlaps calculated using formula~\eref{neel-ov}, and the 
+Bethe-Gaudin-Takahashi equations. Note that only the eigenstates with 
+no zero-momentum strings are shown ($252$ eigenstates) in the Figure. 
+Panel (a) in the Figure is an overview of all the results. Panels (b)-(d) 
+correspond to zooming to the smaller overlap values $|\langle N|\lambda
+\rangle|\lesssim 0.02$, $|\langle N|\lambda\rangle|\lesssim 0.002$, and 
+$|\langle N|\lambda\rangle|\lesssim 10^{-5}$.
+
+Clearly, the overlaps decay rapidly upon increasing the energy density. 
+This is expected since the $XXX$ Hamiltonian expectation value over 
+the N\'eel state is $\langle N|{H}|N\rangle=-1/2$. Importantly, the 
+agreement between the exact diagonalization results and the results 
+obtained using the BGT equations~\eref{ba_eq} is excellent, confirming 
+the validity of the string hypothesis.
 
@@
 
+%##################################################################
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=.9\textwidth]{./draft_figs/L20_BT_check}
+\end{center}
+\caption{ The squared overlap $|\langle N|\lambda\rangle|^2$ between the the 
+ Neel state $|N\rangle$ and the eigenstates $|\lambda\rangle$ of the $XXX$ 
+ chain with $L=20$ sites. Only non-zero overlaps are shown. In all the panels the 
+ $x$-axis shows the eigenstate energy density $E/L$. The circles are the exact 
+ diagonalization results for all the non-zero overlaps. The crosses are the Bethe 
+ ansatz results obtained using the Bethe-Gaudin-Takahashi equations. The missing 
+ crosses correspond to eigenstates containing zero-momentum strings. (a) Overview 
+ of all the non-zero overlaps. (b)(c)(d) The same overlaps as in (a) zooming in 
+ the regions $[0,0.2]$, $[0,0.020]$, and $[0,4\cdot 10^{-5}]$. The discrepancies 
+ between the ED and the Bethe ansatz results are attributed to the string 
+ deviations. 
+}
+\label{fig1-BGT-check}
+\end{figure}
+%##################################################################
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\bibitem{kor-book}
+V.~E.~Korepin, N.~M.~Bogoliubov, and A.~G.~Izergin, \emph{Quantum
+Inverse Scattering Methods and Correlation Functions}, Cambridge
+University Press, Cambridge, 1997.
+
+\bibitem{brockmann-2014}
+M.~Brockmann, J.~De~Nardis, B.~Wouters, and J.-S.~Caux, J.\ Phys.\ A:\ 
+Math.\ Theor. {\bf 47}, 345003 (2014).
+
+\bibitem{pozsgay-2014}
+B.~Pozsgay, J.\ Stat.\ Mech.\ (2014) P06011.
+
+\bibitem{calabrese-2007}
+P.~Calabrese and J.-S.~Caux, Phys.\ Rev.\ Lett.\ {\bf 98}, 150403 (2007).
+
+\bibitem{calabrese-2007-a}
+P.~Calabrese and J.-S.~Caux, J.\ Stat.\ Mech.\ P08032 (2007).
+
+\bibitem{de-nardis-2014}
+J.~De Nardis, B.~Wouters, M.~Brockmann, and J.-S.~Caux, Phys.\ Rev.\ A {\bf 89}, 
+033601 (2014).
+
+\bibitem{pozsgay-2014}
+B.~Pozsgay, M.~Mesty\'an, M.~A.~Werner, M.~Kormos, G.~Zar\'and, and G.~Tak\'acs,
+Phys.\ Rev.\ Lett.\ {\bf 113}, 117203 (2014).
+
+\bibitem{wouters-2014}
+B.~Wouters, M.~Brockmann, J.~De~Nardis, D.~Fioretto, M.~Rigol, and J.-S.~Caux, 
+Phys.\ Rev.\ Lett.\ {\bf 113}, 117202 (2014).
+
+\bibitem{mestyian-2015}
+M~Mesty\'an, B.~Pozsgay, G.~Tak\'acs, and M.~A.~Werner, J.\ Stat.\ Mech.\ (2015) 
+P04001.
+
+\bibitem{ilievski-2015a}
+E.~Ilieveski, J.~De~Nardis, B.~Wouters, J.-S.~Caux, F.~H.~Essler, and T.~Prosen, 
+arXiv:1507.02993.
+
+\bibitem{brockmann-2014a}
+M.~Brockmann, B.~Wouters, D.~Fioretto, J.~De Nardis, R.~Vlijm, and J.-S.~Caux, 
+J.\ Stat.\ Mech.\ (2014) P12009.
+
 \end{thebibliography}

### 2015-09-14 draft/fs_qa_v1.tex
rev 14/09/2015

@@
 \begin{eqnarray}
+\label{Theta}
 \nonumber\fl\Theta_{m,n}(x)\equiv\left\{\begin{array}{cc}
@@
 $\tilde\lambda_{n;\alpha}$ only. Here we restrict ourselves to rapidity 
-configurations with no zero-momentum strings. Our results are not valid for 
-zero-rapidity strings.
+configurations with no zero-momentum strings, i.e., with finite string 
+centers. Our results are not valid for zero-momentum strings.
+
+First, we restrict ourselves to parity-invariant string configurations, 
+i.e., considering only strings having positve string centers. We denote the 
+generic parity-invariant string configuration as $\{\tilde\lambda_{n;
+\gamma}\}$, where $\gamma$ labels the different non-zero string centers, and 
+$n$ is the string length.
 
@@
 two strings.
+
 Using~\eref{G-pm} and~\eref{K}, one has that for two consecutive rapidities in the same 
@@
 
-The result reads 
-%
-\begin{equation}
-\fl \frac{1}{2}G^+_{(n,\alpha)(m,\beta)}=\left\{\begin{array}{cc}
-L\theta_n'(\lambda_{n;\alpha}) -\sum\limits_{(\ell,\gamma)\ne(n,\alpha)}\Big[\Theta'_{n,\ell}
-(\lambda_{n;\alpha}-\lambda_{\ell;\gamma}) & \quad\textrm{if}\,(n,\alpha)=(m,\beta) \\
-+\Theta'_{n,\ell}(\lambda_{n;\alpha}+\lambda_{\ell;\gamma})\Big] & \\ \\
+The finite part of the overlaps~\eref{neel-ov} can be calculated using the same strategy 
+as in Ref.~\cite{calabrese-2007,calabrese-2007-a} (see also Ref.~\cite{brockmann-2014}). 
+The resulting matrix $G^+$ depends only on the ``string center'' indices $(n,\gamma)$ 
+and $(m,\gamma')$ and it is given as  
+%
+\begin{equation}
+\fl \frac{1}{2}G^+_{(n,\gamma)(m,\gamma')}=\left\{\begin{array}{cc}
+L\theta_n'(\tilde\lambda_{n;\gamma}) -\sum\limits_{(\ell,\alpha)\ne(n,\gamma)}\Big[\Theta'_{n,\ell}
+(\tilde\lambda_{n;\gamma}-\tilde\lambda_{\ell;\alpha}) & \quad\textrm{if}\,(n,\gamma)=(m,\gamma') \\
++\Theta'_{n,\ell}(\tilde\lambda_{n;\gamma}+\tilde\lambda_{\ell;\alpha})\Big] & \\ \\
 \Theta'_{n,m}
-(\lambda_{n;\alpha}-\lambda_{m;\beta})+\Theta'_{n,m}
-(\lambda_{n;\alpha}+\lambda_{m;\beta}) & \quad\textrm{if}\,(n,\alpha)\ne(m,\beta)
+(\tilde\lambda_{n;\gamma}-\tilde\lambda_{m;\gamma'})+\Theta'_{n,m}
+(\tilde\lambda_{n;\gamma}+\tilde\lambda_{m;\gamma'}) & \quad\textrm{if}\,(n,\gamma)\ne(m,\gamma')
 \end{array}\right.
@@
 %
-Here $\theta_n'(x)\equiv d\theta_n(x)/dx=2n/(n^2+x^2)$ and $\Theta'(x)\equiv d\Theta(x)/dx$.
-
-For $G^-_{ij}$ one obtains
-
-\begin{equation}
-\fl\frac{1}{2}G^-_{(n,\alpha)(m,\beta)}=\left\{\begin{array}{cc}
-\fl(L-1)\theta'_n(\lambda_{n;\alpha})-2\sum\limits_{k=1}^{n-1}\theta'_k(\lambda_{n;\alpha})
-& \textrm{if}\,(n,\alpha)= (m,\beta)\\
--\hspace{-.5cm}\sum\limits_{(\ell,\gamma)\ne(n,\alpha)}\Big[\Theta'_{n,\ell}
-(\lambda_{n;\alpha}-\lambda_{\ell;\gamma})+\Theta'_{n,\ell}
-(\lambda_{n;\alpha}+\lambda_{\ell;\gamma})\Big] \\\\
+Here $\theta_n'(x)\equiv d\theta_n(x)/dx=2n/(n^2+x^2)$ and $\Theta'(x)\equiv d\Theta(x)/dx$, 
+with $\Theta(x)$ as defined in~\eref{Theta}. 
+Similarly, for $G^-$ one obtains 
+%
+\begin{equation}
+\fl\frac{1}{2}G^-_{(n,\gamma)(m,\gamma')}=\left\{\begin{array}{cc}
+\fl(L-1)\theta'_n(\tilde\lambda_{n;\gamma})-2\sum\limits_{k=1}^{n-1}\theta'_k(
+\tilde\lambda_{n;\gamma})
+& \textrm{if}\,(n,\gamma)= (m,\gamma')\\
+-\hspace{-.5cm}\sum\limits_{(\ell,\alpha)\ne(n,\gamma)}\Big[\Theta'_{n,\ell}
+(\tilde\lambda_{n;\gamma}-\tilde\lambda_{\ell;\alpha})+\Theta'_{n,\ell}
+(\tilde\lambda_{n;\gamma}+\tilde\lambda_{\ell;\alpha})\Big] \\\\
 \Theta'_{n,m}
-(\lambda_{n;\alpha}-\lambda_{m;\beta})-\Theta'_{n,m}
-(\lambda_{n;\alpha}+\lambda_{m;\beta})) & \textrm{if}\,(n,\alpha)\ne(m,\beta)
+(\tilde\lambda_{n;\gamma}-\tilde\lambda_{m;\gamma'})-\Theta'_{n,m}
+(\tilde\lambda_{n;\gamma'}+\tilde\lambda_{m;\gamma'})) & \textrm{if}\,(n,\gamma)\ne(m,\gamma')
 \end{array}\right.
@@
 %
-
-These would require the knowledge of the precise form of the string 
-deviations, i.e., the dependence of the string deviations on $L$, as it has 
-been pointed out in Ref.~\cite{calabrese-2014}.
-
-Finally, the multiplicative prefactor in~\eref{neel-ov} for the generic $n$-string 
-can be rewritten as 
-%
-\begin{equation}
-\prod\limits_{a=1}^n\frac{\sqrt{(\lambda^a_{n;\alpha})^2+1}}{4\lambda^a_{n;\alpha}}=
-\frac{1}{4^n}\left(\frac{\sqrt{n^2+\lambda^2_{n;\alpha}}}{\lambda_{n;\alpha}}
-\prod\limits_{k=0}^{\lceil n/2\rceil-1}\frac{(2k)^2+\lambda^2_{n;\alpha}}{(2k+1)^2+
-\lambda^2_{n;\alpha}}\right)^{{\mathcal P}},
-\end{equation}
-%
-with ${\mathcal P}=+$ and ${\mathcal P}=-$ for even and odd strings, respectively.
+Note that in presence of zero-momentum strings, additional divergences as $1/(\delta_{n;
+\gamma}^{i}+\delta_{n;\gamma}^{i+1})$ appear due to the term $K_1(\lambda+\mu)$ 
+(cf.~\eref{K}). It turns out that the treatment of these diverges is a challenging 
+task because it requires the precise knowledge of the string deviations, meaning 
+their dependence on $L$, for each different type of string. Some results have been 
+provided for small strings in Ref.~\cite{calabrese-2014}.
+
+Finally, using the string hypothesis and the parity-invariance condition, the multiplicative 
+prefactor in~\eref{neel-ov} can be simplified. Here we focus on a generic eigenstate of 
+the $XXX$ identified by $m$ pairs of finite rapidities. 
+Note that due to parity invariance and the exclusion of zero-momentum strings, only 
+strings of length up to $m$ are allowed. The ``reduced'' string content 
+identifying the eigenstate is denoted as $\widetilde{\mathcal S}=\{\tilde s_1,\dots,\tilde s_{m}\}$, 
+with $\tilde s_n$ the number of parity-invariant pairs of $n$-strings. Using the string 
+hypothesis and~\eref{neel-ov}, one can write 
+%
+\begin{equation}
+\fl\quad\prod\limits_{j=1}^m\frac{\sqrt{\tilde\lambda_j^2+1}}{4\tilde\lambda_j}=
+\frac{1}{4^m}\prod\limits_{j=1}^m\prod\limits_{\ell=1}^{\tilde s_j}\left[\frac{\sqrt{j^2+
+\lambda^2_{j;\ell}}}{\lambda_{j;\ell}}
+\prod\limits_{k=0}^{\lceil j/2\rceil-1}\frac{(2k)^2+\lambda^2_{j;\ell}}{(2k+1)^2+
+\lambda^2_{j;\ell}}\right]^{(-1)^j}.
+\end{equation}
+%
 
@@
 
-In the thermodynamic limit the expression for the overlap~\eref{neel-ov} becomes 
+In the thermodynamic limit $L\to\infty$ the expression for the extensive part of the 
+overlap~\eref{neel-ov} can be written as~\cite{brockmann-2014} 
 %
@@
 \label{neel-ov-th}
-\fl\lim_{L\to\infty}\left[\frac{\langle N|\{\pm\lambda_j\}_{j=1}^m,n_\infty
+\fl-\lim_{L\to\infty}\log\left[\frac{\langle N|\{\pm\lambda_j\}_{j=1}^m,n_\infty
 \rangle}{|||\{\lambda_j\}_{j=1}^m,n_\infty\rangle||}\right]=\frac{L}{2}\Big(
-n_\infty\log(2)+\sum_{n=1}^\infty\int_0^\infty d\lambda\rho_n(\lambda)[g_n(\lambda)
+n_\infty\log2+\sum_{n=1}^\infty\int_0^\infty d\lambda\rho_n(\lambda)[g_n(\lambda)
 +2n\log(4)]\Big), 
@@
 %
-with 
-%
-\begin{eqnarray}
-g_n(\lambda)=\sum_{l=1}^{n-1}\Big[f_{n-1-2l}(\lambda)-f_{n-2l}(\lambda)\Big],\\
-f_n(\lambda)=\log\Big(\lambda^2+\frac{n^2}{4}\Big),\\
+where  
+%
+\begin{equation}
+\fl\quad g_n(\lambda)=\sum_{l=1}^{n-1}\Big[f_{n-1-2l}(\lambda)-f_{n-2l}(\lambda)\Big],\quad
+\textrm{with}\quad f_n(\lambda)=\log\Big(\lambda^2+\frac{n^2}{4}\Big),
+\end{equation}
+and
+\begin{equation}
 n_\infty=1-2\sum_{m=1}^\infty m\int_{-\infty}^\infty d\lambda\rho_m(\lambda). 
-\end{eqnarray}
-%
-Note that~\eref{neel-ov-th} is extensive, subextensive contributions 
-are neglected. In particular, Eq.~\eref{neel-ov-th} that the ratio of 
-determinants $\det_m(G^+)/\det_m(G^-)$ does not contribute.
+\end{equation}
+%
+Note that~\eref{neel-ov-th} is extensive. Specifically, in Eq.~\eref{neel-ov-th} 
+subleading (i.e., subextensive) contributions originating from the determinant
+ratio $\det_m(G^+)/\det_m(G^-)$ are neglected.
 
@@
 |MG\rangle\equiv \Big(\frac{|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle}
-{\sqrt{2}}\Big)^{\otimes L/2}
-\end{equation}
-%
-The overlap between the generic eigenstate of the $XXX$ chain and the Majumdar-Ghosh 
-state is obtained fro the overlap with the Neel state as 
+{\sqrt{2}}\Big)^{\otimes L/2}. 
+\end{equation}
+%
+The overlap between a generic eigenstate of the $XXX$ chain and the Majumdar-Ghosh 
+state can be obtained from the N\'eel state overlap in Eq.~\eref{neel-ov} 
+as~\cite{pozsgay-2014} 
 %
@@
 \label{mg-ov}
-\langle MG|\{\lambda_j\}_{j=1}^M\rangle=\prod\limits_{j=1}^M\frac{1}{\sqrt{2}}
-\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)\langle N|\{\lambda_j\}_{j=1}^M\rangle
+\langle MG|\{\pm\lambda_j\}_{j=1}^m\rangle=\prod\limits_{j=1}^m\frac{1}{2}
+\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)
+\Big(1+\frac{\lambda_j+i}{\lambda_j-i}\Big)
+\langle N|\{\pm\lambda_j\}_{j=1}^m\rangle
 \end{equation}

### 2015-09-18 draft/fs_qa_v1.tex
revised 18/09/2015

@@
 
-\title{The Quench-Action method in integrable spin chains: A Monte Carlo 
-approach}
+\title{The quench action approach for integrable models: A Monte Carlo implementation}
 
@@
 {\mathcal H}\equiv J\sum\limits_{i=1}^L\left[\frac{1}{2}(S_i^+S^-_{i+1} 
-+S_i^{-}S_{i+1}^+)+S_i^zS_{i+1}^z\right],  
++S_i^{-}S_{i+1}^+)+S_i^zS_{i+1}^z-\frac{1}{4}\right],  
 \end{equation}
@@
 \limits_{m=1}^Mt_{m,n}s_m),
-\label{bt_qn_bound}
+\label{bt-qn-bound}
 \end{equation}
@@
 %
+For a generic smooth enough observable ${\mathcal O}$ in the thermodynamic 
+limtit its expectation value is expected to become a functional of the root 
+densities $\pmb{\rho}$ as $\langle\pmb{\rho}|{\mathcal O}|\pmb{\rho}\rangle$.
+
+Moreover, for all the local observables considered in this work the contribution of the 
+different type of strings factorize and one can write 
+%
+\begin{equation}
+\langle\pmb{\rho}|{\mathcal O}|\pmb{\rho}\rangle=\sum_{n=1}^\infty
+\int_{-\infty}^{+\infty}d\lambda \rho_n(\lambda) {\mathcal O}_n(\lambda), 
+\end{equation}
+% 
+with ${\mathcal O}_n(\lambda)$ the ... .
 
@@
 \begin{equation}
+\label{q0-th}
 q_n\to\sum_{k=1}^\infty\int_{-\infty}^{+\infty}d\lambda\rho_k(\lambda)g_{n,k}(\lambda), 
@@
 \label{sec:2}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{N\'eel state overlap}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The string hypothesis: Reduced overlap formulas}
+\subsection{The string hypothesis: Reduced N\'eel overlap formulas}
 
@@
 \begin{equation}
+\label{red-G+}
 \fl \frac{1}{2}G^+_{(n,\gamma)(m,\gamma')}=\left\{\begin{array}{cc}
@@
 \begin{equation}
+\label{red-G-}
 \fl\frac{1}{2}G^-_{(n,\gamma)(m,\gamma')}=\left\{\begin{array}{cc}
@@
 \begin{equation}
+\label{neel-k}
 \fl\quad\prod\limits_{j=1}^m\frac{\sqrt{\tilde\lambda_j^2+1}}{4\tilde\lambda_j}=
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Thermodynamic limit}
+\subsection{Overlap with the Majumdar-Ghosh state}
+
+The Majumdar-Ghosh state $|MG\rangle$ is defined as 
+%
+\begin{equation}
+|MG\rangle\equiv \Big(\frac{|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle}
+{\sqrt{2}}\Big)^{\otimes L/2}. 
+\end{equation}
+%
+The overlap between a generic eigenstate of the $XXX$ chain and the Majumdar-Ghosh 
+state can be obtained from the N\'eel state overlap in Eq.~\eref{neel-ov} 
+as~\cite{pozsgay-2014} 
+%
+\begin{equation}
+\label{mg-ov}
+\langle MG|\{\pm\lambda_j\}_{j=1}^m\rangle=\prod\limits_{j=1}^m\frac{1}{2}
+\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)
+\Big(1+\frac{\lambda_j+i}{\lambda_j-i}\Big)
+\langle N|\{\pm\lambda_j\}_{j=1}^m\rangle
+\end{equation}
+%
+The mutliplicative factor in~\eref{mg-ov}, using the string hypothesis is 
+rewritten as 
+%
+\begin{eqnarray}
+\label{mg-k}
+\fl\prod\limits_{j=1}^m\frac{1}{2}
+\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)
+\Big(1+\frac{\lambda_j+i}{\lambda_j-i}\Big)=\\\nonumber\qquad
+2^m\prod\limits_{j=1}^m\prod\limits_{\ell=1}^{\tilde s_j}
+\lambda_{j;\ell}^{1+(-1)^j}(\lambda^2_{j;\ell}+j^2)\prod\limits_{k=0}^{\lfloor 
+j/2\rfloor}\Big[\lambda_{j;\ell}^2+\Big(2k+\frac{1-(-1)^j}{2}\Big)^2\Big]^{-2}
+\end{eqnarray}
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The N\'eel overlap in the thermodynamic limit}
 
@@
 \begin{equation}
-\fl\quad g_n(\lambda)=\sum_{l=1}^{n-1}\Big[f_{n-1-2l}(\lambda)-f_{n-2l}(\lambda)\Big],\quad
-\textrm{with}\quad f_n(\lambda)=\log\Big(\lambda^2+\frac{n^2}{4}\Big),
+\fl\quad g_n(\lambda)=\sum_{l=1}^{n-1}\Big[f_{n-1-2l}(\lambda)-f_{n-2l}(\lambda)
+\Big],\quad\textrm{with}\quad f_n(\lambda)=\log\Big(\lambda^2+\frac{n^2}{4}\Big),
 \end{equation}
@@
 subleading (i.e., subextensive) contributions originating from the determinant
-ratio $\det_m(G^+)/\det_m(G^-)$ are neglected.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overlap with the Majumdar-Ghosh state}
-
-The Majumdar-Ghosh state $|MG\rangle$ is defined as 
-%
-\begin{equation}
-|MG\rangle\equiv \Big(\frac{|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle}
-{\sqrt{2}}\Big)^{\otimes L/2}. 
-\end{equation}
-%
-The overlap between a generic eigenstate of the $XXX$ chain and the Majumdar-Ghosh 
-state can be obtained from the N\'eel state overlap in Eq.~\eref{neel-ov} 
-as~\cite{pozsgay-2014} 
-%
-\begin{equation}
-\label{mg-ov}
-\langle MG|\{\pm\lambda_j\}_{j=1}^m\rangle=\prod\limits_{j=1}^m\frac{1}{2}
-\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)
-\Big(1+\frac{\lambda_j+i}{\lambda_j-i}\Big)
-\langle N|\{\pm\lambda_j\}_{j=1}^m\rangle
-\end{equation}
-%
-The mutliplicative factor in~\eref{ov-MG}, using the string hypothesis for the generic 
-$n$-string is rewritten as 
-%
-\begin{equation}
-\prod\limits_{j=1}^M\frac{1}{\sqrt{2}}
-\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)=2^n\prod\limits_{k=0}^{\lfloor 
-n/2\rfloor}\frac{1}{[\lambda_{n;\gamma}^2+(2k+(1-(-1)^n)/2)^2]^2}
-\end{equation}
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quench Action method}
-\label{quench-action}
-
-For integrable models the Quench-Action approach allows to extract exactly both 
-the steady state after the quench and the relaxation dynamics to the steady state.
-
-In the thermodynamic limit the sum over the model eigenstates is recast into 
-a functional integral over the so-called root distributions $\pmb{\rho}\equiv
-\{\rho_n(\lambda)\}_{n=1}^\infty$ as
+ratio $\det_m(G^+)/\det_m(G^-)$ are neglected. Moreover, the term in~\eref{neel-ov-th} 
+acts as a driving term in the Quech Action formalism (cf. section~\ref{sec:4}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Quench Action treatment of the steady state}
+\label{sec:4}
+
+In the thermodynamic limit the sum over the model eigenstates in~\eref{d-ensemble} 
+can be recast into a functional integral over the BGT root distributions 
+$\pmb{\rho}\equiv\{\rho_n(\lambda)\}_{n=1}^\infty$ (cf. section~\ref{sec:1.4}) 
+as
 %
@@
 \label{eig-sum}
-\sum\limits_{\alpha}\rightarrow\int{\mathcal D}\pmb{\rho}e^{S_{YY}(\pmb{\rho})}. 
+\sum\limits_{\alpha}\rightarrow\int{\mathcal D}\pmb{\rho} e^{S_{YY}(\pmb{\rho})}. 
 \end{equation}
@@
 Here ${\mathcal D}\pmb{\rho}\equiv\prod_{n=1}^\infty{\mathcal D}\rho_n(\lambda)$, 
-$\rho_n(\lambda)$ denote the distribution of the $n$-strings BGT roots, and 
-$S_{YY}(\pmb{\rho})$ is the Yang-Yang entropy, which counts the number of 
-Bethe states leading to the same $\pmb{\rho}$ in the thermodynamic limit. 
-Formally, $\rho_n(\lambda)$  are defined as $\rho_n(\lambda)\equiv\lim_{L\to
-\infty}(\lambda_{n;\gamma+1}-\lambda_{n;\gamma})^{-1}$.
-
-Using~\eref{eig-sum} the diagonal ensemble~\eref{d-ensemble} becomes 
+$\rho_n(\lambda)$, and $S_{YY}(\pmb{\rho})$ is the Yang-Yang entropy, which counts 
+the number of Bethe states leading to the same $\pmb{\rho}$ in the thermodynamic 
+limit. Using~\eref{eig-sum}, for a generic observable ${\mathcal O}$, its diagonal 
+ensemble expectation value~\eref{d-ensemble} becomes 
 %
@@
 \label{qa-d-ensemble}
-\fl
-\quad\langle{\mathcal O}\rangle=\int{\mathcal D}\pmb{\rho}(\lambda)
-\exp\Big(2\Re\log\langle\Psi_0|\pmb{\rho}(\lambda)\rangle 
-+S_{YY}(\pmb{\rho})\Big)\langle\pmb{\rho}(\lambda)|{\mathcal O}|\pmb{\rho}
-(\lambda)\rangle
-\end{equation}
-%
-Note that in~\eref{qa-d-ensemble} it is assumed that in the thermodynamic limit 
-the eigenstate expectation values $\langle\alpha|{\mathcal O}|\alpha\rangle$ 
-become smooth functionals  $\langle\pmb{\rho}(\lambda)|{\mathcal O}|\pmb{\rho}
-(\lambda)\rangle$ of the root distributions $\pmb{\rho}$.
-
-Similarly, in~\eref{qa-d-ensemble} $\langle\Psi_0|\pmb{\rho}(\lambda)\rangle$ 
-denotes the Bethe states overlap density with the prequench state $\Psi_0$.
-
-The strategy is to evaluate the functional integral in~\eref{qa-d-ensemble} 
-using the saddle point approximation.
-
-One has then to minimize the functional ${\mathcal S}(\pmb{\rho})$ defined 
-as 
-%
-\begin{equation}
-L{\mathcal S}(\pmb{\rho})\equiv 2\Re\log\langle\pmb{\rho}|\Psi_0
-\rangle+S_{YY}(\pmb{\rho}(\lambda)). 
-\end{equation}
-% 
-under the constraint that the BGT equations hold. For the quench with initial 
-state the N\'eel state the resulting saddle point root distributions 
-$\rho_n^*(\lambda)$ can be obtained analytically. The first few root distributions 
-are given as 
+\quad\langle{\mathcal O}\rangle=\int{\mathcal D}\pmb{\rho}\exp\Big[2\Re\log\langle
+\Psi_0|\pmb{\rho}\rangle +S_{YY}(\pmb{\rho})\Big]\langle\pmb{\rho}|{\mathcal O}|
+\pmb{\rho}\rangle
+\end{equation}
+%
+Here it is assumed that in the thermodynamic limit the eigenstate expectation 
+values $\langle\alpha|{\mathcal O}|\alpha\rangle$ (cf.~\eref{d-ensemble}) 
+and the overlaps $\langle\Psi_0|\pmb{\rho}\rangle$ become smooth functionals 
+of the root distributions $\pmb{\rho}$.
+
+The functional integral in~\eref{qa-d-ensemble} can be evaluated in the limit 
+$L\to\infty$ using the saddle point approximation. One has to minimize the 
+functional ${\mathcal F}(\pmb{\rho})$ defined as 
+%
+\begin{equation}
+L{\mathcal F}(\pmb{\rho})\equiv 2\Re\log\langle\pmb{\rho}|\Psi_0
+\rangle+S_{YY}(\pmb{\rho}(\lambda))  
+\end{equation}
+% 
+with respect to $\pmb{\rho}$, under the constraint that the thermodynamic BGT 
+equations~\eref{bgt-th} hold. Remarkably, for the quench with initial 
+state the N\'eel state $|\Psi_0\rangle=|N\rangle$ the resulting saddle point root 
+distributions $\rho_n^*(\lambda)$ can be obtained analytically~\cite{brockmann-2014}. 
+The first few are given as 
 %
@@
 %
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{N\'eel overlaps: Numerical results and overview}
+\label{sec:5}
 
@@
 }
-\label{fig0:N-ov-overview}
+\label{fig0:neel-ov}
 \end{figure}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overlap sum rules: the role of the zero-momentum strings}
-\label{ov-sum-rules}
+In this section we present the generic features of the overlaps between the Bethe 
+states of the Heisenberg spin chain and the N\'eel state. We focus on finite chains 
+of length up to $L\lesssim 40$. We consider the full Hilbert space of the chain, 
+i.e., all the eigenstates. These are obtained from the Bethe ansatz approach. 
+We exclude all the eigenstates corrsponding to BGT roots containing zero-momentum 
+strings. The number of remaining eigenstates, that we denote as $\widetilde Z_{Neel}$ 
+is given as a function of the chain size in terms of simple combinatorial formualas 
+that we provide.
+
+Interestingly, we demonstrate that for each finite chain the fraction of the 
+eigenstates with no zero-momentum strings is vanishing in the thermodynamic limit.
+
+We restrict ourselves to eigenstates corresponding to BGT roots with no 
+zero-momentum strings. As expected the N\'eel overlaps decay exponentially with 
+the chain size in the thermodynamic limit.
+
+Moreover, all the overlaps exhibit a vanishing behavior as a function of the eigenstate 
+energy density, signalling that most of the N\'eel overlap is concentrated at low 
+energies.
+
+We observe that the vast majority of eigenstates have negligible N\'eel overlap, 
+as expected.
+
+We show that only a small fraction of the eigenstates are relevant in the 
+thermodynamic limit.
+
+These are the Bethe states that are relevant in the quench action approach.
+
+Finally, we focus on several overlap sum rules. As a consequence of the fact that we 
+neglect the zero-momentum strings, we observe a striking violation of the sum rules 
+for any finite chain. Specifically, all the sum rules exhibit vanishing behavior 
+as $1/\sqrt{L}$ upon increasing the chain size, reflecting the vanishing of the 
+fraction of the eigenstates with no zero-momentum strings.
+
+Similarly, for the Majumdar-Ghosh state the sum rules vanish as $1/L$, again, 
+reflecting the vanishing behaivor of the fraction of eigenstates with no 
+zero-momentum strings.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{N\'eel overlaps from the  full scanning of the Hilbert space}
+\label{sec:5.1}
+
+Here we present numerical results for the overlaps between the eigenstates of the 
+Heisenberg spin chain and the N\'eel state. The data correspond to the full set 
+of eigenstates with no zero-momentum strings and chain lengths $L\le 38$. Their 
+number $\widetilde Z_{Neel}$ is given as (see~\ref{app-2} for the proof) 
+%
+\begin{equation}
+\label{ztilde}
+\widetilde Z_{Neel}=B\Big(\frac{L}{2},\frac{L}{4}\Big).
+\end{equation}
+%
+For $L=38$ from~\eref{ztilde} one has $\widetilde Z_{Neel}\sim 10^5$ eigenstates. 
+Note that the total number of partiy-invariant eigenstates $Z_{Neel}$, which 
+in principle give non-zero N\'eel overlap, is given as 
+%
+\begin{equation}
+\label{zneel1}
+Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1.
+\end{equation}
+%
+The proof of~\eref{zneel1} is reported in~\ref{app-1}.
+
+We should stress that $Z_{Neel}$ provides only an upper bound for the number of 
+eigenstates with non-zero N\'eel overlap (cf. for instance Table~\ref{table:neel}). 
+This is due to the fact that parity-invariant eigenstates with a single even-length 
+string with zero-momentum, which are counted in $Z_{Neel}$, have vanishing N\'eel 
+overlap. This is due to the fact that in~\eref{neel-ov} the ratio of determinants 
+is finite, whereas the prefactor (cf.~\eref{neel-k}) vanishes if a single even-length 
+string with zero momentum is present.
+
+{\bf Clarify what is the number/fraction of the even-length zero-momentum strings}
+
+The results are obtained by generating all the parity-invariant BGT quantum numbers 
+and using them to solve the BGT equations~\eref{bgt-eq}, obtaining the rapidities of 
+the parity-invariant eigenstates of the $XXX$ chain. The overlaps with the N\'eel 
+states are calculated numerically using~\eref{neel-ov}.
+
+Figure~\ref{fig0:neel-ov} plots the squared overlaps $|\langle\lambda|N\rangle|^2$ 
+between the eigenstates $|\lambda\rangle$ of the $XXX$ chain and the N\'eel state 
+$|N\rangle$ for chains with $L=26,32,36,38$. Figure~\ref{fig0:neel-ov} (a) shows the 
+squared overlaps versus the eigenstate energy density $E/L$. Clearly, the overlaps 
+decay exponentially as a function of $L$, as expected. Moreover, for each $L$ 
+we observe a rapid decay as a function of the eigenstate energy density. 
+This decay is exponential, as shown in the inset of Figure~\ref{fig0:neel-ov} (a).
+
+Complementary information is shown in Figure~\ref{fig0:neel-ov} (b) plotting the 
+the histograms of $-2\log|\langle\lambda|N\rangle|/L$ (overlap distribution 
+function). Notice that $2\log|\langle\lambda|N\rangle|/L$ is the driving 
+term in the Quench Action approach. The factor $1/L$ in the definition takes 
+into account that all the overlaps vanish exponentially in the thermodynamic 
+limit, or at least the overlaps that are relevant for the quench action. 
+Notice that larger values of $-2\log|\langle\lambda|N\rangle|/L$, correspond 
+to faster decaying, i.e., asymptotically for large $L$, smaller overlaps.
+
+Figure~\ref{fig0:neel-ov} (b) demonstrates that the vast majority of the eigenstates 
+have small N\'eel overlap. Specifically, a peak at $\sim 0.5$ is visible in the 
+Figure, and a rapid decay at smaller values of ... .
+
+The vertical dotted line in the Figure shows the expected result for 
+$-2\log|\langle\lambda|N\rangle|/L$ in the thermodynamic limit as obtained from 
+the quench action.
+
+This is obtained by usigng~\eref{neel-ov-th} and the saddle point root distributions 
+$\rho_n^*$ (cf.~\eref{rho_sp} for the results up to $n=3$). Note that its position 
+does not coincide with the peak of the overlap distribution function, as expected. 
+This is reflecting the competition between the driving term and the entropy 
+term in the quench action.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{N\'eel overlap sum rules}
+\label{sec:5.2}
 
@@
 }
-\label{fig2-neel-sr}
+\label{fig1:neel-sr}
 \end{figure}
@@
 
-In this section we investigate the role of the zero-momentum strings. We focus on 
-conserved quantities sum rules. Specifically, given a generic conserved quantity 
-(charge) $\hat Q$ we consider the trivial identity  
-%
-\begin{equation}
-\label{sum}
-Q_0\equiv\langle\Psi_0|\hat Q|\Psi_0\rangle=\sum\limits_{\lambda}|\langle\lambda|
-\Psi_0\rangle|^2Q_\lambda, 
-\end{equation}
-%
-where $Q_0$ is the charge expectation values over the initial state $|\Psi_0
-\rangle$, $|\lambda\rangle$ denotes the generic eigenstate of the $XXX$ chain, 
-and $Q_\lambda$ is the charge eigenvalue over the eigenstate.
-
-Here we restrict ourselves to the cases with $\hat Q=\mathbb{I}$ and $\hat 
-Q={\mathcal H}$, considering both the case with $|\Psi\rangle=|N\rangle$ and 
-$|\Psi_0\rangle=|MG\rangle$.
-
-For the N\'eel state, for any finite $L$ Eq.~\eref{sum} gives $Q_0=1,-1/2$ for 
-$\hat{Q}=\mathbb{I}$ and $\hat Q={\mathcal H}$, respectively.
-
-Figure~\ref{fig2-neel-sr} plots the numerical results obtained via a full 
-scanning of the Hilbert space of the Heisenberg chain.
-
-Precisely, the numerical data are obtained by generating all the possible string 
-contents ${\mathcal S}$ compatible with the parity-invariance constraint
-
-Panel (a) and (b) in the 
-Figure plots the sum rule~\eref{sum} for $\hat Q=\mathbb{I}$ and $\hat Q={\mathcal 
-H}$, respectively. The circles are obtained considering all the eigenstates of the 
-Heisenberg spin chain with $L$ sites, excluding eigenstates containing 
-zero-momentum strings.
-
-The total number of eigenstates $\widetilde Z_{Neel}$ containing no zero-momentum 
-strings is given as 
-%
-\begin{equation}
-\label{ztilde}
-\widetilde Z_{Neel}=B\Big(\frac{L}{2},\frac{L}{4}\Big).
-\end{equation}
-%
-The proof of\eref{ztilde} is reported in~\ref{app-2}.
+Here we investigate the effect of the Hilbert space truncation removed the 
+zero-momentum strings on the N\'eel sum rules. 
+We focus on the ``trivial'' sum rule, i.e., the normalization of the initial 
+state 
+%
+\begin{equation}
+\label{sr-trivial}
+\langle N|N\rangle=\sum\limits_{\lambda}|\langle\lambda|N\rangle|^2=1, 
+\end{equation}
+%
+and the local conserved charges sum rules 
+%
+\begin{equation}
+\label{sr-charge}
+Q_n^{(0)}=\langle N|Q_n|N\rangle=\sum\limits_{\lambda}|\langle\lambda|N\rangle|^2
+q_{n}(\lambda)\quad\textrm{with}\quad n\in\mathbb{N}, 
+\end{equation}
+%
+where $Q_n$ are the conserved charges of the $XXX$ chain (cf. 
+subsection~\ref{sec:1.5}) and $q_n(\lambda)$ are the charges eigenvalues over 
+the generic Bethe state $|\lambda\rangle$ (cf.~\eref{qngnk} and~\eref{gnk}).
+
+In~\eref{sr-charge} $Q_n^{(0)}$ is the charge expectation value over the initial 
+state, i.e., the N\'eel state. These can be calculated as done in 
+Ref.~\cite{fagotti-2013}.
+
+Note that due to the locality of $Q_n$, the translational invariance of the initial 
+state, and the periodic boundary conditions, the charge density $Q_n^{(0)}/L$ does 
+not depend on the chain size. For the N\'eel state, in the thermodynamic limit 
+$Q_n^{(0)}$ is obtained using~\eref{q0-th} and the quench action root distributions 
+$\pmb{\rho}^*$ (cf.~\eref{rho_sp}).
+
+The truncation of the chain Hilbert space removing the zero-momentum strings has 
+dramatic effects on the sum rules~\eref{sr-trivial} and~\eref{sr-charge}.
+
+This is illustrated in Figure~\ref{fig1:neel-sr} (a) focusing on the ``trivial'' 
+sum rule~\eref{sr-trivial} and in Figure~\ref{fig1:neel-sr} (b) for~\eref{sr-charge} 
+with $n=2$, i.e., the energy sum rule. 
+For the N\'eel state, for any finite $L$ Eq.~\eref{sum} gives $Q^{(0)}_2/L=-1/2$.
+
+The circles in Figure~\ref{fig1:neel-sr} are the numerical results for the sum rules 
+obtained via a full scanning of the Hilbert space of the Heisenberg chain, excluding 
+the zero momentum strings. The data are plotted against the inverse chain length $1/L$, 
+for $L\le 38$. The expected results including all the eigenstates are shown as 
+horizonthal dotted lines in the Figure.
+
+Clearly, both the sum rules are violated, due to the exclusion of the to zero-momentum 
+strings. Moreover, in both panesl the data suggest a vanishing behavior upon increasing 
+the chain size. In particular, the dash-dotted lines in the Figures are fits to  
+$A/L^{1/2}+B/L$, with $A,B$ fitting parameters, which perfectly describes the behavior 
+of the data.
+
+The vanishing behavior as $\propto 1/L^{1/2}$ is reflecting the vanishing 
+of the fraction of non-zero momentum string eigenstates in the thermodynamic limit.  
+Precisely, from~\eref{zneel1} and~\eref{ztilde} one obtains 
+%
+\begin{equation}
+\label{beh}
+\frac{\widetilde Z_{Neel}}{Z_{Neel}}\propto\frac{4}{\sqrt{\pi L}}. 
+\end{equation}
+% 
+in the thermodynamic limit.
 
@@
 }
-\label{fig3-dimer-sr}
+\label{fig2:dimer-sr}
 \end{figure}
@@
 
-The largest chain size considered is $L=36$. The data are plotted versus $1/L$.
-
-Interestingly, both the sum rules (panels (a)(b)) are not saturated, as expected 
-since the eigenstates corresponding to zero-momentum strings are excluded in the 
-sum in the right-hand-side in~\eref{sum}.
-
-Interestingly, both sum rules exhibit vanishing behavior upon increasing the 
-chain size. The dash-dotted lines in the Figures are fits to the behavior 
-$A/L^{1/2}+B/L$, with $A,B$ fitting parameters, and perfectly describe the 
-behavior of the data.
-
-The vanishing behavior as $\propto 1/L^{1/2}$ of the sum rules reflects the vanishing 
-of the fraction of non-zero momentum string eigenstates in the thermodynamic limit ad 
-%
-\begin{equation}
-\label{beh}
-\frac{\widetilde Z_{Neel}}{Z_{Neel}}\propto\frac{4}{\sqrt{\pi L}}, 
-\end{equation}
-% 
-with $Z_{Neel}$ being the total number of eigenstates corresponding to parity 
-invariant BGT quantum numbers configurations.
-
-One should observe that the asymptotic, i.e., at large $L$, behavior~\eref{beh} 
-is not generic, meaning that different initial states $|\Psi_0\rangle$ might 
-give different behaviors.
-
-This is illustrated in Figure~\ref{fig3-dimer-sr}, focusing on the Majumdar-Ghosh 
-(MG) state. Panels (a) and (b) plot the sum rules with $\hat Q=\mathbb{I}$ and 
-$\hat Q={\mathcal H}$ (same as in Figure~\ref{fig2-neel-sr}). As for the N\'eel 
-state only eigenstates containing no zero-momentum strings are consdidered. 
-Note that their number $\widetilde Z_{MG}$ (see~\ref{app-2}) is now given as 
+The asymptotic, i.e., at large $L$, behavior as $1/\sqrt{L}$ is not generic, 
+meaning that it depends on the initial state $|\Psi_0\rangle$. 
+This is illustrated in Figure~\ref{fig2:dimer-sr}, focusing on the Majumdar-Ghosh 
+(MG) state. Panels (a) and (b) plot are the same as in Figure~\ref{fig1:neel-sr}. 
+The expected value for the energy density sum rule is $Q_2^{(0)}=-2/3$ (horizonthal dotted 
+line in Figure~\ref{fig2:dimer-sr}). 
+As for the N\'eel state only parity-invariant eigenstates containing no zero-momentum 
+strings are consdidered. Note that their number $\widetilde Z_{MG}$ (cf.~\eref{mg-fi}) 
+is now given as 
 %
@@
 %
-Similar to Figure~\ref{fig2-neel-sr}, due to the exclusion of the zero-momentum 
+Similar to Figure~\ref{fig1:neel-sr}, due to the exclusion of the zero-momentum 
 strings, the saturation rules exhibit vanishing behavior in the thermodynamic 
-limit. However, in contrast with the N\'eel case (see Figure~\ref{fig2-neel-sr}), 
-one has the behavior $Q_0\sim 1/L$, as confirmed by the fits (dash-dotted lines 
-in Figure~\ref{fig3-dimer-sr}).
+limit. However, in contrast with the N\'eel case, one has the behavior $\sim 1/L$, 
+as confirmed by the fits (dash-dotted lines in Figure~\ref{fig2:dimer-sr}).
 
@@
 %
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Monte Carlo implementation of the Quench-Action approach}
-\label{mcqa-sec}
-
-For the finite-size Heisenberg spin chain the Quench-Action expectation 
-values can be obtained by sampling the eigenstates of the chain using 
-Monte Carlo. One starts with an eigenstate of the $XXX$ chain with 
-$N_{\infty}$ infinite rapidities and $M\equiv L/2-N_\infty$ finite ones. 
+where $Z_{MG}$ is the total number of parity-invariant eigenstates having non-zero 
+overlap with the Majumdar-Ghosh state.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Monte Carlo implementation of the quench action approach}
+\label{sec6:mcqa}
+
+In this section follwing Ref.~\cite{alba-2015} we present the implementation of 
+the quench action approach, focusing on the $XXX$ chain. The key idea is to sample 
+the eigenstates of the finite-size $XXX$ 
+chain with the quench action probability distribution given in~\eref{qa-d-ensemble}. 
+Importantly, we restrict ourselves to the set of eigenstates of the $XXX$ chain 
+with no zero-momentum strings. In subsection~\ref{sec:6.1} we introduce the Monte 
+Carlo algorithm. Using the Monte Carlo algorithm in subsection~\ref{sec:6.2} we 
+numerically demonstrates that the N\'eel sum rules~\eref{sr-charge} are recovered 
+in the thermodynamic limit. The Hilbert space truncation is reflected in 
+$\propto 1/L$ scaling corrections to the sum rules. Physically, this implies that 
+despite the Hilbert space cut, the remaining eigenstates contain enough information 
+to reproduce the correct physical behavior in the thermodynamic limit.
+
+In the Bethe ansatz framework this means that the eigenstates sampled by the Monte 
+Carlo method approach the quench action representative state in the thermodynamic 
+limit. This is explicitly demonstrated here by numerically calculating the 
+quench action root distributions $\pmb{\rho}^*$, which are found in remarkable 
+agreement with the analytical results.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Quench Action Monte Carlo algorithm}
+\label{sec:6.1}
+
+The Monte Carlo procedure starts with a randomly selected parity-invariant 
+eigenstate (Bethe state) of the $XXX$ chain in the sector with zero magnetization, 
+i.e., $M=L/2$ particles.
+
+Due to the fact that the N\'eel state is not invariant under $SU(2)$ rotations, 
+to characterize the Bethe states one has to specify the number of infinite rapidities. 
+Let us define the number of infinite rapidities $N_{\infty}$. Clearly, one has that 
+the number of particles with finite rapidities $M'$ as $M'=L/2-N_\infty$. 
 The state is identified by a parity-invariant Bethe quantum number 
-configuration ${\mathcal C}$ and by the corresponding parity-invariant 
-rapidities $\{\lambda\}$ as $|\lambda\rangle$. The string content 
-associated with the finite rapidities is denoted as ${\mathcal S}$. The Monte 
-Carlo procedure consists of four steps as follows: 
+configuration ${\mathcal C}$. Due to the parity-invariance and the fact that zero-momentum 
+strings are excluded, the state is characterized by the number $m'$ of parity-invariant 
+rapidity pairs $\{\pm\lambda_j\}_{j=1}^{m'}$. The string content 
+associated with the finite rapidity pairs is denoted as $\widetilde{\mathcal S}=
+\{\tilde s_1,\dots,\tilde s_{m'}\}$. The Monte Carlo procedure generates a new 
+parity-invariant eigenstate of the $XXX$ chain, and it consists of four steps as 
+follows: 
 %
 \begin{enumerate}
-\item[\circled{1}] Choose a new number of finite rapidities $M'$ with 
-probability
+\item[\circled{1}] Choose a new number of finite rapidities $M_{new}'$ and a 
+parity-invariant rapidity pairs $m_{new}'\equiv M_{new}'/2$ with 
+probability ${\mathcal P}(M'_{new})$ as 
 %
@@
 \label{PM}
-{\mathcal P}(M')=\frac{\widetilde Z'_{Neel}(L,M')}{\widetilde{Z}_{Neel}(L)}. 
-\end{equation}
-%
-\item[\circled{2}] Choose a new a new string content ${\mathcal S}'\equiv
-\{s_1',\dots,s_{M'}'\}$ with probability ${\mathcal P}'(M',{\mathcal S}')$
+{\mathcal P}(M'_{new})=\frac{\widetilde Z'_{Neel}(L,M'_{new})}
+{\widetilde{Z}_{Neel}(L)}, 
+\end{equation}
+%
+where $\widetilde Z_{Neel}(L)$ is the total number of parity-invariant eigenstates 
+with no zero-momentum strings (cf.~\eref{ztilde}), and $\widetilde Z'_{Neel}$ is the 
+number of parity invariant eigenstates with no zero-momentum strings in the 
+sector with $M'_{new}$ particles with finite rapidities (cf.~\eref{neel-fi}). 
+\item[\circled{2}] Choose a new a new string content $\widetilde{\mathcal S}'\equiv
+\{\tilde s_1',\dots,\tilde s_{m'_{new}}\}$ with probability ${\mathcal P}'(M'_{new},
+\widetilde{\mathcal S}')$
 %
@@
 \label{PS}
-{\mathcal P}'(M',{\mathcal S}')=\frac{1}{\widetilde Z'_{Neel}(L,M')}
-\prod_{n=1}^{M'}B\Big(\frac{L}{2}-\frac{1}{2}\sum\limits_{m=1}^{M'}t_{nm}
-s'_m,s'_n\Big).
-\end{equation}
-%
+{\mathcal P}'(M'_{new},\widetilde{\mathcal S}')=\frac{1}{\widetilde Z'_{Neel}
+(L,M'_{new})}\prod_{n=1}^{m'_{new}}B\Big(\frac{L}{2}-\sum\limits_{l=1}^{
+m'_{new}}t_{nl}\tilde s'_l,\tilde s'_n\Big), 
+\end{equation}
+%
+where the matrix $t_{nl}$ is defined in~\eref{bt-qn-bound}.
 \item[\circled{3}] Generate a new parity-invariant quantum number configuration 
-${\mathcal C}'$ compatible with the ${\mathcal  S}'$ obtained in step $\circled{2}$. 
-Solve the corresponding BGT equations~\eref{bt_eq}, finding a new eigenstate 
-$|\lambda'\rangle$. 
-\item[\circled{4}] Calculate the overlap $\langle\lambda'|N\rangle$ between the 
-new eigenstate and the N\'eel state and accept the eigenstate with the Metropolis 
-probability 
+${\mathcal C}'$ compatible with the $\widetilde {\mathcal  S}'$ obtained in step 
+$\circled{2}$. Solve the corresponding BGT equations~\eref{bgt-eq}, finding the 
+rapidities $\{\pm\lambda'_j\}_{j=1}^{m'_{new}}$ of the new parity-invariant 
+eigenstate. 
+\item[\circled{4}] Calculate the overlap $\langle\{\lambda'_j\}_{j=1}^{m'_{new}}
+|N\rangle$ between the new eigenstate and the N\'eel state 
+using~\eref{neel-ov}~\eref{red-G+}~\eref{red-G-} and~\eref{neel-k}. Accept the 
+new eigenstate with the quench action Metropolis probability 
 %
@@
 %
-where ${\mathcal E}'\equiv-\log\langle\lambda'|N\rangle$, similarly for 
-${\mathcal E}$, and $\Re$ denotes the real part. 
+where ${\mathcal E}'\equiv-\log\langle\{\lambda'_j\}_{j=1}^{m'_{new}}
+|N\rangle$, ${\mathcal E}\equiv-\log\langle\{\lambda_j\}_{j=1}^{m'_{new}}
+|N\rangle$, and $\Re$ denoting the real part. 
 \end{enumerate}
 %
-
-Afte some necessary thermalization steps the sequence $1-4$ generates eigenstates 
-of the $XXX$ chain distributed according to the Quench-Action probability 
+Note that while the steps $1$-$3$ generate the correct eigenstate energy density 
+distribution, $4$ weigh the different eigenstates with the quench action probability 
 distribution.
 
-For a generic observable ${\mathcal O}$, its Quench-Action expectation value 
-$\langle{\mathcal O}\rangle_{QA}$ is obtained as the arithmetic average of the 
-expectation value over the eigenstates sampled in the Monte Carlo as 
-%
-\begin{equation}
-\langle{\mathcal O}\rangle_{QA}=\frac{1}{N_{mcs}}\sum\limits_{\lambda}
-\langle\lambda|{\mathcal O}|\lambda\rangle, 
-\end{equation}
-%
-with $N_{mcs}$ being the total number of Monte Carlo steps.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Monte Carlo Quench-Action approach: Numerical results}
-\label{MCQA-nr}
+For a generic observable ${\mathcal O}$, the long-time quench action value $\langle{
+\mathcal O}\rangle$ is obtained as the arithmetic average of the expectation value 
+over the eigenstates $|\lambda\rangle$ sampled by the Monte Carlo as 
+%
+\begin{equation}
+\label{qamc-obs}
+\langle{\mathcal O}\rangle=\frac{1}{N_{mcs}}\sum\limits_{\lambda}\langle\lambda|
+{\mathcal O}|\lambda\rangle, 
+\end{equation}
+%
+with $N_{mcs}$ being the total number of Monte Carlo steps. Note that, as usual in 
+Monte Carlo, some initial steps have to be neglected to ensure thermalization. 
+Note that~\eref{qamc-obs} applies to any observable ${\mathcal O}$ for which the 
+the Bethe state expectation value $\langle\lambda|{\mathcal O}|\lambda\rangle$ 
+(form factor) is known.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The N\'eel sum rules: Monte Carlo results}
+\label{sec:6.2}
 
@@
 }
-\label{fig5-neel-sr}
+\label{fig3:neel-qamc-sr}
 \end{figure}
@@
 
-In this section we numerically demonstrate that the only effect of neglecting 
-the zero-momentum strings are finite-size corrections.
-
 The validity of the Monte Carlo approach for simulating the Quench-Action 
-results is demonstrated in Figure~\ref{fig5-neel-sr}. The Figure focuses on 
-the N\'eel sum rules for the conserved charges $Q_2$ and $Q_4$. Specifically, 
-panel (a) shows the sum rules for $\hat Q=\hat Q_2$, $\hat Q=\hat Q_4$, 
-and the corresponding fluctuations $\sigma^2(Q_n)\equiv \langle N|\hat Q_n^2|
-N\rangle-\langle N|\hat Q_n|N\rangle^2$. 
-%
-\begin{equation}
-\langle N|\hat Q_n|N\rangle=\sum\limits_{\lambda}|\langle N|\lambda\rangle|^2
-Q_n.
-\end{equation}
-%
-Note that the N\'eel sum rule for the identity $\mathbb{I}$ is trivially satisfied, 
-and it corresponds to the normalization of the Monte Carlo probability. 
-Figure~\ref{fig5-neel-sr} (a) plots the N\'eel sum rule for the energy density $Q_2/L$. 
-The circles are Monte Carlo data obtained using the procedure outlined in~\ref{mcqa-sec} 
-for several Heisenberg spin chains. The largest chain simulated is for $L=56$ sites. 
-The data correspond to a simulation with $\sim 10^7$ Monte Carlo step (mcs). 
-The expected result $\langle N|\hat Q_2|N\rangle/L=-1/2$ is shown as dash-dotted 
-line.
-
-In stark contrast with Figure~\ref{fig2-neel-sr} and Figure~\ref{fig3-dimer-sr}, 
-while for small chains the sum rule is violated the data strongly suggest that 
-in the thermodynamic limit the sum rule saturates the expected theoretical 
-value.
-
-Furthermore, the data suggest the behavior $\propto 1/L$, as confirmed by the fit 
-to $-1/2+A/L+b/L^2$ (dashed line in the Figure), with $A,B$ fitting parameters.
-
-The same qualitative behavior is demonstrated in panel (b) for the energy 
-fluctuations. Interestingly, for $L=56$ the Monte Carlo result is compatible 
-within the error bar with the expected asymptotic one.
-
-Finally, panels (c)(d) show the same results as for (a)(b) for the conserved 
-charge $Q_4$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Quench-Action root distributions}
-\label{MCQA-root}
+results is demonstrated in Figure~\ref{fig3:neel-qamc-sr}. The Figure focuses on 
+the N\'eel sum rules for the conserved charges densities $Q_2/L$ and $Q_4/L$ 
+(cf. subsection~\ref{sec:1.5} and~\eref{sr-charge}) and their fluctuations 
+$\sigma(Q_n)$, which are defined as 
+%
+\begin{equation}
+\fl\quad\sigma^2(Q_n)\equiv\langle N|Q^2_n|N\rangle-\langle N|Q_n|N\rangle^2=
+\sum\limits_{\lambda}|\langle N|\lambda\rangle|^2q^2_n(\lambda)-\Big(\sum_\lambda|
+\langle N|\lambda\rangle|^2q_n(\lambda)\Big)^2.
+\end{equation}
+%
+Panel (a) and (b) in Figure~\ref{fig3:neel-qamc-sr} show the sum rules for 
+the energy density $Q_2/L$, and its density of fluctutations $\sigma^2(Q_2)/L$. 
+It is straightforward to derive the N\'eel expectation value of the energy 
+density fluctuations as $\sigma(Q_2)/L=1/4$ (dash-dotted line in 
+Figure~\ref{fig3:neel-qamc-sr} (b)).
+
+%Note that the N\'eel sum rule for the identity $\mathbb{I}$ is trivially satisfied, 
+%and it corresponds to the normalization of the Monte Carlo probability. 
+%Figure~\ref{fig5-neel-sr} (a) plots the N\'eel sum rule for the energy density $Q_2/L$. 
+The circles in the Figure are Monte Carlo data obtained using the procedure outlined 
+in~\ref{sec:6.1} for the Heisenberg spin chain with $L\le 56$ sites.  
+The data correspond to Monte Carlo simulations with $N_{mcs}\sim 10^7$ Monte Carlo 
+steps (mcs). For the largest chain size $L=56$ we used $N_{mcs}\sim ...$. The data 
+are plotted versus inverse chain length $1/L$. 
+%The expected result $\langle N|\hat Q_2|N\rangle/L=-1/2$ is shown as dash-dotted 
+%line.
+
+Interestingly, the Monte Carlo data strongly suggest that in the thermodynamic limit 
+the sum rule saturates are restored, while violations are present for finite chains. 
+This numerically demonstrates that the truncation of the Hilbert space, i.e., 
+removing the zero-momentum strings, gives rise to scaling corrections, while the 
+thermodynamic limit behavior is correctly reproduced. 
+Furthermore, the data in panel (a) suggest the behavior $\propto 1/L$ for the scaling 
+corrections, as confirmed by the fit to $-1/2+A/L+b/L^2$ (dashed line in the Figure), 
+with $A,B$ fitting parameters.
+
+The same behavior should be expected for the energy fluctuations $\sigma^2(Q_2)$, 
+although this is difficult to extract numerically due to the large Monte Carlo 
+error bar.
+
+Finally, panels (c) and (d) in Figure~\ref{fig3:neel-qamc-sr} are the same as 
+(a)(b), but for the charge $Q_4$. While for $Q_4/L$ the Monte Carlo result 
+for $L=48$ is already compatible with the expected result $Q_4/L=1/4$ in the 
+thermodynamic limit, the scaling corrections of the fluctuations $\sigma^2(Q_4)$ 
+are larger, and the Monte Carlo data show significant deviations from the 
+thermodynamic limit up to $L=56$.
+
+This is explained that the support of $Q_4$, i.e., the number of sites where 
+the operator acts non trivially is larger than for $Q_2$ (see~\cite{grabowski-1995} 
+for the precise expression), and it is natural 
+to assume that scaling corrections increase upon increasing the support of the 
+operator considered.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The quench action root distributions}
+\label{sec:6.3}
 
@@
 }
-\label{fig6-neel-roots}
+\label{fig4:neel-rho}
 \end{figure}
@@
 
-The BGT root distributions $\rho_n(\lambda)$ identifying the Quench-Action saddle 
-point can be extracted from the Monte Carlo simulation as shown in~\cite{alba-2015}.
-
-Figure~\ref{fig6-neel-roots} displays the first two root distributions 
-$\rho_1(\lambda)$ (panel (a)) and $\rho_2(\lambda)$ (panel (b)), plotted agains 
+The BGT root distributions corresponding to the quench action steady state 
+(cf.~\eref{rho_sp}) $\pmb{\rho}=\{\rho_n(\lambda)\}_{n=1}^{\infty}$ can be extracted 
+from the Monte Carlo simulation.  This has been shown in Ref.~\cite{alba-2015} for 
+the GGE representative state.
+
+The underlying idea is that for the local observables considered in this 
+work the eigenstate expectation value $\langle\lambda|{\mathcal O}|\lambda\rangle$
+entering in~\eref{qamc-obs} becomes
+%
+\begin{equation}
+\langle\lambda|{\mathcal O}|\lambda\rangle=\sum\limits_{n,\gamma}{\mathcal O}
+(\lambda_{n;\gamma}), 
+\end{equation}
+%
+with the set of solutions of the BGT equations $\{\lambda_{n;\gamma}\}$ identifying 
+the Bethe state $|\lambda\rangle$. 
+By comparing~\eref{qamc-obs} and ... one obtains
+%
+\begin{equation}
+\frac{1}{N_{mcs}}\sum\limits_{\{\lambda_{n;\gamma}\}}{\mathcal O}_n(\lambda_{n;\gamma})
+\to\int_{-\infty}^{+\infty}d\lambda\rho_{n}(\lambda){\mathcal O}_n(\lambda). 
+\end{equation}
+%
+This suggests that for any $n$ the histograms of the BGT roots corresponding to the 
+$n$-strings sampled in the Monte Carlo should converge in the thermdynamic limit to 
+the root distribution $\rho_n$.
+
+This is demonstrated numerically in Figure~\ref{fig4:neel-rho} for the first two root 
+distributions $\rho^*_1(\lambda)$ (panel (a)(b)) and $\rho^*_2(\lambda)$ (panel 
+(c)(d)), plotted agains 
 the BGT root $\lambda$. The data are the histograms of the BGT roots sampled 
@@
 quasimomenta, which are more sensitive to the finite size of the chain.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Counting of eigenstates with non-zero Neel overlap}
-
-We numerically checked that the number of states with non-zero overlap 
-with the Neel state is given as 
-%
-\begin{equation}
-\label{Neel-count}
-Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\left(\frac{L}{2},
-\frac{L}{4}\right)+1,
-\end{equation}
-%
-with $B(x,y)$ denoting the binomial coefficient. The contribution $1$ 
-accounts for the ferromagnetic state. Here 
-we assumed that $L$ is divisible by four. Here $Z_N$ is be obtained 
-as the total number of parity-invariant Bethe-Gaudin-Takahashi quantum 
-numbers.
-
-After excluding the zero-momentum strings the total number of states 
-with non-zero overlap with the Neel state is 
-%
-\begin{equation}
-\label{neel-ov-count}
-\widetilde {Z}_{Neel}=\Big(\frac{L}{2},\frac{L}{4}\Big)
-\end{equation}
-%
-Importantly, the fraction of eigenstates corresponding to non-zero momentum 
-strings is vanishing in the thermodynamic limit as 
-%
-\begin{equation}
-\frac{\widetilde Z_{Neel}}{Z_{Neel}}\propto\frac{4}{\sqrt{\pi L}}.
-\end{equation}
-%
 
@@
 
+\bibitem{mazza-2015}
+P.~P.~Mazza, J.-M.~St\'ephan, E.~Canovi, V.~Alba, M.~Brockmann, and M.~Haque, 
+arXiv:1509.04666.
+
+\bibitem{fagotti-2013}
+M.~Fagotti and F.~H.~Essler, J.\ Stat.\ Mech.\ (2013) P07012.
+
+\bibitem{grabowski-1995}
+M.~P.~Grabowski and P.~Mathieu, Ann.\ Phys.\ N.Y. {\bf 243},
+299 (1995).
+
 \end{thebibliography}

### 2015-09-24 draft/fs_qa_v1.tex
rev-24/09/2015

@@
 
+It is useful to rewrite~\eref{d-ensemble} as 
+%
+\begin{equation}
+\label{qa-prob}
+\langle{\mathcal O}\rangle=\sum\limits_{\alpha}\rho^{DE}(\alpha)
+\langle\alpha|{\mathcal O}|\alpha\rangle,\quad\textrm{with}\quad 
+\rho^{DE}(\alpha)=\exp(-2\Re{\mathcal E}(\alpha)).
+\end{equation}
+%
+Here $\rho^{DE}(\alpha)$ is a diagonal ensemble density matrix, and ${\mathcal E}(\alpha)
+\equiv-\log\langle\alpha|\Psi_0\rangle$, with $\Re$ denoting the real part.
+
 %%%%%%%%%%%%%%%%%%%%%%% BETHE ANSATZ FOR THE XXX CHAIN %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{eqnarray}
-\label{rho_sp}
+\label{rho1-sp}
 \fl\quad\rho^*_1(\lambda)=\frac{8(4+\lambda^2)}{\pi(19+3\lambda^2)(1+6\lambda^2+
-\lambda^4)}\\
+\lambda^4)}\\\label{rho2-sp}
 \fl\quad\rho_2^*(\lambda)=\frac{8\lambda^2(9+\lambda^2)(4+3\lambda^2)}{\pi(2+\lambda^2)
-(16+14\lambda^2+\lambda^4)(256+132\lambda^2+9\lambda^4)}\\
+(16+14\lambda^2+\lambda^4)(256+132\lambda^2+9\lambda^4)}\\\label{rho3-sp}
 \fl\quad\rho_3^*=\frac{8(1+\lambda^2)^2(5+\lambda^2)(16+\lambda^2)(21+\lambda^2)}
@@
 
+Interestingly, the data suggest the behavior
+%
+\begin{equation}
+|\langle\lambda|N\rangle|^2\propto\exp(-\kappa L),
+\end{equation}
+%
+with $0.18\lesssim\kappa\lesssim0.7$. The vertical dash-dotted line in 
+Figure~\ref{fig0:neel-ov} is the overlap between the ground state of the 
+$XXX$ chain and the N\'eel state. This is obtained using the ground state 
+root distribution $\rho_1(\lambda)\propto1/\cosh(\pi\lambda)$  
+and~\eref{neel-ov-th}. The dashed line denotes the N\'eel overlap 
+$\sim 2/B(L,L/2)$ with the $S_z=0$ component of the ferromagnetic state.
+
 The vertical dotted line in the Figure shows the expected result for 
-$-2\log|\langle\lambda|N\rangle|/L$ in the thermodynamic limit as obtained from 
-the quench action.
+$-2\log|\langle\lambda|N\rangle|/L$ in the thermodynamic limit as 
+obtained from the quench action.
 
 This is obtained by usigng~\eref{neel-ov-th} and the saddle point root distributions 
-$\rho_n^*$ (cf.~\eref{rho_sp} for the results up to $n=3$). Note that its position 
-does not coincide with the peak of the overlap distribution function, as expected. 
-This is reflecting the competition between the driving term and the entropy 
+$\rho_n^*$ (cf.~\eref{rho1-sp}-\eref{rho3-sp} for the results up to $n=3$). Note that 
+its position does not coincide with the peak of the overlap distribution function, as 
+expected. This is reflecting the competition between the driving term and the entropy 
 term in the quench action.
@@
 $Q_n^{(0)}$ is obtained using~\eref{q0-th} and the quench action root distributions 
-$\pmb{\rho}^*$ (cf.~\eref{rho_sp}).
+$\pmb{\rho}^*$ (cf.~\eref{rho1-sp}-\eref{rho3-sp}).
 
@@
 The BGT root distributions corresponding to the quench action steady state 
-(cf.~\eref{rho_sp}) $\pmb{\rho}=\{\rho_n(\lambda)\}_{n=1}^{\infty}$ can be extracted 
+(cf.~\eref{rho1-sp}-\eref{rho3-sp}) $\pmb{\rho}=\{\rho_n(\lambda)\}_{n=1}^{\infty}$ can be extracted 
 from the Monte Carlo simulation.  This has been shown in Ref.~\cite{alba-2015} for 
@@
 distributions $\rho^*_1(\lambda)$ (panel (a)(b)) and $\rho^*_2(\lambda)$ (panel 
-(c)(d)), plotted agains 
-the BGT root $\lambda$. The data are the histograms of the BGT roots sampled 
-in the Monte Carlo. The data are for a chain with $L=56$ sites and 
-$N_{mcs}\sim 10^7$ Monte Carlo steps. All the data are divided by a factor 
-$10^6$ for plotting convenience. The width of the histogram bins $\Delta\lambda$ 
+(c)(d)). The data are obtained using the algorithm described in subsection~\ref{sec:6.1} 
+for chains with up to $L\le 56$ sites. The data for $L=48$ correspond to a Monte Carlo 
+history with $N_{mcs}\sim 10^7$ Monte Carlo steps (cf.~\eref{qamc-obs}), whereas we 
+used $N_{mcs}\sim 10^8$ for $L=56$.
+
+Panel (a) and (c) show the  histograms of the $1$-string and $2$-string BGT roots sampled 
+in the Monte Carlo, respectively for the chain with $L=56$ sites. The $y$-axis is 
+divided by a factor $10^6$ for convenience. The width of the histogram bins $\Delta\lambda$ 
 is $\Delta\lambda\approx0.02$ and $\Delta\lambda\approx0.001$ for $\rho_1(\lambda)$ 
-and $\rho_2(\lambda)$, respectively.
-
-The histogram fluctuations are due to $N_{mcs}$ being finite, and are expected 
-to vanish in the limit $N_{mcs}\to\infty$.
-
-The continuous lines is the expected analytic result in the thermodynamic limit.
-
+and $\rho_2(\lambda)$, respectively. The histogram fluctuations are due both to the finite 
+statistics (finite $N_{mcs}$) and to the finite size of the chain.
+
+The extracted quench action saddle point root distributions $\rho^*_1(\lambda)$ and 
+$\rho^*(\lambda)$ are shown in panels (b) and (d). The data are the same as in panel 
+(a)(c). The normalization of the histograms is chosen such as to match the analytical 
+results from~\eref{rho1-sp} and~\eref{rho2-sp}, i.e., $\int d\lambda
+\rho^*_1(\lambda)\approx0.31$ and $\int d\lambda\rho^*_2(\lambda)\approx
+0.015$. The Monte Carlo error bars shown in the Figure are obtained with a standard 
+jackknife analysis~\cite{quenouille-1949,wolff-2004}. 
+The continuous lines are the expected analytic result in the thermodynamic limit given 
+in~\eref{rho1-sp} and~\eref{rho2-sp}. 
 Clearly, $\rho_1(\lambda)$ is in good agreement with the Monte Carlo data in the 
-whole range $-2\le\lambda\le2$ considered. 
-On the other hand, larger deviations from the theoretical result are present 
-for $\rho_2(\lambda)$. These deviations are larger on the tails of the 
-distribution. This is expected since large $\lambda$ correspond to large 
-quasimomenta, which are more sensitive to the finite size of the chain.
+whole range $-2\le\lambda\le2$ considered. The statistical error bars are smaller 
+than the symbol size. The oscillations are due to the finite size of the chain, and 
+decrease with the chain size (see the data for $L=48$). 
+On the other hand, larger (oscillating) finite size effects are observed for $\rho_2(\lambda)$. 
+These deviations are larger on the tails of the root distribution. This is expected since 
+large $\lambda$ correspond to large quasimomenta, which are more sensitive to the finite 
+size of the chain. Moreover, the Monte Carlo error bars are clearly visible. This is 
+due to the fact that since $\int d\lambda\rho^*_2(\lambda)/\sum_n\int d\lambda
+\rho_n^*(\lambda)\approx 0.04$, the statistics available to estimate $\rho_2^*(\lambda)$ 
+is effectively reduced as compared to $\rho_1^*(\lambda)$. 
+Finally, we numerically checked that this effect is more dramatic for the longer strings 
+root distribution, and larger statistics and larger chain would be needed already  
+to extract $\rho_3(\lambda)$
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}
+\label{conclusions}
+
+We presented a Monte Carlo implementation of the quench action method for integrable 
+spin chains. We focused on the spin-$1/2$ isotropic Heisenberg spin chain ($XXX$ chain) 
+and the quench from the zero-momentum N\'eel state. 
+The approach extends the Monte Carlo approach developed in Ref.~\cite{alba-2015} to 
+simulate the Generalized Gibbs Ensemble in integrable models. The key idea of the 
+approach is the Monte Carlo sampling of the model Hilbert space with the quench 
+action, equivalently the Diagonal Ensemble, probability distribution given 
+in~\eref{qa-prob}.
+
+The approach is based on the knowledge of the 
+overlaps between the pre-quench N\'eel state $|N\rangle$ and the eigenstates 
+of the model that have been obtained recently~\cite{pozsgay-2014,brockmann-2014,
+brockmann-2014a,brockmann-2014b,brockmann-2014c,piroli-2014}.
+
+Besides the overlaps the method is based on the knowledge of the Hilbert space 
+structure provided by the Bethe ansatz formalism and on the Bethe-Gaudin-Takahashi 
+(BGT) equations. The approach is devised for finite-size systems. Thermodynamic 
+quantities can be extracted using finite-size scaling.
+
+We first focused on the importance of the so-called zero-momentum strings. 
+These corresponds to components of the Bethe wavefunctions corresponding to 
+bound states of many down spins (strings in the Bethe ansatz language) with 
+zero center of mass momentum. These are usually neglected in the quench action 
+approach~\cite{brockmann-2014}. The reason is that zero momentum strings 
+leads to singularities in the overlap formulas, which make extracting the 
+thermodynamic limit tricky. Moreover, it is argued that zero-momentum 
+strings give rise only to scaling corrections to the quench action results, 
+which are unimportant in the thermodynamic limit.
+
+Importantly, one should observe that for a finite chain the vast majority of 
+eigenstates contain zero-momentum strings. More precisely, for the quench from 
+the N\'eel state the fraction of eigenstates with no zero-momentum strings 
+vanish as $\propto L^{-1/2}$.
+
+Moreover, the only eigenstates having non zero N\'eel overlaps (and non zero 
+overlap with the Majumdhar-Ghosh state) are the so-called parity invariant 
+eigenstates. The total number of parity-invariant eigenstates of the Heisenberg 
+spin chain is given in terms of the chain length by a simple combinatorial 
+formula that we provide. We provide similar combinatorial formulas for the 
+total number of parity-invariant eigenstates at fixed number of down spins 
+and fixed string content, i.e., the number of many-spin bound states present in 
+each eigenstates.
+
+In order to understand the importance of the zero-momentum strings we calculated 
+the overlap distribution function including all the eigenstates of the chain for 
+chains up to $L=38$ sites. We excluded the zero-momentum strings.
+
+We focused on some exact sum rules for the local integrals of motion of the 
+$XXX$ chain. Strikingly, the exclusion of the zero momentum strings gives rise 
+to violations of the sum rules. Precisely, we numerically observe that the 
+sum rules exhibit the vanishing behavior $\propto L^{-\frac{1}{2}}$, which 
+reflects the vanishing of the fraction of eigenstates with no zero-momentum 
+strings.
+
+The behavior $\propto L^{-\frac{1}{2}}$ is not generic, but it depends on the 
+pre-quench initial state. We demonstrated that by considering the quench from 
+the Majumdar-Ghosh state. We observed that the sum rule vanish as $1/L$, again 
+reflecting the vanishing as $1/L$ of the fraction of eigenstates with no 
+zero-momentum strings.
+
+We observed that the vast majority of the eigenstates have neglegible overlap 
+with the N\'eel state. This implies that the eigenstates relevant for the 
+quench action are a small fraction of the total number of eingestates having 
+in principle non-zero N\'eel overlap.
+
+Next we presented a Monte Carlo implementation of the quench action method. 
+This is obtained by resampling with the quench action probability measure 
+the Hilbert space of the $XXX$ chain, restricted to the sector of the  Hilbert 
+space with no zero-momentum strings.
+
+This is obtained using a standard Metropolis algorithm. Importantly, we 
+numerically demonstrated that the only consequence of the Hilbert space 
+restriction to strings with finite momentum are scaling corrections $1/L$ 
+to physical observables.
+
+Specifically, we focused on the sum rules for the local conserved quantities 
+of the $XXX$ chain. We numerically observed that, although for finite chains 
+violations of the sum rules are present, these violations decay upon increasing 
+the chain size, and the sum rules are restored in the thermodynamic limit.
+
+Finally, we extracted from the Monte Carlo the BGT root distributions characterizing 
+the quench action saddle point. These are obtained from the BGT roots identifying 
+the $XXX$ chain eigenstates sampled in the Monte Carlo. We observed that, although 
+the finite size gives rise to oscillating scaling corrections, already for 
+relatively small chains with $L=56$ sites, the first BGT root distribution 
+$\rho^*_1(\lambda)$ is in impressive agreement with the analytic result in 
+the thermodynamic limit.
 
@@
 
+\bibitem{bloch-2008}
+I.~Bloch, J.~Dalibard, and W.~Zwerger, Rev.\ Mod.\ Phys.\ {\bf 80},
+885 (2008).
+
+\bibitem{greiner-2002}
+M.~Greiner, O.~Mandel, T. H\"ansch, and I.~Bloch, Nature (London)
+{\bf 419}, 51 (2002).
+
+\bibitem{kinoshita-2006}
+T.~Kinoshita, T.~Wenger, and D.~S.~Weiss, Nature (London) {\bf 440},
+900 (2008).
+
+\bibitem{hofferberth-2007}
+S.~Hofferberth, I.~Lesanovsky, B.~Fischer, T.~Schumm, and J.~Schiedmayer,
+Nature (London) {\bf 449}, 324 (2007).
+
+\bibitem{trotzky-2012}
+S.~Trotzky, Y.-A.~Chen, A.~Flesch, I.~P.~McCulloch, U.~Schollw\"ock,
+J.~Eisert, and I.~Bloch, Nature Phys.\ {\bf 8}, 325 (2012).
+
+\bibitem{gring-2012}
+M.~Gring, M.~Kuhnert, T.~Langen, T.~Kitagawa, B.~Rauer, M.~Schreitl,
+I.~Mazets, D.~A.~Smith, E.~Demler, and J.~Schmiedmayer, Science {\bf 337},
+6100 (2012).
+
+\bibitem{cheneau-2012}
+M.~Cheneau, P.~Barmettler, D.~Poletti, M.~Endres, P.~Schaua, T.~Fukuhara,
+C.~Gross, I.~Bloch, C.~Kollath, and S.~Kuhr, Nature (London) {\bf 481},
+484 (2012).
+
+\bibitem{schneider-2012}
+U.~Schneider, L.~Hackeruller, J.~P.~Ronzheimer, S.~Will, S.~Braun, T.~Best,
+I.~Bloch, E.~Demler, S.~Mandt, D.~Rasch, and A.~Rosch, Nature\ Phys.\
+{\bf 8}, 213 (2012).
+
+\bibitem{kunhert-2013}
+M.~Kuhnert, R.~Geiger, T.~Langen, M.~Gring, B.~Rauer,
+T.~Kitagawa, E.~Demler, D.~Adu Smith, and J.~Schmiedmayer, Phys.\ Rev.\
+Lett.\ {\bf 110}, 090405 (2013).
+
+\bibitem{langen-2013}
+T.~Langen, R.~Geiger, M.~Kuhnert, B.~Rauer, and J.~Schmiedmayer,
+Nature\ Phys.\ {\bf 9}, 640 (2013).
+
+\bibitem{meinert-2013}
+F.~Meinert, M.~J.~Mark, E.~Kirilov, K.~Lauber, P.~Weinmann,
+A.~J.~Daley, and H.-C.~Nagerl, Phys.\ Rev.\ Lett.\ {\bf 111},
+053003 (2013).
+
+\bibitem{fukuhara-2013}
+T.~Fukuhara, A.~Kantian, M.~Endres, M.~Cheneau, P.~Schaua, S.~Hild, C.~Gross,
+U.~Schollw\"ock, T.~Giamarchi, I.~Bloch, and S.~Kuhr, Nature\ Phys.\ {\bf 9},
+235 (2013).
+
+\bibitem{ronzheimer-2013}
+J.~P.~Ronzheimer, M.~Schreiber, S.~Braun, S.~S.~Hodgman, S.~Langer, I.~P.~McCulloch,
+F. Heidrich-Meisner, I.~Bloch, and U.~Schneider, Phys.\ Rev.\ Lett.\ {\bf 110},
+205301 (2013).
+
+\bibitem{braun-2014}
+S.~Braun, M.~Friesdorf, S.~Hodgman, M.~Schreiber, J.~Ronzheimer, A.~Riera, M.~del Rey,
+I.~Bloch, J.~Eisert, and U.~Schneider, PNAS {\bf 112}, 3641 (2015).
+
+\bibitem{langen-2015}
+T.~Langen, S.~Erne, R.~Geiger, B.~Rauer, T.~Schweigier, M.~Kuhnert, W.~Rohringer,
+I.~E.~Mazets, T.~Gasenzer, J.~Schmiedmayer, Science {\bf 348}, 6231 (2015).
+
+\bibitem{polkovnikov-2011}
+A.~Polkovnikov, K.~Sengupta, A~Silva, and M.~Vengalattore, Rev.\ Mod.\ Phys.\
+{\bf 83}, 863 (2011).
+
 \bibitem{calabrese-2014}
@@
 
+\bibitem{brockmann-2014c}
+M.~Brockmann, J.~De~Nardis, B.~Wouters, and J.-S.~Caux, J.\ Phys.\ A:\ 
+Math.\ Theor. {\bf 47}, 145003 (2014).
+
+\bibitem{brockmann-2014b}
+M.~Brockmann, J.\ Stat.\ Mech.\ (2014) P05006.
+
 \bibitem{pozsgay-2014}
@@
 
+\bibitem{quenouille-1949} 
+M.~H.~Quenouille, Ann.\ Math.\ Statist.\ {\bf 20}, 355 (1949).
+
+\bibitem{wolff-2004} 
+U.~Wolff, Comput.\ Phys.\ Comm.\ {\bf 156}, 143 (2004).
+
+\bibitem{piroli-2014}
+L.~Piroli and P.~Calabrese, J.\ Phys.\ A {\bf 47}, 385003 (2014).
+
 \end{thebibliography}

### 2015-09-24 draft/fs_qa_v2.tex
rev-24/09/2015

--- 2015-09-14 draft/fs_qa_v1.tex
@@
 %
+
+It is useful to rewrite~\eref{d-ensemble} as 
+%
+\begin{equation}
+\label{qa-prob}
+\langle{\mathcal O}\rangle=\sum\limits_{\alpha}\rho^{DE}(\alpha)
+\langle\alpha|{\mathcal O}|\alpha\rangle,\quad\textrm{with}\quad 
+\rho^{DE}(\alpha)=\exp(-2\Re{\mathcal E}(\alpha)).
+\end{equation}
+%
+Here $\rho^{DE}(\alpha)$ is a diagonal ensemble density matrix, and ${\mathcal E}(\alpha)
+\equiv-\log\langle\alpha|\Psi_0\rangle$, with $\Re$ denoting the real part.
 
@@
 \label{sec:2}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{N\'eel state overlap}
+\label{sec:2.1}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The string hypothesis: Reduced overlap formulas}
+\subsection{The string hypothesis: Reduced N\'eel overlap formulas}
+\label{sec:2.2}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Thermodynamic limit}
+\subsection{Overlap with the Majumdar-Ghosh state}
+\label{sec:2.3}
+
+The Majumdar-Ghosh state $|MG\rangle$ is defined as 
+%
+\begin{equation}
+\label{mg}
+|MG\rangle\equiv \Big(\frac{|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle}
+{\sqrt{2}}\Big)^{\otimes L/2}. 
+\end{equation}
+%
+The overlap between a generic eigenstate of the $XXX$ chain and the Majumdar-Ghosh 
+state can be obtained from the N\'eel state overlap in Eq.~\eref{neel-ov} 
+as~\cite{pozsgay-2014} 
+%
+\begin{equation}
+\label{mg-ov}
+\langle MG|\{\pm\lambda_j\}_{j=1}^m\rangle=\prod\limits_{j=1}^m\frac{1}{2}
+\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)
+\Big(1+\frac{\lambda_j+i}{\lambda_j-i}\Big)
+\langle N|\{\pm\lambda_j\}_{j=1}^m\rangle
+\end{equation}
+%
+The mutliplicative factor in~\eref{mg-ov}, using the string hypothesis is 
+rewritten as 
+%
+\begin{eqnarray}
+\label{mg-k}
+\fl\prod\limits_{j=1}^m\frac{1}{2}
+\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)
+\Big(1+\frac{\lambda_j+i}{\lambda_j-i}\Big)=\\\nonumber\qquad
+2^m\prod\limits_{j=1}^m\prod\limits_{\ell=1}^{\tilde s_j}
+\lambda_{j;\ell}^{1+(-1)^j}(\lambda^2_{j;\ell}+j^2)\prod\limits_{k=0}^{\lfloor 
+j/2\rfloor}\Big[\lambda_{j;\ell}^2+\Big(2k+\frac{1-(-1)^j}{2}\Big)^2\Big]^{-2}
+\end{eqnarray}
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The N\'eel overlap in the thermodynamic limit}
+\label{sec:2.4}
 
@@
 \label{qa-d-ensemble}
-\fl
-\quad\langle{\mathcal O}\rangle=\int{\mathcal D}\pmb{\rho}(\lambda)
-\exp\Big(2\Re\log\langle\Psi_0|\pmb{\rho}(\lambda)\rangle 
-+S_{YY}(\pmb{\rho})\Big)\langle\pmb{\rho}(\lambda)|{\mathcal O}|\pmb{\rho}
-(\lambda)\rangle
-\end{equation}
-%
-Note that in~\eref{qa-d-ensemble} it is assumed that in the thermodynamic limit 
-the eigenstate expectation values $\langle\alpha|{\mathcal O}|\alpha\rangle$ 
-become smooth functionals  $\langle\pmb{\rho}(\lambda)|{\mathcal O}|\pmb{\rho}
-(\lambda)\rangle$ of the root distributions $\pmb{\rho}$.
-
-Similarly, in~\eref{qa-d-ensemble} $\langle\Psi_0|\pmb{\rho}(\lambda)\rangle$ 
-denotes the Bethe states overlap density with the prequench state $\Psi_0$.
-
-The strategy is to evaluate the functional integral in~\eref{qa-d-ensemble} 
-using the saddle point approximation.
-
-One has then to minimize the functional ${\mathcal S}(\pmb{\rho})$ defined 
-as 
-%
-\begin{equation}
-L{\mathcal S}(\pmb{\rho})\equiv 2\Re\log\langle\pmb{\rho}|\Psi_0
-\rangle+S_{YY}(\pmb{\rho}(\lambda)). 
-\end{equation}
-% 
-under the constraint that the BGT equations hold. For the quench with initial 
-state the N\'eel state the resulting saddle point root distributions 
-$\rho_n^*(\lambda)$ can be obtained analytically. The first few root distributions 
-are given as 
+\quad\langle{\mathcal O}\rangle=\int{\mathcal D}\pmb{\rho}\exp\Big[2\Re\log\langle
+\Psi_0|\pmb{\rho}\rangle +S_{YY}(\pmb{\rho})\Big]\langle\pmb{\rho}|{\mathcal O}|
+\pmb{\rho}\rangle
+\end{equation}
+%
+Here it is assumed that in the thermodynamic limit the eigenstate expectation 
+values $\langle\alpha|{\mathcal O}|\alpha\rangle$ (cf.~\eref{d-ensemble}) 
+and the overlaps $\langle\Psi_0|\pmb{\rho}\rangle$ become smooth functionals 
+of the root distributions $\pmb{\rho}$.
+
+The functional integral in~\eref{qa-d-ensemble} can be evaluated in the limit 
+$L\to\infty$ using the saddle point approximation. One has to minimize the 
+functional ${\mathcal F}(\pmb{\rho})$ defined as 
+%
+\begin{equation}
+L{\mathcal F}(\pmb{\rho})\equiv 2\Re\log\langle\pmb{\rho}|\Psi_0
+\rangle+S_{YY}(\pmb{\rho}(\lambda))  
+\end{equation}
+% 
+with respect to $\pmb{\rho}$, i.e., solving $\delta{\mathcal F}(\pmb{\rho})/\delta
+\pmb{\rho}|_{\pmb{\rho}=\pmb{\rho^*}}=0$, under the constraint that the thermodynamic BGT 
+equations~\eref{bgt-th} hold. Finally, one obtains from~\eref{qa-d-ensemble} that in the 
+thermodynamic limit 
+%
+\begin{equation}
+\label{obs-th}
+\langle{\mathcal O}\rangle=\langle\pmb{\rho^*}|{\mathcal O}|\pmb{\rho^*}\rangle. 
+\end{equation}
+%
+Remarkably, for the quench with initial state the N\'eel state $|\Psi_0\rangle=|N\rangle$ the 
+saddle point root distributions ${\rho_n^*(\lambda)}_{n=1}^\infty$ can be obtained 
+analytically~\cite{brockmann-2014}. The first few are given as 
 %
 \begin{eqnarray}
-\label{rho_sp}
+\label{rho1-sp}
 \fl\quad\rho^*_1(\lambda)=\frac{8(4+\lambda^2)}{\pi(19+3\lambda^2)(1+6\lambda^2+
-\lambda^4)}\\
+\lambda^4)}\\\label{rho2-sp}
 \fl\quad\rho_2^*(\lambda)=\frac{8\lambda^2(9+\lambda^2)(4+3\lambda^2)}{\pi(2+\lambda^2)
-(16+14\lambda^2+\lambda^4)(256+132\lambda^2+9\lambda^4)}\\
-\fl\quad\rho_3^*=\frac{8(1+\lambda^2)^2(5+\lambda^2)(16+\lambda^2)(21+\lambda^2)}
+(16+14\lambda^2+\lambda^4)(256+132\lambda^2+9\lambda^4)}\\\label{rho3-sp}
+\fl\quad\rho_3^*(\lambda)=\frac{8(1+\lambda^2)^2(5+\lambda^2)(16+\lambda^2)(21+\lambda^2)}
 {\pi(19+3\lambda^2)(9+624\lambda^2+262\lambda^4+32\lambda^6+\lambda^8)
@@
 %
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{N\'eel overlaps: The role of the zero-momentum strings Bethe states}
+\label{sec:5}
+
+In this section we discuss generic features of the overlaps between the 
+eigenstates (Bethe states) of the Heisenberg spin chain and the N\'eel state 
+(cf.~\eref{neel}). We exploit the Bethe ansatz solution of the chain (see 
+section~\ref{sec:1}) as well as exact results for the N\'eel overlaps (see 
+section~\ref{sec:2}). We focus on finite chains with $L\lesssim 40$ sites, 
+considering, for any $L$, the full Hilbert space of the chain. 
+The Bethe states having, in principle, non zero N\'eel overlap are the 
+so-called parity-invariant Bethe states (see section~\ref{sec:2}). We 
+denote their total number as $Z_{Neel}$. Crucially, here we restrict 
+ourselves to the subset of parity-invariant Bethe states corresponding 
+to solutions of the Bethe-Gaudin-Takahashi (BGT) equations~\eref{bgt-eq} 
+that do not contain zero-momentum strings. We denote the total number of 
+these eigenstates as $\widetilde Z_{Neel}$. Both $Z_{Neel}$ and $\widetilde 
+Z_{Neel}$ are given in terms of the chain length $L$ by simple combinatorial 
+formulas that we provide.
 
@@
 \end{center}
-\caption{ N\'eel state overlaps in the Heisenberg spin chain. (a) 
- The N\'eel state overlaps with the eigenstates of the Heisenberg 
- spin chain: Squared overlaps $|\langle\lambda|N\rangle|^2$ plotted 
- as a function of the eigenstates energy density $E/L$. Here $|\lambda
- \rangle$ denotes the generic eigenstate of the Heisenberg spin chain. 
- The data are for chains with length $26\le L\le 38$. The data are 
- obtained from a full scanning of the chains Hilbert space. 
- Eigenstates containing strings with zero-momentum components 
- are escluded. The overlaps decay exponentially with the chain size. 
- (b) Histograms of $-2\log|\langle\lambda|N\rangle|/L$. Different 
- histograms are for different chain sizes. The histogram bin width 
- is $\sim 2/L$. The $y$-axis is rescaled by a factor $10^5$ for 
- convenience. Note the peaking of the histograms around 
- $-2\log|\langle\lambda|N\rangle|\sim 0.5$ in the thermodynamic 
- limit {\bf really??}. The dotted vertical line is the expected 
- Quench-Action result in the thermodynamic limit.  
+\caption{ N\'eel overlaps with the eigenstates of the Heisenberg spin 
+ chain: Numerical results obtained from the full scanning of the chain 
+ Hilbert space. Eigenstates corresponding to zero-momentum strings are 
+ escluded. (a) Squared overlaps $|\langle\lambda|N\rangle|^2$ plotted as 
+ function of the eigenstates energy density $E/L$. Here $|\lambda\rangle$ 
+ denotes the generic eigenstate. The data are for chains with length $26
+ \le L\le 38$. The inset is to highlight the exponential decay as a 
+ function of $E/L$. Note the logarithmic scale on the $y$ axis. (b) 
+ Overlap distribution function: Histograms of $-2\log\langle\lambda|N\rangle/L$. 
+ The $y$-axis is rescaled by a factor $10^5$ for convenience. The dash-dotted 
+ and dashed vertical lines are the N\'eel overlaps with the $XXX$ chain ground 
+ state and the ferromagnetic state, respectively. The dotted line (see 
+ the arrow) is the result obtained using the quench action approach. 
 }
-\label{fig0:N-ov-overview}
+\label{fig0:neel-ov}
 \end{figure}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overlap sum rules: the role of the zero-momentum strings}
-\label{ov-sum-rules}
+Interestingly, the fraction of eigenstates with no zero-momentum strings, i.e.,  
+$\widetilde Z_{Neel}/Z_{Neel}$, is vanishing as $L^{-1/2}$ in the thermodynamic 
+limit, meaning that zero-momentum strings eigenstates are dominant, at least 
+in number, for large chains. This has dramatic consequences, for instance, at 
+the level of the overlap sum rules for the local conservation laws of the model. 
+Precisely, although the sum rules are fixed by the initial (N\'eel) state 
+expectation value of the local charges, we observe striking violations for 
+any finite chain. Moreover, all the sum rules exhibit vanishing behavior as 
+$L^{-1/2}$ upon increasing the chain size, reflecting the same vanishing behavior 
+as $\widetilde Z_{Neel}/Z_{Neel}$. A similar scenario holds for the overlaps with 
+the Majumdar-Ghosh state, where, however, excluding the zero-momentum strings leads 
+to a $1/L$ behavior. This demonstrates that for finite chains the physical effects 
+of zero-momentum strings eigenstates are not negligible.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{N\'eel overlap distribution function: Overview}
+\label{sec:5.1}
+
+Here we overview the Bethe ansatz results for the N\'eel overlaps with the 
+eigenstates of the $XXX$ chain. The total number of partiy-invariant 
+eigenstates $Z_{Neel}$ having, in principle, non-zero N\'eel overlap is given 
+as 
+%
+\begin{equation}
+\label{zneel1}
+Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1, 
+\end{equation}
+%
+with $B(n,m)\equiv n!/(m!(n-m)!)$ the Newton binomial. The proof of~\eref{zneel1} 
+is obtained by counting all the parity-invariant BGT quantum number configurations, 
+and it is reported in~\ref{app-1}. Note that $Z_{Neel}$ provides only an upper 
+bound for the number of eigenstates with non-zero N\'eel overlap, as it is clear 
+from the exact diagonalization results shown in Table~\ref{table:neel}. This is 
+because parity-invariant eigenstates with a single zero-momentum even-length 
+string, which are included in~\eref{zneel1}, have identically zero N\'eel 
+overlap~\cite{brockmann-2014}. This is not related to the symmetries of the N\'eel 
+state, but to the ``accidental'' vanishing of the prefactor in the overlap 
+formula~\eref{neel-ov}. Finally, after excluding the zero-momentum strings 
+eigenstates, the total number of remaining eigenstates $\widetilde Z_{Neel}$, 
+which are the ones considered here, is given as (see~\ref{app-2} for the proof) 
+%
+\begin{equation}
+\label{ztilde}
+\widetilde Z_{Neel}=B\Big(\frac{L}{2},\frac{L}{4}\Big).
+\end{equation}
+%
+An overview of generic features of the overlaps is given in Figure~\ref{fig0:neel-ov} 
+(a) plotting the squared N\'eel overlaps $|\langle\lambda|N\rangle|^2$ with the $XXX$ 
+chain eigenstates $|\lambda\rangle$ versus the energy density $E/L$. The figure shows 
+results for chains with $26\le L\le 38$ sites. The data are obtained by generating all 
+the relevant parity-invariant BGT quantum numbers, and solving the associated BGT 
+equations~\eref{bgt-eq}, to obtain the rapidities of $XXX$ chain eigenstates. The 
+N\'eel overlaps are calculated numerically using~\eref{neel-ov}. Note that for $L=38$ 
+from~\eref{ztilde} the total number of overlap shown in the Figure is $\widetilde Z_{Neel}
+\sim 10^5$.
+
+Clearly, the overlaps decay exponentially as a function of $L$, as expected. Moreover, 
+at each finite $L$ a rapid decay as a function of $E/L$ is observed. The inset of 
+Figure~\ref{fig0:neel-ov} (a) suggests that the decay is exponential. Complementary 
+information about the overlaps is shown in Figure~\ref{fig0:neel-ov} (b) plotting the 
+histograms of $\kappa\equiv-2\log|\langle\lambda|N\rangle|/L$ (overlap distribution 
+function). Larger values of $\kappa$, correspond to a faster decay with $L$ of the 
+overlaps. The factor $1/L$ in the definition takes into account that the N\'eel 
+overlaps vanish exponentially as $|\langle\lambda|N\rangle|^2\propto e^{-\kappa L}$ in 
+the thermodynamic limit. Note that $\kappa$ is the driving term in the quench action 
+approach (cf~\eref{neel-ov-th}). As expected, from Figure~\ref{fig0:neel-ov} (b) one 
+has that the majority of the $XXX$ chain eigenstates give small N\'eel overlap (note 
+the maximum at $\kappa\sim 0.5$). Interestingly, the data suggest that with 
+$0.18\lesssim\kappa\lesssim0.7$. The vertical dash-dotted line in the figure is 
+the $\kappa$ obtained from the N\'eel overlap of the ground state of the $XXX$ 
+chain in the thermodynamic limit. This is derived using the ground state root 
+distribution $\rho_1(\lambda)\propto1/\cosh(\pi\lambda)$ and~\eref{neel-ov-th}. 
+On the other hand, the vertical dashed line denotes the N\'eel overlap $\sim 2/B(L,L/2)$ 
+of the $S_z=0$ component of the ferromagnetic multiplet, which is at the top of the
+chain energy spectrum. Finally, the vertical dotted line in Figure~\ref{fig0:neel-ov} 
+(b) shows the quench action result for $\kappa$ in the thermodynamic limit. This is 
+obtained by using~\eref{neel-ov-th} and the saddle point root distributions $\rho_n^*$ 
+(cf.~\eref{rho1-sp}-\eref{rho3-sp} for the results up to $n=3$). Note that $\kappa$ 
+does not coincide with the peak of the overlap distribution function, as expected, 
+due to the effect of the driving term~\eref{neel-ov-th} in the quench action approach.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{N\'eel overlap sum rules}
+\label{sec:5.2}
 
@@
 \end{center}
-\caption{ Overlap sum rules for the Neel state: The role of the zero-momentum 
- strings. (a) The overlap sum rule $\sum_{\lambda}|\langle\lambda|N\rangle|^2=1$, 
- with $|N\rangle$ the Neel state and $|\lambda\rangle$ the eigenstates  of 
- the $XXX$ spin chain. The $x$-axis shows $1/L$, with $L$ the chain length. 
- The circles are Bethe ansatz results for chains up to $L=36$. The results 
- are obtained via a full scanning of the chain Hilbert space. Only the 
- eigenstates with no zero-momentum strings are considered. The dash-dotted 
- line is a fit to $A/L^{1/2}+B/L$, with $A,B$ fitting parameters. Inset: 
- The same data as in the main Figure plotted versus $1/L^{1/2}$. (b) 
- The same as in (a) for the sum rule $\sum_{\lambda}|\langle
- \lambda|N\rangle|^2e(\lambda)=1/2$, with $e(\lambda)$  the 
- eigenstates energy density. 
+\caption{Overlap sum rules for the N\'eel state $|N\rangle$: The role of 
+ the zero-momentum strings. (a) The overlap sum rule $\sum_{\lambda}|
+ \langle\lambda|N\rangle|^2=1$. Here $|\lambda\rangle$ are the eigenstates  
+ of the $XXX$ chain. The $x$-axis shows the inverse chain length $1/L$. 
+ The circles are Bethe ansatz results for chains up to $L=38$. The data  
+ are obtained by  a full scanning of the chain Hilbert space. Eigenstates  
+ corresponding to zero-momentum strings are excluded. The dotted line is 
+ the expected result at any $L$. The data are compatible with a vanishing 
+ behavior in the thermodynamic limit. The dash-dotted line is a fit to 
+ $A/L^{1/2}+B/L$, with $A,B$ fitting parameters. Inset: The same data as 
+ in the main Figure now plotted versus $1/L^{1/2}$. (b) 
+ The same as in (a) for the energy sum rule $\sum_{\lambda}|\langle
+ \lambda|N\rangle|^2Q_2(\lambda)=Q_2^{(0)}$, with $Q_2(\lambda)$ the 
+ energy of the eigenstate $|\lambda\rangle$ and $Q_2^{(0)}/L=-1/2$ the 
+ N\'eel state energy density (dotted line in the Figure). 
 }
-\label{fig2-neel-sr}
+\label{fig1:neel-sr}
 \end{figure}
@@
 
-In this section we investigate the role of the zero-momentum strings. We focus on 
-conserved quantities sum rules. Specifically, given a generic conserved quantity 
-(charge) $\hat Q$ we consider the trivial identity  
-%
-\begin{equation}
-\label{sum}
-Q_0\equiv\langle\Psi_0|\hat Q|\Psi_0\rangle=\sum\limits_{\lambda}|\langle\lambda|
-\Psi_0\rangle|^2Q_\lambda, 
-\end{equation}
-%
-where $Q_0$ is the charge expectation values over the initial state $|\Psi_0
-\rangle$, $|\lambda\rangle$ denotes the generic eigenstate of the $XXX$ chain, 
-and $Q_\lambda$ is the charge eigenvalue over the eigenstate.
-
-Here we restrict ourselves to the cases with $\hat Q=\mathbb{I}$ and $\hat 
-Q={\mathcal H}$, considering both the case with $|\Psi\rangle=|N\rangle$ and 
-$|\Psi_0\rangle=|MG\rangle$.
-
-For the N\'eel state, for any finite $L$ Eq.~\eref{sum} gives $Q_0=1,-1/2$ for 
-$\hat{Q}=\mathbb{I}$ and $\hat Q={\mathcal H}$, respectively.
-
-Figure~\ref{fig2-neel-sr} plots the numerical results obtained via a full 
-scanning of the Hilbert space of the Heisenberg chain.
-
-Precisely, the numerical data are obtained by generating all the possible string 
-contents ${\mathcal S}$ compatible with the parity-invariance constraint
-
-Panel (a) and (b) in the 
-Figure plots the sum rule~\eref{sum} for $\hat Q=\mathbb{I}$ and $\hat Q={\mathcal 
-H}$, respectively. The circles are obtained considering all the eigenstates of the 
-Heisenberg spin chain with $L$ sites, excluding eigenstates containing 
-zero-momentum strings.
-
-The total number of eigenstates $\widetilde Z_{Neel}$ containing no zero-momentum 
-strings is given as 
-%
-\begin{equation}
-\label{ztilde}
-\widetilde Z_{Neel}=B\Big(\frac{L}{2},\frac{L}{4}\Big).
-\end{equation}
-%
-The proof of\eref{ztilde} is reported in~\ref{app-2}.
+Here we illustrate the effect of the zero-momentum strings eigenstates on the 
+N\'eel overlap sum rules. We focus on the ``trivial'' sum rule, i.e., the 
+normalization of the N\'eel state  
+%
+\begin{equation}
+\label{sr-trivial}
+\langle N|N\rangle=\sum\limits_{\lambda}|\langle\lambda|N\rangle|^2=1. 
+\end{equation}
+%
+We also consider the N\'eel expectation value of the local conserved charge 
+$Q_n$ of the $XXX$ chain (see subsection~\ref{sec:1.5}), which provide 
+the additional sum rules
+%
+\begin{equation}
+\label{sr-charge}
+Q_n^{(0)}=\langle N|Q_n|N\rangle=\sum\limits_{\lambda}|\langle\lambda|N\rangle|^2
+Q_{n}(\lambda)\quad\textrm{with}\quad n\in\mathbb{N}, 
+\end{equation}
+%
+where $Q_n(\lambda)$ are the charges eigenvalues over the generic Bethe state 
+$|\lambda\rangle$ (cf.~\eref{qngnk} and~\eref{gnk}). 
+In both~\eref{sr-trivial} and~\eref{sr-charge} the sum are restricted to the 
+eigenstates with containing no zero-momentum strings. 
+In~\eref{sr-charge} $Q_n^{(0)}$ is the charge expectation value over the initial 
+state, i.e., the N\'eel state, which has been calculated in Ref.~\cite{fagotti-2013}. 
+Due to the locality of $Q_n$, the translational invariance of the initial 
+state, and the periodic boundary conditions, the density $Q_n^{(0)}/L$ does 
+not depend on the chain size. For the N\'eel state, $Q_n^{(0)}$ can be calculated 
+directly in the thermodynamic limit using~\eref{q0-th} and the root distributions 
+$\pmb{\rho}^*$ (cf.~\eref{rho1-sp}-\eref{rho3-sp}).
+
+The sum rules~\eref{sr-trivial} and~\eref{sr-charge} (for $n=2$, i.e., the energy 
+sum rule), are shown in Figure~\ref{fig1:neel-sr} (a) and (b), respectively. 
+Note that $Q^{(0)}_2/L=-1/2$ in~\eref{sr-charge} (horizonthal dotted line in 
+Figure~\ref{fig1:neel-sr} (b)). 
+The circles in Figure~\ref{fig1:neel-sr} (a) are the Bethe ansatz results excluding 
+the zero momentum strings. The data are the same as in Figure~\ref{fig0:neel-ov}. 
+The sum rules are plotted against the inverse chain length $1/L$, for $L\le 38$.
+
+Clearly, both the sum rules are violated, due to the exclusion of the to zero-momentum 
+strings. Moreover, in both Figure~\ref{fig1:neel-sr} (a) and (b) the data suggest a 
+vanishing behavior upon increasing $L$. The dash-dotted lines in the Figures are fits to  
+$A/L^{1/2}+B/L$, with $A,B$ fitting parameters. Interestingly, the behavior as $\propto 
+L^{-1/2}$ of the sum rules reflects that of the fraction of non-zero momentum string 
+eigenstates in the thermodynamic limit $\widetilde Z_{Neel}/Z_{Neel}$. Specifically, 
+from~\eref{zneel1} and~\eref{ztilde} it is straightforward to derive that in the 
+thermodynamic limit 
+%
+\begin{equation}
+\label{beh}
+\frac{\widetilde Z_{Neel}}{Z_{Neel}}\propto\frac{4}{\sqrt{\pi L}}. 
+\end{equation}
+%
 
@@
 \end{center}
-\caption{ Overlap sum rules for the Majumdar-Ghosh (MG) state. (a) The 
- overlap sum rule $\sum_{\lambda}|\langle\lambda|MG\rangle|^2=1$, 
- with $|MG\rangle$ the Majumdar-Ghosh state and $|\lambda\rangle$ 
- the eigenstates  of the $XXX$ spin chain. The $x$-axis shows $1/L$, 
- with $L$ the chain length. The circles are Bethe ansatz results for 
- chains up to $L=36$. The results are obtained via a full scanning of 
- the chain Hilbert space. Only the eigenstates with no zero-momentum 
- strings are considered. The dash-dotted line is a fit to $A/L+B/L^2$, 
- with $A,B$ fitting parameters. (b) The same as in (a) for the sum 
- rule $\sum_{\lambda}|\langle\lambda|MG\rangle|^2e(\lambda)=
- 2/3$, with $e(\lambda)\equiv E/L$  the eigenstates energy density. 
+\caption{Overlap sum rules for the Majumdar-Ghosh state $|MG\rangle$: 
+ The role of the zero-momentum strings. (a) The sum rule $\sum_{\lambda}|
+ \langle\lambda|MG\rangle|^2=1$, with $|\lambda\rangle$ the eigenstates   
+ of the $XXX$ chain. The $x$-axis plots the inverse chain length $1/L$. 
+ The circles are Bethe ansatz results for chains up to $L=32$. The results 
+ are obtained by a full scanning of the chain Hilbert space. Eigenstates 
+ corresponding to zero-momentum strings are excluded. The dash-dotted line 
+ is a fit to $A/L+B/L^2$, with $A,B$ fitting parameters. (b) The same as 
+ in (a) for the energy sum rule $\sum_{\lambda}|\langle\lambda|MG\rangle
+ |^2Q_2(\lambda)=Q_2^{(0)}$, with $Q_2(\lambda)$  the energy of $|\lambda
+ \rangle$ and $Q_2^{(0)}/L=-2/3$ the Majumdar-Ghosh energy density (dotted 
+ line in the Figure). 
 }
-\label{fig3-dimer-sr}
+\label{fig2:dimer-sr}
 \end{figure}
@@
 
-The largest chain size considered is $L=36$. The data are plotted versus $1/L$.
-
-Interestingly, both the sum rules (panels (a)(b)) are not saturated, as expected 
-since the eigenstates corresponding to zero-momentum strings are excluded in the 
-sum in the right-hand-side in~\eref{sum}.
-
-Interestingly, both sum rules exhibit vanishing behavior upon increasing the 
-chain size. The dash-dotted lines in the Figures are fits to the behavior 
-$A/L^{1/2}+B/L$, with $A,B$ fitting parameters, and perfectly describe the 
-behavior of the data.
-
-The vanishing behavior as $\propto 1/L^{1/2}$ of the sum rules reflects the vanishing 
-of the fraction of non-zero momentum string eigenstates in the thermodynamic limit ad 
-%
-\begin{equation}
-\label{beh}
-\frac{\widetilde Z_{Neel}}{Z_{Neel}}\propto\frac{4}{\sqrt{\pi L}}, 
-\end{equation}
-% 
-with $Z_{Neel}$ being the total number of eigenstates corresponding to parity 
-invariant BGT quantum numbers configurations.
-
-One should observe that the asymptotic, i.e., at large $L$, behavior~\eref{beh} 
-is not generic, meaning that different initial states $|\Psi_0\rangle$ might 
-give different behaviors.
-
-This is illustrated in Figure~\ref{fig3-dimer-sr}, focusing on the Majumdar-Ghosh 
-(MG) state. Panels (a) and (b) plot the sum rules with $\hat Q=\mathbb{I}$ and 
-$\hat Q={\mathcal H}$ (same as in Figure~\ref{fig2-neel-sr}). As for the N\'eel 
-state only eigenstates containing no zero-momentum strings are consdidered. 
-Note that their number $\widetilde Z_{MG}$ (see~\ref{app-2}) is now given as 
-%
-\begin{equation}
+It is interesting to observe that the large $L$ behavior as $L^{-1/2}$  is not 
+generic, meaning that it depends on the initial state $|\Psi_0\rangle$. This is 
+illustrated in Figure~\ref{fig2:dimer-sr}, focusing on the Majumdar-Ghosh (MG) 
+state. As for the N\'eel state, only parity-invariant eigenstates can have 
+non-zero Majumdar-Ghosh overlap. Their total number $Z_{MG}$ (cf.~\eref{p-inv-mg}) 
+is given as 
+%
+\begin{equation}
+\label{mg1}
+Z_{MG}=B\Big(\frac{L}{2}-1,\frac{L}{4}-1\Big)+B\Big(\frac{L}{2}-1,
+\frac{L}{4}-1\Big). 
+\end{equation}
+%
+Note that at any size $L$ one has $Z_{MG}<Z_{Neel}$. This is due to the fact that 
+the Majumdar-Ghosh state is invariant under $SU(2)$ rotations, since it contains 
+only spin singlets, and it has non-zero overlap only with the $S^z_T=0$ sector 
+of the $XXX$ chain spectrum. The total number of parity-invariant eigenstates 
+that contain no zero-momentum strings $\widetilde Z_{MG}$ is instead (
+cf.~\eref{mg-fi})
+%
+\begin{equation}
+\label{mg2}
 \widetilde Z_{MG}=B\Big(\frac{L}{2},\frac{L}{4}\Big)-B\Big(\frac{L}{2},
@@
 %
-Similar to Figure~\ref{fig2-neel-sr}, due to the exclusion of the zero-momentum 
-strings, the saturation rules exhibit vanishing behavior in the thermodynamic 
-limit. However, in contrast with the N\'eel case (see Figure~\ref{fig2-neel-sr}), 
-one has the behavior $Q_0\sim 1/L$, as confirmed by the fits (dash-dotted lines 
-in Figure~\ref{fig3-dimer-sr}).
-
-Similar to the N\'eel case this reflects the same vanishing behavior of the 
-eigenstates containing no zero-momentum strings $\widetilde Z_{MG}/Z_{MG}$ as 
+Panels (a) and (b) in Figure~\ref{fig2:dimer-sr} plot the sum rules~\eref{sr-trivial} 
+and~\eref{sr-charge} for the Majumdar-Ghosh state. The data are obtained using the 
+analytic results for the overlaps in subsection~\ref{sec:2.3}. The expected value for 
+the energy density sum rule is $Q_2^{(0)}=-2/3$ (horizonthal dotted line in 
+Figure~\ref{fig2:dimer-sr} (b)). Similar to Figure~\ref{fig1:neel-sr}, due to the exclusion 
+of the zero-momentum strings, the sum rules are violated, exhibiting vanishing behavior in 
+the thermodynamic limit. However, in contrast with the N\'eel case, one has the behavior 
+as $1/L$, as confirmed by the fits (dash-dotted lines in Figure~\ref{fig2:dimer-sr}). 
+Similar to the N\'eel case, the vanishing of the sum rules in the thermodynamic limit 
+reflects the behavior of $\widetilde Z_{MG}/Z_{MG}$ as (see~\eref{mg1} and~\eref{mg2})
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Monte Carlo implementation of the Quench-Action approach}
-\label{mcqa-sec}
-
-For the finite-size Heisenberg spin chain the Quench-Action expectation 
-values can be obtained by sampling the eigenstates of the chain using 
-Monte Carlo. One starts with an eigenstate of the $XXX$ chain with 
-$N_{\infty}$ infinite rapidities and $M\equiv L/2-N_\infty$ finite ones. 
-The state is identified by a parity-invariant Bethe quantum number 
-configuration ${\mathcal C}$ and by the corresponding parity-invariant 
-rapidities $\{\lambda\}$ as $|\lambda\rangle$. The string content 
-associated with the finite rapidities is denoted as ${\mathcal S}$. The Monte 
-Carlo procedure consists of four steps as follows: 
+\section{Monte Carlo implementation of the quench action approach}
+\label{sec6:mcqa}
+
+Here, by generalizing the results presented in Ref.~\cite{alba-2015}, we present 
+a Monte Carlo implementation of the quench action approach for N\'eel quench in 
+the $XXX$ chain. The key idea is to sample the eigenstates of the finite-size $XXX$ 
+chain with the diagonal ensemble, equivalently the quench action, probability 
+distribution, given in~\eref{qa-d-ensemble}. Importantly, we consider a truncated  
+Hilbert space, restricting ourselves to the eigenstates corresponding to 
+solutions of the BGT equations with no zero-momentum strings. Our main physical 
+result is that, despite this restriction, the remaining eigenstates contain enough 
+information to correctly reproduce the post-quench thermodynamic behavior of 
+the $XXX$ chain.
+
+In subsection~\ref{sec:6.1} we detail the Monte Carlo algorithm. In 
+subsection~\ref{sec:6.2} we numerically demonstrate that after the Monte Carlo 
+``resampling'' the N\'eel sum rules~\eref{sr-charge} are restored, in the 
+thermodynamic limit. The Hilbert space truncation is reflected only in 
+$\propto 1/L$ finite-size corrections to the sum rules. In the Bethe ansatz language 
+our results mean that the eigenstates sampled by the Monte Carlo approach the 
+quench action representative state in the thermodynamic limit. This is explicitly 
+demonstrated here by numerically extracting the quench action root distributions 
+$\pmb{\rho}^*$ (cf.~\eref{rho1-sp}-\eref{rho3-sp}). The numerical results are found 
+in remarkable agreement with the quench action.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The quench action Monte Carlo algorithm}
+\label{sec:6.1}
+
+The Monte Carlo procedure starts with a randomly selected parity-invariant eigenstate 
+(Bethe state) of the $XXX$ chain, in the sector with zero magnetization, i.e., $M=L/2$ 
+particles. Due to the fact that the N\'eel state is not invariant under $SU(2)$ rotations, 
+in order to characterize the Bethe states one has to specify the number $N_{\infty}$ of 
+infinite rapidities. The number of remaining particles corresponding to finite roots 
+$M'$ is $M'=L/2-N_\infty$. The state is identified by a parity-invariant BGT quantum number 
+configuration that we denote as ${\mathcal C}$. Due to the parity-invariance and the 
+zero-momentum strings being excluded, ${\mathcal C}$ is identified by the number $m'$ 
+of parity-invariant rapidities $\{\pm\lambda_j\}_{j=1}^{m'}$. The string content 
+associated with the state is denoted as $\widetilde{\mathcal S}=\{\tilde s_1,\dots,
+\tilde s_{m'}\}$, where $\tilde s_n$ is the number of pairs of $n$-strings. The Monte 
+Carlo procedure generates a new parity-invariant eigenstate of the $XXX$ chain, and 
+it consists of four steps: 
 %
 \begin{enumerate}
-\item[\circled{1}] Choose a new number of finite rapidities $M'$ with 
-probability
+\item[\circled{1}] Choose a new number of finite-momentum particles $M''$ and of 
+parity-invariant rapidity pairs $m''\equiv M''/2$ with 
+probability ${\mathcal P}(M'')$ as 
 %
@@
 \label{PM}
-{\mathcal P}(M')=\frac{\widetilde Z'_{Neel}(L,M')}{\widetilde{Z}_{Neel}(L)}. 
-\end{equation}
-%
-\item[\circled{2}] Choose a new a new string content ${\mathcal S}'\equiv
-\{s_1',\dots,s_{M'}'\}$ with probability ${\mathcal P}'(M',{\mathcal S}')$
+{\mathcal P}(M'')=\frac{\widetilde Z'_{Neel}(L,M'')}
+{\widetilde{Z}_{Neel}(L)}, 
+\end{equation}
+%
+where $\widetilde Z_{Neel}(L)$ is defined in~\eref{ztilde}, and $\widetilde 
+Z'_{Neel}$ is the number of parity-invariant eigenstates with no zero-momentum 
+strings in the sector with fixed particle number $M''$  (cf.~\eref{neel-fi} for 
+the precise expression). 
+\item[\circled{2}] Choose a new string content $\widetilde{\mathcal S}'\equiv
+\{\tilde s_1',\dots,\tilde s'_{m''}\}$ with probability ${\mathcal P}'(M'',
+\widetilde{\mathcal S}')$
 %
@@
 \label{PS}
-{\mathcal P}'(M',{\mathcal S}')=\frac{1}{\widetilde Z'_{Neel}(L,M')}
-\prod_{n=1}^{M'}B\Big(\frac{L}{2}-\frac{1}{2}\sum\limits_{m=1}^{M'}t_{nm}
-s'_m,s'_n\Big).
-\end{equation}
-%
+{\mathcal P}'(M'',\widetilde{\mathcal S}')=\frac{1}{\widetilde Z'_{Neel}
+(L,M'')}\prod_{n=1}^{m''}B\Big(\frac{L}{2}-\sum\limits_{l=1}^{
+m''}t_{nl}\tilde s'_l,\tilde s'_n\Big), 
+\end{equation}
+%
+where the matrix $t_{nl}$ is defined in~\eref{bt-qn-bound}.
 \item[\circled{3}] Generate a new parity-invariant quantum number configuration 
-${\mathcal C}'$ compatible with the ${\mathcal  S}'$ obtained in step $\circled{2}$. 
-Solve the corresponding BGT equations~\eref{bt_eq}, finding a new eigenstate 
-$|\lambda'\rangle$. 
-\item[\circled{4}] Calculate the overlap $\langle\lambda'|N\rangle$ between the 
-new eigenstate and the N\'eel state and accept the eigenstate with the Metropolis 
+${\mathcal C}'$ compatible with the $\widetilde {\mathcal  S}'$ obtained in step 
+$\circled{2}$. Solve the corresponding BGT equations~\eref{bgt-eq}, finding the 
+rapidities $\{\pm\lambda'_j\}_{j=1}^{m''}$ of the new parity-invariant eigenstate. 
+\item[\circled{4}] Calculate the N\'eel overlap $\langle\{\pm\lambda'_j\}_{j=1}^{m''}
+|N\rangle$ for the new eigenstate,  using~\eref{neel-ov}~\eref{red-G+}~\eref{red-G-} 
+and~\eref{neel-k}. Accept the new eigenstate with the quench action Metropolis 
 probability 
@@
 %
-where ${\mathcal E}'\equiv-\log\langle\lambda'|N\rangle$, similarly for 
-${\mathcal E}$, and $\Re$ denotes the real part. 
+where ${\mathcal E}'\equiv-\log\langle\{\pm\lambda'_j\}_{j=1}^{m''}
+|N\rangle$, ${\mathcal E}\equiv-\log\langle\{\pm\lambda_j\}_{j=1}^{m''}
+|N\rangle$, and $\Re$ denoting the real part. 
 \end{enumerate}
 %
-
-Afte some necessary thermalization steps the sequence $1-4$ generates eigenstates 
-of the $XXX$ chain distributed according to the Quench-Action probability 
-distribution.
-
-For a generic observable ${\mathcal O}$, its Quench-Action expectation value 
-$\langle{\mathcal O}\rangle_{QA}$ is obtained as the arithmetic average of the 
-expectation value over the eigenstates sampled in the Monte Carlo as 
-%
-\begin{equation}
-\langle{\mathcal O}\rangle_{QA}=\frac{1}{N_{mcs}}\sum\limits_{\lambda}
-\langle\lambda|{\mathcal O}|\lambda\rangle, 
-\end{equation}
-%
-with $N_{mcs}$ being the total number of Monte Carlo steps.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Monte Carlo Quench-Action approach: Numerical results}
-\label{MCQA-nr}
+Note that while the steps $1$-$3$ account for the string content and particle 
+number probabilities of the parity-invariant states, step $4$ assigns to the 
+different eigenstates the right quench action, equivalently diagonal ensemble, 
+probability.
+
+For a generic observable ${\mathcal O}$, its quench action, or diagonal ensemble 
+average, $\langle{\mathcal O}\rangle$ is obtained from the Monte Carlo simulation 
+as the arithmetic average of the eigenstates expectation values $\langle\lambda
+|{\mathcal O}|\lambda\rangle$, with $|\lambda\rangle$ the eigenstates sampled by 
+the Monte Carlo, as 
+%
+\begin{equation}
+\label{qamc-obs}
+\langle{\mathcal O}\rangle=\frac{1}{N_{mcs}}\sum\limits_{\lambda}\langle\lambda|
+{\mathcal O}|\lambda\rangle. 
+\end{equation}
+%
+Here $N_{mcs}$ being the total number of Monte Carlo steps. Note that, as usual in 
+Monte Carlo, some initial steps have to be neglected to ensure thermalization. 
+Note that~\eref{qamc-obs} can be used for any observable ${\mathcal O}$ for which 
+the the Bethe state expectation value $\langle\lambda|{\mathcal O}|\lambda\rangle$ 
+(form factor) is known.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The N\'eel overlap sum rules: Monte Carlo results}
+\label{sec:6.2}
 
@@
 \end{center}
-\caption{The overlap sum rules for the Neel state: Numerical results 
- obtained using the Hilbert space Monte Carlo sampling approach. (a) 
- The energy sum rule $\langle N|Q_2|N\rangle/L=-1/2$, with $Q_2/L$ 
- the Hamiltonian density. We plot $\sum_{\lambda}|\langle\lambda|
- N\rangle|^2Q_2(\lambda)/L=1/2$, with $|\lambda\rangle$ the 
- eigenstates of the $XXX$ chain, versus the inverse chain length $1/L$. 
- The symbols are Monte Carlo data obtained by sampling the eigenstates 
- of the $XXX$ chain. The dash-dotted line is the expected result. The 
- dashed line is a fit to the behavior $-1/2+A/L+B/L^2$, with $A,B$ 
- fitting parameters. (b) The energy fluctuations sum rule $\sigma^2(Q_2)/
- L\equiv(\langle N|Q_2^2|N\rangle-\langle N|Q_2|N\rangle^2)/L=1/4$. The 
- horizontal line is the expected result. (c)(d) Same as in (a)(b) for 
- the charge $Q_4$ and its fluctuations. 
+\caption{The overlap sum rules for the N\'eel state $|N\rangle$ in the 
+ Heisenberg spin chain: Numerical results obtained by the Monte Carlo 
+ sampling of the chain Hilbert space. In all panels the $x$ axis shows 
+ the inverse chain length $1/L$ (a) The energy sum rule $\sum_\lambda|
+ \langle N|\lambda\rangle|^2Q_2(\lambda)/L=Q^{(0)}_2$, with $|\lambda
+ \rangle$ the generic eigenstate of the $XXX$ chain, $Q_2(\lambda)/L$ 
+ the associated energy density, and $Q_2^{(0)}=-1/2$ the N\'eel energy 
+ density. The symbols are Monte Carlo data. The dash-dotted line is the 
+ expected result $Q_2^{(0)}$. The dashed line is a fit to the behavior 
+ $-1/2+A/L+B/L^2$, with $A,B$ fitting parameters. (b) The N\'eel sum rule 
+ for the energy fluctuations $\sigma^2(Q_2)$ (cf.~\eref{sigma-sr} for 
+ the definition). The horizontal line is the expected result $1/4$. 
+ (c)(d) Same as in (a)(b) for the charge $Q_4$ and its fluctuations. 
 }
-\label{fig5-neel-sr}
+\label{fig3:neel-qamc-sr}
 \end{figure}
@@
 
-In this section we numerically demonstrate that the only effect of neglecting 
-the zero-momentum strings are finite-size corrections.
-
-The validity of the Monte Carlo approach for simulating the Quench-Action 
-results is demonstrated in Figure~\ref{fig5-neel-sr}. The Figure focuses on 
-the N\'eel sum rules for the conserved charges $Q_2$ and $Q_4$. Specifically, 
-panel (a) shows the sum rules for $\hat Q=\hat Q_2$, $\hat Q=\hat Q_4$, 
-and the corresponding fluctuations $\sigma^2(Q_n)\equiv \langle N|\hat Q_n^2|
-N\rangle-\langle N|\hat Q_n|N\rangle^2$. 
-%
-\begin{equation}
-\langle N|\hat Q_n|N\rangle=\sum\limits_{\lambda}|\langle N|\lambda\rangle|^2
-Q_n.
-\end{equation}
-%
-Note that the N\'eel sum rule for the identity $\mathbb{I}$ is trivially satisfied, 
-and it corresponds to the normalization of the Monte Carlo probability. 
-Figure~\ref{fig5-neel-sr} (a) plots the N\'eel sum rule for the energy density $Q_2/L$. 
-The circles are Monte Carlo data obtained using the procedure outlined in~\ref{mcqa-sec} 
-for several Heisenberg spin chains. The largest chain simulated is for $L=56$ sites. 
-The data correspond to a simulation with $\sim 10^7$ Monte Carlo step (mcs). 
-The expected result $\langle N|\hat Q_2|N\rangle/L=-1/2$ is shown as dash-dotted 
-line.
-
-In stark contrast with Figure~\ref{fig2-neel-sr} and Figure~\ref{fig3-dimer-sr}, 
-while for small chains the sum rule is violated the data strongly suggest that 
-in the thermodynamic limit the sum rule saturates the expected theoretical 
-value.
-
-Furthermore, the data suggest the behavior $\propto 1/L$, as confirmed by the fit 
-to $-1/2+A/L+b/L^2$ (dashed line in the Figure), with $A,B$ fitting parameters.
-
-The same qualitative behavior is demonstrated in panel (b) for the energy 
-fluctuations. Interestingly, for $L=56$ the Monte Carlo result is compatible 
-within the error bar with the expected asymptotic one.
-
-Finally, panels (c)(d) show the same results as for (a)(b) for the conserved 
-charge $Q_4$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Quench-Action root distributions}
-\label{MCQA-root}
+The validity of the Monte Carlo approach for simulating the quench action 
+is demonstrated in Figure~\ref{fig3:neel-qamc-sr} (a)-(d). The Figure focuses on 
+the N\'eel overlap sum rules for the conserved charges densities $Q_2/L$ and $Q_4/L$ 
+(cf. subsection~\ref{sec:1.5} for the definition of the charges, and~\eref{sr-charge} 
+for the associated sum rules). We also consider the corresponding fluctuations 
+$\sigma^2(Q_n)$, which are defined as 
+%
+\begin{equation}
+\label{sigma-sr}
+\fl\quad\sigma^2(Q_n)\equiv\langle N|Q^2_n|N\rangle-\langle N|Q_n|N\rangle^2=
+\sum\limits_{\lambda}|\langle N|\lambda\rangle|^2Q^2_n(\lambda)-\Big(\sum_\lambda|
+\langle N|\lambda\rangle|^2Q_n(\lambda)\Big)^2.
+\end{equation}
+%
+Note that in both~\eref{sr-charge} and~\eref{sigma-sr} the sum is now over the 
+eignestates $|\lambda\rangle$ sampled by the Monte Carlo. 
+Panel (a) and (b) in Figure~\ref{fig3:neel-qamc-sr} plot the sum rules for 
+the energy density $Q_2/L$, and its density of fluctutations $\sigma^2(Q_2)/L$. 
+It is straightforward to derive the N\'eel expectation value of the energy 
+density fluctuations as $\sigma(Q_2)/L=1/4$. This is shown as dash-dotted line 
+in Figure~\ref{fig3:neel-qamc-sr} (b).
+
+The circles in the Figure are Monte Carlo data obtained using the procedure outlined 
+in~\ref{sec:6.1} for the Heisenberg chain with $L\le 56$ sites. The data correspond 
+to Monte Carlo simulations with $N_{mcs}\sim 10^7$ Monte Carlo steps (mcs). For the 
+largest chain size $L=56$ we used $N_{mcs}\sim ...$. In all panels the $x$-axis shows 
+the inverse chain length $1/L$.
+
+Clearly, the Monte Carlo data suggest that in the thermodynamic limit the N\'eel 
+overlap sum rules~\eref{sr-charge} are restored, while violations are present for 
+finite chains. This numerically confirms that the truncation of the Hilbert space, 
+i.e., removing the zero-momentum strings, gives rise only to scaling corrections, 
+while the thermodynamic behavior after the quench is correctly reproduced. 
+Note that the data in panel (a) suggest the behavior $\propto 1/L$ for the scaling 
+corrections, as confirmed by the fit to $-1/2+A/L+b/L^2$ (dashed line in the Figure), 
+with $A,B$ fitting parameters. The same behavior should be expected for the energy 
+fluctuations $\sigma^2(Q_2)$ (panel (b) in the Figure), although the data suggest 
+that this asymptotic behvior sets in for $L\gg 56$.
+
+Similarly, panels (c) and (d) in Figure~\ref{fig3:neel-qamc-sr} plot the charge 
+density $Q_4/L$ and its fluctuations $\sigma^2(Q_4)/L$. While for $Q_4/L$ the Monte 
+Carlo data for $L=48$ are already compatible with the expected result $Q_4/L=1/4$ 
+in the thermodynamic limit, $\sigma^2(Q_4)$ exhibits large scaling corrections. 
+This could be attributed to fact that the support of $Q_n$, i.e., the number of 
+sites where the operator acts non trivially, increases linearly with $n$ 
+(see~\cite{grabowski-1995} for the precise expression).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Extracting the quench action root distributions}
+\label{sec:6.3}
 
@@
 \end{center}
-\caption{ The Quench-Action steady state root ddistributions $\rho_1(x)$ 
- and $\rho_2(x)$: Monte Carlos results. (a) The histograms of the $1$-string 
- rapidities sampled in the Monte Carlo. The $x$-axis shows the $1$-string BGT 
- root $\lambda$. The data are for a chain with $L=56$ sites and $N_{mcs}\sim 
- 10^7$ Monte Carlo steps. The data are divided by a factor $10^6$ for plotting 
- convenience. The width of the histogram bin is $\Delta\lambda\sim 0.07$. (b) 
- The same as in (a) for the $2$-string roots sampled in the Monte Carlo. (b) 
- The extracted $1$-string root distribution $\rho_1(\lambda)$ plotted versus 
- $\lambda$ for two chains with $L=48$ and $L=56$ (diamond and circles, respectively). 
- The full line is the Quench-Action analytic result in the thermodynamic limit. (d) 
- The same as in (c) for the $2$-string root density $\rho_2(\lambda)$. In both 
- (c)(d) the oscillations are finite-size effects, whereas the error bars 
- show the statistical Monte Carlo error. 
+\caption{ The quench action root distributions $\rho^*_1(\lambda)$ and 
+ $\rho^*_2(\lambda)$ for the $1$-strings and $2$-strings, respectively: Monte 
+ Carlos results. (a) The histograms of the $1$-string Bethe-Gaudin-Takahashi 
+ (BGT) roots $\lambda$ sampled in the Monte Carlo. The data are for a chain 
+ with $L=56$ sites and a Monte Carlo history with $N_{mcs}\sim 10^7$ Monte 
+ Carlo steps. The $y$-axis is divided by a factor $10^6$ for convenience. 
+ The width of the histogram bin is $\Delta\lambda\sim 0.07$. (c) The same as 
+ in (a) for the $2$-string roots. (b) The $1$-string root distribution 
+ $\rho^*_1(\lambda)$ plotted versus $\lambda$ for two chains with $L=48$ 
+ and $L=56$ (diamond and circles, respectively). The full line 
+ is the quench action analytic result in the thermodynamic limit. (d) 
+ The same as in (b) for the $2$-string root distribution $\rho^*_2(\lambda)$. 
+ In both (b) and (d) the oscillations are finite-size effects, whereas 
+ the error bars are the statistical Monte Carlo errors. 
 }
-\label{fig6-neel-roots}
+\label{fig4:neel-rho}
 \end{figure}
@@
 
-The BGT root distributions $\rho_n(\lambda)$ identifying the Quench-Action saddle 
-point can be extracted from the Monte Carlo simulation as shown in~\cite{alba-2015}.
-
-Figure~\ref{fig6-neel-roots} displays the first two root distributions 
-$\rho_1(\lambda)$ (panel (a)) and $\rho_2(\lambda)$ (panel (b)), plotted agains 
-the BGT root $\lambda$. The data are the histograms of the BGT roots sampled 
-in the Monte Carlo. The data are for a chain with $L=56$ sites and 
-$N_{mcs}\sim 10^7$ Monte Carlo steps. All the data are divided by a factor 
-$10^6$ for plotting convenience. The width of the histogram bins $\Delta\lambda$ 
-is $\Delta\lambda\approx0.02$ and $\Delta\lambda\approx0.001$ for $\rho_1(\lambda)$ 
-and $\rho_2(\lambda)$, respectively.
-
-The histogram fluctuations are due to $N_{mcs}$ being finite, and are expected 
-to vanish in the limit $N_{mcs}\to\infty$.
-
-The continuous lines is the expected analytic result in the thermodynamic limit.
-
-Clearly, $\rho_1(\lambda)$ is in good agreement with the Monte Carlo data in the 
-whole range $-2\le\lambda\le2$ considered. 
-On the other hand, larger deviations from the theoretical result are present 
-for $\rho_2(\lambda)$. These deviations are larger on the tails of the 
-distribution. This is expected since large $\lambda$ correspond to large 
-quasimomenta, which are more sensitive to the finite size of the chain.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Counting of eigenstates with non-zero Neel overlap}
-
-We numerically checked that the number of states with non-zero overlap 
-with the Neel state is given as 
-%
-\begin{equation}
-\label{Neel-count}
-Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\left(\frac{L}{2},
-\frac{L}{4}\right)+1,
-\end{equation}
-%
-with $B(x,y)$ denoting the binomial coefficient. The contribution $1$ 
-accounts for the ferromagnetic state. Here 
-we assumed that $L$ is divisible by four. Here $Z_N$ is be obtained 
-as the total number of parity-invariant Bethe-Gaudin-Takahashi quantum 
-numbers.
-
-After excluding the zero-momentum strings the total number of states 
-with non-zero overlap with the Neel state is 
-%
-\begin{equation}
-\label{neel-ov-count}
-\widetilde {Z}_{Neel}=\Big(\frac{L}{2},\frac{L}{4}\Big)
-\end{equation}
-%
-Importantly, the fraction of eigenstates corresponding to non-zero momentum 
-strings is vanishing in the thermodynamic limit as 
-%
-\begin{equation}
-\frac{\widetilde Z_{Neel}}{Z_{Neel}}\propto\frac{4}{\sqrt{\pi L}}.
-\end{equation}
-%
-
+The BGT root distributions corresponding to the quench action steady state 
+(cf.~\eref{rho1-sp}-\eref{rho3-sp}) $\pmb{\rho^*}=\{\rho^*_n(\lambda)\}_{n=
+1}^{\infty}$ can be extracted from the Monte Carlo simulation,  as it has been 
+done in Ref.~\cite{alba-2015} for the Generalized Gibbs Ensemble (GGE) 
+representative state.
+
+For the local observables considered here, in each eigenstate expectation value 
+$\langle\lambda|{\mathcal O}|\lambda\rangle$ in~\eref{qamc-obs} one can isolate 
+the contribution of the different string sectors as 
+%
+\begin{equation}
+\langle\lambda|{\mathcal O}|\lambda\rangle=\sum\limits_{n,\gamma}{\mathcal O}_n
+(\lambda_{n;\gamma}), 
+\end{equation}
+%
+where ${\mathcal O}_n$ is the contribution of the BGT $n$-strings to the expectation 
+value of ${\mathcal O}$, and $\pm\lambda_{n;\gamma}$, with $\gamma$ labeling the 
+different $n$-strings, are the solutions of the BGT equations~\eref{bgt-eq} 
+identifying the Bethe state $|\lambda\rangle$. By comparing~\eref{qamc-obs} 
+and~\eref{obs-th} one obtains that in the limit $L,N_{mcs}\to\infty$ 
+%
+\begin{equation}
+\quad\fl\lim_{N_{mcs}\to\infty}\,\frac{1}{N_{mcs}}\sum\limits_{\lambda_{n;\gamma}}
+{\mathcal O}_n(\lambda_{n;\gamma})\,\stackrel{L\to\infty}{\overrightarrow{\hspace{40pt}}}
+\,\langle\pmb{\rho^*}|{\mathcal O}|\pmb{\rho^*}\rangle\equiv\sum_n\int_{-\infty}^{+\infty}d
+\lambda\rho^*_{n}(\lambda){\mathcal O}_n(\lambda). 
+\end{equation}
+%
+This suggests that the histogram of the $n$-strings BGT roots sampled in the Monte 
+Carlo converges in the thermdynamic limit to the saddle point root distribution 
+$\rho^*_n(\lambda)$.
+
+This is demonstrated numerically in Figure~\ref{fig4:neel-rho} considering $\rho^*_1(\lambda)$ 
+(panels (a)(b)) and $\rho^*_2(\lambda)$ (panel (c)(d)). The histograms correspond to Monte 
+Carlo data for $L=48$ and $L=56$ sites. Panel (a) and (c) show the  histograms of the 
+$1$-string and $2$-string BGT roots sampled in the Monte Carlo. The $y$-axis is rescaled 
+by a factor $10^6$ for convenience. The width of the histogram bins $\Delta\lambda$ is 
+$\Delta\lambda\approx0.02$ and $\Delta\lambda\approx0.001$ for $\rho_1(\lambda)$ and 
+$\rho_2(\lambda)$, respectively. The histogram fluctuations are due both to the finite 
+statistics (finite $N_{mcs}$) and to the finite size of the chain.
+
+The extracted quench-action root distributions $\rho^*_1(\lambda)$ and $\rho^*(\lambda)$ 
+are shown in panels (b) and (d). The data are the same as in panel (a)(c). The normalization 
+of the distributions is chosen such as to match the analytical results from~\eref{rho1-sp} 
+and~\eref{rho2-sp}, i.e., $\int d\lambda\rho^*_1(\lambda)\approx0.31$ and $\int d\lambda
+\rho^*_2(\lambda)\approx0.015$. The Monte Carlo error bars shown in the Figure are obtained 
+with a standard jackknife analysis~\cite{quenouille-1949,wolff-2004}. 
+The continuous lines are the expected analytic result in the thermodynamic limit 
+(cf.~\eref{rho1-sp}~\eref{rho2-sp}).
+
+Clearly, the Monte Carlo data for $\rho^*_1(\lambda)$ are in excellent agreement 
+with~\eref{rho1-sp} in the whole range $-2\le\lambda\le2$ considered. The statistical error 
+bars are smaller than the symbol size. The oscillating (with $\lambda$) corrections 
+visible at $|\lambda|\sim0.5$ are lattice effects, which decrease with the chain size 
+(see the data for $L=48$). Much larger finite-size effects are observed for 
+$\rho^*_2(\lambda)$ (panel (d) in the Figure). The corrections are larger on the tails of 
+the root distribution. Moreover, the Monte Carlo error bars are clearly visible. This is 
+due to the fact that since $\int d\lambda\rho^*_2(\lambda)/\sum_n\int d\lambda
+\rho_n^*(\lambda)\approx 0.04$, the Monte Carlo statistics available to estimate 
+$\rho_2^*(\lambda)$ is effectively reduced as compared to $\rho_1^*(\lambda)$. 
+Finally, we numerically checked that these corrections are even larger for the $3$-strings,  
+and much larger chains would be needed to extract $\rho^*_3(\lambda)$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}
+\label{conclusions}
+
+We presented a Monte Carlo implementation of the quench action method for integrable 
+spin chains. We focused on the spin-$1/2$ isotropic Heisenberg ($XXX$) chain, considering  
+the quench from the zero-momentum N\'eel state. The method is similar to the Monte Carlo 
+approach developed in Ref.~\cite{alba-2015} to simulate the Generalized Gibbs Ensemble 
+(GGE) in integrable models. The key idea is the Monte Carlo sampling of the chain Hilbert 
+space with the quench action probability distribution given in~\eref{qa-prob}.
+
+The approach heavily relies on the knowledge of the overlaps between the pre-quench N\'eel 
+state $|N\rangle$ and the chain eigenstates, which have been obtained recently~\cite{
+pozsgay-2014,brockmann-2014,brockmann-2014a,brockmann-2014b,brockmann-2014c,piroli-2014}. 
+Moreover, the method is based on the detailed knowledge of the Hilbert space 
+structure of the model provided by the Bethe ansatz formalism, in particular, on the 
+so-called string hypothesis, and on the Bethe-Gaudin-Takahashi (BGT) equations. Although 
+the approach is devised for finite-size systems, thermodynamic quantities can be extracted 
+using finite-size scaling. Importantly, we restricted ourselves to a truncated Hilbert space, 
+excluding the chain eigenstates containing zero-momentum strings. The reason is that 
+zero-momentum strings lead to singularities in the N\'eel overlap formulas, which are 
+tricky to deal with in the framework of the string hypothesis. Note that for the same 
+reason the zero-momentum strings are neglected in the quench action approach~\cite{brockmann-2014} 
+as well, although it has been argued that their effect should be irrelevant in the 
+thermodynamic limit~\cite{brockmann-2014}.
+
+In order to understand the effect of the zero-momentum strings in {\it finite} chains 
+we first investigated the overlap distribution, including {\it all} the eigenstates 
+with no zero-momentum strings, for chains up to $L=38$ sites. Interestingly, the total 
+number of eigenstates having, in principle, non-zero N\'eel overlap is given in terms of 
+the chain length by a simple combinatorial formula that we provided. Additional 
+combinatorial formulas are provided for the case without zero-momentum strings, or 
+at fixed particle number (i.e., magnetization), or fixed ``string content'' of the 
+eigenstates. Surprisingly, for any finite chain the majority of eigenstates contain 
+zero-momentum strings. Moreover, the fraction of eigenstates with nonzero-momentum 
+strings vanishes as $L^{-1/2}$ in the thermdodynamic limit. This is reflected in the 
+N\'eel overlap sum rules for the local conserved charges of the model. 
+Although for any chain size their value is fixed by the N\'eel state expectation 
+value, violations of the sum rules are observed, due to the Hilbert space truncation. 
+Moreover, we numerically observed that the sum rules vanish as $L^{-1/2}$ in the 
+thermodynamic limit. This behavior reflects the vanishing of the fraction of 
+eigenstates with no zero-momentum strings, confirming that their contribution 
+cannot be trivially neglected. This behavior as$L^{-1/2}$, however, is not generic, 
+but it depends on the pre-quench initial state. This was demonstrated by 
+considering the quench from the Majumdar-Ghosh state. We observed that the sum 
+rules vanish as $1/L$, again reflecting the vanishing as $1/L$ of the fraction of 
+eigenstates with no zero-momentum strings.
+
+Next we presented a Monte Carlo implementation of the quench action method. 
+We numerically demonstrated the validity of the approach, focusing on the N\'eel 
+overlap sum rules for the local conserved quantities of the $XXX$ chain. Although 
+for finite chains violations of the sum rules are present, their effect decays 
+as $1/L$ upon increasing the chain size, meaning that overlap sum rules are 
+restored in the thermodynamic limit. This implies that the only effect of the 
+Hilbert space truncation is to give rise to scaling corrections. Physically, 
+this means that the remaining eigenstates after the Hilber space truncation 
+contain enough information about the post-quench thermodynamic behavior of the 
+model. Finally, following Ref.~\cite{alba-2015} we extracted from the Monte Carlo 
+the quench action BGT root distributions. Although finite-size oscillating 
+corrections are present, already for relatively small chains with $L=56$ sites, 
+the first two BGT root distributions are in impressive agreement with the 
+analytic result in the thermodynamic limit.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \appendix
@@
 
-\bibitem{calabrese-2014}
-P.~Calabrese and P.~Le Doussal, J.\ Stat.\ Mech.\ (2014) P05004.
-
-\bibitem{alba-2015}
-V.~Alba, arXiv:1507.06994.
-
-\bibitem{bethe-1931}
-H.~Bethe, Zur Theorie der Metalle. I. Eigenwerte und Eigenfunktionen 
-der linearen Atomkette, Z.\ Phys.\ {\bf 71}, 205 (1931).
+\bibitem{bloch-2008}
+I.~Bloch, J.~Dalibard, and W.~Zwerger, Rev.\ Mod.\ Phys.\ {\bf 80},
+885 (2008).
+
+\bibitem{greiner-2002}
+M.~Greiner, O.~Mandel, T. H\"ansch, and I.~Bloch, Nature (London)
+{\bf 419}, 51 (2002).
+
+\bibitem{kinoshita-2006}
+T.~Kinoshita, T.~Wenger, and D.~S.~Weiss, Nature (London) {\bf 440},
+900 (2008).
+
+\bibitem{hofferberth-2007}
+S.~Hofferberth, I.~Lesanovsky, B.~Fischer, T.~Schumm, and J.~Schiedmayer,
+Nature (London) {\bf 449}, 324 (2007).
+
+\bibitem{trotzky-2012}
+S.~Trotzky, Y.-A.~Chen, A.~Flesch, I.~P.~McCulloch, U.~Schollw\"ock,
+J.~Eisert, and I.~Bloch, Nature Phys.\ {\bf 8}, 325 (2012).
+
+\bibitem{gring-2012}
+M.~Gring, M.~Kuhnert, T.~Langen, T.~Kitagawa, B.~Rauer, M.~Schreitl,
+I.~Mazets, D.~A.~Smith, E.~Demler, and J.~Schmiedmayer, Science {\bf 337},
+6100 (2012).
+
+\bibitem{cheneau-2012}
+M.~Cheneau, P.~Barmettler, D.~Poletti, M.~Endres, P.~Schaua, T.~Fukuhara,
+C.~Gross, I.~Bloch, C.~Kollath, and S.~Kuhr, Nature (London) {\bf 481},
+484 (2012).
+
+\bibitem{schneider-2012}
+U.~Schneider, L.~Hackeruller, J.~P.~Ronzheimer, S.~Will, S.~Braun, T.~Best,
+I.~Bloch, E.~Demler, S.~Mandt, D.~Rasch, and A.~Rosch, Nature\ Phys.\
+{\bf 8}, 213 (2012).
+
+\bibitem{kunhert-2013}
+M.~Kuhnert, R.~Geiger, T.~Langen, M.~Gring, B.~Rauer,
+T.~Kitagawa, E.~Demler, D.~Adu Smith, and J.~Schmiedmayer, Phys.\ Rev.\
+Lett.\ {\bf 110}, 090405 (2013).
+
+\bibitem{langen-2013}
+T.~Langen, R.~Geiger, M.~Kuhnert, B.~Rauer, and J.~Schmiedmayer,
+Nature\ Phys.\ {\bf 9}, 640 (2013).
+
+\bibitem{meinert-2013}
+F.~Meinert, M.~J.~Mark, E.~Kirilov, K.~Lauber, P.~Weinmann,
+A.~J.~Daley, and H.-C.~Nagerl, Phys.\ Rev.\ Lett.\ {\bf 111},
+053003 (2013).
+
+\bibitem{fukuhara-2013}
+T.~Fukuhara, A.~Kantian, M.~Endres, M.~Cheneau, P.~Schaua, S.~Hild, C.~Gross,
+U.~Schollw\"ock, T.~Giamarchi, I.~Bloch, and S.~Kuhr, Nature\ Phys.\ {\bf 9},
+235 (2013).
+
+\bibitem{ronzheimer-2013}
+J.~P.~Ronzheimer, M.~Schreiber, S.~Braun, S.~S.~Hodgman, S.~Langer, I.~P.~McCulloch,
+F. Heidrich-Meisner, I.~Bloch, and U.~Schneider, Phys.\ Rev.\ Lett.\ {\bf 110},
+205301 (2013).
+
+\bibitem{braun-2014}
+S.~Braun, M.~Friesdorf, S.~Hodgman, M.~Schreiber, J.~Ronzheimer, A.~Riera, M.~del Rey,
+I.~Bloch, J.~Eisert, and U.~Schneider, PNAS {\bf 112}, 3641 (2015).
+
+\bibitem{langen-2015}
+T.~Langen, S.~Erne, R.~Geiger, B.~Rauer, T.~Schweigier, M.~Kuhnert, W.~Rohringer,
+I.~E.~Mazets, T.~Gasenzer, J.~Schmiedmayer, Science {\bf 348}, 6231 (2015).
+
+\bibitem{polkovnikov-2011}
+A.~Polkovnikov, K.~Sengupta, A~Silva, and M.~Vengalattore, Rev.\ Mod.\ Phys.\
+{\bf 83}, 863 (2011).
+
+\begin{comment}
+\bibitem{calabrese-2006}
+P.~Calabrese and J.~Cardy, Phys.\ Rev.\ Lett.\ {\bf 96}, 136801 (2006).
+
+\bibitem{rigol-2007}
+M.~Rigol, V.~Dunjko, V.~Yurovsky, and M.~Olshanii, Phys.\ Rev.\ Lett.\ 
+{\bf 98}, 050405 (2007).
+
+\bibitem{calabrese-2007}
+P.~Calabrese and J.~Cardy, J.\ Stat.\ Mech.\ (2007) P06008.
+
+\bibitem{kollath-2007}
+C.~Kollath, A.~M.~L\"auchli, and E.~Altman, Phys.\ Rev.\ Lett.\ 
+{\bf 98}, 180601 (2007).
+
+\bibitem{manmana-2007}
+S.~R.~Manmana, S.~Wessel, R.~M.~Noack, and A.~Muramatsu, 
+Phys.\ Rev.\ Lett.\ {\bf 98}, 210405 (2007).
+
+\bibitem{rigol-2008}
+M.~Rigol, V.~Dunjko, and M.~Olshanii, Nature {\bf 452}, 854 (2008).
+
+\bibitem{cramer-2008}
+M.~Cramer, C.~M.~Dawson, J.~Eisert, and T.~J.~Osborne, Phys.\ Rev.\ 
+Lett.\ {\bf 100}, 030602 (2008).
+
+\bibitem{barthel-2008}
+T.~Barthel and U.~Schollw\"ock, Phys.\ Rev.\ Lett.\ {\bf 100}, 100601 
+(2008).
+
+\bibitem{kollar-2008}
+M.~Kollar and M.~Eckstein, Phys.\ Rev.\ A {\bf 78}, 013626 (2008).
+
+\bibitem{moeckel-2008}
+M.~Moeckel and S.~Kehrein, Phys.\ Rev.\ Lett.\ {\bf 100}, 175702 (2008).
+
+\bibitem{iucci-2009}
+A.~Iucci and M.~A.~Cazalilla, Phys.\ Rev.\ A\ {\bf 80}, 063619 (2009).
+
+\bibitem{rossini-2009}
+D.~Rossini, A.~Silva, G.~Mussardo, and G.~E.~Santoro, Phys.\ Rev.\ 
+Lett.\ {\bf 102}, 127204 (2009).
+
+\bibitem{barmettler-2009}
+P.~Barmettler, M.~Punk, V.~Gritsev, E.~Demler, and E.~Altman, Phys.\ Rev.\ 
+Lett.\ {\bf 102}, 130603 (2009).
+
+\bibitem{biroli-2010}
+G.~Biroli, C.~Kollath, and A.~M.~L\"auchli, Phys.\ Rev.\ Lett.\ 
+{\bf 105}, 250401 (2010).
+
+\bibitem{rossini-2010}
+D.~Rossini, S.~Suzuki, G.~Mussardo, G.~E.~Santoro, and A.~Silva, 
+Phys.\ Rev.\ B\ {\bf 82}, 144302 (2010).
+
+\bibitem{fioretto-2010}
+D.~Fioretto and G.~Mussardo, New\ J.\ Phys.\ {\bf 12}, 
+055015 (2010).
+
+\bibitem{gogolin-2011}
+C.~Gogolin, M.~P.~Mueller, and J.~Eisert, Phys.\ Rev.\ Lett.\ 
+{\bf 106}, 040401 (2011).
+
+\bibitem{banuls-2011}
+M.~C.~Ba\~nuls, J.~I.~Cirac, and M.~B.~Hastings, Phys.\ Rev.\ Lett.\ 
+{\bf 106}, 050405 (2011).
+
+\bibitem{calabrese-2011}
+P.~Calabrese, F.~H.~L.~Essler, and M.~Fagotti, Phys.\ Rev.\ Lett.\ {\bf106}, 227203 (2011).
+
+\bibitem{rigol-2011}
+M.~Rigol and M.~Fitzpatrick, Phys.\ Rev.\ A {\bf 84}, 033640 (2011).
+
+\bibitem{calabrese-2012}
+P.~Calabrese, F.~H.~L.~Essler, and M.~Fagotti, J.\ Stat.\ Mech.\ (2012) P07016.
+
+\bibitem{caux-2012}
+J.-S.~Caux and R.~M.~Konik, Phys.\ Rev.\ Lett.\ {\bf 109}, 175301 (2012).
+
+\bibitem{essler-2012}
+F.~H.~L.~Essler, S.~Evangelisti, and M.~Fagotti, Phys.\ Rev.\ Lett.\ 
+{\bf 109}, 247206 (2012).
+
+\bibitem{cazalilla-2012}
+M.~A.~Cazalilla, A.~Iucci, and M.-C.~Chung, Phys.\ Rev.\ E {\bf 85}, 
+011133 (2012).
+
+\bibitem{mossel-2012a}
+J.~Mossel and J.-S.~Caux, New\ J.\ Phys.\ {\bf 14} 075006 (2012).
+
+\bibitem{collura-2013}
+M.~Collura, S.~Sotiriadis and P.~Calabrese, Phys.\ Rev.\ Lett.\ {\bf 110}, 245301 (2013)
+
+\bibitem{mussardo-2013}
+G.~Mussardo, Phys.\ Rev.\ Lett.\ {\bf 111}, 100401 (2013).
+
+\bibitem{caux-2013}
+J.-S.~Caux and F.~H.~L.~Essler, Phys.\ Rev.\ Lett.\ {\bf 110}, 
+257203 (2013).
+
+\bibitem{fagotti-2013a}
+M.~Fagotti and F.~H.~L.~Essler, J.\ Stat.\ Mech.\ (2013), P07012.
+
+\bibitem{fagotti-2013}
+M.~Fagotti and F.~H.~L.~Essler, Phys.\ Rev.\ B\ {\bf87}, 245107 (2013).
+
+\bibitem{sotiriadis-2014}
+S.~Sotiriadis and P.~Calabrese, J.\ Stat.\ Mech.\ (2014) P07024.
+
+\bibitem{fagotti-2014}
+M.~Fagotti, M.~Collura, F.~H.~L.~Essler, and P.~Calabrese, Phys.\ Rev.\ B {\bf 89}, 
+125101 (2014).
+
+\bibitem{essler-2014}
+F.~H.~L.~Essler, S.~Kehrein, S.~R.~Manmana, and N.~J.~Robinson, Phys.\ Rev.\ B {\bf 89}, 
+165104 (2014).
+
+\bibitem{goldstein-2014}
+G.~Goldstein and N.~Andrei, arXiv:1405.4224.
+
+\bibitem{de-nardis-2014}
+J.~De Nardis, B.~Wouters, M.~Brockmann, and J.-S.~Caux, Phys.\ Rev.\ A {\bf 89}, 
+033601 (2014).
+
+\bibitem{wright-2014}
+T.~M.~Wright, M.~Rigol, M.~J.~Davis, and K.~V.~Kheruntsyan, Phys.\ Rev.\ Lett.\ {\bf 113}, 
+050601 (2014).
+
+\bibitem{pozsgay-2014}
+B.~Pozsgay, M.~Mesty\'an, M.~A.~Werner, M.~Kormos, G.~Zar\'and, and G.~Tak\'acs,
+Phys.\ Rev.\ Lett.\ {\bf 113}, 117203 (2014).
+
+\bibitem{wouters-2014}
+B.~Wouters, M.~Brockmann, J.~De~Nardis, D.~Fioretto, M.~Rigol, and J.-S.~Caux, 
+Phys.\ Rev.\ Lett.\ {\bf 113}, 117202 (2014).
+
+\bibitem{mestyian-2015}
+M~Mesty\'an, B.~Pozsgay, G.~Tak\'acs, and M.~A.~Werner, J.\ Stat.\ Mech.\ (2015) 
+P04001.
+
+\bibitem{ilievski-2015a}
+E.~Ilieveski, J.~De~Nardis, B.~Wouters, J.-S.~Caux, F.~H.~Essler, and T.~Prosen, 
+arXiv:1507.02993.
+
+\bibitem{kcc14}
+M.~Kormos, M.~Collura, and P.~Calabrese, Phys.\ Rev.\ A {\bf 89}, 013609 
+(2014).
+
+\bibitem{kcc14a}
+P.~P.~Mazza, M.\ Collura, M.\ Kormos, and P.\ Calabrese, J.\ Stat.\ Mech.\  
+(2014) P11016.
+
+\bibitem{prosen-2014}
+T.~Prosen, Nucl.\ Phys.\ B\ {\bf 886}, (2014) 1177.
+
+\bibitem{pereira-2014}
+R.~G.~Pereira, V.~Pasquier, J.~Sirker, and I.~Affleck, J.\ Stat.\ Mech.\ 
+(2014) P09037.
+
+\bibitem{ilievski-2015}
+E.~Ilievski, M.~Medejak, and T.~Prosen, arXiv:1506.05049.
+
+\bibitem{essler-2015}
+F.~H.~L.~Essler, G.~Mussardo, and M.~Panfil, Phys.\ Rev.\ A {\bf 91}, 051602 (2015).
+
+\bibitem{cardy-2015}
+J.~Cardy,  arXiv:1507.07266.
+
+\bibitem{iyer-2015}
+D.~Iyer, M.~Srednicki, and M.~Rigol, Phys.\ Rev.\ E\ {\bf 91}, 062142 (2015).
+
+\bibitem{takahashi-1971} 
+M.~Takahashi, Prog.\ Theor.\ Phys.\ {\bf 46}, 401 (1971).
+
+\end{comment}
 
@@
 Cambridge University Press, Cambridge, 1999.
+
+\bibitem{gu-2005}
+S.-J.~Gu, N.~M.~R.~Peres, Y.-Q.~Li, Eur.\ Phys.\ J.\ B {\bf 48}, 157 (2005).
+
+\bibitem{grabowski-1995}
+M.~P.~Grabowski and P.~Mathieu, Ann.\ Phys.\ N.Y. {\bf 243}, 
+299 (1995).
+
+\bibitem{bethe-1931}
+H.~Bethe, Z.\ Phys.\ {\bf 71}, 205 (1931).
+
+\bibitem{mossel-2012}
+J.~Mossel and J.-S.~Caux, J.\ Phys.\ A:\ Math.\ Theor.\ {\bf 45}, 
+255001 (2012).
+
+\bibitem{pozsgay-2013}
+B.~Pozsgay, J.\ Stat.\ Mech.\ (2013) P07003.
 
@@
 
+\bibitem{landau-binder}
+D.~P.~Landau and K.~Binder, \emph{A Guide to Monte Carlo Simulations in 
+Statistical Physics}, Cambridge University Press, Cambridge, 2000.
+
+\bibitem{faddeev-1996}
+L.~D.~Faddeev, arXiv:9605187.
+
+\bibitem{yang-1969}
+C.~N.~Yang and C.~P.~Yang, J.\ Math.\ Phys. {\bf 10}, 1115 (1969).
+
+\bibitem{calabrese-2014}
+P.~Calabrese and P.~Le Doussal, J.\ Stat.\ Mech.\ (2014) P05004.
+
+\bibitem{alba-2015}
+V.~Alba, arXiv:1507.06994.
+
+\bibitem{bethe-1931}
+H.~Bethe, Zur Theorie der Metalle. I. Eigenwerte und Eigenfunktionen 
+der linearen Atomkette, Z.\ Phys.\ {\bf 71}, 205 (1931).
+
 \bibitem{brockmann-2014}
@@
 
+\bibitem{mazza-2015}
+P.~P.~Mazza, J.-M.~St\'ephan, E.~Canovi, V.~Alba, M.~Brockmann, and M.~Haque, 
+arXiv:1509.04666.
+
+\bibitem{fagotti-2013}
+M.~Fagotti and F.~H.~Essler, J.\ Stat.\ Mech.\ (2013) P07012.
+
+\bibitem{grabowski-1995}
+M.~P.~Grabowski and P.~Mathieu, Ann.\ Phys.\ N.Y. {\bf 243},
+299 (1995).
+
+\bibitem{quenouille-1949} 
+M.~H.~Quenouille, Ann.\ Math.\ Statist.\ {\bf 20}, 355 (1949).
+
+\bibitem{wolff-2004} 
+U.~Wolff, Comput.\ Phys.\ Comm.\ {\bf 156}, 143 (2004).
+
+\bibitem{piroli-2014}
+L.~Piroli and P.~Calabrese, J.\ Phys.\ A {\bf 47}, 385003 (2014).
+
 \end{thebibliography}

### 2015-09-25 draft/fs_qa_v3.tex
rev-25/09/2015

--- 2015-09-24 draft/fs_qa_v2.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Eigenstates with nonzero N\'eel overlap: eigenstates counting and 
-string content}
+\section{Counting and string content of the eigenstates with nonzero overlap}
 \label{app-1}
 
-Here we prove that the total number of eigenstates with N\'eel nozero overlap 
-$Z_{Neel}(L)$for a chain of length $L$ is given as 
+Here we provide some exact combinatorial formulas for the total number of 
+parity-invariant eigenstates of the $XXX$ chain having non-zero overlap with 
+the N\'eel state and the Majumdar-Ghosh state. We consider both the situations  
+with constrained and unconstrained string content and particle number (i.e., 
+total magnetization). In~\ref{app-1.1} we consider all possible parity-invariant 
+eigenstates, whereas in~\ref{app-1.2} we exclude the eigenstates containing 
+zero-momentum strings. Note that the result in~\ref{app-1.1} is only an upper 
+bound, while the counting in~\ref{app-1.2} is exact. The strategy of the proof 
+is the same as that used to count the number of solutions of the 
+Bethe-Gaudin-Takahashi equations (see for instance Ref.~\cite{faddeev-1996}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Allowing the zero-momentum strings}
+\label{app-1.1}
+
+Here we prove that the total number of parity-invariant eigenstates $Z_{Neel}$ 
+with, in principle, non-zero N\'eel overlap for a chain of length $L$ is given 
+as 
 %
@@
 %
-For simplicity here we restrict ourselves to the situation with $L$ divisible by 
-four. The strategy to prove~\eref{N-count} is to count all the possible parity-invariant 
-BGT quantum numbers configurations. Let us consider the sector with fixed number of 
-particles $M$, and a generic string content ${\mathcal S}=\{s_1,s_2,\dots,s_{M}\}$. 
-Here $s_n$ is the number of $n$-strings, and one has the constraint $\sum_k ks_k=M$.
-
-It is straightforward to check that total number of parity-invariant quantum number 
-pairs ${\mathcal N}_n(L,{\mathcal S})$ in the $n$-string sector is given as 
+We restrict ourselves to the situation with $L$ divisible by four. The strategy to 
+prove~\eref{N-count} is to count all the possible parity-invariant BGT quantum numbers 
+configurations (cf. section~\ref{sec:1.3}). Let us consider the sector with fixed number 
+of particles $M$, and string content ${\mathcal S}=\{s_1,s_2,\dots,s_{M}\}$. Here $s_n$ is 
+the number of $n$-strings, with the constraint $\sum_k ks_k=M$. One should stress that 
+$M$ is the number of particles corresponding to {\it finite} solutions of the Bethe 
+equations. The total number of particles is $L/2$, due to the fact that the N\'eel 
+state has $S_T^z=0$. The remaining $L/2-M$ particles correspond to infinite solutions 
+of the Bethe equations (see section~\ref{sec:1.2}). It is straightforward to check that 
+total number of parity-invariant quantum number pairs ${\mathcal N}_n(L,{\mathcal S})$ 
+in the $n$-string sector is given as 
 %
@@
 {\mathcal N}_n(L,{\mathcal S})=\Big\lfloor\frac{L}{2}-\frac{1}{2}
-\sum_{m=1}^{M}t_{nm}s_m\Big\rfloor.
-\end{equation}
-%
-where $t_{nm}\equiv 2\textrm{Min}(n,m)-\delta_{n,m}$. The number of parity-invariant 
-quantum number configurations (i.e., eigenstates) ${\mathcal N}(L,{\mathcal S})$ 
-compatible with string content ${\mathcal S}$ is obtained by choosing in all the 
-possible ways the parity-invariant quantum number pairs independently in each 
-$n$-string sector, which implies that    
+\sum_{m=1}^{M}t_{nm}s_m\Big\rfloor,
+\end{equation}
+%
+where $t_{nm}\equiv 2\textrm{Min}(n,m)-\delta_{n,m}$. Thus, the number of parity-invariant 
+eigenstates of the $XXX$ chain ${\mathcal N}(L,{\mathcal S})$ compatible with string content 
+${\mathcal S}$ is obtained by choosing in all the possible ways the associated parity-invariant 
+quantum number pairs as     
 %
@@
 factor $1/2$ in $s_m/2$ is because since all quantum numbers are organized in pairs, 
-only half of the quantum numbers have to be specified. Note that in each $n$-string 
-sector only one zero momentum (i.e., zero quantum number) string is allowed, due to 
-the Pauli principle. Moreover, $s_m$ is odd (even) only if the zero momentum string 
-is (not) present. The floor function $\lfloor\cdot\rfloor$ in~\eref{NLS} reflects 
-that the quantum number of zero-momentum strings is fixed.
-
-We now consider the string configurations with particle number $0\le\ell\le M$ and 
-fixed number of strings $1\le q\le M/2$. Note that the maximul allowed string length 
-is $M/2$ beacause of parity invariance. Note also that in determining $q$ strings of 
-different length are treated equally. Clearly, one has that $\sum_m s_m=q$. 
-For a given fixed pair $\ell,q$ the total number of quantum number configurations 
-is given as 
+only half of them have to be specified. Note that in each $n$-string sector only one 
+zero momentum (i.e., zero quantum number) string is allowed, due to the fact that 
+repeated solutions of the BGT equation are discarded. Moreover, from~\eref{NnLS} one has 
+that $s_m$ is odd (even) only if this zero momentum string is (not) present. Finally, 
+the floor function $\lfloor\cdot\rfloor$ in~\eref{NLS} reflects that the quantum number 
+of zero-momentum strings is fixed.
+
+We now proceed to consider the string configurations with fixed particle number $0\le\ell
+\le M$ and fixed number of strings $1\le q\le M/2$. Note that the maximum allowed string 
+length is $M/2$ beacause of parity invariance. Note also that in determining $q$, strings 
+of different length are treated equally, i.e., $q=\sum_m s_m$. For a given fixed pair 
+$\ell,q$ the total number of allowed quantum number configurations by definition is given 
+as 
 %
@@
 %
-where the sum is over the content $\{s_m\}_{m=1}^M$ compatible with the constraints 
-$\sum_m s_m=q$ and $\sum_m m s_m=\ell$. The strategy is to write a recursive relation 
-for ${\mathcal N}'(L,\ell,q)$. To this purpose it is useful to consider the shifted 
-string content ${\mathcal S}'$ defined as  
+where the sum is over the string content $\{s_m\}_{m=1}^M$ compatible with the constraints 
+$\sum_m s_m=q$ and $\sum_m m s_m=\ell$. The strategy now is to write a recursive relation 
+in both $\ell,q$ for ${\mathcal N}'(L,\ell,q)$. It is useful to consider a shifted string 
+content ${\mathcal S}'$ defined as  
 %
@@
 \begin{equation}
+\label{inter}
 {\mathcal N}_n(L,{\mathcal S})={\mathcal N}_{n-1}(L-2q,{\mathcal S}'). 
@@
 %
-After substituting in~\eref{NLS} one obtains 
+After substituting~\eref{inter} in~\eref{NLS} one obtains 
 %
@@
 \label{NLSr}
-{\mathcal N}(L,{\mathcal S})=B\Big({\mathcal N}_1(L,{\mathcal S}),\Big\lfloor \frac{s_1}{2}
-\Big\rfloor\Big){\mathcal N}(L-2q,{\mathcal S}'). 
-\end{equation}
-%
-Finally, after substituting~\eref{NLSr} in~\eref{NLlq}, one obtains a recursive relation 
-for ${\mathcal N}'(L,\ell,q)$ as 
+{\mathcal N}(L,{\mathcal S})=B\Big({\mathcal N}_1(L,{\mathcal S}),\Big\lfloor 
+\frac{s_1}{2}\Big\rfloor\Big){\mathcal N}(L-2q,{\mathcal S}'). 
+\end{equation}
+%
+Finally, using~\eref{NLSr} in~\eref{NLlq}, one obtains a recursive relation for 
+${\mathcal N}'(L,\ell,q)$ as 
 %
@@
 \label{NpLlq}
-{\mathcal N}'(L,\ell,q)=\sum_{s=0}^{q-1}B\Big(\frac{L}{2}-q+\Big\lfloor\frac{s}{2}\Big\rfloor,
-\left\lfloor\frac{s}{2}\right\rfloor\Big){\mathcal N}'\left(L-2q,\ell-q,
-q-s\right), 
-\end{equation}
-%
-with the constraint that when $\ell=q$ one has 
-%
-\begin{equation}
-{\mathcal N}'(L,q,q)=B\Big(\Big\lfloor\frac{L-q}{2}\Big\rfloor,\Big\lfloor\frac{q}{2} 
-\Big\rfloor\Big).
-\end{equation}
-%
-This is obtained by observing that if $\ell=q$ only $1$-strings are allowed and~\eref{NnLS} 
-gives ${\mathcal N}_n(L,{\mathcal S})=\lfloor (L-q)/2\rfloor$.
-
-It is straightforward to check that for even $q$ the ansatz 
-%
-\begin{equation}
+{\mathcal N}'(L,\ell,q)=\sum_{s=0}^{q-1}B\Big(\frac{L}{2}-q+\Big\lfloor
+\frac{s}{2}\Big\rfloor,\left\lfloor\frac{s}{2}\right\rfloor\Big){\mathcal N}'
+\left(L-2q,\ell-q,q-s\right), 
+\end{equation}
+%
+with the condition that for $\ell=q$ one has 
+%
+\begin{equation}
+{\mathcal N}'(L,q,q)=B\Big(\Big\lfloor\frac{L-q}{2}\Big\rfloor,\Big\lfloor
+\frac{q}{2} \Big\rfloor\Big).
+\end{equation}
+%
+This is obtained by observing that if $\ell=q$ only $1$-strings are allowed 
+and~\eref{NnLS} gives ${\mathcal N}_n(L,{\mathcal S})=\lfloor (L-q)/2\rfloor$. 
+It is straightforward to check that for $q$ even the ansatz 
+%
+\begin{equation}
+\label{inter1}
 {\mathcal N}'(L,\ell,q)=\frac{q}{\ell}B\Big(\frac{L-\ell}{2},\frac{q}{2}\Big)
@@
 % 
-satisfies~\eref{NpLlq}. For odd $q$ the solution of~\eref{NpLlq} is 
-%
-\begin{equation}
+satisfies~\eref{NpLlq}. Instead, for $q$ odd the solution of~\eref{NpLlq} is 
+%
+\begin{equation}
+\label{inter2}
 {\mathcal N}'(L,\ell,q)=\frac{\ell-q+1}{\ell}B\Big(\frac{L-\ell}{2},\frac{q-1}{2}
@@
 %
-The number of eigenstates in the sector with $\ell$ particles with nonzero 
-N\'eel overlap $Z'_{Neel}(L,\ell)$ are obtained by summing over all possible values 
-of $q$ as 
+The number of eigenstates in the sector with $\ell$ particles having nonzero N\'eel 
+overlap $Z'_{Neel}(L,\ell)$ is obtained from~\eref{inter1} and~\eref{inter2} by 
+summing over all possible values of $q$ as 
 %
@@
 %
-It is convenient to split the summation in~\eref{sum1} considering odd values of $q$ 
-and even $q$ separately. For odd $q$ one obtains 
+It is convenient to split the summation in~\eref{sum1} considering odd and even 
+$q$ separately. For $q$ odd one obtains 
 %
@@
 %
-while for even $q$ one has 
+while for $q$ even one has 
 %
@@
 The total number of eigenstates with nonzero N\'eel overlap $Z_{Neel}(L)$ 
-(cf.~\eref{N-count}) is obtained from~\eref{N-count-p} by summing over 
-the allowed values of $\ell=2k$ with $k=0,1,\dots,\ell/2$.
-
-Note that the total number $Z_{MG}$ of parity-invariant eigenstates having non 
-zero overlap with the Majumdar-Ghosh state is obtained from Eq~\eref{N-count-p} 
-replacing $\ell=L/2$, to obtain 
+(cf.~\eref{N-count}) is obtained from~\eref{N-count-p} by summing over the allowed 
+values of $\ell=2k$ with $k=0,1,\dots,\ell/2$. Note that the sum is over $\ell$ even 
+due to the parity invariance.
+
+Finally, it is interesting to observe that the total number $Z_{MG}$ of parity-invariant 
+eigenstates having non zero overlap with the Majumdar-Ghosh state is obtained from 
+Eq~\eref{N-count-p} by replacing $\ell=L/2$, to obtain 
 %
@@
 %
-Physically, this is due to the fact that the 
-Majumdar-Ghosh state is invariant under $SU(2)$ rotations, which implies 
-that only eigenstates with zero total spin $S=0$ can have non zero overlap.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Excluding the zero-momentum strings}
-\label{app-2}
-
-Here we demonstrate that the total number of eigenstates with nonzero N\'eel overlap, 
-which do not contain zero-momentum strings, $\widetilde Z_{Neel}(L)$ is given as 
+Physically, this is due to the fact that the Majumdar-Ghosh state is invariant under 
+$SU(2)$ rotations, implying that only eigenstates with zero total spin $S=0$ can have 
+non-zero overlap.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Excluding the zero-momentum strings}
+\label{app-1.2}
+
+Here we demonstrate that the total number of eigenstates $\widetilde Z_{Neel}(L)$ 
+with nonzero N\'eel overlap, after excluding the zero-momentum strings, is given as 
 %
@@
 %
-Given a generic $M$-particle eigenstate of the $XXX$ chain, due to parity invariance, 
-if one excludes the zero-momentum strings only $n$-strings with length $n\le M/2$ 
-are allowed. Similarly, the string content is of the form $\widetilde{\mathcal S}
-\equiv\{\tilde s_1,\dots,\tilde s_{M/2}\}$, i.e., $\tilde s_m=0$ $\forall m>M/2$.
-Note that due to parity invariance and to the exclusion of the zero-momentum strings 
-one has that $\tilde s_m$ is always an even integer. Clearly one has $\sum_{m=1}^{M/2}
-m \tilde s_m=M$.
+In  generic $M$-particle eigenstate of the $XXX$ chain, due to parity invariance, only 
+$n$-strings with length $n\le M/2$ are allowed. The string content can be written as 
+$\widetilde{\mathcal S}\equiv\{\tilde s_1,\dots,\tilde s_{M/2}\}$, i.e., $\tilde s_m=0$ 
+$\forall m>M/2$. Moreover, due to the parity invariance one has that $\tilde s_m$ is 
+always even. Clearly one has $\sum_{m=1}^{M/2}m \tilde s_m=M$.
 

### 2015-09-28 draft/fs_qa_v3.tex
rev-28/09/2015

@@
 
-%\usepackage{cite}
+\usepackage{cite}
 
@@
 Due to the zero-momentum constraint, only parity-invariant Bethe states can have non-zero 
-N\'eel overlap~\cite{brockmann-2014}. Parity-invariant Bethe states contain only pairs of 
+N\'eel overlap~\cite{brockmann-2014,wouters-2014}. Parity-invariant Bethe states contain only pairs of 
 solutions of the Bethe equations~\eref{ba-eq} with opposite sign.  Here we denote the generic 
@@
 considering, for any $L$, the full Hilbert space of the chain. 
-The Bethe states having, in principle, non zero N\'eel overlap are the 
+The only Bethe states having, in principle, non zero N\'eel overlap are the 
 so-called parity-invariant Bethe states (see section~\ref{sec:2}). We 
 denote their total number as $Z_{Neel}$. Crucially, here we restrict 
-ourselves to the subset of parity-invariant Bethe states corresponding 
+ourselves to the subset of parity-invariant Bethe states. These correspond 
 to solutions of the Bethe-Gaudin-Takahashi (BGT) equations~\eref{bgt-eq} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Acknowledgments}
+
+We are very grateful to ... for discussions. V.~A. and P.~C acknowledge 
+support by the ERC under Starting Grant 279391 EDEQS.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \appendix
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Counting and string content of the eigenstates with nonzero overlap}
+\section{Counting and string content of the eigenstates with nonzero N\'eel and 
+Majumdar-Ghosh overlap}
 \label{app-1}
@@
 parity-invariant eigenstates of the $XXX$ chain having non-zero overlap with 
-the N\'eel state and the Majumdar-Ghosh state. We consider both the situations  
-with constrained and unconstrained string content and particle number (i.e., 
-total magnetization). In~\ref{app-1.1} we consider all possible parity-invariant 
+the N\'eel state and the Majumdar-Ghosh state. 
+%We consider both the situations  
+%with constrained and unconstrained string content and particle number (i.e., 
+%total magnetization). 
+In~\ref{app-1.1} we consider all possible parity-invariant 
 eigenstates, whereas in~\ref{app-1.2} we exclude the eigenstates containing 
@@
 \begin{equation}
+\label{result}
 \widetilde Z_{Neel}(L)=B\Big(\frac{L}{2},\frac{L}{4}\Big). 
 \end{equation}
-%
-In  generic $M$-particle eigenstate of the $XXX$ chain, due to parity invariance, only 
-$n$-strings with length $n\le M/2$ are allowed. The string content can be written as 
-$\widetilde{\mathcal S}\equiv\{\tilde s_1,\dots,\tilde s_{M/2}\}$, i.e., $\tilde s_m=0$ 
-$\forall m>M/2$. Moreover, due to the parity invariance one has that $\tilde s_m$ is 
-always even. Clearly one has $\sum_{m=1}^{M/2}m \tilde s_m=M$.
-
-The total number of parity-invariant quantum numbers $\widetilde{\mathcal N}_n$ in the 
-$n$-string sector is given as  
+One should first observe that in a generic $M$-particle eigenstate of the $XXX$ chain, 
+due to parity invariance, only $n$-strings with length $n\le M/2$ are allowed. Also, the 
+string content can be written as $\widetilde{\mathcal S}\equiv\{\tilde s_1,\dots,\tilde 
+s_{M/2}\}$, i.e., $\tilde s_m=0$ $\forall m>M/2$. Due to the parity invariance 
+one has that $\tilde s_m$ is always even. Clearly one has $\sum_{m=1}^{M/2}m \tilde 
+s_m=M$. Finally, the total number of parity-invariant quantum numbers $\widetilde{
+\mathcal N}_n$ in the $n$-string sector is given as  
 %
@@
 The proof now proceeds as in~\ref{app-1}. One can define the total number of eigenstates 
-with nonzero N\'eel overla in the sector with $\ell$ particles and $q$ different strings as 
-$\widetilde{\mathcal N}'(L,\ell,q)$. Note that due to parity invariance and the exclusion of 
-zero-momentum strings, $q$ must be even. It is straigtforward to show that $\widetilde
-{\mathcal N}'(L,\ell,q)$ obeys the recursive relation
+with nonzero N\'eel overlap in the sector with fixed $\ell$ particles and $q$ different 
+string types as $\widetilde{\mathcal N}'(L,\ell,q)$. It is straigtforward to show that 
+$\widetilde{\mathcal N}'(L,\ell,q)$ obeys the recursive relation
 %
@@
 %
-It is straightforward to check that the solution of~\eref{NpLlq-1} is given as 
+One can check that the solution of~\eref{NpLlq-1} is given as 
 %
@@
 %
-Summing over $\ell$ one obtains~\eref{neel-ov-count}.
-Similar to~\eref{p-inv-mg} the total number of eigenstates $\widetilde Z_{MG}$ 
-with no zero-momentum strings having non-zero overlap with the Majumdar-Ghosh 
-state is obtained from~\eref{neel-fi} replacing $\ell\to L/2$, to obtain 
+Summing over $\ell$ one obtains~\eref{result}. Similar to~\eref{p-inv-mg} the total number 
+of eigenstates $\widetilde Z_{MG}$ having non-zero overlap with the Majumdar-Ghosh state 
+is obtained from~\eref{neel-fi} by replacing $\ell\to L/2$, to obtain 
 %
@@
 
-In this section we provide exact diagonalization results for the overlap of both the 
-N\'eel state and the Majumdar-Ghosh (MG) state with all the eigenstates of the Heisenberg 
-spin chain with $L=12$ sites. We also provide the corresponding results obtained 
-using the string hypothesis and the overlap formulas~\eref{neel-ov} and~\eref{mg-ov}, 
-restricting ourselves to eigenstates with no zero-momentum strings.
+In this section we provide exact diagonalization results for the overlap between the 
+N\'eel state and the Majumdar-Ghosh (MG) state and all the eigenstates of the Heisenberg 
+spin chain with $L=12$ sites. For the eigenstates without zero-momentum strings, we 
+also provide the overlaps obtained using the string hypothesis~\eref{neel-ov}\eref{mg-ov}. 
+This allows to check the validity of the string hypothesis when calculating overlaps. 
+Moreover, this also provides a simple check of the counting formula~\eref{result}.
 
@@
 \label{app-neel}
-
-The overlaps between all the eigenstates of the Heisenberg spin chain and the N\'eel 
-state are reported in Table~\ref{table:neel}. The first column in the Table shows 
-the string content ${\mathcal S}\equiv\{s_1,\dots,s_M\}$, with $M$ being the number 
-of finite rapidities. The number of infinite rapidities $N_{\infty}=L/2-M$ is also 
-reported. Note that eigenstates containing infinite rapidities correspond to 
-different $S_z$ eigenvalue. The second column shows 
-$2I_n^+$, with $I_n$ the Bethe-Gaudin-Takahashi quantum number identifying the 
-BGT rapidity of the $n$-string. Due to the parity invariance only the positive 
-quantum numbers are reported. The total number of independent strings, i.e., 
-$q\equiv\sum_js_j$, is reported in the third column. The fourth column is the 
-eigenstate's energy eigenvalue $E$. The last two columns show the squared N\'eel 
-overlaps and the corresponding result obtained using the Bethe-Gaudin-Takahashi 
-equations, respectively. In the last column only the case with no zero-momentum 
-strings is considered. The deviations from the exact diagonalization results (digits 
-with different colors) have to be attributed to the string hypothesis. Notice that  
-the overlap between the N\'eel state and the $S_z=0$ eigenstate in the sector with 
-maximal total spin $S=L/2$ (first column in Table~\ref{table:neel}), is given 
-analytically as $2/B(L,L/2)$, with $B(x,y)$ the Newton binomial.
-
-Figure~\ref{fig1-BGT-check} plots the squared overlaps $|\langle\lambda|
-N\rangle|^2$ between the N\'eel state and the eigenstates of the chain. 
-The overlaps are plotted against the eigenstate energy density $E/L
-\in[-\log(2),0]$. The circles are exact diagonalization results for all 
-the chain eigenstates ($382$ eigenstates), whereas the crosses denote the 
-overlaps calculated using formula~\eref{neel-ov}, and the 
-Bethe-Gaudin-Takahashi equations. Note that only the eigenstates with 
-no zero-momentum strings are shown ($252$ eigenstates) in the Figure. 
-Panel (a) in the Figure is an overview of all the results. Panels (b)-(d) 
-correspond to zooming to the smaller overlap values $|\langle N|\lambda
-\rangle|\lesssim 0.02$, $|\langle N|\lambda\rangle|\lesssim 0.002$, and 
-$|\langle N|\lambda\rangle|\lesssim 10^{-5}$.
-
-Clearly, the overlaps decay rapidly upon increasing the energy density. 
-This is expected since the $XXX$ Hamiltonian expectation value over 
-the N\'eel state is $\langle N|{H}|N\rangle=-1/2$. Importantly, the 
-agreement between the exact diagonalization results and the results 
-obtained using the BGT equations~\eref{ba_eq} is excellent, confirming 
-the validity of the string hypothesis.
 
@@
 \toprule
-String content & $2I^+_n$ & $q$ & E & $|\langle\lambda|N\rangle|^2$ (exact) & $|\langle
+String content & $2I_n$ & $q$ & E & $|\langle\lambda|N\rangle|^2$ (exact) & $|\langle
 \lambda|N\rangle|^2$ (BGT) \\[0.3em]
@@
  The first column shows the string content of the Bethe states, including the number of infinite 
- rapidities. The second and third column show $2I_n^+$, with $I_n^+$ the BGT quantum numbers 
- identifying the different states, and the number $q$ of independent strings. In the second 
+ rapidities. The second and third column show $2I_n$, with $I_n$ the BGT quantum numbers 
+ identifying the different states, and the number $q$ of independent strings. Due to the parity invariance, 
+ only positive quantum numbers are reported. In the second 
  column only the positive BGT numbers are shown. The fourth column is the Bethe state eigenenergy. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The overlaps between all the eigenstates of the Heisenberg spin chain and the N\'eel 
+state are reported in Table~\ref{table:neel}. The first column in the Table shows 
+the string content ${\mathcal S}\equiv\{s_1,\dots,s_M\}$, with $M$ being the number 
+of finite rapidities. The number of infinite rapidities $N_{\infty}=L/2-M$ (see 
+section~\ref{sec:1.2}) is also reported. The second column shows $2I_n$, with $I_n$ 
+the Bethe-Gaudin-Takahashi quantum numbers (see section~\ref{sec:1.3}) identifying 
+the $XXX$ chain eigenstates. Due to the parity invariance, only the positive quantum 
+numbers are reported. The total number of independent strings, i.e., $q\equiv\sum_js_j$, 
+is shown in the third column. The fourth column is the eigenstates energy eigenvalue 
+$E$. The last two columns show the squared N\'eel overlaps and the corresponding result 
+obtained using the Bethe-Gaudin-Takahashi equations, respectively. In the last 
+column only the case with no zero-momentum strings is considered. The deviations 
+from the exact diagonalization results (digits with different colors) have to be 
+attributed to the string hypothesis. Notice that the overlap between the N\'eel 
+state and the $S_z=0$ eigenstate in the sector with maximal total spin $S=L/2$ 
+(first column in Table~\ref{table:neel}), is given analytically as $2/B(L,L/2)$, 
+with $B(x,y)$ the Newton binomial.
+
+Some results for a larger chain with $L=20$ sites are reported in 
+Figure~\ref{fig1-BGT-check}.  The squared overlaps $|\langle\lambda|
+N\rangle|^2$ between the N\'eel state and the $XXX$ chain eigenstates $|\lambda
+\rangle$ are plotted against the eigenstate energy density $E/L
+\in[-\log(2),0]$. The circles are exact diagonalization results for all 
+the chain eigenstates ($382$ eigenstates), whereas the crosses denote the 
+overlaps calculated using formula~\eref{neel-ov}. Note that only the 
+eigenstates with no zero-momentum strings are shown ($252$ eigenstates) 
+in the Figure. Panel (a) gives an overview of all the overlaps. Panels (b)-(d) 
+correspond to zooming to the smaller overlap values $|\langle N|\lambda
+\rangle|\lesssim 0.02$, $|\langle N|\lambda\rangle|\lesssim 0.002$, and 
+$|\langle N|\lambda\rangle|\lesssim 10^{-5}$. 
+Although some deviations are present, the overall agreement between the exact 
+diagonalization results and the Bethe ansatz is satisfactory, confirming 
+the validity of the string hypothesis for overlap calculations.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Majumdar-Ghosh overlap}
-\label{app-mg}
-The overlap between the Heisenberg chain eigenstates with the Majumdar-Ghosh state are shown in 
-Table~\ref{table:mg}. The conventions on the representation of the eigenstates is the same as in 
-Table~\ref{table:neel}. Note that in contrast with the N\'eel state, only the eigenstates with 
-zero total spin $S=0$ have non zero overlap, i.e., no eigenstates with infinite rapidities are 
-present, which reflect that the Majumdar-Ghosh state is unvariant under $SU(2)$ rotations.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \toprule
-String content & $2I^+_n$ & $q$ & E & $|\langle\lambda|MG\rangle|^2$ (exact) & $|\langle\lambda|MG\rangle|^2$ (BGT) \\[0.3em]
+String content & $2I_n$ & $q$ & E & $|\langle\lambda|MG\rangle|^2$ (exact) & $|\langle\lambda|MG\rangle|^2$ (BGT) \\[0.3em]
 \toprule
@@
  state. The first column shows the string content of the Bethe states. The second and third column show 
- $2I_n^+$, with $I_n^+$ the BGT quantum numbers identifying the different states, and the number $q$ 
- of independent strings. In the second column only the positive BGT numbers are shown. Note that, in 
+ $2I_n$, with $I_n$ the BGT quantum numbers identifying the different states, and the number $q$ 
+ of independent strings. Due to the parity invariance, we show only the positive quantum numbers. 
+ In the second column only the positive BGT numbers are shown. Note that, in 
  contrast to Table~\ref{table:neel} no states with infinite rapidities are present. The fourth column 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Majumdar-Ghosh overlap}
+\label{app-mg}
+
+The overlap between all the Heisenberg chain eigenstates with the Majumdar-Ghosh state are shown in 
+Table~\ref{table:mg} for the chain with $L=12$ sites. The conventions on the representation of 
+the eigenstates is the same as in Table~\ref{table:neel}. Note that in contrast with the N\'eel 
+state, only the eigenstates with zero total spin $S=0$ have non zero overlap, i.e., no eigenstates 
+with infinite rapidities are present, which reflect that the Majumdar-Ghosh state is unvariant 
+under $SU(2)$ rotations.
+
+\newpage
+
 %%%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{References}
 \begin{thebibliography}{99}
 
+%%% EXPERIMENTS
 \bibitem{bloch-2008}
@@
 
+%%% QUENCHES
 \bibitem{polkovnikov-2011}
@@
 
-\begin{comment}
 \bibitem{calabrese-2006}
@@
 
-\bibitem{fagotti-2013a}
-M.~Fagotti and F.~H.~L.~Essler, J.\ Stat.\ Mech.\ (2013), P07012.
-
 \bibitem{fagotti-2013}
@@
 
+\bibitem{wright-2014}
+T.~M.~Wright, M.~Rigol, M.~J.~Davis, and K.~V.~Kheruntsyan, Phys.\ Rev.\ Lett.\ {\bf 113}, 
+050601 (2014).
+
+\bibitem{pozsgay-2014}
+B.~Pozsgay, M.~Mesty\'an, M.~A.~Werner, M.~Kormos, G.~Zar\'and, and G.~Tak\'acs,
+Phys.\ Rev.\ Lett.\ {\bf 113}, 117203 (2014).
+
+\bibitem{mestyian-2015}
+M~Mesty\'an, B.~Pozsgay, G.~Tak\'acs, and M.~A.~Werner, J.\ Stat.\ Mech.\ (2015) 
+P04001.
+
+\bibitem{kcc14}
+M.~Kormos, M.~Collura, and P.~Calabrese, Phys.\ Rev.\ A {\bf 89}, 013609 
+(2014).
+
+\bibitem{kcc14a}
+P.~P.~Mazza, M.\ Collura, M.\ Kormos, and P.\ Calabrese, J.\ Stat.\ Mech.\  
+(2014) P11016.
+
+\bibitem{mossel-2012}
+J.~Mossel and J.-S.~Caux, J.\ Phys.\ A:\ Math.\ Theor.\ {\bf 45}, 
+255001 (2012).
+
+\bibitem{pozsgay-2013}
+B.~Pozsgay, J.\ Stat.\ Mech.\ (2013) P07003.
+
+\bibitem{calabrese-2014}
+P.~Calabrese and P.~Le Doussal, J.\ Stat.\ Mech.\ (2014) P05004.
+
+\bibitem{alba-2015}
+V.~Alba, arXiv:1507.06994.
+
+\bibitem{calabrese-2007}
+P.~Calabrese and J.-S.~Caux, Phys.\ Rev.\ Lett.\ {\bf 98}, 150403 (2007).
+
+\bibitem{calabrese-2007-a}
+P.~Calabrese and J.-S.~Caux, J.\ Stat.\ Mech.\ P08032 (2007).
+
 \bibitem{de-nardis-2014}
@@
 
-\bibitem{wright-2014}
-T.~M.~Wright, M.~Rigol, M.~J.~Davis, and K.~V.~Kheruntsyan, Phys.\ Rev.\ Lett.\ {\bf 113}, 
-050601 (2014).
-
 \bibitem{pozsgay-2014}
@@
 
-\bibitem{mestyian-2015}
-M~Mesty\'an, B.~Pozsgay, G.~Tak\'acs, and M.~A.~Werner, J.\ Stat.\ Mech.\ (2015) 
-P04001.
-
-\bibitem{ilievski-2015a}
-E.~Ilieveski, J.~De~Nardis, B.~Wouters, J.-S.~Caux, F.~H.~Essler, and T.~Prosen, 
-arXiv:1507.02993.
-
-\bibitem{kcc14}
-M.~Kormos, M.~Collura, and P.~Calabrese, Phys.\ Rev.\ A {\bf 89}, 013609 
-(2014).
-
-\bibitem{kcc14a}
-P.~P.~Mazza, M.\ Collura, M.\ Kormos, and P.\ Calabrese, J.\ Stat.\ Mech.\  
-(2014) P11016.
-
-\bibitem{prosen-2014}
-T.~Prosen, Nucl.\ Phys.\ B\ {\bf 886}, (2014) 1177.
-
-\bibitem{pereira-2014}
-R.~G.~Pereira, V.~Pasquier, J.~Sirker, and I.~Affleck, J.\ Stat.\ Mech.\ 
-(2014) P09037.
-
-\bibitem{ilievski-2015}
-E.~Ilievski, M.~Medejak, and T.~Prosen, arXiv:1506.05049.
-
-\bibitem{essler-2015}
-F.~H.~L.~Essler, G.~Mussardo, and M.~Panfil, Phys.\ Rev.\ A {\bf 91}, 051602 (2015).
-
-\bibitem{cardy-2015}
-J.~Cardy,  arXiv:1507.07266.
-
-\bibitem{iyer-2015}
-D.~Iyer, M.~Srednicki, and M.~Rigol, Phys.\ Rev.\ E\ {\bf 91}, 062142 (2015).
-
-\bibitem{takahashi-1971} 
-M.~Takahashi, Prog.\ Theor.\ Phys.\ {\bf 46}, 401 (1971).
-
-\end{comment}
-
-\bibitem{taka-book}
-M.~Takahashi, {\it Thermodynamics of one-dimensional solvable models}, 
-Cambridge University Press, Cambridge, 1999.
-
-\bibitem{gu-2005}
-S.-J.~Gu, N.~M.~R.~Peres, Y.-Q.~Li, Eur.\ Phys.\ J.\ B {\bf 48}, 157 (2005).
-
-\bibitem{grabowski-1995}
-M.~P.~Grabowski and P.~Mathieu, Ann.\ Phys.\ N.Y. {\bf 243}, 
-299 (1995).
-
+\bibitem{brockmann-2014a}
+M.~Brockmann, B.~Wouters, D.~Fioretto, J.~De Nardis, R.~Vlijm, and J.-S.~Caux, 
+J.\ Stat.\ Mech.\ (2014) P12009.
+
+\bibitem{mazza-2015}
+P.~P.~Mazza, J.-M.~St\'ephan, E.~Canovi, V.~Alba, M.~Brockmann, and M.~Haque, 
+arXiv:1509.04666.
+
+\bibitem{fagotti-2013}
+M.~Fagotti and F.~H.~Essler, J.\ Stat.\ Mech.\ (2013) P07012.
+
+%%% BETHE ANSATZ
 \bibitem{bethe-1931}
 H.~Bethe, Z.\ Phys.\ {\bf 71}, 205 (1931).
-
-\bibitem{mossel-2012}
-J.~Mossel and J.-S.~Caux, J.\ Phys.\ A:\ Math.\ Theor.\ {\bf 45}, 
-255001 (2012).
-
-\bibitem{pozsgay-2013}
-B.~Pozsgay, J.\ Stat.\ Mech.\ (2013) P07003.
 
@@
 
+\bibitem{takahashi-1971} 
+M.~Takahashi, Prog.\ Theor.\ Phys.\ {\bf 46}, 401 (1971).
+
+\bibitem{taka-book}
+M.~Takahashi, {\it Thermodynamics of one-dimensional solvable models}, 
+Cambridge University Press, Cambridge, 1999.
+
+\bibitem{gu-2005}
+S.-J.~Gu, N.~M.~R.~Peres, Y.-Q.~Li, Eur.\ Phys.\ J.\ B {\bf 48}, 157 (2005).
+
+\bibitem{faddeev-1996}
+L.~D.~Faddeev, arXiv:9605187.
+
+\bibitem{yang-1969}
+C.~N.~Yang and C.~P.~Yang, J.\ Math.\ Phys. {\bf 10}, 1115 (1969).
+
+%%%CHARGES
+\bibitem{grabowski-1995}
+M.~P.~Grabowski and P.~Mathieu, Ann.\ Phys.\ N.Y. {\bf 243}, 
+299 (1995).
+
+\bibitem{prosen-2014}
+T.~Prosen, Nucl.\ Phys.\ B\ {\bf 886}, (2014) 1177.
+
+\bibitem{pereira-2014}
+R.~G.~Pereira, V.~Pasquier, J.~Sirker, and I.~Affleck, J.\ Stat.\ Mech.\ 
+(2014) P09037.
+
+\bibitem{ilievski-2015}
+E.~Ilievski, M.~Medejak, and T.~Prosen, arXiv:1506.05049.
+
+\bibitem{ilievski-2015a}
+E.~Ilieveski, J.~De~Nardis, B.~Wouters, J.-S.~Caux, F.~H.~Essler, and T.~Prosen, 
+arXiv:1507.02993.
+
+\bibitem{essler-2015}
+F.~H.~L.~Essler, G.~Mussardo, and M.~Panfil, Phys.\ Rev.\ A {\bf 91}, 051602 (2015).
+
+\bibitem{cardy-2015}
+J.~Cardy,  arXiv:1507.07266.
+
+%%%MONTE CARLO
 \bibitem{landau-binder}
@@
 
-\bibitem{faddeev-1996}
-L.~D.~Faddeev, arXiv:9605187.
-
-\bibitem{yang-1969}
-C.~N.~Yang and C.~P.~Yang, J.\ Math.\ Phys. {\bf 10}, 1115 (1969).
-
-\bibitem{calabrese-2014}
-P.~Calabrese and P.~Le Doussal, J.\ Stat.\ Mech.\ (2014) P05004.
-
-\bibitem{alba-2015}
-V.~Alba, arXiv:1507.06994.
-
-\bibitem{bethe-1931}
-H.~Bethe, Zur Theorie der Metalle. I. Eigenwerte und Eigenfunktionen 
-der linearen Atomkette, Z.\ Phys.\ {\bf 71}, 205 (1931).
-
+\bibitem{quenouille-1949} 
+M.~H.~Quenouille, Ann.\ Math.\ Statist.\ {\bf 20}, 355 (1949).
+
+\bibitem{wolff-2004} 
+U.~Wolff, Comput.\ Phys.\ Comm.\ {\bf 156}, 143 (2004).
+
+%%% OVERLAPS
 \bibitem{brockmann-2014}
@@
 
-\bibitem{pozsgay-2014}
+\bibitem{pozsgay-2014a}
 B.~Pozsgay, J.\ Stat.\ Mech.\ (2014) P06011.
-
-\bibitem{calabrese-2007}
-P.~Calabrese and J.-S.~Caux, Phys.\ Rev.\ Lett.\ {\bf 98}, 150403 (2007).
-
-\bibitem{calabrese-2007-a}
-P.~Calabrese and J.-S.~Caux, J.\ Stat.\ Mech.\ P08032 (2007).
-
-\bibitem{de-nardis-2014}
-J.~De Nardis, B.~Wouters, M.~Brockmann, and J.-S.~Caux, Phys.\ Rev.\ A {\bf 89}, 
-033601 (2014).
-
-\bibitem{pozsgay-2014}
-B.~Pozsgay, M.~Mesty\'an, M.~A.~Werner, M.~Kormos, G.~Zar\'and, and G.~Tak\'acs,
-Phys.\ Rev.\ Lett.\ {\bf 113}, 117203 (2014).
-
-\bibitem{wouters-2014}
-B.~Wouters, M.~Brockmann, J.~De~Nardis, D.~Fioretto, M.~Rigol, and J.-S.~Caux, 
-Phys.\ Rev.\ Lett.\ {\bf 113}, 117202 (2014).
-
-\bibitem{mestyian-2015}
-M~Mesty\'an, B.~Pozsgay, G.~Tak\'acs, and M.~A.~Werner, J.\ Stat.\ Mech.\ (2015) 
-P04001.
-
-\bibitem{ilievski-2015a}
-E.~Ilieveski, J.~De~Nardis, B.~Wouters, J.-S.~Caux, F.~H.~Essler, and T.~Prosen, 
-arXiv:1507.02993.
-
-\bibitem{brockmann-2014a}
-M.~Brockmann, B.~Wouters, D.~Fioretto, J.~De Nardis, R.~Vlijm, and J.-S.~Caux, 
-J.\ Stat.\ Mech.\ (2014) P12009.
-
-\bibitem{mazza-2015}
-P.~P.~Mazza, J.-M.~St\'ephan, E.~Canovi, V.~Alba, M.~Brockmann, and M.~Haque, 
-arXiv:1509.04666.
-
-\bibitem{fagotti-2013}
-M.~Fagotti and F.~H.~Essler, J.\ Stat.\ Mech.\ (2013) P07012.
-
-\bibitem{grabowski-1995}
-M.~P.~Grabowski and P.~Mathieu, Ann.\ Phys.\ N.Y. {\bf 243},
-299 (1995).
-
-\bibitem{quenouille-1949} 
-M.~H.~Quenouille, Ann.\ Math.\ Statist.\ {\bf 20}, 355 (1949).
-
-\bibitem{wolff-2004} 
-U.~Wolff, Comput.\ Phys.\ Comm.\ {\bf 156}, 143 (2004).
 
@@
 
+%%%ETH
+\bibitem{alba-2015a}
+V.~Alba, Phys.\ Rev.\ B {\bf 91}, 155123 (2015).
+
+\bibitem{ikeda-2013}
+T.~N.~Ikeda, Y.~Watanabe, and M.~Ueda, Phys.\ Rev.\ E {\bf 87}, 012125 (2013).
+
 \end{thebibliography}

### 2015-10-02 draft/fs_qa_v3.tex
rev-02/10/2015

@@
 BGT equations in the thermodynamic limit is discussed in section~\ref{sec:1.4}. 
-Finally, in section~\ref{sec:1.5} we provide some exact formulas for the 
+Finally, in section~\ref{sec:1.5} we provide the exact formulas for the 
 local conserved charges of the model.
@@
 %
-The eigenenergy associated to the eigenstate~\eref{ba-eig} is  
+The eigenenergy associated with the eigenstate~\eref{ba-eig} is  
 %
@@
 $J_\alpha$ are half-integers and integers for $L-M$ even and odd, 
-respectively.
-
-Finally, one should remark that $M$-particle eigenstates corresponding to 
+respectively~\cite{taka-book}.
+
+Importantly, the $M$-particle Bethe states~\eref{ba-eig} corresponding to 
 {\it finite} rapidities are eigenstates with maximum allowed magnetization 
@@
 are obtained by multiple applications of the total-spin lowering operator 
-$S_T^-\equiv\sum_iS_i^-$ on the highest-weight eigenstates. In the Bethe ansatz 
-framework the rapidities of a generic $M$-particle descendant eigenstate with 
-$S_T^T=L/2-M'$, with $M'<M$, are obtained by supplementing the $M$ rapidities 
-of the highest-weight state with $M'-M$  infinite rapidities. We anticipate 
-that descendant eigenstates have non-zero overlap with the zero-momentum 
+$S_T^-\equiv\sum_iS_i^-$ on the highest-weight states. In the Bethe ansatz 
+framework, given a highest-weight eigenstate with $M'$ particles (i.e., $M'$ 
+finite rapidities), its descendants are obtained by supplementing the $M'$ 
+rapidities with infinite rapidities. We anticipate that descendant eigenstates 
+are important here since they have non-zero overlap with the zero-momentum 
 N\'eel state (cf. section~\ref{sec:2}).
@@
 deviations, which typically, i.e., for most of the chain eigenstates, vanish 
-exponentially with $L$ in the thermodynamic limit. 
-Note that real rapidities correspond to strings of unit length ($1$-strings), i.e., 
-$n=1$ in Eq.~\eref{str-hyp}.
+exponentially with $L$ in the thermodynamic limit. Note that real rapidities 
+correspond to strings of unit length ($1$-strings), i.e., $n=1$ in Eq.~\eref{str-hyp}.
 
 The string centers $\lambda_{n;\gamma}$ are obtained by solving the so-called 
-Bethe-Gaudin-Takahashi equations
+Bethe-Gaudin-Takahashi equations~\cite{taka-book}
 %
@@
 %
-The generalized scattering phases $\Theta_{m,n}$ read 
+Here the generalized scattering phases $\Theta_{m,n}$ read 
 %
@@
 %
-with $\theta_\alpha(x)\equiv 2\arctan(x/\alpha)$. Here $I_{n;\gamma}$ are the 
+with $\theta_\alpha(x)\equiv 2\arctan(x/\alpha)$, and $I_{n;\gamma}$  the 
 Bethe-Takahashi quantum numbers associated with $\lambda_{n;\gamma}$. 
-The solutions of~\eref{bgt-eq}, and the Bethe states thereof, are naturally 
-classified according to their ``string content'' ${\mathcal S}\equiv\{s_n
-\}_{n=1}^M$, with $s_n$ the number of $n$-strings. Clearly, the constraint 
-$\sum_{n=1}^{M}n s_n=M$ has to be satisfied. It can be shown that 
+The solutions of~\eref{bgt-eq}, and the Bethe states~\eref{ba-eig} thereof, 
+are naturally classified according to their ``string content'' ${\mathcal S}
+\equiv\{s_n\}_{n=1}^M$, with $s_n$ the number of $n$-strings. Clearly, the 
+constraint $\sum_{n=1}^{M}n s_n=M$ has to be satisfied. It can be shown that 
 the BGT quantum numbers $I_{n;\gamma}$ associated with the $n$-strings are 
 integers and half-integers for $L-s_n$ odd and even, respectively. 
-An upper bound for the BGT quantum numbers can be derived as~\cite{taka-book} 
+Moreover, an upper bound for the BGT quantum numbers can be 
+derived as~\cite{taka-book} 
 %
@@
 \lambda)\}_{n=1}^\infty$, with $\rho_n(\lambda)\equiv\lim_{L\to\infty}[
-\lambda_{n;\gamma+1}-\lambda_{n;\gamma}]^{-1}$. Thus the  BGT 
+\lambda_{n;\gamma+1}-\lambda_{n;\gamma}]^{-1}$. As a consequence, the  BGT 
 equations~\eref{bgt-eq} become an infinite set of coupled non-linear integral 
@@
 %
-where $\rho_n^{h}$ are the hole-distributions, and the functions $a_n(\lambda)$ 
-are defined as 
+where $\rho_n^{h}$ are the so-called hole-distributions, and the functions 
+$a_n(\lambda)$ are defined as 
 %
@@
 %
-For a generic smooth enough observable ${\mathcal O}$ in the thermodynamic 
-limtit its expectation value is expected to become a functional of the root 
+Given a generic, smooth enough, observable ${\mathcal O}$, in thermodynamic 
+limit its eigenstate expectation value is replaced by a functional of the root 
 densities $\pmb{\rho}$ as $\langle\pmb{\rho}|{\mathcal O}|\pmb{\rho}\rangle$. 
-
-Moreover, for all the local observables considered in this work the contribution of the 
-different type of strings factorize and one can write 
+Moreover, we should stress that for all the local observables considered here 
+the contribution of the different type of strings factorize, and $\langle\pmb{
+\rho}|{\mathcal O}|\pmb{\rho}\rangle$ becomes 
 %
@@
 % 
-with ${\mathcal O}_n(\lambda)$ the ... .
+with ${\mathcal O}_n(\lambda)$ the .
 
@@
 \begin{equation}
+\label{qa-term}
 L{\mathcal F}(\pmb{\rho})\equiv 2\Re\log\langle\pmb{\rho}|\Psi_0
@@
 section~\ref{sec:2}). We focus on finite chains with $L\lesssim 40$ sites, 
-considering, for any $L$, the full Hilbert space of the chain. 
-The only Bethe states having, in principle, non zero N\'eel overlap are the 
-so-called parity-invariant Bethe states (see section~\ref{sec:2}). We 
-denote their total number as $Z_{Neel}$. Crucially, here we restrict 
-ourselves to the subset of parity-invariant Bethe states. These correspond 
-to solutions of the Bethe-Gaudin-Takahashi (BGT) equations~\eref{bgt-eq} 
-that do not contain zero-momentum strings. We denote the total number of 
-these eigenstates as $\widetilde Z_{Neel}$. Both $Z_{Neel}$ and $\widetilde 
-Z_{Neel}$ are given in terms of the chain length $L$ by simple combinatorial 
-formulas that we provide.
+considering, for any $L$. The only Bethe states having, in principle, non 
+zero N\'eel overlap are the so-called parity-invariant Bethe states (see 
+section~\ref{sec:2}). We denote their total number as $Z_{Neel}$. Crucially, 
+here we restrict ourselves to the parity-invariant Bethe states that do not 
+contain zero-momentum strings. We denote the total number of these eigenstates 
+as $\widetilde Z_{Neel}$. Both $Z_{Neel}$ and $\widetilde Z_{Neel}$ are given 
+in terms of the chain length $L$ by simple combinatorial formulas that we 
+provide.
+
+Interestingly, the fraction of eigenstates with no zero-momentum strings, i.e.,  
+$\widetilde Z_{Neel}/Z_{Neel}$, is vanishing as $L^{-1/2}$ in the thermodynamic 
+limit, meaning that zero-momentum strings eigenstates are dominant in number 
+for large chains. This, however, has dramatic consequences, for instance, at the 
+level of the overlap sum rules for the local conservation laws of the model. 
+Precisely, although the sum rules are fixed by the initial (N\'eel) state 
+expectation value of the local charges, we observe striking violations for 
+any finite chain. Moreover, all the sum rules exhibit vanishing behavior as 
+$L^{-1/2}$ upon increasing the chain size, reflecting the same vanishing behavior 
+as $\widetilde Z_{Neel}/Z_{Neel}$. A similar scenario holds for the overlaps with 
+the Majumdar-Ghosh state, where excluding the zero-momentum strings leads to a $1/L$ 
+behavior. This demonstrates that for finite chains the physical effects of 
+zero-momentum strings eigenstates are not negligible.
 
@@
 
-Interestingly, the fraction of eigenstates with no zero-momentum strings, i.e.,  
-$\widetilde Z_{Neel}/Z_{Neel}$, is vanishing as $L^{-1/2}$ in the thermodynamic 
-limit, meaning that zero-momentum strings eigenstates are dominant, at least 
-in number, for large chains. This has dramatic consequences, for instance, at 
-the level of the overlap sum rules for the local conservation laws of the model. 
-Precisely, although the sum rules are fixed by the initial (N\'eel) state 
-expectation value of the local charges, we observe striking violations for 
-any finite chain. Moreover, all the sum rules exhibit vanishing behavior as 
-$L^{-1/2}$ upon increasing the chain size, reflecting the same vanishing behavior 
-as $\widetilde Z_{Neel}/Z_{Neel}$. A similar scenario holds for the overlaps with 
-the Majumdar-Ghosh state, where, however, excluding the zero-momentum strings leads 
-to a $1/L$ behavior. This demonstrates that for finite chains the physical effects 
-of zero-momentum strings eigenstates are not negligible.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 overlap~\cite{brockmann-2014}. This is not related to the symmetries of the N\'eel 
-state, but to the ``accidental'' vanishing of the prefactor in the overlap 
+state, but to an ``accidental'' vanishing of the prefactor in the overlap 
 formula~\eref{neel-ov}. Finally, after excluding the zero-momentum strings 
 eigenstates, the total number of remaining eigenstates $\widetilde Z_{Neel}$, 
-which are the ones considered here, is given as (see~\ref{app-2} for the proof) 
+which are the ones considered here, is given as (see~\ref{app-1.2} for the proof) 
 %
@@
 the relevant parity-invariant BGT quantum numbers, and solving the associated BGT 
-equations~\eref{bgt-eq}, to obtain the rapidities of $XXX$ chain eigenstates. The 
-N\'eel overlaps are calculated numerically using~\eref{neel-ov}. Note that for $L=38$ 
+equations~\eref{bgt-eq}, to obtain the rapidities of $XXX$ chain eigenstates. Finally, 
+the overlaps are calculated numerically using~\eref{neel-ov}. Note that for $L=38$ 
 from~\eref{ztilde} the total number of overlap shown in the Figure is $\widetilde Z_{Neel}
@@
 
-Clearly, the overlaps decay exponentially as a function of $L$, as expected. Moreover, 
-at each finite $L$ a rapid decay as a function of $E/L$ is observed. The inset of 
-Figure~\ref{fig0:neel-ov} (a) suggests that the decay is exponential. Complementary 
-information about the overlaps is shown in Figure~\ref{fig0:neel-ov} (b) plotting the 
-histograms of $\kappa\equiv-2\log|\langle\lambda|N\rangle|/L$ (overlap distribution 
-function). Larger values of $\kappa$, correspond to a faster decay with $L$ of the 
-overlaps. The factor $1/L$ in the definition takes into account that the N\'eel 
-overlaps vanish exponentially as $|\langle\lambda|N\rangle|^2\propto e^{-\kappa L}$ in 
-the thermodynamic limit. Note that $\kappa$ is the driving term in the quench action 
-approach (cf~\eref{neel-ov-th}). As expected, from Figure~\ref{fig0:neel-ov} (b) one 
-has that the majority of the $XXX$ chain eigenstates give small N\'eel overlap (note 
-the maximum at $\kappa\sim 0.5$). Interestingly, the data suggest that with 
-$0.18\lesssim\kappa\lesssim0.7$. The vertical dash-dotted line in the figure is 
-the $\kappa$ obtained from the N\'eel overlap of the ground state of the $XXX$ 
-chain in the thermodynamic limit. This is derived using the ground state root 
-distribution $\rho_1(\lambda)\propto1/\cosh(\pi\lambda)$ and~\eref{neel-ov-th}. 
-On the other hand, the vertical dashed line denotes the N\'eel overlap $\sim 2/B(L,L/2)$ 
-of the $S_z=0$ component of the ferromagnetic multiplet, which is at the top of the
-chain energy spectrum. Finally, the vertical dotted line in Figure~\ref{fig0:neel-ov} 
-(b) shows the quench action result for $\kappa$ in the thermodynamic limit. This is 
-obtained by using~\eref{neel-ov-th} and the saddle point root distributions $\rho_n^*$ 
-(cf.~\eref{rho1-sp}-\eref{rho3-sp} for the results up to $n=3$). Note that $\kappa$ 
-does not coincide with the peak of the overlap distribution function, as expected, 
-due to the effect of the driving term~\eref{neel-ov-th} in the quench action approach.
+Clearly, from Figure~\ref{fig0:neel-ov} one has that the overlaps decay exponentially 
+as a function of $L$, as expected. Moreover, at each finite $L$ a rapid decay as a 
+function of $E/L$ is observed. The inset of Figure~\ref{fig0:neel-ov} (a) (note the 
+logarithmic scale on the $y$-axis) suggests that this decay is exponential. Complementary 
+information is shown in Figure~\ref{fig0:neel-ov} (b) plotting the histograms of $\kappa
+\equiv-2\log|\langle\lambda|N\rangle|/L$ (overlap distribution function). Larger values 
+of $\kappa$, correspond to a faster decay with $L$ of the overlaps. The factor $1/L$ 
+in the definition takes into account that the N\'eel overlaps typically vanish 
+exponentially as $|\langle\lambda|N\rangle|^2\propto e^{-\kappa L}$ in the thermodynamic 
+limit. Note that $\kappa$ is the driving term in the quench action approach (cf~\eref{neel-ov-th}). 
+As expected, from Figure~\ref{fig0:neel-ov} (b) one has that the majority of the 
+$XXX$ chain eigenstates exhibit small N\'eel overlap (note the maximum at $\kappa\sim 0.5$). 
+Interestingly, the data suggest that $0.18\lesssim\kappa\lesssim0.7$. The vertical 
+dash-dotted line in the figure is the $\kappa$ obtained from the N\'eel overlap of 
+the ground state of the $XXX$ chain in the thermodynamic limit. This is derived using 
+the ground state root distribution $\rho_1(\lambda)\propto1/\cosh(\pi\lambda)$~\cite{taka-book} 
+and~\eref{neel-ov-th}. On the other hand, the vertical dashed line denotes the N\'eel 
+overlap $\sim 2/B(L,L/2)$ of the $S_z=0$ component of the ferromagnetic multiplet, which 
+is at the top of the $XXX$ chain energy spectrum. Finally, the vertical dotted line in 
+Figure~\ref{fig0:neel-ov} (b) shows the quench action result for $\kappa$ in the thermodynamic 
+limit. This is obtained by using~\eref{neel-ov-th} and the saddle point root distributions 
+$\rho_n^*$ (cf.~\eref{rho1-sp}-\eref{rho3-sp} for the results up to $n=3$). Note that $\kappa$ 
+does not coincide with the peak of the overlap distribution function, as expected. This is  
+due to the competition between the driving term~\eref{neel-ov-th} and the Yang-Yang entropy 
+$S_{YY}$ (cf.~\eref{qa-term}) in the quench action treatment of the N\'eel quench.
 
@@
 We also consider the N\'eel expectation value of the local conserved charge 
-$Q_n$ of the $XXX$ chain (see subsection~\ref{sec:1.5}), which provide 
-the additional sum rules
+$Q_n$ of the $XXX$ chain (see subsection~\ref{sec:1.5}). These provide the 
+additional sum rules
 %
@@
 where $Q_n(\lambda)$ are the charges eigenvalues over the generic Bethe state 
-$|\lambda\rangle$ (cf.~\eref{qngnk} and~\eref{gnk}). 
-In both~\eref{sr-trivial} and~\eref{sr-charge} the sum are restricted to the 
-eigenstates with containing no zero-momentum strings. 
-In~\eref{sr-charge} $Q_n^{(0)}$ is the charge expectation value over the initial 
-state, i.e., the N\'eel state, which has been calculated in Ref.~\cite{fagotti-2013}. 
-Due to the locality of $Q_n$, the translational invariance of the initial 
+$|\lambda\rangle$ (cf.~\eref{qngnk} and~\eref{gnk}). In both~\eref{sr-trivial} 
+and~\eref{sr-charge} the sums are restricted to the eigenstates with no zero-momentum 
+strings. In~\eref{sr-charge} $Q_n^{(0)}$ is the expectation value of $Q_n$ over the 
+initial N\'eel state. $Q_n^{(0)}$ have been calculated in Ref.~\cite{fagotti-2013} 
+for any $n$. Due to the locality of $Q_n$, the translational invariance of the initial 
 state, and the periodic boundary conditions, the density $Q_n^{(0)}/L$ does 
-not depend on the chain size. For the N\'eel state, $Q_n^{(0)}$ can be calculated 
-directly in the thermodynamic limit using~\eref{q0-th} and the root distributions 
-$\pmb{\rho}^*$ (cf.~\eref{rho1-sp}-\eref{rho3-sp}).
+not depend on the chain size. Note also that the N\'eel state, $Q_n^{(0)}$ can be 
+calculated directly in the thermodynamic limit using~\eref{q0-th} and the root 
+distributions $\pmb{\rho}^*$ (cf.~\eref{rho1-sp}-\eref{rho3-sp}).
 
@@
 sum rule), are shown in Figure~\ref{fig1:neel-sr} (a) and (b), respectively. 
-Note that $Q^{(0)}_2/L=-1/2$ in~\eref{sr-charge} (horizonthal dotted line in 
-Figure~\ref{fig1:neel-sr} (b)). 
+Note that $Q^{(0)}_2/L=-1/2$ in~\eref{sr-charge} (horizonthal dotted line). 
 The circles in Figure~\ref{fig1:neel-sr} (a) are the Bethe ansatz results excluding 
@@
 strings. Moreover, in both Figure~\ref{fig1:neel-sr} (a) and (b) the data suggest a 
-vanishing behavior upon increasing $L$. The dash-dotted lines in the Figures are fits to  
-$A/L^{1/2}+B/L$, with $A,B$ fitting parameters. Interestingly, the behavior as $\propto 
+vanishing behavior upon increasing $L$. The dash-dotted lines are fits to  $A/L^{1/2}
++B/L$, with $A,B$ fitting parameters. Interestingly, the behavior as $\propto 
 L^{-1/2}$ of the sum rules reflects that of the fraction of non-zero momentum string 
-eigenstates in the thermodynamic limit $\widetilde Z_{Neel}/Z_{Neel}$. Specifically, 
-from~\eref{zneel1} and~\eref{ztilde} it is straightforward to derive that in the 
-thermodynamic limit 
+eigenstates $\widetilde Z_{Neel}/Z_{Neel}$. Specifically, from~\eref{zneel1} and~\eref{ztilde} 
+it is straightforward to derive that for $L\to\infty$
 %
@@
 
-It is interesting to observe that the large $L$ behavior as $L^{-1/2}$  is not 
-generic, meaning that it depends on the initial state $|\Psi_0\rangle$. This is 
-illustrated in Figure~\ref{fig2:dimer-sr}, focusing on the Majumdar-Ghosh (MG) 
-state. As for the N\'eel state, only parity-invariant eigenstates can have 
-non-zero Majumdar-Ghosh overlap. Their total number $Z_{MG}$ (cf.~\eref{p-inv-mg}) 
+It is interesting to observe that the large $L$ behavior as $L^{-1/2}$  of the sum 
+rules is not generic, meaning that it depends on the pre-quench initial state $|\Psi_0
+\rangle$. This is illustrated in Figure~\ref{fig2:dimer-sr}, focusing on the 
+Majumdar-Ghosh (MG) state. As for the N\'eel state, only parity-invariant eigenstates 
+can have non-zero Majumdar-Ghosh overlap. Their total number $Z_{MG}$ (cf.~\eref{p-inv-mg}) 
 is given as 
@@
 %
-Note that at any size $L$ one has $Z_{MG}<Z_{Neel}$. This is due to the fact that 
-the Majumdar-Ghosh state is invariant under $SU(2)$ rotations, since it contains 
-only spin singlets, and it has non-zero overlap only with the $S^z_T=0$ sector 
-of the $XXX$ chain spectrum. The total number of parity-invariant eigenstates 
-that contain no zero-momentum strings $\widetilde Z_{MG}$ is instead (
-cf.~\eref{mg-fi})
+As for~\eref{zneel1}, $Z_{MG}$ is only un upper bound for the number of Bethe states with 
+non-zero Majumdar-Ghosh overlaps. Note also that at any size $L$ one has $Z_{MG}<Z_{Neel}$. 
+This is due to the Majumdar-Ghosh state being invariant under $SU(2)$ rotations, since it 
+contains only spin singlets. In constrast with the N\'eel state, this implies that the 
+Majumdar-Ghosh stat has non-zero overlap only with the $S^z_T=0$ sector of the $XXX$ chain 
+spectrum. After restricting to the situation with no zero-momentum strings, the total number 
+of parity-invariant eigenstates $\widetilde Z_{MG}$ in the sector with $S_T^z=0$ is now 
+(cf.~\eref{mg-fi})
 %
@@
 
-Here, by generalizing the results presented in Ref.~\cite{alba-2015}, we present 
-a Monte Carlo implementation of the quench action approach for N\'eel quench in 
+In this section, by generalizing the results in~\cite{alba-2015}, we present 
+a Monte Carlo implementation of the quench action approach for the N\'eel quench in 
 the $XXX$ chain. The key idea is to sample the eigenstates of the finite-size $XXX$ 
-chain with the diagonal ensemble, equivalently the quench action, probability 
-distribution, given in~\eref{qa-d-ensemble}. Importantly, we consider a truncated  
-Hilbert space, restricting ourselves to the eigenstates corresponding to 
-solutions of the BGT equations with no zero-momentum strings. Our main physical 
-result is that, despite this restriction, the remaining eigenstates contain enough 
-information to correctly reproduce the post-quench thermodynamic behavior of 
-the $XXX$ chain.
+chain with the quench action probability distribution, given in~\eref{qa-d-ensemble}. 
+Importantly, we consider a truncated Hilbert space, restricting ourselves to the 
+eigenstates corresponding to solutions of the BGT equations with no zero-momentum 
+strings. Our main physical result is that, despite this restriction, the remaining 
+eigenstates contain enough information to correctly reproduce the post-quench 
+thermodynamic behavior of the $XXX$ chain.
 
@@
 thermodynamic limit. The Hilbert space truncation is reflected only in 
-$\propto 1/L$ finite-size corrections to the sum rules. In the Bethe ansatz language 
-our results mean that the eigenstates sampled by the Monte Carlo approach the 
-quench action representative state in the thermodynamic limit. This is explicitly 
-demonstrated here by numerically extracting the quench action root distributions 
-$\pmb{\rho}^*$ (cf.~\eref{rho1-sp}-\eref{rho3-sp}). The numerical results are found 
-in remarkable agreement with the quench action.
+$\propto 1/L$ finite-size corrections to the sum rules. In the Bethe ansatz 
+language the eigenstates sampled by the Monte Carlo become equivalent to the 
+quench action representative state in the thermodynamic limit. Here this is 
+explicitly demonstrated by numerically extracting the quench action root 
+distributions $\pmb{\rho}^*$ (cf.~\eref{rho1-sp}-\eref{rho3-sp}). The 
+numerical results are found in remarkable agreement with the quench action.
 
@@
 (Bethe state) of the $XXX$ chain, in the sector with zero magnetization, i.e., $M=L/2$ 
-particles. Due to the fact that the N\'eel state is not invariant under $SU(2)$ rotations, 
-in order to characterize the Bethe states one has to specify the number $N_{\infty}$ of 
-infinite rapidities. The number of remaining particles corresponding to finite roots 
-$M'$ is $M'=L/2-N_\infty$. The state is identified by a parity-invariant BGT quantum number 
-configuration that we denote as ${\mathcal C}$. Due to the parity-invariance and the 
-zero-momentum strings being excluded, ${\mathcal C}$ is identified by the number $m'$ 
-of parity-invariant rapidities $\{\pm\lambda_j\}_{j=1}^{m'}$. The string content 
-associated with the state is denoted as $\widetilde{\mathcal S}=\{\tilde s_1,\dots,
-\tilde s_{m'}\}$, where $\tilde s_n$ is the number of pairs of $n$-strings. The Monte 
-Carlo procedure generates a new parity-invariant eigenstate of the $XXX$ chain, and 
-it consists of four steps: 
+particles. As the N\'eel state is not invariant under $SU(2)$ rotations, in order to 
+characterize the Bethe states one has to specify the number $N_{\infty}$ of infinite 
+rapidities (see~\ref{sec:1.2}). The number of remaining particles corresponding to finite 
+BGT rapidities $M'$ is $M'=L/2-N_\infty$. The Bethe state is identified by a parity-invariant 
+BGT quantum number configuration that we denote as ${\mathcal C}$. Due to the parity-invariance 
+and the zero-momentum strings being excluded, ${\mathcal C}$ is identified by the 
+number $m'$ of parity-invariant quantum numbers $\{\pm I_j\}_{j=1}^{m'}$ (equivalently, 
+root pairs $\{\pm\lambda_j\}_{j=1}^{m'}$). The string 
+content associated with the state is denoted as $\widetilde{\mathcal S}=\{\tilde s_1,
+\dots,\tilde s_{m'}\}$, where $\tilde s_n$ is the number of pairs of $n$-strings. The 
+Monte Carlo procedure generates a new parity-invariant eigenstate of the $XXX$ chain, 
+and it consists of four steps: 
 %
@@
 number probabilities of the parity-invariant states, step $4$ assigns to the 
-different eigenstates the right quench action, equivalently diagonal ensemble, 
-probability.
-
-For a generic observable ${\mathcal O}$, its quench action, or diagonal ensemble 
-average, $\langle{\mathcal O}\rangle$ is obtained from the Monte Carlo simulation 
-as the arithmetic average of the eigenstates expectation values $\langle\lambda
-|{\mathcal O}|\lambda\rangle$, with $|\lambda\rangle$ the eigenstates sampled by 
-the Monte Carlo, as 
+different eigenstates the correct quench action probability.
+
+For a generic observable ${\mathcal O}$, its quench action $\langle{\mathcal O}
+\rangle$ is obtained from the Monte Carlo simulation as the arithmetic average 
+of the eigenstates expectation values $\langle\lambda|{\mathcal O}|\lambda\rangle$, 
+with $|\lambda\rangle$ the eigenstates sampled by the Monte Carlo, as 
 %
@@
 %
-Here $N_{mcs}$ being the total number of Monte Carlo steps. Note that, as usual in 
-Monte Carlo, some initial steps have to be neglected to ensure thermalization. 
-Note that~\eref{qamc-obs} can be used for any observable ${\mathcal O}$ for which 
-the the Bethe state expectation value $\langle\lambda|{\mathcal O}|\lambda\rangle$ 
-(form factor) is known.
+Here $N_{mcs}$ is the total number of Monte Carlo steps. Note that, as usual in 
+Monte Carlo, some initial steps have to be neglected to ensure equilibration. 
+Note that~\eref{qamc-obs} can be used for any observable ${\mathcal O}$ for 
+which the the Bethe state expectation value $\langle\lambda|{\mathcal O}|\lambda
+\rangle$ (form factor) is known.
 
@@
 
-The validity of the Monte Carlo approach for simulating the quench action 
-is demonstrated in Figure~\ref{fig3:neel-qamc-sr} (a)-(d). The Figure focuses on 
-the N\'eel overlap sum rules for the conserved charges densities $Q_2/L$ and $Q_4/L$ 
-(cf. subsection~\ref{sec:1.5} for the definition of the charges, and~\eref{sr-charge} 
-for the associated sum rules). We also consider the corresponding fluctuations 
+The validity of the Monte Carlo approach outlined in~\ref{sec:6.2} is demonstrated 
+in Figure~\ref{fig3:neel-qamc-sr} (a)-(d). The Figure focuses on the N\'eel overlap 
+sum rules for the conserved charges densities $Q_2/L$ and $Q_4/L$ (cf. 
+subsection~\ref{sec:1.5} for the definition of the charges, and~\eref{sr-charge} 
+for the associated sum rules). Here we also consider the corresponding fluctuations 
 $\sigma^2(Q_n)$, which are defined as 
@@
 Note that in both~\eref{sr-charge} and~\eref{sigma-sr} the sum is now over the 
-eignestates $|\lambda\rangle$ sampled by the Monte Carlo. 
+eigenstates $|\lambda\rangle$ sampled by the Monte Carlo. 
 Panel (a) and (b) in Figure~\ref{fig3:neel-qamc-sr} plot the sum rules for 
 the energy density $Q_2/L$, and its density of fluctutations $\sigma^2(Q_2)/L$. 
-It is straightforward to derive the N\'eel expectation value of the energy 
-density fluctuations as $\sigma(Q_2)/L=1/4$. This is shown as dash-dotted line 
-in Figure~\ref{fig3:neel-qamc-sr} (b).
-
-The circles in the Figure are Monte Carlo data obtained using the procedure outlined 
-in~\ref{sec:6.1} for the Heisenberg chain with $L\le 56$ sites. The data correspond 
-to Monte Carlo simulations with $N_{mcs}\sim 10^7$ Monte Carlo steps (mcs). For the 
-largest chain size $L=56$ we used $N_{mcs}\sim ...$. In all panels the $x$-axis shows 
-the inverse chain length $1/L$.
+It is straightforward to derive that $\sigma(Q_2)/L=1/4$, which is shown as dash-dotted 
+line in Figure~\ref{fig3:neel-qamc-sr} (b). 
+The circles in the Figure are Monte Carlo data for the Heisenberg chain with $L\le 56$ 
+sites. The data correspond to Monte Carlo simulations with $N_{mcs}\sim 10^7$ Monte 
+Carlo steps (mcs). In all panels the $x$-axis shows the inverse chain length $1/L$.
 
@@
 while the thermodynamic behavior after the quench is correctly reproduced. 
-Note that the data in panel (a) suggest the behavior $\propto 1/L$ for the scaling 
-corrections, as confirmed by the fit to $-1/2+A/L+b/L^2$ (dashed line in the Figure), 
+Note that the data in panel (a) are suggestive  of the behavior $\propto 1/L$ for 
+the scaling corrections, as confirmed by the fit to $-1/2+A/L+b/L^2$ (dashed line in the Figure), 
 with $A,B$ fitting parameters. The same behavior should be expected for the energy 
-fluctuations $\sigma^2(Q_2)$ (panel (b) in the Figure), although the data suggest 
-that this asymptotic behvior sets in for $L\gg 56$.
+fluctuations $\sigma^2(Q_2)$ (panel (b) in the Figure), although the asymptotic  
+behvior sets in for $L\gg 56$.
 
@@
 (cf.~\eref{rho1-sp}-\eref{rho3-sp}) $\pmb{\rho^*}=\{\rho^*_n(\lambda)\}_{n=
-1}^{\infty}$ can be extracted from the Monte Carlo simulation,  as it has been 
-done in Ref.~\cite{alba-2015} for the Generalized Gibbs Ensemble (GGE) 
-representative state.
-
-For the local observables considered here, in each eigenstate expectation value 
-$\langle\lambda|{\mathcal O}|\lambda\rangle$ in~\eref{qamc-obs} one can isolate 
-the contribution of the different string sectors as 
+1}^{\infty}$ can be extracted from the Monte Carlo simulation,  similar to 
+what has been done in Ref.~\cite{alba-2015} for the Generalized Gibbs Ensemble 
+(GGE) representative state. The idea is that for the local observables considered 
+here, in each eigenstate expectation value $\langle\lambda|{\mathcal O}|\lambda
+\rangle$ in~\eref{qamc-obs} one can isolate the contribution of the different 
+string sectors as 
 %
@@
 \langle\lambda|{\mathcal O}|\lambda\rangle=\sum\limits_{n,\gamma}{\mathcal O}_n
-(\lambda_{n;\gamma}), 
-\end{equation}
-%
-where ${\mathcal O}_n$ is the contribution of the BGT $n$-strings to the expectation 
+(\lambda_{n;\gamma}). 
+\end{equation}
+%
+Here ${\mathcal O}_n$ is the contribution of the BGT $n$-strings to the expectation 
 value of ${\mathcal O}$, and $\pm\lambda_{n;\gamma}$, with $\gamma$ labeling the 
@@
 with a standard jackknife analysis~\cite{quenouille-1949,wolff-2004}. 
-The continuous lines are the expected analytic result in the thermodynamic limit 
+The continuous lines are the expected analytic results in the thermodynamic limit 
 (cf.~\eref{rho1-sp}~\eref{rho2-sp}).
 
-Clearly, the Monte Carlo data for $\rho^*_1(\lambda)$ are in excellent agreement 
-with~\eref{rho1-sp} in the whole range $-2\le\lambda\le2$ considered. The statistical error 
-bars are smaller than the symbol size. The oscillating (with $\lambda$) corrections 
-visible at $|\lambda|\sim0.5$ are lattice effects, which decrease with the chain size 
-(see the data for $L=48$). Much larger finite-size effects are observed for 
-$\rho^*_2(\lambda)$ (panel (d) in the Figure). The corrections are larger on the tails of 
-the root distribution. Moreover, the Monte Carlo error bars are clearly visible. This is 
-due to the fact that since $\int d\lambda\rho^*_2(\lambda)/\sum_n\int d\lambda
-\rho_n^*(\lambda)\approx 0.04$, the Monte Carlo statistics available to estimate 
-$\rho_2^*(\lambda)$ is effectively reduced as compared to $\rho_1^*(\lambda)$. 
-Finally, we numerically checked that these corrections are even larger for the $3$-strings,  
-and much larger chains would be needed to extract $\rho^*_3(\lambda)$.
+Clearly, the Monte Carlo data are in excellent agreement with~\eref{rho1-sp} in the whole 
+range $-2\le\lambda\le2$ considered. For $\rho^*_1(\lambda)$ the statistical error bars 
+are smaller than the symbol size. The oscillating corrections around $|\lambda|\sim0.5$ 
+are lattice effects, which decrease with incresing the chain size 
+(see the data for $L=48$ in the Figure). Much larger finite-size effects are observed for 
+$\rho^*_2(\lambda)$ (panel (d) in the Figure). Specifically, the corrections are larger on 
+the tails of the root distribution. Moreover, the Monte Carlo error bars are clearly 
+larger than for $\rho_1^*(\lambda)$. This is due to the fact that since $\int d\lambda
+\rho^*_2(\lambda)/\sum_n\int d\lambda\rho_n^*(\lambda)\approx 0.04$, the Monte Carlo 
+statistics available for estimating $\rho_2^*(\lambda)$ is effectively reduced as 
+compared to $\rho_1^*(\lambda)$. Finally, we numerically checked that finite-size 
+corrections and Monte Carlo error bars are even larger for the $3$-strings root 
+distribution $\rho^*_3(\lambda)$, which makes its numerical determination more 
+tricky.
 
@@
 spin chains. We focused on the spin-$1/2$ isotropic Heisenberg ($XXX$) chain, considering  
-the quench from the zero-momentum N\'eel state. The method is similar to the Monte Carlo 
+the quench from the zero-momentum N\'eel state. The method is inspired by the Monte Carlo 
 approach developed in Ref.~\cite{alba-2015} to simulate the Generalized Gibbs Ensemble 
@@
 
-The approach heavily relies on the knowledge of the overlaps between the pre-quench N\'eel 
-state $|N\rangle$ and the chain eigenstates, which have been obtained recently~\cite{
+The approach relies on the knowledge of the overlaps between the pre-quench N\'eel 
+state and the $XXX$ chain  eigenstates, which have been obtained recently~\cite{
 pozsgay-2014,brockmann-2014,brockmann-2014a,brockmann-2014b,brockmann-2014c,piroli-2014}. 
-Moreover, the method is based on the detailed knowledge of the Hilbert space 
-structure of the model provided by the Bethe ansatz formalism, in particular, on the 
-so-called string hypothesis, and on the Bethe-Gaudin-Takahashi (BGT) equations. Although 
-the approach is devised for finite-size systems, thermodynamic quantities can be extracted 
-using finite-size scaling. Importantly, we restricted ourselves to a truncated Hilbert space, 
+The method is based on the detailed knowledge of the Hilbert space structure of the model 
+provided by the Bethe ansatz formalism, in particular, on the so-called string hypothesis, 
+and on the Bethe-Gaudin-Takahashi (BGT) equations. Although the approach is devised for 
+finite-size systems, thermodynamic quantities can be extracted using finite-size scaling. 
+Importantly, we restricted ourselves to a truncated Hilbert space, which is obtained by 
 excluding the chain eigenstates containing zero-momentum strings. The reason is that 
 zero-momentum strings lead to singularities in the N\'eel overlap formulas, which are 
-tricky to deal with in the framework of the string hypothesis. Note that for the same 
-reason the zero-momentum strings are neglected in the quench action approach~\cite{brockmann-2014} 
-as well, although it has been argued that their effect should be irrelevant in the 
+tricky to deal with in the framework of the string hypothesis. Note that it has been 
+argued that the physical effects of these eigenstates should be irrelevant in the 
 thermodynamic limit~\cite{brockmann-2014}.
@@
 In order to understand the effect of the zero-momentum strings in {\it finite} chains 
-we first investigated the overlap distribution, including {\it all} the eigenstates 
-with no zero-momentum strings, for chains up to $L=38$ sites. Interestingly, the total 
-number of eigenstates having, in principle, non-zero N\'eel overlap is given in terms of 
-the chain length by a simple combinatorial formula that we provided. Additional 
-combinatorial formulas are provided for the case without zero-momentum strings, or 
-at fixed particle number (i.e., magnetization), or fixed ``string content'' of the 
-eigenstates. Surprisingly, for any finite chain the majority of eigenstates contain 
-zero-momentum strings. Moreover, the fraction of eigenstates with nonzero-momentum 
-strings vanishes as $L^{-1/2}$ in the thermdodynamic limit. This is reflected in the 
-N\'eel overlap sum rules for the local conserved charges of the model. 
+we first investigated the full overlap distribution function for chains up to $L=38$ sites. 
+The eigenstates having, in principle, non-zero N\'eel overlap are the so-called 
+parity-invariant eigenstates. Their total number is given in terms of the chain length 
+by a simple combinatorial formula that we provided. We also provided additional  
+formulas for the total number of eigenstates with non-zero N\'eel overlap and no 
+zero-momentum strings, in the different magnetization sectors, and for fixed eigenstate 
+``string content''. We found that for any finite chain the majority of eigenstates 
+contain zero-momentum strings. Specifically, the fraction of eigenstates with nonzero-momentum 
+strings vanishes as $L^{-1/2}$ in the thermdodynamic limit. This is dramatically reflected 
+in the N\'eel overlap sum rules for the local conserved charges of the $XXX$ chain. 
 Although for any chain size their value is fixed by the N\'eel state expectation 
-value, violations of the sum rules are observed, due to the Hilbert space truncation. 
-Moreover, we numerically observed that the sum rules vanish as $L^{-1/2}$ in the 
+value, violations are observed. Moreover, the sum rules vanish as $L^{-1/2}$ in the 
 thermodynamic limit. This behavior reflects the vanishing of the fraction of 
 eigenstates with no zero-momentum strings, confirming that their contribution 
-cannot be trivially neglected. This behavior as$L^{-1/2}$, however, is not generic, 
-but it depends on the pre-quench initial state. This was demonstrated by 
+cannot be trivially neglected. This behavior as $L^{-1/2}$, however, is not generic, 
+but it depends on the pre-quench initial state. This was demonstrated here by 
 considering the quench from the Majumdar-Ghosh state. We observed that the sum 
@@
 
-Next we presented a Monte Carlo implementation of the quench action method. 
-We numerically demonstrated the validity of the approach, focusing on the N\'eel 
+Finally, we presented a Monte Carlo implementation of the quench action method. 
+We numerically demonstrated the validity of the approach focusing on the N\'eel 
 overlap sum rules for the local conserved quantities of the $XXX$ chain. Although 
@@
 model. Finally, following Ref.~\cite{alba-2015} we extracted from the Monte Carlo 
-the quench action BGT root distributions. Although finite-size oscillating 
-corrections are present, already for relatively small chains with $L=56$ sites, 
-the first two BGT root distributions are in impressive agreement with the 
-analytic result in the thermodynamic limit.
+the quench action BGT root distributions. Although finite-size corrections are 
+present, already for relatively small chains with $L=56$ sites, the first two 
+BGT root distributions are in impressive agreement with the analytic (quench action) 
+result in the thermodynamic limit.
 

### 2015-10-04 draft/fs_qa_v3.tex
rev-05/10/2015

@@
 
+Understanding the out-of-equilibrium dynamics in {\it isolated} quantum 
+many-body systems is one of the most intriguing research topics in 
+contemporary physics~\cite{polkovnikov-2011}, both theoretically and 
+experimentally. The most common out-of-equilibrium protocol is the {\it 
+quantum quench} in which a system is initially prepared in an eigenstate 
+$|\Psi_0\rangle$ of a many-body hamiltonian ${\mathcal H}$. Then a global 
+parameter of the hamiltonian is suddenly changed, and the system is let 
+to evolve unitarily under a new Hamiltonian ${\mathcal H}'$.
+
+While there is now compelling evidence that at long times after the 
+quench a steady state arises, its nature is still highly debated. 
+In the thermodynamic limit it is natural to expect that the steady-state 
+value of any local observable ${\mathcal O}$ is given by the so-called 
+diagonal ensemble as 
+%
+\begin{equation}
+\label{d-ensemble}
+\langle{\mathcal O}\rangle_{DE}=\sum\limits_{\lambda}|\langle\Psi_0|\lambda
+\rangle|^2\langle\lambda|{\mathcal O}|\lambda\rangle,
+\end{equation}
+%
+where the sum is over the eigenstates $|\lambda\rangle$ of the post-quench 
+final hamiltonian ${\mathcal H}'$. For generic, i.e., non-integrable, models 
+the Eigenstate Thermalization Hypothesis ensures that the ensemble~\eref{d-ensemble} 
+becomes equivalent to the Gibbs (thermal) ensemble, implying 
+%
+\begin{equation}
+\langle{\mathcal O}\rangle_{DE}=\langle{\mathcal O}\rangle_{Gibbs}\equiv
+\frac{1}{Z}\Tr({\mathcal O}\rho^{Gibbs}),\quad\textrm{with}\quad\rho^{Gibbs}
+=e^{-\beta{\mathcal H}'},
+\end{equation}
+%
+where $\beta$ is the inverse temperature of the system and $Z$ a normalization 
+factor. For one-dimensional integrable models, the presence of local or quasi-local 
+integrals of motion strongly affects the dynamics, preventing the onset of 
+thermal behavior at long times. It has been suggested that the long time 
+steady state behavior is described by the so-called Generalized Gibbs 
+ensemble as 
+%
+\begin{equation}
+\langle{\mathcal O}\rangle_{GGE}=\frac{1}{Z}\Tr({\mathcal O}\rho^{GGE}), 
+\quad\textrm{with}\quad\rho^{GGE}\equiv\frac{1}{Z}\exp\Big(-\sum_j\beta_jQ_j\Big)
+\end{equation}
+%
 We show that it is possible to numerically simulate the Quench Action approach 
@@
 calculation of the overlap.
-
-In the thermodynamic limit it is natural to assume that the steady-state expectation 
-values are obtained using the so-called diagonal ensemble, which is defined as 
-%
-\begin{equation}
-\label{d-ensemble}
-\langle{\mathcal O}\rangle=\sum\limits_{\alpha}|\langle\Psi_0|\alpha\rangle|^2
-\langle\alpha|{\mathcal O}|\alpha\rangle. 
-\end{equation}
-%
 
@@
 \equiv-\log\langle\alpha|\Psi_0\rangle$, with $\Re$ denoting the real part.
+
+The N\'eel state is defined as 
+%
+\begin{equation}
+\label{neel}
+|N\rangle\equiv\frac{1}{\sqrt{2}}\big(|N_1\rangle
++|N_2\rangle\big), 
+\end{equation}
+%
+with $|N_1\rangle\equiv |\uparrow\downarrow\rangle^{\otimes L/2}$, and $|N_2\rangle\equiv 
+|\downarrow\uparrow\rangle^{\otimes L/2}$. Note that $|N_1\rangle=\hat T|N_2\rangle$, 
+with $\hat T$ the one-site shift operator.
+
+The Majumdar-Ghosh state $|MG\rangle$ is defined as 
+%
+\begin{equation}
+\label{mg}
+|MG\rangle\equiv \Big(\frac{|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle}
+{\sqrt{2}}\Big)^{\otimes L/2}. 
+\end{equation}
+%
 
@@
 where $S^{\pm}_i\equiv (\sigma_i^x\pm i\sigma_i^y)/2$ are spin operators acting on the 
-site $i$, $S_i^z\equiv\sigma_i^z/2$, and $\sigma^{x,y,z}_i$ the Pauli matrices. We fix 
-$J=1$ and use periodic boundary conditions, identifying sites $L+1$ and $1$. The total 
-magnetization $S_{T}^z\equiv\sum_iS_i^z=L/2-M$, with $M$ number of down spins (particles), 
-commutes with~\eref{xxx-ham}, and it is here used to label its eigenstates.
+site $i$, $S_i^z\equiv\sigma_i^z/2$, and $\sigma^{x,y,z}_i$ the Pauli matrices. Here we 
+fix $J=1$ and use periodic boundary conditions, identifying sites $L+1$ and $1$. The 
+total magnetization $S_{T}^z\equiv\sum_iS_i^z=L/2-M$, with $M$ number of down spins 
+(particles), commutes with~\eref{xxx-ham}, and it is used to label its eigenstates.
 
@@
 x_2,\dots,x_M)$ is the eigenstate amplitude corresponding to the particles 
-being at positions $x_1,x_2,\dots, x_M$. Here $A_M(x_1,x_2,\dots, x_M)$ is 
+being at positions $x_1,x_2,\dots, x_M$. The amplitude $A_M(x_1,x_2,\dots, x_M)$ is 
 given as 
@@
 %
-Taking the logarithm on both sides in~\eref{ba-eq}, and using~\eref{rap}, 
+Taking the logarithm on both sides in~\eref{ba-eq} and using~\eref{rap}, 
 one obtains the Bethe equations in logarithmic form as 
@@
 %
-where $-L/2<J_\alpha\le L/2$ are the so-called Bethe quantum numbers. The 
-$J_\alpha$ are half-integers and integers for $L-M$ even and odd, 
-respectively~\cite{taka-book}.
+where $-L/2<J_\alpha\le L/2$ are the so-called Bethe quantum numbers. It can 
+be shown that $J_\alpha$ is half-integer(integer) for $L-M$ even(odd)~\cite{taka-book}.
 
@@
 Due to the $SU(2)$ invariance of~\eref{xxx-ham}, all the states in the same 
-$S_T$ multiplet and different $-S_T\le S_T^z\le S_T$ are eigenstates of the 
-$XXX$ chain with the same energy eigenvalue. These eigenstates (descendants) 
-are obtained by multiple applications of the total-spin lowering operator 
-$S_T^-\equiv\sum_iS_i^-$ on the highest-weight states. In the Bethe ansatz 
-framework, given a highest-weight eigenstate with $M'$ particles (i.e., $M'$ 
-finite rapidities), its descendants are obtained by supplementing the $M'$ 
-rapidities with infinite rapidities. We anticipate that descendant eigenstates 
-are important here since they have non-zero overlap with the zero-momentum 
-N\'eel state (cf. section~\ref{sec:2}).
+$S_T$ multiplet and with different $-S_T\le S_T^z\le S_T$ are eigenstates of the 
+$XXX$ chain as well, with the same energy eigenvalue. These eigenstates 
+(descendants) are obtained by multiple applications of the total-spin lowering 
+operator $S_T^-\equiv\sum_iS_i^-$ onto the highest-weight states. In the Bethe 
+ansatz framework, given a highest-weight eigenstate with $M'$ particles (i.e., 
+$M'$ finite rapidities), its descendants are obtained by supplementing the $M'$ 
+rapidities with infinite ones. We anticipate that descendant eigenstates 
+are important here since they have non-zero overlap with the N\'eel state (cf. 
+section~\ref{sec:2}).
 
@@
 
-In the thermodynamic limit $L\to\infty$ the solutions of the Bethe 
-equations~\eref{ba-eq} form particular ``string'' patterns in the complex plane, 
-(string hypothesis)~\cite{bethe-1931,taka-book}. Specifically, the rapidities 
-forming a ``string'' of length $1\le n\le M$ (that we defined here as 
-$n$-string) can be parametrized as 
+In the thermodynamic limit $L\to\infty$ the solutions of the Bethe equations~\eref{ba-eq} 
+form particular ``string'' patterns in the complex plane, (string hypothesis)~\cite{
+bethe-1931,taka-book}. Specifically, the rapidities forming a ``string'' of length $1
+\le n\le M$ (that we defined here as $n$-string) can be parametrized as 
 %
@@
 $\gamma$ labelling strings with different centers, and $j$ labelling the different 
-components of the string. In Eq.~\eref{str-hyp} $\delta_{n;\gamma}^j$ are the string 
+components of the string. In~\eref{str-hyp} $\delta_{n;\gamma}^j$ are the string 
 deviations, which typically, i.e., for most of the chain eigenstates, vanish 
 exponentially with $L$ in the thermodynamic limit. Note that real rapidities 
-correspond to strings of unit length ($1$-strings), i.e., $n=1$ in Eq.~\eref{str-hyp}.
+correspond to strings of unit length ($1$-strings, i.e., $n=1$ in~\eref{str-hyp}).
 
@@
 %
-Here the generalized scattering phases $\Theta_{m,n}$ read 
+Here the generalized scattering phases $\Theta_{m,n}(x)$ read 
 %
@@
 integers and half-integers for $L-s_n$ odd and even, respectively. 
-Moreover, an upper bound for the BGT quantum numbers can be 
-derived as~\cite{taka-book} 
+Moreover, an upper bound for $I_{n;\gamma}$ can be derived as~\cite{taka-book} 
 %
@@
 %
-where $t_{m,n}\equiv 2\mbox{min}(n,m)-\delta_{m,n}$. Using the string hypothesis 
-Bethe states energy eigenvalue~\eref{ba-ener} becomes
+where $t_{m,n}\equiv 2\mbox{min}(n,m)-\delta_{m,n}$. Using the string 
+hypothesis~\eref{str-hyp} the Bethe states energy eigenvalue~\eref{ba-ener} 
+becomes
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Thermodynamic limit}
+\subsection{The thermodynamic limit}
 \label{sec:1.4}
@@
 In the thermodynamic limit $L\to\infty$ at fixed finite particle density $M/L$ 
-the solutions of the BGT equations~\eref{bgt-eq} become dense. One then defines 
+the roots of the BGT equations~\eref{bgt-eq} become dense. One then defines 
 the BGT root distributions for the $n$-strings as $\pmb{\rho}\equiv\{\rho_n(
 \lambda)\}_{n=1}^\infty$, with $\rho_n(\lambda)\equiv\lim_{L\to\infty}[
-\lambda_{n;\gamma+1}-\lambda_{n;\gamma}]^{-1}$. As a consequence, the  BGT 
+\lambda_{n;\gamma+1}-\lambda_{n;\gamma}]^{-1}$. Consequently, the  BGT 
 equations~\eref{bgt-eq} become an infinite set of coupled non-linear integral 
@@
 %
-where $\rho_n^{h}$ are the so-called hole-distributions, and the functions 
+where $\rho_n^{h}(\lambda)$ are the so-called hole-distributions, and the functions 
 $a_n(\lambda)$ are defined as 
@@
 densities $\pmb{\rho}$ as $\langle\pmb{\rho}|{\mathcal O}|\pmb{\rho}\rangle$. 
-Moreover, we should stress that for all the local observables considered here 
-the contribution of the different type of strings factorize, and $\langle\pmb{
-\rho}|{\mathcal O}|\pmb{\rho}\rangle$ becomes 
+Moreover, for all the local observables considered here the contribution of the 
+different type of strings factorize, and $\langle\pmb{\rho}|{\mathcal O}|\pmb{\rho}
+\rangle$ becomes 
 %
@@
 % 
-with ${\mathcal O}_n(\lambda)$ the .
+with ${\mathcal O}_n(\lambda)$ the $n$-string contribution to the expectation 
+value of ${\mathcal O}$.
 
@@
 The $XXX$ chain exhibits an extensive number of mutually commuting local conserved 
-charges $Q_n$, with $n\in\mathbb{N}$, i.e., 
+charges~\cite{grabowski-1995} $Q_n$ ($n\in\mathbb{N}$), i.e., 
 %
@@
 %
-The eigenvalues $q_n$ of the conserved charges over the Bethe eigenstates 
-(cf.~\eref{ba-eig}) are given as 
+The corresponding charges eigenvalues are given as 
 %
@@
 \label{Q-def}
-\left.q_{n+1}\equiv\frac{i}{(n-1)!}\frac{d^n}{dy^n}\log\tau
+\left.Q_{n+1}\equiv\frac{i}{(n-1)!}\frac{d^n}{dy^n}\log\tau
 (y)\right|_{y=i},
@@
 %
-where $y$ is a spectral parameter and $\tau(y)$ is the Bethe state eigenvalue of the 
-so-called transfer matrix in the Algebraic Bethe Ansatz framework~\cite{kor-book}. 
-The analytic expression for $\tau(y)$ in terms of the solutions 
-$\{\lambda_\alpha\}_{\alpha=1}^M$ of the Bethe equations~\eref{ba-eq} is given as 
+where $y$ is a spectral parameter and $\tau(y)$ is the eigenvalue of the so-called 
+transfer matrix in the Algebraic Bethe Ansatz framework~\cite{kor-book}. The analytic 
+expression for $\tau(y)$ in terms of the solutions $\{\lambda_\alpha\}$ of the Bethe 
+equations~\eref{ba-eq} is given as 
 %
@@
 %
-Interestingly, from~\eref{Q-def} one has that the second term in~\eref{tau} does not 
-contribute to $q_n$, at least for $n\le L-2$. 
-For a generic Bethe state $q_n$ is obtained by summing independently the contributions 
-of the BGT roots as 
+Interestingly, one can check that the second term in~\eref{tau} does not contribute to 
+$Q_n$, at least for small enough $n\ll L$. For a generic Bethe state, using the string 
+hypothesis~\eref{str-hyp} the eigenvalue of $Q_n$ is obtained by summing 
+independently the contributions of the BGT roots (see~\eref{bgt-eq}) as 
 %
@@
 \label{qngnk}
-q_n=\sum_{k,\gamma}g_{n,k}(\lambda_{k;\gamma}).
-\end{equation}
-%
-Using the string hypothesis~\eref{str-hyp}, and~\eref{Q-def},~\eref{tau}, one obtains  
-the the first few functions $g_{n,k}$ in terms of the solutions of the BGT equations as 
+Q_n=\sum_{k,\gamma}g_{n,k}(\lambda_{k;\gamma}).
+\end{equation}
+%
+Using the string hypothesis (cf.~\eref{str-hyp}) and~\eref{Q-def}~\eref{tau}, one obtains  
+the first few functions $g_{n,k}$ in terms of the solutions of the BGT equations~\eref{bgt-eq} 
+as 
 %
@@
 \label{gnk}
-g_{3,k}=-\frac{4k\lambda_{k;\gamma}}{(\lambda_{k;\gamma}^2+k^2)^2}, &\quad  
-g_{4,k}=\frac{2k(k^2-3\lambda_{k;\gamma}^2)}{(k^2+\lambda_{k;\gamma}^2)^3}\\\nonumber 
+g_{2,k}=-\frac{2k}{\lambda^2_{k;\gamma}+k^2}, &\quad g_{3,k}=-\frac{4k\lambda_{k;\gamma}}
+{(\lambda_{k;\gamma}^2+k^2)^2}\\\nonumber  
+g_{4,k}=\frac{2k(k^2-3\lambda_{k;\gamma}^2)}{(k^2+\lambda_{k;\gamma}^2)^3}, &\quad 
 g_{5,k}=\frac{8k\lambda_{k;\gamma}(k^2-\lambda_{k;\gamma}^2)}{(k^2+
-\lambda_{k;\gamma}^2)^4}, & \quad
+\lambda_{k;\gamma}^2)^4}\\\nonumber
 g_{6,k}=-\frac{2k(5\lambda_{k;\gamma}^4-10k^2\lambda_{k;\gamma}^2+k^4)}{(k^2+
@@
 %
-Note that $q_2$ is the Bethe state energy eigenvalue and is given in~\eref{ener-str}. 
-It is also interesting to observe that $g_{n,k}$ (cf.~\eref{gnk}) is vanishing for 
-infinite BGT roots. This is expected to hold for the generic $g_{n,k}$, i.e., for any 
-$n$, and it is a consequence of the $SU(2)$ invariance of the conserved charges. Finally, 
-in the thermodynamic limit $L\to\infty$ from~\eref{qngnk} one has 
+It is interesting to observe that $g_{n,k}$ is vanishing in the limit $\lambda_{k;\gamma}\to\infty$. 
+This is expected to hold for the generic $n,k$, and it is a consequence of the $SU(2)$ invariance 
+of the conserved charges. Finally, in the thermodynamic limit $L\to\infty$ one can replace the 
+sum over $\gamma$ in~\eref{qngnk} with an integral to obtain  
 %
@@
 %
-where the BGT root distributions $\rho_k(\lambda)$ are solutions of~\eref{bgt-th}.
+where the BGT root distributions $\rho_k(\lambda)$ are solutions of the system of integral 
+equations~\eref{bgt-th}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{N\'eel state overlap}
+\subsection{N\'eel state overlaps}
 \label{sec:2.1}
@@
 Here we detail the Bethe ansatz results for the overlap of the Bethe states (cf.~\eref{ba-eig}) 
-with the zero-momentum (one-site shift invariant) N\'eel state $|N\rangle$ and the 
-Majumdar-Ghosh (MG) $|MG\rangle$ state. We stard discussing the N\'eel state. This is 
-defined as 
-%
-\begin{equation}
-\label{neel}
-|N\rangle\equiv\frac{1}{\sqrt{2}}\big(|N_1\rangle
-+|N_2\rangle\big), 
-\end{equation}
-%
-with $|N_1\rangle\equiv |\uparrow\downarrow\rangle^{\otimes L/2}$, and $|N_2\rangle\equiv 
-|\downarrow\uparrow\rangle^{\otimes L/2}$. Note that $|N_1\rangle=\hat T|N_2\rangle$, 
-with $\hat T$ the one-site shift operator.
-
-Due to the zero-momentum constraint, only parity-invariant Bethe states can have non-zero 
-N\'eel overlap~\cite{brockmann-2014,wouters-2014}. Parity-invariant Bethe states contain only pairs of 
-solutions of the Bethe equations~\eref{ba-eq} with opposite sign.  Here we denote the generic 
-parity-invariant rapidity configuration as $|\{\pm\tilde\lambda_\alpha\}_{\alpha=1}^m,n_\infty
-\rangle$, i.e., considering only positive rapidities. Here $m$ is the number of rapidity pairs. 
-Since the N\'eel state is not invariant under $SU(2)$ rotations, eigenstates with 
-infinite rapidities can have non-zero N\'eel overlaps.
-Here the number of infinite rapidities is denoted as $N_{\infty}$. Note that one has $M=L/2=
-N_\infty+2m$. We denote as $n_\infty\equiv N_\infty/L$ the density of infinite rapidities. 
-Finally, the overlap between the Bethe states and the Neel state $|N\rangle$ 
-reads~\cite{brockmann-2014,pozsgay-2014} 
+with the zero-momentum (one-site shift invariant) N\'eel state $|N\rangle$ (cf.~\eref{neel}) 
+and the Majumdar-Ghosh (MG) $|MG\rangle$ state (cf.~\eref{mg}). We stard discussing the N\'eel 
+state. Due to the zero-momentum constraint, only parity-invariant Bethe states can have non-zero 
+N\'eel overlap~\cite{brockmann-2014,wouters-2014}. The corresponding solutions of the Bethe 
+equations~\eref{ba-eq} contain only pairs of rapidities with opposite sign.  Here we denote the 
+generic parity-invariant rapidity configuration as $|\{\pm\tilde\lambda_j\}_{j=1}^m,n_\infty
+\rangle$, i.e., considering only positive rapidities (as stressed by the tilde in $\tilde
+\lambda_j$). Here $m$ is the number of rapidity pairs. Since the N\'eel state is not invariant 
+under $SU(2)$ rotations, eigenstates with infinite rapidities can have non-zero N\'eel overlaps.
+We denote the number of infinite rapidities as $N_{\infty}$. Note that one has $M=L/2=
+N_\infty+2m$. The density of infinite rapidities is denoted as $n_\infty\equiv N_\infty/L$. 
+The overlap between the Bethe states and the Neel state $|N\rangle$ reads~\cite{brockmann-2014,
+pozsgay-2014} 
 %
@@
 Ref.~\cite{brockmann-2014}, due to a factor $2$ in the definition of the 
-rapidities (see also~\eref{str-hyp}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The string hypothesis: Reduced N\'eel overlap formulas}
+rapidities (cf.~\eref{str-hyp}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The string hypothesis: Reduced formulas for the N\'eel overlaps}
 \label{sec:2.2}
@@
 limit $L\to\infty$, assuming that the rapidities form perfect strings, i.e., 
-$\delta_{n;\gamma}^j=0$ in~\eref{str-hyp}.  
-Then it is possible to rewrite~\eref{neel-ov} in terms of the string centers 
-$\tilde\lambda_{n;\alpha}$ only. Here we restrict ourselves to rapidity 
-configurations with no zero-momentum strings, i.e., with finite string 
-centers. Our results are not valid for zero-momentum strings.
-
-First, we restrict ourselves to parity-invariant string configurations, 
-i.e., considering only strings having positve string centers. We denote the 
-generic parity-invariant string configuration as $\{\tilde\lambda_{n;
-\gamma}\}$, where $\gamma$ labels the different non-zero string centers, and 
-$n$ is the string length.
-
-It is convenient to first split the indices $i,j$ of $G^\pm_{ij}$ as $i=(n,\gamma,i)$ 
-and $j=(m,\gamma',j)$, with $n,m$ being the length of the strings, $\gamma,\gamma'$ 
-labelling the corresponding string centers, and $i,j$ the components of the 
-two strings.
-
-Using~\eref{G-pm} and~\eref{K}, one has that for two consecutive rapidities in the same 
-string, i.e., for $m=n,\gamma=\gamma',|i-j|=2$, the matrices $G^{\pm}_{jk}$ become 
-ill-defined in the thermodynamic limit. Precisely, since $K_{1}(\tilde\lambda_{n;\gamma}^i-
-\tilde\lambda_{n;\gamma}^{i+1})\sim 1/(\delta_{n;\gamma}^i-\delta_{n;\gamma}^{i+1})$, 
-$G_{ij}^\pm$ diverges in the thermodynamic limit. Importantly, as the same type of 
-divergence occur in both $G^+$ and $G^-$, their ratio (cf.~\eref{neel-ov}), and 
-the overlaps, are finite.
-
-The finite part of the overlaps~\eref{neel-ov} can be calculated using the same strategy 
-as in Ref.~\cite{calabrese-2007,calabrese-2007-a} (see also Ref.~\cite{brockmann-2014}). 
-The resulting matrix $G^+$ depends only on the ``string center'' indices $(n,\gamma)$ 
+$\delta_{n;\gamma}^j=0$ in~\eref{str-hyp}. Then it is possible to 
+rewrite~\eref{neel-ov} in terms of the string centers $\tilde\lambda_{n;\alpha}$ 
+only. We restrict ourselves to parity-invariant rapidity configurations with no 
+zero-momentum strings, i.e., with finite string centers (cf.~\eref{str-hyp}). 
+We denote the generic parity-invariant string configuration as $\{\tilde
+\lambda_{n;\gamma}\}$, where $\gamma$ labels the different non-zero string 
+centers, and $n$ is the string length. Note that due to parity invariance and 
+the exclusion of zero-momentum strings, only strings of length up to $m$ are 
+allowed, with $m$ the number of parity-invariant rapidity pairs. The string 
+content (cf.~\ref{sec:1.3}) of parity-invariant Bethe states is denoted as 
+$\widetilde{\mathcal S}=\{\tilde s_1,\dots,\tilde s_{m}\}$, with $\tilde s_n$ 
+the number pairs of $n$-strings.
+
+It is convenient to split the indices $i,j$ in $G^\pm_{ij}$ (cf.~\eref{G-pm}) as 
+$i=(n,\gamma,i)$ and $j=(m,\gamma',j)$, with $n,m$ being the length of the strings, 
+$\gamma,\gamma'$ labelling the corresponding string centers, and $i,j$ the components 
+of the two strings. Using~\eref{G-pm} and~\eref{K}, one has that for two consecutive 
+rapidities in the same string, i.e., for $m=n,\gamma=\gamma',|i-j|=2$, the matrices 
+$G^{\pm}_{jk}$ become ill-defined in the thermodynamic limit. Precisely, $K_{1}(\tilde
+\lambda_{n;\gamma}^i-\tilde\lambda_{n;\gamma}^{i+1})\sim 1/(\delta_{n;\gamma}^i-
+\delta_{n;\gamma}^{i+1})$, implying that $G_{ij}^\pm$ diverges in the thermodynamic 
+limit. However, as the same type of divergence occurs in both $G^+$ and $G^-$, their 
+ratio (cf.~\eref{neel-ov}) is finite.
+
+The finite part of the ratio $\det G^+/\det G^-$ can be extracted using the same 
+strategy as in Ref.~\cite{calabrese-2007,calabrese-2007-a} (see also Ref.~\cite{brockmann-2014}). 
+One obtains that $\det G^+/\det G^-\to \det\widetilde G^+/\det\widetilde G^-$. The reduced 
+matrix $\widetilde G^+$ depends only on the ``string center'' indices $(n,\gamma)$ 
 and $(m,\gamma')$ and it is given as  
@@
 \label{red-G+}
-\fl \frac{1}{2}G^+_{(n,\gamma)(m,\gamma')}=\left\{\begin{array}{cc}
+\fl \frac{1}{2}\widetilde G^+_{(n,\gamma)(m,\gamma')}=\left\{\begin{array}{cc}
 L\theta_n'(\tilde\lambda_{n;\gamma}) -\sum\limits_{(\ell,\alpha)\ne(n,\gamma)}\Big[\Theta'_{n,\ell}
@@
 with $\Theta(x)$ as defined in~\eref{Theta}. 
-Similarly, for $G^-$ one obtains 
+Similarly, for $\widetilde G^-$ one obtains 
 %
@@
 \label{red-G-}
-\fl\frac{1}{2}G^-_{(n,\gamma)(m,\gamma')}=\left\{\begin{array}{cc}
+\fl\frac{1}{2}\widetilde G^-_{(n,\gamma)(m,\gamma')}=\left\{\begin{array}{cc}
 \fl(L-1)\theta'_n(\tilde\lambda_{n;\gamma})-2\sum\limits_{k=1}^{n-1}\theta'_k(
@@
 %
-Note that in presence of zero-momentum strings, additional divergences as $1/(\delta_{n;
-\gamma}^{i}+\delta_{n;\gamma}^{i+1})$ appear due to the term $K_1(\lambda+\mu)$ 
-(cf.~\eref{K}). It turns out that the treatment of these diverges is a challenging 
-task because it requires the precise knowledge of the string deviations, meaning 
-their dependence on $L$, for each different type of string. Some results have been 
-provided for small strings in Ref.~\cite{calabrese-2014}.
-
-Finally, using the string hypothesis and the parity-invariance condition, the multiplicative 
-prefactor in~\eref{neel-ov} can be simplified. Here we focus on a generic eigenstate of 
-the $XXX$ identified by $m$ pairs of finite rapidities. 
-Note that due to parity invariance and the exclusion of zero-momentum strings, only 
-strings of length up to $m$ are allowed. The ``reduced'' string content 
-identifying the eigenstate is denoted as $\widetilde{\mathcal S}=\{\tilde s_1,\dots,\tilde s_{m}\}$, 
-with $\tilde s_n$ the number of parity-invariant pairs of $n$-strings. Using the string 
-hypothesis and~\eref{neel-ov}, one can write 
+We should stress that in presence of zero-momentum strings, additional divergences as 
+$1/(\delta_{n;\gamma}^{i}+\delta_{n;\gamma}^{i+1})$ appear, due to the term $K_1(\lambda+\mu)$ 
+in~\eref{G-pm}. The treatment of these diverges is a challenging task because it requires, for each 
+different type of string, the precise knowledge of the string deviations, meaning their dependence 
+on $L$. Some results have been provided for small strings in Ref.~\cite{calabrese-2014}. 
+Finally, using the string hypothesis and the parity-invariance condition, the prefactor of the 
+determinant ratio in~\eref{neel-ov} becomes  
 %
@@
 \frac{1}{4^m}\prod\limits_{j=1}^m\prod\limits_{\ell=1}^{\tilde s_j}\left[\frac{\sqrt{j^2+
-\lambda^2_{j;\ell}}}{\lambda_{j;\ell}}
-\prod\limits_{k=0}^{\lceil j/2\rceil-1}\frac{(2k)^2+\lambda^2_{j;\ell}}{(2k+1)^2+
-\lambda^2_{j;\ell}}\right]^{(-1)^j}.
-\end{equation}
-%
+\tilde\lambda^2_{j;\ell}}}{\tilde\lambda_{j;\ell}}
+\prod\limits_{k=0}^{\lceil j/2\rceil-1}\frac{(2k)^2+\tilde\lambda^2_{j;\ell}}{(2k+1)^2+
+\tilde\lambda^2_{j;\ell}}\right]^{(-1)^j}, 
+\end{equation}
+%
+where $\tilde s_j$ is the number of $j$-string pairs in the Bethe state.
 
@@
 
-The Majumdar-Ghosh state $|MG\rangle$ is defined as 
-%
-\begin{equation}
-\label{mg}
-|MG\rangle\equiv \Big(\frac{|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle}
-{\sqrt{2}}\Big)^{\otimes L/2}. 
-\end{equation}
-%
-The overlap between a generic eigenstate of the $XXX$ chain and the Majumdar-Ghosh 
-state can be obtained from the N\'eel state overlap in Eq.~\eref{neel-ov} 
-as~\cite{pozsgay-2014} 
+The overlap between a generic eigenstate of the $XXX$ chain $|\{\pm\tilde\lambda_j\}
+\rangle$ and the Majumdar-Ghosh state~\eref{mg} can be obtained from the N\'eel state 
+overlap~\eref{neel-ov} as~\cite{pozsgay-2014} 
 %
@@
 \label{mg-ov}
-\langle MG|\{\pm\lambda_j\}_{j=1}^m\rangle=\prod\limits_{j=1}^m\frac{1}{2}
-\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)
-\Big(1+\frac{\lambda_j+i}{\lambda_j-i}\Big)
-\langle N|\{\pm\lambda_j\}_{j=1}^m\rangle
-\end{equation}
-%
-The mutliplicative factor in~\eref{mg-ov}, using the string hypothesis is 
-rewritten as 
+\langle MG|\{\pm\tilde\lambda_j\}_{j=1}^m\rangle=\prod\limits_{j=1}^m\frac{1}{2}
+\Big(1-\frac{\tilde\lambda_j-i}{\tilde\lambda_j+i}\Big)
+\Big(1+\frac{\tilde\lambda_j+i}{\tilde\lambda_j-i}\Big)
+\langle N|\{\pm\tilde\lambda_j\}_{j=1}^m\rangle
+\end{equation}
+%
+Notice that the Bethe states having non-zero overlap with the Majumdar-Ghosh state 
+do not contain infinite rapidities ($N_\infty=0$), in contrast with the N\'eel case 
+(cf.~\eref{neel-ov}). Using the string hypothesis, the mutliplicative factor 
+in~\eref{mg-ov} is rewritten as 
 %
@@
 \fl\prod\limits_{j=1}^m\frac{1}{2}
-\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)
-\Big(1+\frac{\lambda_j+i}{\lambda_j-i}\Big)=\\\nonumber\qquad
+\Big(1-\frac{\tilde\lambda_j-i}{\tilde\lambda_j+i}\Big)
+\Big(1+\frac{\tilde\lambda_j+i}{\tilde\lambda_j-i}\Big)=\\\nonumber\qquad
 2^m\prod\limits_{j=1}^m\prod\limits_{\ell=1}^{\tilde s_j}
-\lambda_{j;\ell}^{1+(-1)^j}(\lambda^2_{j;\ell}+j^2)\prod\limits_{k=0}^{\lfloor 
-j/2\rfloor}\Big[\lambda_{j;\ell}^2+\Big(2k+\frac{1-(-1)^j}{2}\Big)^2\Big]^{-2}
+\tilde\lambda_{j;\ell}^{1+(-1)^j}(\tilde\lambda^2_{j;\ell}+j^2)\prod\limits_{k=0}^{
+\lfloor j/2\rfloor}\Big[\tilde\lambda_{j;\ell}^2+\Big(2k+\frac{1-(-1)^j}{2}\Big)^2
+\Big]^{-2}.
 \end{eqnarray}
@@
 
-In the thermodynamic limit $L\to\infty$ the expression for the extensive part of the 
+In the thermodynamic limit $L\to\infty$ the extensive part of the N\'eel 
 overlap~\eref{neel-ov} can be written as~\cite{brockmann-2014} 
@@
 \label{neel-ov-th}
-\fl-\lim_{L\to\infty}\log\left[\frac{\langle N|\{\pm\lambda_j\}_{j=1}^m,n_\infty
-\rangle}{|||\{\lambda_j\}_{j=1}^m,n_\infty\rangle||}\right]=\frac{L}{2}\Big(
+\fl-\lim_{L\to\infty}\log\left[\frac{\langle N|\{\pm\tilde\lambda_j\}_{j=1}^m,n_\infty
+\rangle}{|||\{\tilde\lambda_j\}_{j=1}^m,n_\infty\rangle||}\right]=\frac{L}{2}\Big(
 n_\infty\log2+\sum_{n=1}^\infty\int_0^\infty d\lambda\rho_n(\lambda)[g_n(\lambda)
@@
 %
-Note that~\eref{neel-ov-th} is extensive. Specifically, in Eq.~\eref{neel-ov-th} 
-subleading (i.e., subextensive) contributions originating from the determinant
-ratio $\det_m(G^+)/\det_m(G^-)$ are neglected. Moreover, the term in~\eref{neel-ov-th} 
-acts as a driving term in the Quech Action formalism (cf. section~\ref{sec:4}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quench Action treatment of the steady state}
+Note that~\eref{neel-ov-th} is extensive, due to the prefactor $L/2$. Also, 
+\eref{neel-ov-th} is obtained only from~\eref{neel-k}, while the subextensive 
+contributions originating from the determinant ratio $\det_m(G^+)/\det_m(G^-)$ 
+in~\eref{neel-ov} are neglected. We should mention that~\eref{neel-ov-th} 
+acts as a driving term in the quech action formalism (cf. section~\ref{sec:4}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Quench action treatment of the steady state}
 \label{sec:4}
 
-In the thermodynamic limit the sum over the model eigenstates in~\eref{d-ensemble} 
+The quench action formalism~\cite{caux-2013} allows one to construct a saddle 
+point approximation for the diagonal ensemble. First, in the 
+thermodynamic limit the sum over the chain eigenstates in~\eref{d-ensemble} 
 can be recast into a functional integral over the BGT root distributions 
@@
 Here ${\mathcal D}\pmb{\rho}\equiv\prod_{n=1}^\infty{\mathcal D}\rho_n(\lambda)$, 
-$\rho_n(\lambda)$, and $S_{YY}(\pmb{\rho})$ is the Yang-Yang entropy, which counts 
-the number of Bethe states leading to the same $\pmb{\rho}$ in the thermodynamic 
-limit. Using~\eref{eig-sum}, for a generic observable ${\mathcal O}$, its diagonal 
-ensemble expectation value~\eref{d-ensemble} becomes 
+$\rho_n(\lambda)$, and $S_{YY}(\pmb{\rho})$ is the Yang-Yang entropy
+%
+\begin{equation}
+\fl\quad S_{YY}(\pmb{\rho})\equiv L\sum_{n=1}^\infty\int_{-\infty}^{+\infty}d
+\lambda\Big[\rho_n(\lambda)\log\Big(1+\frac{\rho_n^h(\lambda)}{\rho_n(\lambda)}
+\Big)+\rho_n^h(\lambda)\log\Big(1+\frac{\rho_n(\lambda)}{\rho^h_n(\lambda)}\Big)
+\Big],
+\end{equation}
+%
+which counts the number of microscopic Bethe states~\eref{ba-eig} leading to the same 
+$\pmb{\rho}$ in the thermodynamic limit. Using~\eref{eig-sum}, the diagonal ensemble 
+expectation value~\eref{d-ensemble} of a generic observable ${\mathcal O}$ becomes 
 %
@@
 \Psi_0|\pmb{\rho}\rangle +S_{YY}(\pmb{\rho})\Big]\langle\pmb{\rho}|{\mathcal O}|
-\pmb{\rho}\rangle
+\pmb{\rho}\rangle.
 \end{equation}
@@
 values $\langle\alpha|{\mathcal O}|\alpha\rangle$ (cf.~\eref{d-ensemble}) 
-and the overlaps $\langle\Psi_0|\pmb{\rho}\rangle$ become smooth functionals 
-of the root distributions $\pmb{\rho}$.
+become smooth functionals of the root distributions $\pmb{\rho}$, whereas 
+$\langle\pmb{\rho}|\Psi_0\rangle$ for the N\'eel state is readily obtained 
+from~\eref{neel-ov-th}.
 
@@
 
-\newpage
-
 %%%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-10-25 draft/fs_qa_v4.tex
rev 25/10/2015

--- 2015-10-04 draft/fs_qa_v3.tex
@@
 
-\title{The quench action approach for integrable models: A Monte Carlo implementation}
+\title{The quench action approach for integrable models: A Monte Carlo study}
 
@@
 many-body systems is one of the most intriguing research topics in 
-contemporary physics~\cite{polkovnikov-2011}, both theoretically and 
-experimentally. The most common out-of-equilibrium protocol is the {\it 
-quantum quench} in which a system is initially prepared in an eigenstate 
-$|\Psi_0\rangle$ of a many-body hamiltonian ${\mathcal H}$. Then a global 
-parameter of the hamiltonian is suddenly changed, and the system is let 
-to evolve unitarily under a new Hamiltonian ${\mathcal H}'$.
-
-While there is now compelling evidence that at long times after the 
-quench a steady state arises, its nature is still highly debated. 
-In the thermodynamic limit it is natural to expect that the steady-state 
-value of any local observable ${\mathcal O}$ is given by the so-called 
-diagonal ensemble as 
+contemporary physics, both theoretically~\cite{polkovnikov-2011} and 
+experimentally~\cite{bloch-2008,greiner-2002,kinoshita-2006,
+hofferberth-2007,trotzky-2012,gring-2012,cheneau-2012,
+schneider-2012,kunhert-2013,langen-2013,meinert-2013,fukuhara-2013,
+ronzheimer-2013,braun-2014,langen-2015}. The most popular out-of-equilibrium 
+protocol is that of the {\it quantum quench} in which a system is initially 
+prepared in an eigenstate $|\Psi_0\rangle$ of a many-body hamiltonian ${\mathcal H}_0$. 
+Then a global parameter is suddenly changed, and the system is let to evolve 
+unitarily under a new hamiltonian ${\mathcal H}$. There is now compelling 
+evidence that at long times after the quench an equilibrium steady state 
+arises (see for instance Ref.~\cite{kinoshita-2006}).
+
+In the thermodynamic limit, due to dephasing, it is natural to expect that the 
+equilibrium value of any local observable ${\mathcal O}$ is described by the 
+so-called diagonal ensemble as 
 %
@@
 where the sum is over the eigenstates $|\lambda\rangle$ of the post-quench 
-final hamiltonian ${\mathcal H}'$. For generic, i.e., non-integrable, models 
-the Eigenstate Thermalization Hypothesis ensures that the ensemble~\eref{d-ensemble} 
-becomes equivalent to the Gibbs (thermal) ensemble, implying 
-%
-\begin{equation}
-\langle{\mathcal O}\rangle_{DE}=\langle{\mathcal O}\rangle_{Gibbs}\equiv
-\frac{1}{Z}\Tr({\mathcal O}\rho^{Gibbs}),\quad\textrm{with}\quad\rho^{Gibbs}
-=e^{-\beta{\mathcal H}'},
-\end{equation}
-%
-where $\beta$ is the inverse temperature of the system and $Z$ a normalization 
-factor. For one-dimensional integrable models, the presence of local or quasi-local 
-integrals of motion strongly affects the dynamics, preventing the onset of 
-thermal behavior at long times. It has been suggested that the long time 
-steady state behavior is described by the so-called Generalized Gibbs 
-ensemble as 
-%
-\begin{equation}
+hamiltonian ${\mathcal H}$. For generic, i.e., non-integrable, models 
+the Eigenstate Thermalization Hypothesis~\cite{deutsch-1991,srednicki-1994} 
+(ETH) implies that the diagonal ensemble~\eref{d-ensemble} becomes equivalent 
+to the usual Gibbs (thermal) ensemble. 
+%, implying 
+%
+%\begin{equation}
+%\langle{\mathcal O}\rangle_{DE}=\langle{\mathcal O}\rangle_{Gibbs}\equiv
+%\frac{1}{Z}\Tr({\mathcal O}\rho^{Gibbs}),\quad\textrm{with}\quad\rho^{Gibbs}
+%=e^{-\beta{\mathcal H}},
+%\end{equation}
+%
+%where $\beta$ is the inverse temperature of the system and $Z$ a normalization 
+%factor. 
+In integrable models, however, the presence of an extensive number of local or 
+quasi-local integrals of motion strongly affects the dynamics, preventing the onset of 
+thermal behavior. It has been suggested in Ref.~\cite{rigol-2007,rigol-2008} that   
+in this situation the post-quench steady-state can be described by the so-called 
+Generalized Gibbs Ensemble ($GGE$) as 
+%
+\begin{equation}
+\label{gge}
 \langle{\mathcal O}\rangle_{GGE}=\frac{1}{Z}\Tr({\mathcal O}\rho^{GGE}), 
-\quad\textrm{with}\quad\rho^{GGE}\equiv\frac{1}{Z}\exp\Big(-\sum_j\beta_jQ_j\Big)
-\end{equation}
-%
-We show that it is possible to numerically simulate the Quench Action approach 
-combining Monte Carlo methods and Bethe ansatz techniques.
+\quad\textrm{with}\quad\rho^{GGE}\equiv\frac{1}{Z}\exp\Big(-\sum_j\beta_jQ_j\Big). 
+\end{equation}
+%
+Here $Q_j$ are mutually commuting conserved quantities, i.e., $[{\mathcal H},Q_j]=0\,
+\forall j$ and $[Q_j,Q_k]=0\,\forall j,k$, whereas $\beta_j$ are Lagrange multipliers 
+to be fixed by imposing that  $\langle Q_j\rangle_{GGE}=\langle\Psi_0|Q_j|\Psi_0\rangle$. 
+The validity of the GGE has been confirmed in non-interacting theories~\cite{calabrese-2011,
+calabrese-2012,fagotti-2013,kcc14,kcc14a}, whereas in interacting ones the scenario is 
+still not settled. A recent work~\cite{ilievski-2015a} suggests that the $GGE$ 
+description of the steady state  is complete provided that the so-called quasi-local 
+charges~\cite{prosen-2014,pereira-2014,ilievski-2015} are included in~\eref{gge}.
+
+Valuable insights into this issue have been provided by the so-called quench-action 
+approach~\cite{caux-2013}. For Bethe ansatz integrable models this allows to construct 
+the diagonal ensemble average~\eref{d-ensemble} in the thermodynamic limit, provided 
+that the overlaps $\langle\lambda|\Psi_0\rangle$ are known. The physical idea is that 
+for large system sizes it is possible to approximate the sum over the eigenstates 
+in~\eref{d-ensemble} using a saddle point argument. Specifically, one starts with 
+rewriting~\eref{d-ensemble} as 
+%
+\begin{equation}
+\label{de1}
+\langle{\mathcal O}\rangle_{DE}= \sum\limits_{\lambda}\rho^{DE}\langle\lambda|
+{\mathcal O}|\lambda\rangle,\quad\textrm{with}\quad\rho^{DE}=\exp(-2\Re{\mathcal 
+E}(\lambda)), 
+\end{equation}
+%
+where ${\mathcal E}(\lambda)\equiv-\log\langle\lambda|\Psi_0\rangle$, and $\Re$ 
+denoting the real part. For typical initial states $|\Psi_0\rangle$
+one has ${\mathcal E}\propto L$, with $L$ the system size, reflecting  a typical 
+vanishing of the overlaps as $\langle\Psi_0|\lambda\rangle\propto e^{-c L}$. 
+Similar to the standard Thermodynamic Bethe Ansatz (TBA)~\cite{taka-book}, the 
+extensivity of 
+${\mathcal E}$ suggests that in the thermodynamic limit~\eref{de1} is dominated 
+by a saddle point. Surprisingly, for some Bethe ansatz solvable models and some 
+simple initial states standard TBA techniques, 
+complemented with analytical knowledge of the overlaps $\langle\Psi_0|\lambda
+\rangle$, allow to determine {\it analytically} this saddle point, and for some  
+local observables, the diagonal ensemble expectation values~\eref{de1}, in the 
+thermodynamic limit. This has been done succesfully for instance in the Lieb-Liniger 
+model for the quench from the Bose-Einstein condensate~\cite{de-nardis-2014} 
+(BEC) and for the $XXZ$ spin chain for the quench from the N\'eel state~\cite{wouters-2014,
+brockmann-2014}. Interestingly, recently it has been suggested that the quench action 
+approach could allow to reconstruct the full relaxation dynamics to the steady 
+state~\cite{de-nardis-2015a,de-nardis-2015}.
+
+%Formally,~\eref{de1} is equivalent to the standard Gibbs 
+%ensemble after replacing ${\mathcal H}\to{\mathcal E}$. A crucial difference is 
+%that while typical hamiltonians are local, ensuring the extensivity of the energy, 
+%this is not guaranteed for ${\mathcal E}$.
+
+Here we provide a Monte Carlo implementation of the quench action approach in the 
+finite-size spin-$1/2$ Heisenberg chain ($XXX$ chain). combining Monte Carlo methods and Bethe ansatz techniques.
 
@@
 
-It is useful to rewrite~\eref{d-ensemble} as 
-%
-\begin{equation}
-\label{qa-prob}
-\langle{\mathcal O}\rangle=\sum\limits_{\alpha}\rho^{DE}(\alpha)
-\langle\alpha|{\mathcal O}|\alpha\rangle,\quad\textrm{with}\quad 
-\rho^{DE}(\alpha)=\exp(-2\Re{\mathcal E}(\alpha)).
-\end{equation}
-%
-Here $\rho^{DE}(\alpha)$ is a diagonal ensemble density matrix, and ${\mathcal E}(\alpha)
-\equiv-\log\langle\alpha|\Psi_0\rangle$, with $\Re$ denoting the real part.
+%It is useful to rewrite~\eref{d-ensemble} as 
+%
+%\begin{equation}
+%\label{qa-prob}
+%\langle{\mathcal O}\rangle=\sum\limits_{\alpha}\rho^{DE}(\alpha)
+%\langle\alpha|{\mathcal O}|\alpha\rangle,\quad\textrm{with}\quad 
+%\rho^{DE}(\alpha)=\exp(-2\Re{\mathcal E}(\alpha)).
+%\end{equation}
+%
+%Here $\rho^{DE}(\alpha)$ is a diagonal ensemble density matrix, and ${\mathcal E}(\alpha)
+%\equiv-\log\langle\alpha|\Psi_0\rangle$, with $\Re$ denoting the real part.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overlap between the Bethe states and some initial states} 
+\section{Overlap between the Bethe states and some simple roduct states} 
 \label{sec:2}
+
+Here we detail the Bethe ansatz results for the overlap of the Bethe states (cf.~\eref{ba-eig}) 
+with the zero-momentum (one-site shift invariant) N\'eel state $|N\rangle$ (cf.~\eref{neel}) 
+and the Majumdar-Ghosh (MG) $|MG\rangle$ state (cf.~\eref{mg}). In particular, we specialize 
+the Bethe ansatz results to the case of eigenstates described by perfect strings.
 
@@
 
-Here we detail the Bethe ansatz results for the overlap of the Bethe states (cf.~\eref{ba-eig}) 
-with the zero-momentum (one-site shift invariant) N\'eel state $|N\rangle$ (cf.~\eref{neel}) 
-and the Majumdar-Ghosh (MG) $|MG\rangle$ state (cf.~\eref{mg}). We stard discussing the N\'eel 
-state. Due to the zero-momentum constraint, only parity-invariant Bethe states can have non-zero 
+We stard discussing the overlaps with the N\'eel state. Due to the zero-momentum 
+constraint, only parity-invariant Bethe states can have non-zero 
 N\'eel overlap~\cite{brockmann-2014,wouters-2014}. The corresponding solutions of the Bethe 
@@
 where $\tilde s_j$ is the number of $j$-string pairs in the Bethe state.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The low-density regime ({\bf PROBLEM !!!})}
+\label{sec:low-density}
+
+It is interesting to consider the situation with $M/L\to\infty$ (low-density limit). 
+We first consider the case with all the particles forming a single zero-momentum 
+string. Due to parity invariance only strings of even length are allowed. 
+We assume the string hypothesis~\eref{str-hyp}, restricting ourselves to zero-momentum 
+strings, i.e., 
+%
+\begin{equation}
+\lambda^{j}_{n}=-i(n-1-2j)+i\delta_{n}^j,
+\end{equation}
+%
+with $n$ the length of the string and $j$ labelling the different string components. 
+Due to parity invariance we restrict ourselves to half strings, i.e., $j=1,\dots,n/2$.
+We verified by explicit computation that for a single $m$ string one has (at leading order 
+in the string deviations) 
+%
+\begin{equation}
+\det(G^+)=-\frac{2^{n/2}}{\delta_n^{n/2}}L\prod_{j>k=1}^{n/2-1}(\delta_n^k-\delta_n^j)^{-1},
+\end{equation}
+%
+and 
+%
+\begin{equation}
+\det(G^-)=-\frac{2^{n/2}}{\delta_n^{n/2}}(L-1)\prod_{j>k=1}^{n/2-1}(\delta_n^k-\delta_n^j)^{-1}.
+\end{equation}
+%
+This implies that 
+%
+\begin{equation}
+\frac{\det_n(G^+)}{\det_n(G^-)}\to\frac{L}{L-1},\quad\forall n.
+\end{equation}
+%
+However, it is straightforward to check that  
+%
+\begin{equation}
+\prod_{j=1}^{n/2}\frac{\sqrt{\lambda_j^2+1}}{4\lambda_j}\propto\sqrt{\delta_n^{n/2}}.
+\end{equation}
+%
+{\bf The prefactor does not seem to be a simple function of $n$}.
+
+We conclude that Bethe states corresponding to a single string have zero N\'eel 
+overlap.
+
+A problem arises if one considers the Majumdar-Ghosh state. The overlap is obtained 
+rescaling the N\'eel overlap (see below) with the prefactor
+%
+\begin{equation}
+\prod\limits_{j=1}^n\frac{1}{2}
+\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big). 
+\end{equation}
+%
+Note that the product above is over all the string components. 
+For a single string one gets 
+%
+\begin{equation}
+\prod\limits_{j=1}^n\frac{1}{2}
+\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)\propto\frac{1}{\delta_n^{n/2}}.
+\end{equation}
+%
+Putting everything together one would get a diverging MG overlap which is clearly wrong.
 
@@
 
+%%%QA FULL DYNAMICS
+\bibitem{de-nardis-2015}
+J.~De~Nardis, L.~Piroli, and J.-S.~Caux, arXiv:1505.03080.
+
+\bibitem{de-nardis-2015a}
+J.~De~Nardis and J.-S.~Caux, J.\ Stat.\ Mech.\ (2014) P12012.
+
+%%% ETH
+\bibitem{deutsch-1991} 
+J.~M.~Deutsch, Phys.\ Rev.\ A\ {\bf 43}, 2046 (1991).
+
+\bibitem{srednicki-1994}
+M.~Srednicki, Phys.\ Rev.\ E\ {\bf 50}, 888 (1994).
+
 \end{thebibliography}

### 2015-11-02 draft/fs_qa_v4.tex
rev-latest

@@
 many-body systems is one of the most intriguing research topics in 
-contemporary physics, both theoretically~\cite{polkovnikov-2011} and 
-experimentally~\cite{bloch-2008,greiner-2002,kinoshita-2006,
-hofferberth-2007,trotzky-2012,gring-2012,cheneau-2012,
+contemporary physics, both experimentally~\cite{bloch-2008,greiner-2002,
+kinoshita-2006,hofferberth-2007,trotzky-2012,gring-2012,cheneau-2012,
 schneider-2012,kunhert-2013,langen-2013,meinert-2013,fukuhara-2013,
-ronzheimer-2013,braun-2014,langen-2015}. The most popular out-of-equilibrium 
-protocol is that of the {\it quantum quench} in which a system is initially 
-prepared in an eigenstate $|\Psi_0\rangle$ of a many-body hamiltonian ${\mathcal H}_0$. 
-Then a global parameter is suddenly changed, and the system is let to evolve 
-unitarily under a new hamiltonian ${\mathcal H}$. There is now compelling 
-evidence that at long times after the quench an equilibrium steady state 
-arises (see for instance Ref.~\cite{kinoshita-2006}).
-
-In the thermodynamic limit, due to dephasing, it is natural to expect that the 
-equilibrium value of any local observable ${\mathcal O}$ is described by the 
-so-called diagonal ensemble as 
+ronzheimer-2013,braun-2014,langen-2015} and theoretically~\cite{polkovnikov-2011}. 
+The most investigated protocol is that of the {\it quantum quench}, in 
+which a system is initially prepared in an eigenstate $|\Psi_0\rangle$ of 
+a many-body hamiltonian ${\mathcal H}_0$. Then a global parameter is 
+suddenly changed, and the system is let to evolve unitarily under a new 
+hamiltonian ${\mathcal H}$. There is now compelling evidence that at long 
+times after the quench an equilibrium steady state arises (see for instance 
+Ref.~\cite{kinoshita-2006}), although its nature is not fully understood yet. 
+In the thermodynamic limit, due to dephasing, it is natural to expect that 
+the equilibrium value of any local observable ${\mathcal O}$ is described 
+by the so-called diagonal ensemble as 
 %
@@
 where the sum is over the eigenstates $|\lambda\rangle$ of the post-quench 
-hamiltonian ${\mathcal H}$. For generic, i.e., non-integrable, models 
+hamiltonian ${\mathcal H}$. Moreover, for generic, i.e., non-integrable, models 
 the Eigenstate Thermalization Hypothesis~\cite{deutsch-1991,srednicki-1994} 
@@
 to the usual Gibbs (thermal) ensemble.
-%, implying 
-%
-%\begin{equation}
-%\langle{\mathcal O}\rangle_{DE}=\langle{\mathcal O}\rangle_{Gibbs}\equiv
-%\frac{1}{Z}\Tr({\mathcal O}\rho^{Gibbs}),\quad\textrm{with}\quad\rho^{Gibbs}
-%=e^{-\beta{\mathcal H}},
-%\end{equation}
-%
-%where $\beta$ is the inverse temperature of the system and $Z$ a normalization 
-%factor. 
+
 In integrable models, however, the presence of an extensive number of local or 
-quasi-local integrals of motion strongly affects the dynamics, preventing the onset of 
-thermal behavior. It has been suggested in Ref.~\cite{rigol-2007,rigol-2008} that   
-in this situation the post-quench steady-state can be described by the so-called 
-Generalized Gibbs Ensemble ($GGE$) as 
+quasi-local integrals of motion strongly affects the dynamics, preventing the 
+onset of thermal behavior. It has been suggested in Ref.~\cite{rigol-2007,
+rigol-2008} that in this situation the post-quench steady-state can be described 
+by the so-called Generalized Gibbs Ensemble ($GGE$) as 
 %
@@
 to be fixed by imposing that  $\langle Q_j\rangle_{GGE}=\langle\Psi_0|Q_j|\Psi_0\rangle$. 
+Note that for the diagonal ensemble~\eref{d-ensemble}  one has trivially that $\langle
+{\mathcal O}\rangle_{DE}=\langle\Psi_0|{\mathcal O}|\Psi_0\rangle$. We anticipate that 
+this provides  useful sum rules that will be the main object of interest in the paper. 
 The validity of the GGE has been confirmed in non-interacting theories~\cite{calabrese-2011,
 calabrese-2012,fagotti-2013,kcc14,kcc14a}, whereas in interacting ones the scenario is 
-still not settled. A recent work~\cite{ilievski-2015a} suggests that the $GGE$ 
+still not settled. Note that a recent work~\cite{ilievski-2015a} suggests that the $GGE$ 
 description of the steady state  is complete provided that the so-called quasi-local 
@@
 Valuable insights into this issue have been provided by the so-called quench-action 
-approach~\cite{caux-2013}. For Bethe ansatz integrable models this allows to construct 
-the diagonal ensemble average~\eref{d-ensemble} in the thermodynamic limit, provided 
-that the overlaps $\langle\lambda|\Psi_0\rangle$ are known. The physical idea is that 
-for large system sizes it is possible to approximate the sum over the eigenstates 
-in~\eref{d-ensemble} using a saddle point argument. Specifically, one starts with 
-rewriting~\eref{d-ensemble} as 
+approach~\cite{caux-2013}. For Bethe ansatz integrable models this method allows one 
+to construct the diagonal ensemble~\eref{d-ensemble} directly in the thermodynamic 
+limit, provided that the overlaps $\langle\lambda|\Psi_0\rangle$ are known. The 
+physical idea is that for large system sizes it is possible to approximate the sum 
+over the eigenstates in~\eref{d-ensemble} using a saddle point argument. Specifically, 
+one starts with rewriting~\eref{d-ensemble} as 
 %
@@
 where ${\mathcal E}(\lambda)\equiv-\log\langle\lambda|\Psi_0\rangle$, and $\Re$ 
-denoting the real part. For typical initial states $|\Psi_0\rangle$
-one has ${\mathcal E}\propto L$, with $L$ the system size, reflecting  a typical 
+denotes the real part. For typical initial states $|\Psi_0\rangle$
+one has ${\mathcal E}\propto L$, with $L$ the system size. This reflects the 
 vanishing of the overlaps as $\langle\Psi_0|\lambda\rangle\propto e^{-c L}$.  
-Similar to the standard Thermodynamic Bethe Ansatz (TBA)~\cite{taka-book}, the 
-extensivity of 
-${\mathcal E}$ suggests that in the thermodynamic limit~\eref{de1} is dominated 
-by a saddle point. Surprisingly, for some Bethe ansatz solvable models and some 
-simple initial states standard TBA techniques, 
-complemented with analytical knowledge of the overlaps $\langle\Psi_0|\lambda
-\rangle$, allow to determine {\it analytically} this saddle point, and for some  
-local observables, the diagonal ensemble expectation values~\eref{de1}, in the 
-thermodynamic limit. This has been done succesfully for instance in the Lieb-Liniger 
-model for the quench from the Bose-Einstein condensate~\cite{de-nardis-2014} 
-(BEC) and for the $XXZ$ spin chain for the quench from the N\'eel state~\cite{wouters-2014,
-brockmann-2014}. Interestingly, recently it has been suggested that the quench action 
-approach could allow to reconstruct the full relaxation dynamics to the steady 
-state~\cite{de-nardis-2015a,de-nardis-2015}.
-
-%Formally,~\eref{de1} is equivalent to the standard Gibbs 
-%ensemble after replacing ${\mathcal H}\to{\mathcal E}$. A crucial difference is 
-%that while typical hamiltonians are local, ensuring the extensivity of the energy, 
-%this is not guaranteed for ${\mathcal E}$.
-
-Here we provide a Monte Carlo implementation of the quench action approach in the 
-finite-size spin-$1/2$ Heisenberg chain ($XXX$ chain). combining Monte Carlo methods and Bethe ansatz techniques.
-
-We focus on the situation in which the pre-quench initial state is the Neel 
-state or the Majumdar-Ghosh state.
-
-We investigate the importance of the zero-momentum strings in the Quench Action.
-
-Without zero-momentum strings the overlap saturation rules are not valid, 
-i.e., in finite size systems the vast majority of the eigenstates contain 
-zero momentum strings.
-
-The details on the eigenstates counting depend on the pre-quench initial state.
-
-However, we show that one can restrict to the set of non-zero momentum strings. 
-The fact that one neglects zero-momentum strings gives rise only to scaling 
-corrections.
-
-We also investigate the validity of the Bethe-Takahashi approximation for the 
-calculation of the overlap.
+As in the standard Thermodynamic Bethe Ansatz (TBA)~\cite{taka-book}, the 
+extensivity of ${\mathcal E}$ suggests that in the thermodynamic limit the 
+sum in~\eref{de1} is dominated by a saddle point. Remarkably, for some Bethe 
+ansatz solvable models and for simple-enough initial states, it is possible to 
+determine this saddle point {\it analytically}. This has been done succesfully, 
+for instance, for the quench from the Bose-Einstein condensate~\cite{de-nardis-2014} 
+(BEC) in the Lieb-Liniger model and for the quench from the N\'eel 
+state~\cite{wouters-2014,brockmann-2014} in the $XXZ$ spin chain. Interestingly, 
+it has been suggested recently that the quench action approach could allow to 
+reconstruct the full relaxation dynamics to the steady state~\cite{de-nardis-2015a,
+de-nardis-2015}.
+
+\paragraph*{Outline of the results.} 
+In this paper, by combining exact Bethe ansatz and Monte Carlo techniques, we investigate 
+the diagonal ensemble and the quench action approach in {\it finite} size integrable models. 
+We focus on the spin-$1/2$ isotropic Heisenberg ($XXX$) chain with $L$ sites, which is 
+defined by the Hamiltonian 
+%
+\begin{equation}
+\label{xxx-ham}
+{\mathcal H}\equiv J\sum\limits_{i=1}^L\left[\frac{1}{2}(S_i^+S^-_{i+1} 
++S_i^{-}S_{i+1}^+)+S_i^zS_{i+1}^z-\frac{1}{4}\right].
+\end{equation}
+%
+Here $S^{\pm}_i\equiv (\sigma_i^x\pm i\sigma_i^y)/2$ are spin operators acting on the 
+site $i$, $S_i^z\equiv\sigma_i^z/2$, and $\sigma^{x,y,z}_i$ the Pauli matrices. We 
+fix $J=1$ in~\eref{xxx-ham} and use periodic boundary conditions, identifying sites 
+$L+1$ and $1$. The total magnetization $S_{T}^z\equiv\sum_iS_i^z=L/2-M$, with $M$ number 
+of down spins (particles), commutes with~\eref{xxx-ham}, and it is used to label its 
+eigenstates. The $XXX$ chain is Bethe ansatz solvable~\cite{bethe-1931} and its eigenstates 
+are in one-to-one correspondence with the solutions of the so-called Bethe equations 
+(see~\ref{sec:1.2}). We restrict ourselves to quenches from the zero-momentum N\'eel 
+state $|N\rangle$ and the Majumdar-Ghosh state $|MG\rangle$, which are defined as  
+%
+\begin{equation}
+\label{psi0}
+|N\rangle\equiv\Big(\frac{|N_1\rangle
++|N_2\rangle}{\sqrt{2}}\Big), \qquad 
+|MG\rangle\equiv \Big(\frac{|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle}
+{\sqrt{2}}\Big)^{\otimes L/2}. 
+\end{equation}
+%
+Here $|N_1\rangle\equiv |\uparrow\downarrow\rangle^{\otimes L/2}$, and $|N_2\rangle
+\equiv |\downarrow\uparrow\rangle^{\otimes L/2}$, with $\otimes$ denoting the tensor 
+product. Note that both $|N\rangle$ and $|MG\rangle$ are invariant under one site 
+translations. Our study relies on the analytical knowledge of the overlaps between 
+the N\'eel and Majumdar-Ghosh state and the eigenstates of~\eref{xxx-ham}~\cite{
+brockmann-2014,brockmann-2014a,brockmann-2014b,brockmann-2014c,pozsgay-2014a,
+piroli-2014}.
+
+We first present a detailed overview of the distribution of the overlaps between 
+the initial states and the eigenstates of the model (overlap distribution function). 
+Precisely, we provide numerical results for all the overlaps for finite chains up 
+to $L\le 38$. Our results are obtained exploiting the analytical formulas 
+presented in Ref.~\cite{brockmann-2014} and~\cite{pozsgay-2014a}. Crucially, 
+we restrict ourselves to a truncated Hilbert space, considering only eigenstates 
+of~\eref{xxx-ham} that do not contain zero-momentum strings. Physically, 
+zero-momentum strings correspond to eigenstates amplitudes containing multi-particle  
+bound states which are fully delocalized in the chain. From the Bethe ansatz perspective, 
+in the thermodynamic limit the presence of zero-momentum strings leads to fictitious 
+singularities in the overlap formulas. Dealing with these singularities is 
+a formidable task that requires detailed knowledge of the solutions of the 
+Bethe equations, and it can be done only in very simple cases, e.g., for small 
+chains. On the other hand, it has been argued that zero-momentum strings are irrelevant 
+in the thermodynamic limtit~\cite{brockmann-2014a}.
+
+For a finite chain here we find that for both the N\'eel and the Majumdar-Ghosh 
+cases, the fraction of eigenstates that do not contain zero-momentum strings 
+is vanishing in the thermodynamic limit, meaning that for finite large-enough 
+systems the vast majority of the eigenstates contain zero momentum strings. Specifically, 
+the total number of eigenstates without zero-momentum strings is given in terms of the 
+chain size $L$ by simple combinatorial formulas that we provide. We investigate the 
+effect of the Hilbert space truncation on the diagonal ensemble focusing on the  
+sum rules $\langle Q_j\rangle_{DE}=\langle\Psi_0|Q_j|\Psi_0\rangle$ for the conserved 
+quantities $Q_j$. We numerically demonstrate that truncating the diagonal ensemble to 
+eigenstates with no zero-momentum strings leads to striking violations of the sum 
+rules. Precisely, we numerically observe that the truncated diagonal ensemble 
+average $\langle Q_j\rangle$ vanish in the thermodynamic limit reflecting the 
+vanishing behavior of the fraction of finite-momentum strings eigenstates. 
+This allows us to conclude that for finite chaings eigenstates corresponding 
+to zero-momentum strings cannot be trivially neglected when considering 
+diagonal ensemble averages.
+
+However, we provide numerical evidence that the correct diagonal ensemble 
+sum rules can be recovered in the thermodynamic limit by appropriately 
+reweighting the contribution of the finite-momentum strings eigenstates.  
+We focus only on the situation with the N\'eel state (cf.~\eref{psi0}) as 
+initial state. The key idea is to sample the eigenstates with no zero-momentum 
+strings with the diagonal ensemble probability measure $\rho^{DE}$ (cf.~\eref{de1}). 
+To this purpose we develop a Monte Carlo scheme, which is a generalization of 
+the approach presented in Ref.~\cite{alba-2015} to simulate the Generalize 
+Gibbs Ensemble. The method is based on the knowledge of the N\'eel overlaps 
+$\langle\lambda|N\rangle$ and on the knowledge of the Hilbert space structure 
+of the $XXX$ chain in the Bethe ansatz formalism. The approach allowed us to 
+simulate effectively chain with $L\lesssim 60$, although larger systems 
+sizes can in principle be reached.
+
+Strikingly, although for small chains violations of the conserved quantities 
+sum rules are present, these violations vanish in the thermodynamic limit 
+and the sum rules are restored. This implies that the only effect of the 
+Hilbert space truncation is to introduce scaling corrections. In the quench 
+action language, this means that the eigenstates corresponding to no 
+zero-momentum strings contain enough physical information about saddle point. 
+This is numerically confirmed by extracting the so-called saddle point 
+root distributions, which in the Bethe ansatz language fully characterize 
+the diagonal ensemble averages in the thermodynamic limit. In the numerical  
+ approach these are obtained from the histograms of the Bethe ansatz 
+solutions sampled during the Monte Carlo. A part from finite size scaling 
+corrections, we observe striking agreement with analytical results, at least 
+for the first few root distributions.
 
@@
 
-The N\'eel state is defined as 
-%
-\begin{equation}
-\label{neel}
-|N\rangle\equiv\frac{1}{\sqrt{2}}\big(|N_1\rangle
-+|N_2\rangle\big), 
-\end{equation}
-%
-with $|N_1\rangle\equiv |\uparrow\downarrow\rangle^{\otimes L/2}$, and $|N_2\rangle\equiv 
-|\downarrow\uparrow\rangle^{\otimes L/2}$. Note that $|N_1\rangle=\hat T|N_2\rangle$, 
-with $\hat T$ the one-site shift operator.
-
-The Majumdar-Ghosh state $|MG\rangle$ is defined as 
-%
-\begin{equation}
-\label{mg}
-|MG\rangle\equiv \Big(\frac{|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle}
-{\sqrt{2}}\Big)^{\otimes L/2}. 
-\end{equation}
+%The N\'eel state is defined as 
+%
+%\begin{equation}
+%\label{neel}
+%|N\rangle\equiv\frac{1}{\sqrt{2}}\big(|N_1\rangle
+%+|N_2\rangle\big), 
+%\end{equation}
+%
+
+%The Majumdar-Ghosh state $|MG\rangle$ is defined as 
+%
+%\begin{equation}
+%\label{mg}
+%|MG\rangle\equiv \Big(\frac{|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle}
+%{\sqrt{2}}\Big)^{\otimes L/2}. 
+%\end{equation}
 %
@@
 Here we review some Bethe ansatz results for the spin-$\frac{1}{2}$ Heisenberg 
-($XXX$) chain. Specifically, in section~\ref{sec:1.1} we introduce the model. 
-Its eigenstates (Bethe states) and the Bethe equations are discussed in 
-section~\ref{sec:1.2}. Section~\ref{sec:1.3} focuses on the string hypothesis 
+($XXX$) chain. Specifically, in section~\ref{sec:1.2} discuss the structure of  
+its eigenstates (Bethe states) and the associated Bethe equations. 
+Section~\ref{sec:1.3} focuses on the string hypothesis 
 and the so-called Bethe-Gaudin-Takahashi (BGT) equations. The form of the 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The spin-$\frac{1}{2}$ Heisenberg chain}
-\label{sec:1.1}
-
-The spin-$\frac{1}{2}$ isotropic Heisenberg chain ($XXX$ chain) with $L$ sites 
-is defined by the Hamiltonian 
-%
-\begin{equation}
-\label{xxx-ham}
-{\mathcal H}\equiv J\sum\limits_{i=1}^L\left[\frac{1}{2}(S_i^+S^-_{i+1} 
-+S_i^{-}S_{i+1}^+)+S_i^zS_{i+1}^z-\frac{1}{4}\right],  
-\end{equation}
-%
-where $S^{\pm}_i\equiv (\sigma_i^x\pm i\sigma_i^y)/2$ are spin operators acting on the 
-site $i$, $S_i^z\equiv\sigma_i^z/2$, and $\sigma^{x,y,z}_i$ the Pauli matrices. Here we 
-fix $J=1$ and use periodic boundary conditions, identifying sites $L+1$ and $1$. The 
-total magnetization $S_{T}^z\equiv\sum_iS_i^z=L/2-M$, with $M$ number of down spins 
-(particles), commutes with~\eref{xxx-ham}, and it is used to label its eigenstates.
+%\subsection{The spin-$\frac{1}{2}$ Heisenberg chain}
+%\label{sec:1.1}
 
@@
 \begin{equation}
+\label{wrong}
 \prod_{j=1}^{n/2}\frac{\sqrt{\lambda_j^2+1}}{4\lambda_j}\propto\sqrt{\delta_n^{n/2}}.
@@
 \begin{equation}
+\label{wrong1}
 \prod\limits_{j=1}^n\frac{1}{2}
@@
 %
-Putting everything together one would get a diverging MG overlap which is clearly wrong.
+Putting everything together (\eref{wrong} and~\eref{wrong1}) one would get a 
+diverging MG overlap, which is clearly impossible.
 

### 2015-11-02 draft/fs_qa_v5.tex
rev-latest

--- 2015-11-02 draft/fs_qa_v4.tex
@@
 where $\tilde s_j$ is the number of $j$-string pairs in the Bethe state.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The low-density regime ({\bf PROBLEM !!!})}
-\label{sec:low-density}
-
-It is interesting to consider the situation with $M/L\to\infty$ (low-density limit). 
-We first consider the case with all the particles forming a single zero-momentum 
-string. Due to parity invariance only strings of even length are allowed. 
-We assume the string hypothesis~\eref{str-hyp}, restricting ourselves to zero-momentum 
-strings, i.e., 
-%
-\begin{equation}
-\lambda^{j}_{n}=-i(n-1-2j)+i\delta_{n}^j,
-\end{equation}
-%
-with $n$ the length of the string and $j$ labelling the different string components. 
-Due to parity invariance we restrict ourselves to half strings, i.e., $j=1,\dots,n/2$.
-We verified by explicit computation that for a single $m$ string one has (at leading order 
-in the string deviations) 
-%
-\begin{equation}
-\det(G^+)=-\frac{2^{n/2}}{\delta_n^{n/2}}L\prod_{j>k=1}^{n/2-1}(\delta_n^k-\delta_n^j)^{-1},
-\end{equation}
-%
-and 
-%
-\begin{equation}
-\det(G^-)=-\frac{2^{n/2}}{\delta_n^{n/2}}(L-1)\prod_{j>k=1}^{n/2-1}(\delta_n^k-\delta_n^j)^{-1}.
-\end{equation}
-%
-This implies that 
-%
-\begin{equation}
-\frac{\det_n(G^+)}{\det_n(G^-)}\to\frac{L}{L-1},\quad\forall n.
-\end{equation}
-%
-However, it is straightforward to check that  
-%
-\begin{equation}
-\label{wrong}
-\prod_{j=1}^{n/2}\frac{\sqrt{\lambda_j^2+1}}{4\lambda_j}\propto\sqrt{\delta_n^{n/2}}.
-\end{equation}
-%
-{\bf The prefactor does not seem to be a simple function of $n$}.
-
-We conclude that Bethe states corresponding to a single string have zero N\'eel 
-overlap.
-
-A problem arises if one considers the Majumdar-Ghosh state. The overlap is obtained 
-rescaling the N\'eel overlap (see below) with the prefactor
-%
-\begin{equation}
-\prod\limits_{j=1}^n\frac{1}{2}
-\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big). 
-\end{equation}
-%
-Note that the product above is over all the string components. 
-For a single string one gets 
-%
-\begin{equation}
-\label{wrong1}
-\prod\limits_{j=1}^n\frac{1}{2}
-\Big(1-\frac{\lambda_j-i}{\lambda_j+i}\Big)\propto\frac{1}{\delta_n^{n/2}}.
-\end{equation}
-%
-Putting everything together (\eref{wrong} and~\eref{wrong1}) one would get a 
-diverging MG overlap, which is clearly impossible.
 

### 2015-12-05 QAMC_draft/fs_qa_v6.tex
05/12/2015

--- 2015-11-02 draft/fs_qa_v5.tex
@@
 
-\title{The quench action approach for integrable models: A Monte Carlo study}
-
-\author{Authors}
-%\address{$^1$ International School for Advanced Studies (SISSA),
-%Via Bonomea 265, 34136, Trieste, Italy,
-%INFN, Sezione di Trieste}
+\title{The quench action approach in finite integrable spin chains}
+
+\author{Vincenzo Alba and Pasquale Calabrese }
+%
+\address{$^1$\,SISSA and INFN, via Bonomea 265, 34136 Trieste, Italy. }
+%\address{$^2$\,The Rudolf Peierls Centre for Theoretical Physics,
+   % Oxford University, Oxford, OX1 3NP, United Kingdom.   }
 
@@
 
-fdasfa
+We consider the problem of constructing the stationary state following a quantum quench, 
+using the exact overlaps for finite size integrable models. 
+We focus on the isotropic Heisenberg spin chain with initial state N\'eel or Majumdar-Ghosh (dimer),
+although the proposed approach is valid for an arbitrary integrable model. 
+We consider only those states which do not contain zero-momentum strings because the latter 
+are affected by fictitious singularities that are very difficult to take into account. 
+We show that the fraction of eigenstates that do not contain zero-momentum strings is vanishing in the thermodynamic limit.
+Consequently, restricting to this part of the Hilbert space would lead to vanishing expectation values of local observables. 
+It is, however, possible to reconstruct the asymptotic values by properly reweighing the expectations in the considered 
+subspace at the price of introducing finite-size corrections. 
+We also develop a Monte Carlo sampling of the Hilbert space which allows us to study larger systems. 
+We accurately reconstruct the expectation values of the conserved charged and the root distributions in the stationary state, 
+which turn out to match the exact thermodynamic results. 
+The proposed method can be  implemented even in cases in which an analytic thermodynamic solution is not obtainable.
+
 \end{abstract}
@@
 schneider-2012,kunhert-2013,langen-2013,meinert-2013,fukuhara-2013,
-ronzheimer-2013,braun-2014,langen-2015} and theoretically~\cite{polkovnikov-2011}. 
+ronzheimer-2013,braun-2014,langen-2015} and theoretically~\cite{polkovnikov-2011,efg-15}. 
 The most investigated protocol is that of the {\it quantum quench}, in 
@@
 (ETH) implies that the diagonal ensemble~\eref{d-ensemble} becomes equivalent 
-to the usual Gibbs (thermal) ensemble.
-
-In integrable models, however, the presence of an extensive number of local or 
+to the usual Gibbs (thermal) ensemble (a conjecture which has been investigated in many 
+numerical studies \cite{tvar,alba-2015a}).
+
+In integrable models, however, the presence of local or 
 quasi-local integrals of motion strongly affects the dynamics, preventing the 
@@
 to be fixed by imposing that  $\langle Q_j\rangle_{GGE}=\langle\Psi_0|Q_j|\Psi_0\rangle$. 
-Note that for the diagonal ensemble~\eref{d-ensemble}  one has trivially that $\langle
-{\mathcal O}\rangle_{DE}=\langle\Psi_0|{\mathcal O}|\Psi_0\rangle$. We anticipate that 
-this provides  useful sum rules that will be the main object of interest in the paper. 
-The validity of the GGE has been confirmed in non-interacting theories~\cite{calabrese-2011,
-calabrese-2012,fagotti-2013,kcc14,kcc14a}, whereas in interacting ones the scenario is 
-still not settled. Note that a recent work~\cite{ilievski-2015a} suggests that the $GGE$ 
+%Note that for the diagonal ensemble~\eref{d-ensemble}  one has trivially that $\langle
+%{\mathcal O}\rangle_{DE}=\langle\Psi_0|{\mathcal O}|\Psi_0\rangle$. 
+This also provides  useful sum rules that will be of interest in this paper. 
+The validity of the GGE has been confirmed in non-interacting theories~\cite{calabrese-2006,cramer-2008,barthel-2008,rossini-2009,calabrese-2011,cazalilla-2012,se-12,mossel-2012a,collura-2013,fagotti-2013,kcc14,kcc14a,sotiriadis-2014,bkc-14},
+whereas in interacting ones the scenario is 
+still not fully settled and some recent works~\cite{ilievski-2015a,cardy-2015} suggest that the $GGE$ 
 description of the steady state  is complete provided that the so-called quasi-local 
-charges~\cite{prosen-2014,pereira-2014,ilievski-2015} are included in~\eref{gge}.
+charges~\cite{prosen-2014,pereira-2014,ilievski-2015,essler-2015} are included in the GGE~\eref{gge}.
 
@@
 \langle{\mathcal O}\rangle_{DE}= \sum\limits_{\lambda}\rho^{DE}\langle\lambda|
-{\mathcal O}|\lambda\rangle,\quad\textrm{with}\quad\rho^{DE}=\exp(-2\Re{\mathcal 
-E}(\lambda)), 
-\end{equation}
-%
-where ${\mathcal E}(\lambda)\equiv-\log\langle\lambda|\Psi_0\rangle$, and $\Re$ 
-denotes the real part. For typical initial states $|\Psi_0\rangle$
+{\mathcal O}|\lambda\rangle,\quad\textrm{with}\quad\rho^{DE}=\exp(-2{\rm Re}({\mathcal 
+E}(\lambda))), 
+\end{equation}
+%
+where ${\mathcal E}(\lambda)\equiv-\ln\langle\lambda|\Psi_0\rangle$. 
+For typical initial states $|\Psi_0\rangle$,
 one has ${\mathcal E}\propto L$, with $L$ the system size. This reflects the 
@@
 sum in~\eref{de1} is dominated by a saddle point. Remarkably, for some Bethe 
-ansatz solvable models and for simple-enough initial states, it is possible to 
-determine this saddle point {\it analytically}. This has been done succesfully, 
-for instance, for the quench from the Bose-Einstein condensate~\cite{de-nardis-2014} 
-(BEC) in the Lieb-Liniger model and for the quench from the N\'eel 
-state~\cite{wouters-2014,brockmann-2014} in the $XXZ$ spin chain. Interestingly, 
-it has been suggested recently that the quench action approach could allow to 
-reconstruct the full relaxation dynamics to the steady state~\cite{de-nardis-2015a,
-de-nardis-2015}.
+ansatz solvable models and for simple enough initial states, it is possible to 
+determine this saddle point {\it analytically}. This has been done successfully, 
+for instance, for the quench from the Bose-Einstein condensate
+ in the Lieb-Liniger model ~\cite{de-nardis-2014,ga-15,pce-2015,b-15}, 
+ for the quench from some product states in the $XXZ$ spin chain \cite{pozsgay-2014A,wouters-2014A}, 
+for transport in spin chains \cite{de_luca}, and for some interacting field theories \cite{bse-14}.  
+The quench action approach allows in principle also to reconstruct the full relaxation dynamics to the steady state \cite{caux-2013}
+as numerically done for the 1D Bose gas~\cite{de-nardis-2015a,de-nardis-2015}.
 
@@
 the diagonal ensemble and the quench action approach in {\it finite} size integrable models. 
-We focus on the spin-$1/2$ isotropic Heisenberg ($XXX$) chain with $L$ sites, which is 
-defined by the Hamiltonian 
+%
+We consider the spin-$1/2$ XXZ spin-chain with $L$ sites, which is defined by the Hamiltonian 
 %
@@
 {\mathcal H}\equiv J\sum\limits_{i=1}^L\left[\frac{1}{2}(S_i^+S^-_{i+1} 
-+S_i^{-}S_{i+1}^+)+S_i^zS_{i+1}^z-\frac{1}{4}\right].
++S_i^{-}S_{i+1}^+)+\Delta S_i^zS_{i+1}^z-\frac{1}{4}\right].
 \end{equation}
@@
 of down spins (particles), commutes with~\eref{xxx-ham}, and it is used to label its 
-eigenstates. The $XXX$ chain is Bethe ansatz solvable~\cite{bethe-1931} and its eigenstates 
+eigenstates. The $XXZ$ chain is Bethe ansatz solvable~\cite{bethe-1931,kor-book} and its eigenstates 
 are in one-to-one correspondence with the solutions of the so-called Bethe equations 
-(see~\ref{sec:1.2}). We restrict ourselves to quenches from the zero-momentum N\'eel 
+(see~\ref{sec:1.2}). 
+%
+The non-equilibrium quench dynamics of the XXZ spin chain has been investigated numerically intensively \cite{dmcf-06,bar-09,krs-12,cbp-13,cce-15,fagotti-2014},
+the GGE with all the local charges has been explicitly constructed \cite{fagotti-2014,pozsgay-2013,fagotti-2013b}, 
+and the quench action solution provided for some initial states \cite{pozsgay-2014A,wouters-2014A}.
+
+For concreteness reasons, we focus on the isotropic Heisenberg point ($XXX$), i.e. Hamiltonian \eref{xxx-ham} with $\Delta=1$, 
+but we stress that our approach applies to arbitrary $\Delta$, and  also to arbitrary integrable models. 
+We consider the quenches from the zero-momentum N\'eel 
 state $|N\rangle$ and the Majumdar-Ghosh state $|MG\rangle$, which are defined as  
@@
 the N\'eel and Majumdar-Ghosh state and the eigenstates of~\eref{xxx-ham}~\cite{
-brockmann-2014,brockmann-2014a,brockmann-2014b,brockmann-2014c,pozsgay-2014a,
-piroli-2014}.
+brockmann-2014,brockmann-2014b,brockmann-2014c,pozsgay-2014a,piroli-2014,mazza-2015}.
 
@@
 Bethe equations, and it can be done only in very simple cases, e.g., for small 
-chains. On the other hand, it has been argued that zero-momentum strings are irrelevant 
-in the thermodynamic limtit~\cite{brockmann-2014a}.
-
-For a finite chain here we find that for both the N\'eel and the Majumdar-Ghosh 
-cases, the fraction of eigenstates that do not contain zero-momentum strings 
+chains (as explicitly done for the attractive Lieb-Liniger gas for small number of particles \cite{calabrese-2014}). 
+On the other hand, it has been argued that zero-momentum strings are irrelevant for the reconstruction of the 
+representative state in the thermodynamic limit~\cite{wouters-2014A}.
+
+For a finite chain, we find that for both the N\'eel and the Majumdar-Ghosh initial states, 
+the fraction of eigenstates that do not contain zero-momentum strings 
 is vanishing in the thermodynamic limit, meaning that for finite large-enough 
@@
 the total number of eigenstates without zero-momentum strings is given in terms of the 
-chain size $L$ by simple combinatorial formulas that we provide. We investigate the 
-effect of the Hilbert space truncation on the diagonal ensemble focusing on the  
-sum rules $\langle Q_j\rangle_{DE}=\langle\Psi_0|Q_j|\Psi_0\rangle$ for the conserved 
-quantities $Q_j$. We numerically demonstrate that truncating the diagonal ensemble to 
-eigenstates with no zero-momentum strings leads to striking violations of the sum 
-rules. Precisely, we numerically observe that the truncated diagonal ensemble 
+chain size $L$ by simple combinatorial formulas that we provide. 
+%
+We investigate the effect of the Hilbert space truncation on the diagonal ensemble focusing on the  
+sum rules $\langle Q_j\rangle_{DE}=\langle\Psi_0|Q_j|\Psi_0\rangle$ for the conserved quantities $Q_j$. 
+We numerically demonstrate that truncating the diagonal ensemble to 
+eigenstates with no zero-momentum strings leads to striking violations of the sum rules,  
+as one would naively expect since most of the states with non zero overlaps have not been included. 
+Precisely, we numerically observe that the truncated diagonal ensemble 
 average $\langle Q_j\rangle$ vanish in the thermodynamic limit reflecting the 
-vanishing behavior of the fraction of finite-momentum strings eigenstates. 
-This allows us to conclude that for finite chaings eigenstates corresponding 
+vanishing behavior of the fraction of eigenstates with finite-momentum strings. 
+Thus, for finite chains, eigenstates corresponding 
 to zero-momentum strings cannot be trivially neglected when considering 
@@
 
-However, we provide numerical evidence that the correct diagonal ensemble 
+However, this does not imply that the diagonal ensemble cannot be reconstructed  
+from the eigenstates without zero-momentum strings and it is not in contrast 
+with the previous quench action results in the thermodynamic limit \cite{wouters-2014A,pozsgay-2014A}.
+Indeed, we show  that the correct diagonal ensemble 
 sum rules can be recovered in the thermodynamic limit by appropriately 
-reweighting the contribution of the finite-momentum strings eigenstates.  
-We focus only on the situation with the N\'eel state (cf.~\eref{psi0}) as 
-initial state. The key idea is to sample the eigenstates with no zero-momentum 
-strings with the diagonal ensemble probability measure $\rho^{DE}$ (cf.~\eref{de1}). 
-To this purpose we develop a Monte Carlo scheme, which is a generalization of 
+reweighing the contribution of the finite-momentum strings eigenstates.
+
+%The key idea is to sample the eigenstates with no zero-momentum 
+%strings with the diagonal ensemble probability measure $\rho^{DE}$ (cf.~\eref{de1}). 
+We also develop a Monte Carlo scheme, which is a generalization of 
 the approach presented in Ref.~\cite{alba-2015} to simulate the Generalize 
@@
 $\langle\lambda|N\rangle$ and on the knowledge of the Hilbert space structure 
-of the $XXX$ chain in the Bethe ansatz formalism. The approach allowed us to 
+of the $XXX$ chain in the Bethe ansatz formalism. The approach allows us to 
 simulate effectively chain with $L\lesssim 60$, although larger systems 
@@
 
-Strikingly, although for small chains violations of the conserved quantities 
+Strikingly, after the reweighing, although for small chains violations of the conserved quantities 
 sum rules are present, these violations vanish in the thermodynamic limit 
 and the sum rules are restored. This implies that the only effect of the 
-Hilbert space truncation is to introduce scaling corrections. In the quench 
-action language, this means that the eigenstates corresponding to no 
+Hilbert space truncation is to introduce finite size scaling corrections. 
+In the quench action language, this means that the eigenstates corresponding to non 
 zero-momentum strings contain enough physical information about saddle point. 
@@
 %Here $\rho^{DE}(\alpha)$ is a diagonal ensemble density matrix, and ${\mathcal E}(\alpha)
-%\equiv-\log\langle\alpha|\Psi_0\rangle$, with $\Re$ denoting the real part.
+%\equiv-\ln\langle\alpha|\Psi_0\rangle$, with $\Re$ denoting the real part.
 
@@
 %\begin{equation}
-%\label{neel}
+%\label{N\'eel}
 %|N\rangle\equiv\frac{1}{\sqrt{2}}\big(|N_1\rangle
@@
 
-Here we review some Bethe ansatz results for the spin-$\frac{1}{2}$ Heisenberg 
-($XXX$) chain. Specifically, in section~\ref{sec:1.2} discuss the structure of  
+In this section we review some Bethe ansatz results for the spin-$\frac{1}{2}$ Heisenberg 
+($XXX$) chain. Specifically, in subsection~\ref{sec:1.2} we discuss the structure of  
 its eigenstates (Bethe states) and the associated Bethe equations. 
-Section~\ref{sec:1.3} focuses on the string hypothesis 
+Subsection~\ref{sec:1.3} focuses on the string hypothesis 
 and the so-called Bethe-Gaudin-Takahashi (BGT) equations. The form of the 
-BGT equations in the thermodynamic limit is discussed in section~\ref{sec:1.4}. 
-Finally, in section~\ref{sec:1.5} we provide the exact formulas for the 
+BGT equations in the thermodynamic limit is discussed in subsection~\ref{sec:1.4}. 
+Finally, in subsection~\ref{sec:1.5} we provide the exact formulas for the 
 local conserved charges of the model.
@@
 \label{s_phases}
-\theta_{\alpha,\beta}\equiv \frac{1}{2i}\log\Big[-\frac{e^{ik_\alpha+ik_\beta}-
+\theta_{\alpha,\beta}\equiv \frac{1}{2i}\ln\Big[-\frac{e^{ik_\alpha+ik_\beta}-
 2e^{ik_\alpha}+1}{e^{ik_\alpha+ik_\beta}-2e^{ik_\beta}+1}\Big].
@@
 $S_T$ multiplet and with different $-S_T\le S_T^z\le S_T$ are eigenstates of the 
-$XXX$ chain as well, with the same energy eigenvalue. These eigenstates 
+$XXX$ chain, with the same energy eigenvalue. These eigenstates 
 (descendants) are obtained by multiple applications of the total-spin lowering 
@@
 %
-with the matrix $T_{n,m}(x)\equiv\Theta'(x)$ being dfined as 
+with the matrix $T_{n,m}(x)\equiv\Theta'(x)$ being defined as 
 %
@@
 \label{Q-def}
-\left.Q_{n+1}\equiv\frac{i}{(n-1)!}\frac{d^n}{dy^n}\log\tau
+\left.Q_{n+1}\equiv\frac{i}{(n-1)!}\frac{d^n}{dy^n}\ln\tau
 (y)\right|_{y=i},
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overlap between the Bethe states and some simple roduct states} 
+\section{Overlap between the Bethe states and some simple product states} 
 \label{sec:2}
@@
 Here we detail the Bethe ansatz results for the overlap of the Bethe states (cf.~\eref{ba-eig}) 
-with the zero-momentum (one-site shift invariant) N\'eel state $|N\rangle$ (cf.~\eref{neel}) 
-and the Majumdar-Ghosh (MG) $|MG\rangle$ state (cf.~\eref{mg}). In particular, we specialize 
+with the zero-momentum (one-site shift invariant) N\'eel state $|N\rangle$ 
+and the Majumdar-Ghosh (MG) $|MG\rangle$ state (cf.~\eref{psi0}). In particular, we specialize 
 the Bethe ansatz results to the case of eigenstates described by perfect strings.
@@
 
-We stard discussing the overlaps with the N\'eel state. Due to the zero-momentum 
-constraint, only parity-invariant Bethe states can have non-zero 
-N\'eel overlap~\cite{brockmann-2014,wouters-2014}. The corresponding solutions of the Bethe 
-equations~\eref{ba-eq} contain only pairs of rapidities with opposite sign.  Here we denote the 
-generic parity-invariant rapidity configuration as $|\{\pm\tilde\lambda_j\}_{j=1}^m,n_\infty
-\rangle$, i.e., considering only positive rapidities (as stressed by the tilde in $\tilde
-\lambda_j$). Here $m$ is the number of rapidity pairs. Since the N\'eel state is not invariant 
+We start discussing the overlaps with the N\'eel state. 
+As shown in Ref. \cite{brockmann-2014,wouters-2014A}, only parity-invariant Bethe states have non-zero overlap with the N\'eel state. 
+The corresponding solutions of the Bethe equations~\eref{ba-eq} contain only pairs of rapidities with opposite sign.  
+Here we denote the generic parity-invariant rapidity configuration as $|\{\pm\tilde\lambda_j\}_{j=1}^m,n_\infty\rangle$, 
+i.e., considering only positive rapidities (as stressed by the tilde in $\tilde\lambda_j$). 
+Here $m$ is the number of rapidity pairs. Since the N\'eel state is not invariant 
 under $SU(2)$ rotations, eigenstates with infinite rapidities can have non-zero N\'eel overlaps.
@@
 N_\infty+2m$. The density of infinite rapidities is denoted as $n_\infty\equiv N_\infty/L$. 
-The overlap between the Bethe states and the Neel state $|N\rangle$ reads~\cite{brockmann-2014,
-pozsgay-2014} 
-%
-\begin{equation}
-\label{neel-ov}
+The overlap between the Bethe states and the N\'eel state $|N\rangle$ reads~\cite{wouters-2014A,
+pozsgay-2014a} 
+%
+\begin{equation}
+\label{Neel-ov}
 \frac{\langle N|\{\pm\tilde\lambda_j\}_{j=1}^m,n_\infty\rangle}{|||\{\tilde\lambda_j\}_{j=1}^m,
@@
 
-Here we consider the overlap formula for the Neel state~\eref{neel-ov} in the 
+Here we consider the overlap formula for the N\'eel state~\eref{Neel-ov} in the 
 limit $L\to\infty$, assuming that the rapidities form perfect strings, i.e., 
 $\delta_{n;\gamma}^j=0$ in~\eref{str-hyp}. Then it is possible to 
-rewrite~\eref{neel-ov} in terms of the string centers $\tilde\lambda_{n;\alpha}$ 
+rewrite~\eref{Neel-ov} in terms of the string centers $\tilde\lambda_{n;\alpha}$ 
 only. We restrict ourselves to parity-invariant rapidity configurations with no 
@@
 the exclusion of zero-momentum strings, only strings of length up to $m$ are 
-allowed, with $m$ the number of parity-invariant rapidity pairs. The string 
+allowed. The string 
 content (cf.~\ref{sec:1.3}) of parity-invariant Bethe states is denoted as 
 $\widetilde{\mathcal S}=\{\tilde s_1,\dots,\tilde s_{m}\}$, with $\tilde s_n$ 
-the number pairs of $n$-strings.
+the number of pairs of $n$-strings.
 
@@
 limit. However, as the same type of divergence occurs in both $G^+$ and $G^-$, their 
-ratio (cf.~\eref{neel-ov}) is finite.
+ratio (cf.~\eref{Neel-ov}) is finite.
 
 The finite part of the ratio $\det G^+/\det G^-$ can be extracted using the same 
-strategy as in Ref.~\cite{calabrese-2007,calabrese-2007-a} (see also Ref.~\cite{brockmann-2014}). 
+strategy as in Ref.~\cite{calabrese-2007,calabrese-2007-a} (see also Ref.~\cite{brockmann-2014,calabrese-2014}). 
 One obtains that $\det G^+/\det G^-\to \det\widetilde G^+/\det\widetilde G^-$. The reduced 
-matrix $\widetilde G^+$ depends only on the ``string center'' indices $(n,\gamma)$ 
-and $(m,\gamma')$ and it is given as  
+matrix $\widetilde G^+$ depends only on the indices $(n,\gamma)$ 
+and $(m,\gamma')$ of the ``string center''  and it is given as  
 %
@@
 We should stress that in presence of zero-momentum strings, additional divergences as 
-$1/(\delta_{n;\gamma}^{i}+\delta_{n;\gamma}^{i+1})$ appear, due to the term $K_1(\lambda+\mu)$ 
-in~\eref{G-pm}. The treatment of these diverges is a challenging task because it requires, for each 
+$1/(\delta_{n;\gamma}^{i}+\delta_{n;\gamma}^{i+1})$ appear in $\widetilde G^\pm$, due to the term $K_1(\lambda+\mu)$ 
+in~\eref{G-pm}. The treatment of these divergences is a challenging task because it requires, for each 
 different type of string, the precise knowledge of the string deviations, meaning their dependence 
 on $L$. Some results have been provided for small strings in Ref.~\cite{calabrese-2014}.
+
 Finally, using the string hypothesis and the parity-invariance condition, the prefactor of the 
-determinant ratio in~\eref{neel-ov} becomes  
-%
-\begin{equation}
-\label{neel-k}
+determinant ratio in~\eref{Neel-ov} becomes  
+%
+\begin{equation}
+\label{Neel-k}
 \fl\quad\prod\limits_{j=1}^m\frac{\sqrt{\tilde\lambda_j^2+1}}{4\tilde\lambda_j}=
@@
 The overlap between a generic eigenstate of the $XXX$ chain $|\{\pm\tilde\lambda_j\}
-\rangle$ and the Majumdar-Ghosh state~\eref{mg} can be obtained from the N\'eel state 
-overlap~\eref{neel-ov} as~\cite{pozsgay-2014} 
+\rangle$ and the Majumdar-Ghosh state can be obtained from the N\'eel state 
+overlap~\eref{Neel-ov} as~\cite{pozsgay-2014a} 
 %
@@
 \Big(1+\frac{\tilde\lambda_j+i}{\tilde\lambda_j-i}\Big)
-\langle N|\{\pm\tilde\lambda_j\}_{j=1}^m\rangle
+\langle N|\{\pm\tilde\lambda_j\}_{j=1}^m\rangle.
 \end{equation}
@@
 do not contain infinite rapidities ($N_\infty=0$), in contrast with the N\'eel case 
-(cf.~\eref{neel-ov}). Using the string hypothesis, the mutliplicative factor 
+(cf.~\eref{Neel-ov}). Using the string hypothesis, the multiplicative factor 
 in~\eref{mg-ov} is rewritten as 
@@
 In the thermodynamic limit $L\to\infty$ the extensive part of the N\'eel 
-overlap~\eref{neel-ov} can be written as~\cite{brockmann-2014} 
-%
-\begin{equation}
-\label{neel-ov-th}
-\fl-\lim_{L\to\infty}\log\left[\frac{\langle N|\{\pm\tilde\lambda_j\}_{j=1}^m,n_\infty
+overlap~\eref{Neel-ov} can be written as~\cite{brockmann-2014} 
+%
+\begin{equation}
+\label{Neel-ov-th}
+\fl-\lim_{L\to\infty}\ln\left[\frac{\langle N|\{\pm\tilde\lambda_j\}_{j=1}^m,n_\infty
 \rangle}{|||\{\tilde\lambda_j\}_{j=1}^m,n_\infty\rangle||}\right]=\frac{L}{2}\Big(
-n_\infty\log2+\sum_{n=1}^\infty\int_0^\infty d\lambda\rho_n(\lambda)[g_n(\lambda)
-+2n\log(4)]\Big), 
+n_\infty\ln2+\sum_{n=1}^\infty\int_0^\infty d\lambda\rho_n(\lambda)[g_n(\lambda)
++2n\ln(4)]\Big), 
 \end{equation}
@@
 \fl\quad g_n(\lambda)=\sum_{l=1}^{n-1}\Big[f_{n-1-2l}(\lambda)-f_{n-2l}(\lambda)
-\Big],\quad\textrm{with}\quad f_n(\lambda)=\log\Big(\lambda^2+\frac{n^2}{4}\Big),
+\Big],\quad\textrm{with}\quad f_n(\lambda)=\ln\Big(\lambda^2+\frac{n^2}{4}\Big),
 \end{equation}
@@
 %
-Note that~\eref{neel-ov-th} is extensive, due to the prefactor $L/2$. Also, 
-\eref{neel-ov-th} is obtained only from~\eref{neel-k}, while the subextensive 
+Note that~\eref{Neel-ov-th} is extensive, due to the prefactor $L/2$. Also, 
+\eref{Neel-ov-th} is obtained only from~\eref{Neel-k}, while the subextensive 
 contributions originating from the determinant ratio $\det_m(G^+)/\det_m(G^-)$ 
-in~\eref{neel-ov} are neglected. We should mention that~\eref{neel-ov-th} 
-acts as a driving term in the quech action formalism (cf. section~\ref{sec:4}).
+in~\eref{Neel-ov} are neglected. We should mention that~\eref{Neel-ov-th} 
+acts as a driving term in the quench action formalism (cf. section~\ref{sec:4}).
 
@@
 %
-Here ${\mathcal D}\pmb{\rho}\equiv\prod_{n=1}^\infty{\mathcal D}\rho_n(\lambda)$, 
-$\rho_n(\lambda)$, and $S_{YY}(\pmb{\rho})$ is the Yang-Yang entropy
+Here ${\mathcal D}\pmb{\rho}\equiv\prod_{n=1}^\infty{\mathcal D}\rho_n(\lambda)$
+ and $S_{YY}(\pmb{\rho})$ is the Yang-Yang entropy
 %
@@
 \fl\quad S_{YY}(\pmb{\rho})\equiv L\sum_{n=1}^\infty\int_{-\infty}^{+\infty}d
-\lambda\Big[\rho_n(\lambda)\log\Big(1+\frac{\rho_n^h(\lambda)}{\rho_n(\lambda)}
-\Big)+\rho_n^h(\lambda)\log\Big(1+\frac{\rho_n(\lambda)}{\rho^h_n(\lambda)}\Big)
+\lambda\Big[\rho_n(\lambda)\ln\Big(1+\frac{\rho_n^h(\lambda)}{\rho_n(\lambda)}
+\Big)+\rho_n^h(\lambda)\ln\Big(1+\frac{\rho_n(\lambda)}{\rho^h_n(\lambda)}\Big)
 \Big],
@@
 \label{qa-d-ensemble}
-\quad\langle{\mathcal O}\rangle=\int{\mathcal D}\pmb{\rho}\exp\Big[2\Re\log\langle
+\quad\langle{\mathcal O}\rangle=\int{\mathcal D}\pmb{\rho}\exp\Big[2\Re\ln\langle
 \Psi_0|\pmb{\rho}\rangle +S_{YY}(\pmb{\rho})\Big]\langle\pmb{\rho}|{\mathcal O}|
@@
 $\langle\pmb{\rho}|\Psi_0\rangle$ for the N\'eel state is readily obtained 
-from~\eref{neel-ov-th}.
+from~\eref{Neel-ov-th}.
 
@@
 \label{qa-term}
-L{\mathcal F}(\pmb{\rho})\equiv 2\Re\log\langle\pmb{\rho}|\Psi_0
-\rangle+S_{YY}(\pmb{\rho}(\lambda))  
+L{\mathcal F}(\pmb{\rho})\equiv 2\Re\ln\langle\pmb{\rho}|\Psi_0
+\rangle+S_{YY}(\pmb{\rho}(\lambda))  ,
 \end{equation}
@@
 \fl\quad\rho^*_1(\lambda)=\frac{8(4+\lambda^2)}{\pi(19+3\lambda^2)(1+6\lambda^2+
-\lambda^4)}\\\label{rho2-sp}
+\lambda^4)}, \\\label{rho2-sp}
 \fl\quad\rho_2^*(\lambda)=\frac{8\lambda^2(9+\lambda^2)(4+3\lambda^2)}{\pi(2+\lambda^2)
-(16+14\lambda^2+\lambda^4)(256+132\lambda^2+9\lambda^4)}\\\label{rho3-sp}
+(16+14\lambda^2+\lambda^4)(256+132\lambda^2+9\lambda^4)}, \\\label{rho3-sp}
 \fl\quad\rho_3^*(\lambda)=\frac{8(1+\lambda^2)^2(5+\lambda^2)(16+\lambda^2)(21+\lambda^2)}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{N\'eel overlaps: The role of the zero-momentum strings Bethe states}
+\section{The role of the zero-momentum strings Bethe states}
 \label{sec:5}
@@
 In this section we discuss generic features of the overlaps between the 
-eigenstates (Bethe states) of the Heisenberg spin chain and the N\'eel state 
-(cf.~\eref{neel}). We exploit the Bethe ansatz solution of the chain (see 
+eigenstates (Bethe states) of the Heisenberg spin chain and the N\'eel state. 
+We exploit the Bethe ansatz solution of the chain (see 
 section~\ref{sec:1}) as well as exact results for the N\'eel overlaps (see 
-section~\ref{sec:2}). We focus on finite chains with $L\lesssim 40$ sites, 
-considering, for any $L$. The only Bethe states having, in principle, non 
-zero N\'eel overlap are the so-called parity-invariant Bethe states (see 
+section~\ref{sec:2}). We focus on finite chains with $L\lesssim 40$ sites. 
+The only Bethe states having non zero N\'eel overlap are the parity-invariant Bethe states (see 
 section~\ref{sec:2}). We denote their total number as $Z_{Neel}$. Crucially, 
@@
 contain zero-momentum strings. We denote the total number of these eigenstates 
-as $\widetilde Z_{Neel}$. Both $Z_{Neel}$ and $\widetilde Z_{Neel}$ are given 
-in terms of the chain length $L$ by simple combinatorial formulas that we 
-provide.
+as $\widetilde Z_{Neel}$. 
+%Both $Z_{Neel}$ and $\widetilde Z_{Neel}$ are given 
+%in terms of the chain length $L$ by simple combinatorial formulas. % that we provide.
 
@@
 limit, meaning that zero-momentum strings eigenstates are dominant in number 
-for large chains. This, however, has dramatic consequences, for instance, at the 
-level of the overlap sum rules for the local conservation laws of the model. 
-Precisely, although the sum rules are fixed by the initial (N\'eel) state 
-expectation value of the local charges, we observe striking violations for 
-any finite chain. Moreover, all the sum rules exhibit vanishing behavior as 
+for large chains. This has consequences at the level of the overlap sum rules for the local conservation laws of 
+the model that cannot be saturated by a vanishing fraction of states. 
+Indeed, limiting ourselves to states that do not contain zero momentum strings, we find  that  all sum rules exhibit vanishing behavior as 
 $L^{-1/2}$ upon increasing the chain size, reflecting the same vanishing behavior 
-as $\widetilde Z_{Neel}/Z_{Neel}$. A similar scenario holds for the overlaps with 
-the Majumdar-Ghosh state, where excluding the zero-momentum strings leads to a $1/L$ 
-behavior. This demonstrates that for finite chains the physical effects of 
-zero-momentum strings eigenstates are not negligible.
+as $\widetilde Z_{Neel}/Z_{Neel}$. 
+%
+A similar scenario holds for the overlaps with 
+the Majumdar-Ghosh state, where excluding the zero-momentum strings leads to a $1/L$ behavior. 
+This shows that zero-momentum strings eigenstates are not naively negligible.
 
@@
  Hilbert space. Eigenstates corresponding to zero-momentum strings are 
- escluded. (a) Squared overlaps $|\langle\lambda|N\rangle|^2$ plotted as 
+ excluded. (a) Squared overlaps $|\langle\lambda|N\rangle|^2$ plotted as 
  function of the eigenstates energy density $E/L$. Here $|\lambda\rangle$ 
  denotes the generic eigenstate. The data are for chains with length $26
- \le L\le 38$. The inset is to highlight the exponential decay as a 
- function of $E/L$. Note the logarithmic scale on the $y$ axis. (b) 
- Overlap distribution function: Histograms of $-2\log\langle\lambda|N\rangle/L$. 
+ \le L\le 38$. The inset highlights the exponential decay as a 
+ function of $E/L$ (note the logarithmic scale on the $y$ axis). (b) 
+ Overlap distribution function: Histograms of $-2\ln\langle\lambda|N\rangle/L$. 
  The $y$-axis is rescaled by a factor $10^5$ for convenience. The dash-dotted 
@@
 }
-\label{fig0:neel-ov}
+\label{fig0:Neel-ov}
 \end{figure}
@@
 Here we overview the Bethe ansatz results for the N\'eel overlaps with the 
-eigenstates of the $XXX$ chain. The total number of partiy-invariant 
+eigenstates of the $XXX$ chain. The total number of parity-invariant 
 eigenstates $Z_{Neel}$ having, in principle, non-zero N\'eel overlap is given 
@@
 \begin{equation}
-\label{zneel1}
+\label{zNeel1}
 Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1, 
@@
 %
-with $B(n,m)\equiv n!/(m!(n-m)!)$ the Newton binomial. The proof of~\eref{zneel1} 
+with $B(n,m)\equiv n!/(m!(n-m)!)$ the Newton binomial. The proof of~\eref{zNeel1} 
 is obtained by counting all the parity-invariant BGT quantum number configurations, 
-and it is reported in~\ref{app-1}. Note that $Z_{Neel}$ provides only an upper 
+and it is reported in~\ref{app-1}. Note that $Z_{Neel}$ provides  an upper 
 bound for the number of eigenstates with non-zero N\'eel overlap, as it is clear 
-from the exact diagonalization results shown in Table~\ref{table:neel}. This is 
+from the exact diagonalization results shown in Table~\ref{table:Neel}. This is 
 because parity-invariant eigenstates with a single zero-momentum even-length 
-string, which are included in~\eref{zneel1}, have identically zero N\'eel 
+string, which are included in~\eref{zNeel1}, have identically zero N\'eel 
 overlap~\cite{brockmann-2014}. This is not related to the symmetries of the N\'eel 
 state, but to an ``accidental'' vanishing of the prefactor in the overlap 
-formula~\eref{neel-ov}. Finally, after excluding the zero-momentum strings 
+formula~\eref{Neel-ov}. Finally, after excluding the zero-momentum strings 
 eigenstates, the total number of remaining eigenstates $\widetilde Z_{Neel}$, 
@@
 %
-An overview of generic features of the overlaps is given in Figure~\ref{fig0:neel-ov} 
-(a) plotting the squared N\'eel overlaps $|\langle\lambda|N\rangle|^2$ with the $XXX$ 
+An overview of generic features of the overlaps is given in Figure~\ref{fig0:Neel-ov} 
+(a) that shows  the squared N\'eel overlaps $|\langle\lambda|N\rangle|^2$ with the $XXX$ 
 chain eigenstates $|\lambda\rangle$ versus the energy density $E/L$. The figure shows 
@@
 equations~\eref{bgt-eq}, to obtain the rapidities of $XXX$ chain eigenstates. Finally, 
-the overlaps are calculated numerically using~\eref{neel-ov}. Note that for $L=38$ 
+the overlaps are calculated numerically using~\eref{Neel-ov}. Note that for $L=38$ 
 from~\eref{ztilde} the total number of overlap shown in the Figure is $\widetilde Z_{Neel}
@@
 
-Clearly, from Figure~\ref{fig0:neel-ov} one has that the overlaps decay exponentially 
+Clearly, from Figure~\ref{fig0:Neel-ov} one has that the overlaps decay exponentially 
 as a function of $L$, as expected. Moreover, at each finite $L$ a rapid decay as a 
-function of $E/L$ is observed. The inset of Figure~\ref{fig0:neel-ov} (a) (note the 
+function of $E/L$ is observed. The inset of Figure~\ref{fig0:Neel-ov} (a) (note the 
 logarithmic scale on the $y$-axis) suggests that this decay is exponential. Complementary 
-information is shown in Figure~\ref{fig0:neel-ov} (b) plotting the histograms of $\kappa
-\equiv-2\log|\langle\lambda|N\rangle|/L$ (overlap distribution function). Larger values 
+information is shown in Figure~\ref{fig0:Neel-ov} (b) reporting the histograms of $\kappa
+\equiv-2\ln|\langle\lambda|N\rangle|/L$ (overlap distribution function). Larger values 
 of $\kappa$, correspond to a faster decay with $L$ of the overlaps. The factor $1/L$ 
@@
 exponentially as $|\langle\lambda|N\rangle|^2\propto e^{-\kappa L}$ in the thermodynamic 
-limit. Note that $\kappa$ is the driving term in the quench action approach (cf~\eref{neel-ov-th}). 
-As expected, from Figure~\ref{fig0:neel-ov} (b) one has that the majority of the 
-$XXX$ chain eigenstates exhibit small N\'eel overlap (note the maximum at $\kappa\sim 0.5$). 
+limit. Note that $\kappa$ is the driving term in the quench action approach (cf~\eref{Neel-ov-th}). 
+As expected, from Figure~\ref{fig0:Neel-ov} (b) one has that the majority of the 
+eigenstates exhibit small N\'eel overlap (note the maximum at $\kappa\sim 0.5$). 
 Interestingly, the data suggest that $0.18\lesssim\kappa\lesssim0.7$. The vertical 
@@
 the ground state root distribution $\rho_1(\lambda)\propto1/\cosh(\pi\lambda)$~\cite{taka-book} 
-and~\eref{neel-ov-th}. On the other hand, the vertical dashed line denotes the N\'eel 
+and~\eref{Neel-ov-th}. On the other hand, the vertical dashed line denotes the N\'eel 
 overlap $\sim 2/B(L,L/2)$ of the $S_z=0$ component of the ferromagnetic multiplet, which 
 is at the top of the $XXX$ chain energy spectrum. Finally, the vertical dotted line in 
-Figure~\ref{fig0:neel-ov} (b) shows the quench action result for $\kappa$ in the thermodynamic 
-limit. This is obtained by using~\eref{neel-ov-th} and the saddle point root distributions 
+Figure~\ref{fig0:Neel-ov} (b) shows the quench action result for $\kappa$ in the thermodynamic 
+limit. This is obtained by using~\eref{Neel-ov-th} and the saddle point root distributions 
 $\rho_n^*$ (cf.~\eref{rho1-sp}-\eref{rho3-sp} for the results up to $n=3$). Note that $\kappa$ 
 does not coincide with the peak of the overlap distribution function, as expected. This is  
-due to the competition between the driving term~\eref{neel-ov-th} and the Yang-Yang entropy 
+due to the competition between the driving term~\eref{Neel-ov-th} and the Yang-Yang entropy 
 $S_{YY}$ (cf.~\eref{qa-term}) in the quench action treatment of the N\'eel quench.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{N\'eel overlap sum rules}
+\subsection{Overlap sum rules}
 \label{sec:5.2}
@@
  of the $XXX$ chain. The $x$-axis shows the inverse chain length $1/L$. 
- The circles are Bethe ansatz results for chains up to $L=38$. The data  
- are obtained by  a full scanning of the chain Hilbert space. Eigenstates  
- corresponding to zero-momentum strings are excluded. The dotted line is 
- the expected result at any $L$. The data are compatible with a vanishing 
- behavior in the thermodynamic limit. The dash-dotted line is a fit to 
- $A/L^{1/2}+B/L$, with $A,B$ fitting parameters. Inset: The same data as 
- in the main Figure now plotted versus $1/L^{1/2}$. (b) 
- The same as in (a) for the energy sum rule $\sum_{\lambda}|\langle
+ The circles are Bethe ansatz results for chains up to $L=38$. 
+ The data are obtained by  a full scanning of the  Hilbert space excluding eigenstates  
+ with  zero-momentum strings. 
+ The dotted line is the expected result at any $L$. 
+ The data are compatible with a vanishing behavior in the thermodynamic limit. 
+ The dash-dotted line is a fit to $A/L^{1/2}+B/L$, with $A,B$ fitting parameters. 
+ Inset: The same data as in the main Figure now plotted versus $1/L^{1/2}$. 
+ (b) The same as in (a) for the energy sum rule $\sum_{\lambda}|\langle
  \lambda|N\rangle|^2Q_2(\lambda)=Q_2^{(0)}$, with $Q_2(\lambda)$ the 
@@
 }
-\label{fig1:neel-sr}
+\label{fig1:Neel-sr}
 \end{figure}
@@
 
-Here we illustrate the effect of the zero-momentum strings eigenstates on the 
+Here we study the effect of the zero-momentum strings eigenstates on the 
 N\'eel overlap sum rules. We focus on the ``trivial'' sum rule, i.e., the 
@@
 where $Q_n(\lambda)$ are the charges eigenvalues over the generic Bethe state 
-$|\lambda\rangle$ (cf.~\eref{qngnk} and~\eref{gnk}). In both~\eref{sr-trivial} 
-and~\eref{sr-charge} the sums are restricted to the eigenstates with no zero-momentum 
-strings. In~\eref{sr-charge} $Q_n^{(0)}$ is the expectation value of $Q_n$ over the 
+$|\lambda\rangle$ (cf.~\eref{qngnk} and~\eref{gnk}). 
+%
+In~\eref{sr-charge} $Q_n^{(0)}$ is the expectation value of $Q_n$ over the 
 initial N\'eel state. $Q_n^{(0)}$ have been calculated in Ref.~\cite{fagotti-2013} 
@@
 state, and the periodic boundary conditions, the density $Q_n^{(0)}/L$ does 
-not depend on the chain size. Note also that the N\'eel state, $Q_n^{(0)}$ can be 
-calculated directly in the thermodynamic limit using~\eref{q0-th} and the root 
-distributions $\pmb{\rho}^*$ (cf.~\eref{rho1-sp}-\eref{rho3-sp}).
-
-The sum rules~\eref{sr-trivial} and~\eref{sr-charge} (for $n=2$, i.e., the energy 
-sum rule), are shown in Figure~\ref{fig1:neel-sr} (a) and (b), respectively. 
-Note that $Q^{(0)}_2/L=-1/2$ in~\eref{sr-charge} (horizonthal dotted line). 
-The circles in Figure~\ref{fig1:neel-sr} (a) are the Bethe ansatz results excluding 
-the zero momentum strings. The data are the same as in Figure~\ref{fig0:neel-ov}. 
+not depend on the length of the chain. 
+%Note also that the N\'eel state, $Q_n^{(0)}$ can be 
+%calculated directly in the thermodynamic limit using~\eref{q0-th} and the root 
+%distributions $\pmb{\rho}^*$ (cf.~\eref{rho1-sp}-\eref{rho3-sp}).
+
+Now we consider the sums \eref{sr-trivial} and~\eref{sr-charge} (for $n=2$, i.e., the energy sum rule)
+restricted to the eigenstates with no zero-momentum strings.
+These are shown in Figure~\ref{fig1:Neel-sr} (a) and (b), respectively. 
+Note that $Q^{(0)}_2/L=-1/2$ in~\eref{sr-charge} (horizontal dotted line). 
+The circles in Figure~\ref{fig1:Neel-sr} (a) are the Bethe ansatz results excluding 
+the zero momentum strings. The data are the same as in Figure~\ref{fig0:Neel-ov}. 
 The sum rules are plotted against the inverse chain length $1/L$, for $L\le 38$. 
-
-Clearly, both the sum rules are violated, due to the exclusion of the to zero-momentum 
-strings. Moreover, in both Figure~\ref{fig1:neel-sr} (a) and (b) the data suggest a 
+%
+As expected, both the sum rules are strongly violated, due to the exclusion of the to zero-momentum 
+strings. Moreover, in both Figure~\ref{fig1:Neel-sr} (a) and (b) the data suggest a 
 vanishing behavior upon increasing $L$. The dash-dotted lines are fits to  $A/L^{1/2}
@@
 L^{-1/2}$ of the sum rules reflects that of the fraction of non-zero momentum string 
-eigenstates $\widetilde Z_{Neel}/Z_{Neel}$. Specifically, from~\eref{zneel1} and~\eref{ztilde} 
+eigenstates $\widetilde Z_{Neel}/Z_{Neel}$. Specifically, from~\eref{zNeel1} and~\eref{ztilde} 
 it is straightforward to derive that for $L\to\infty$
@@
  The circles are Bethe ansatz results for chains up to $L=32$. The results 
- are obtained by a full scanning of the chain Hilbert space. Eigenstates 
- corresponding to zero-momentum strings are excluded. The dash-dotted line 
- is a fit to $A/L+B/L^2$, with $A,B$ fitting parameters. (b) The same as 
- in (a) for the energy sum rule $\sum_{\lambda}|\langle\lambda|MG\rangle
+ are obtained by a full scanning of the chain Hilbert space excluding eigenstates with zero-momentum strings. 
+ The dash-dotted line is a fit to $A/L+B/L^2$, with $A,B$ fitting parameters. 
+ (b) The same as in (a) for the energy sum rule $\sum_{\lambda}|\langle\lambda|MG\rangle
  |^2Q_2(\lambda)=Q_2^{(0)}$, with $Q_2(\lambda)$  the energy of $|\lambda
- \rangle$ and $Q_2^{(0)}/L=-2/3$ the Majumdar-Ghosh energy density (dotted 
+ \rangle$ and $Q_2^{(0)}/L=-5/8$ the Majumdar-Ghosh energy density (dotted 
  line in the Figure). 
@@
 
-It is interesting to observe that the large $L$ behavior as $L^{-1/2}$  of the sum 
+The large $L$ behavior as $L^{-1/2}$  of the restricted sum 
 rules is not generic, meaning that it depends on the pre-quench initial state $|\Psi_0
@@
 %
-As for~\eref{zneel1}, $Z_{MG}$ is only un upper bound for the number of Bethe states with 
+As for~\eref{zNeel1}, $Z_{MG}$ is only un upper bound for the number of Bethe states with 
 non-zero Majumdar-Ghosh overlaps. Note also that at any size $L$ one has $Z_{MG}<Z_{Neel}$. 
 This is due to the Majumdar-Ghosh state being invariant under $SU(2)$ rotations, since it 
-contains only spin singlets. In constrast with the N\'eel state, this implies that the 
+contains only spin singlets. In contrast with the N\'eel state, this implies that the 
 Majumdar-Ghosh stat has non-zero overlap only with the $S^z_T=0$ sector of the $XXX$ chain 
@@
 %
-Panels (a) and (b) in Figure~\ref{fig2:dimer-sr} plot the sum rules~\eref{sr-trivial} 
+Panels (a) and (b) in Figure~\ref{fig2:dimer-sr} report the restricted sums~\eref{sr-trivial} 
 and~\eref{sr-charge} for the Majumdar-Ghosh state. The data are obtained using the 
 analytic results for the overlaps in subsection~\ref{sec:2.3}. The expected value for 
-the energy density sum rule is $Q_2^{(0)}=-2/3$ (horizonthal dotted line in 
-Figure~\ref{fig2:dimer-sr} (b)). Similar to Figure~\ref{fig1:neel-sr}, due to the exclusion 
+the energy density sum rule is $Q_2^{(0)}=-5/8$ (horizontal dotted line in 
+Figure~\ref{fig2:dimer-sr} (b)). Similar to Figure~\ref{fig1:Neel-sr}, due to the exclusion 
 of the zero-momentum strings, the sum rules are violated, exhibiting vanishing behavior in 
@@
 as $1/L$, as confirmed by the fits (dash-dotted lines in Figure~\ref{fig2:dimer-sr}). 
-Similar to the N\'eel case, the vanishing of the sum rules in the thermodynamic limit 
+The vanishing of the sum rules in the thermodynamic limit 
 reflects the behavior of $\widetilde Z_{MG}/Z_{MG}$ as (see~\eref{mg1} and~\eref{mg2})
@@
 %
+
+\subsection{Quench action reweighing}
+
+The results in the previous section could lead to the {\it erroneous} conclusion that the states with zero momentum strings 
+are essential in order to reconstruct the thermodynamic values of any observables, in stark contrast with the quench action 
+results \cite{pozsgay-2014A,wouters-2014A} that fit perfectly with the numerical simulations reported in the same papers. 
+%
+The solution to this apparent paradox is understood within the quench action formalism, 
+which predicts that the {\it representative state} of the stationary state in the thermodynamic limit can be completely described 
+restricting to the states without zero momentum strings. 
+However, when reconstructing this state (both analytically and numerically), it must be properly normalised to unity in the 
+reduced subspace we are considering. 
+Consequently, we expect that after a quench from the initial state $\Psi_0$ the stationary expectation value 
+of any local observables ${\cal O}$ can rewritten as 
+\begin{equation}
+\langle{\cal O}\rangle= \frac{\sum_{\lambda} |\langle \lambda| \Psi_0\rangle|^2   \langle\lambda|{\mathcal O}|\lambda\rangle }{ 
+\sum_{\lambda} |\langle \lambda| \Psi_0\rangle|^2}, 
+\qquad w_{\Psi_0}\equiv \sum_{\lambda} |\langle \lambda| \Psi_0\rangle|^2\,,
+\label{rewe}
+\end{equation}
+where, crucially, the sums over $\lambda$ are restricted to the states without zero momentum strings. 
+This means that any local observable must be reweighed by the factor $w_{\Psi_0}$, reflecting the fact that we are considering 
+only a small portion of the total Hilbert space.
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=.95\textwidth]{./draft_figs/full_vs_mc.pdf}
+\end{center}
+\caption{Energy density expectation values for a quench from N\'eel (a) and Majumdar-Ghosh state (b) obtained by means of the 
+reweighing \eref{rewe}.
+For the Majumdar-Ghosh state a quadratic fit (forcing the asymptotic value $Q_2^{(0)}=-5/8$) describes perfectly the reweighed 
+data.
+For the N\'eel state we also report the Monte Carlo data obtained in the next section, showing perfect agreement with the 
+reweighed Bethe ansatz data. 
+}
+\label{fig:rew}
+\end{figure}
+
+The results obtained by reweighing the data in Figs. \ref{fig1:Neel-sr} and \ref{fig2:dimer-sr}
+are shown in Fig. \ref{fig:rew} focusing on the conserved energy density for both the N\'eel and 
+Majumdar-Ghosh initial states. 
+It is evident that the data after reweighing approach a finite value for large $L$ in contrast with the bare vanishing values 
+(cf. Figs.  \ref{fig1:Neel-sr} and \ref{fig2:dimer-sr}). 
+It is, however, also clear that this procedure introduces some finite size corrections due to the restriction of the Hilbert space that is 
+only justified in the thermodynamic limit. 
+%
+For the Majumdar-Ghosh state these corrections are monotonous and one can extrapolate with a quadratic fit in $1/L$
+to infinite size, in order to reproduce the correct thermodynamic expectation (see Fig. \ref{fig:rew} panel (b)).
+%
+For the N\'eel initial state instead, the corrections to the scaling are not monotonous and an extrapolation 
+based only on the data up to $L=38$ are inconclusive. 
+In Fig. \ref{fig:rew} we plot on top of the exact Bethe ansatz data, also Monte Carlo results obtained by sampling the restricted 
+Hilbert space (see next section). 
+The Monte Carlo allows to consider larger system sizes, which turns out to be enough for a good extrapolation, as we
+will discuss in the next section. 
+We limit here to notice that the agreement between exact and Monte Carlo data is excellent, corroborating 
+the correctness of both approaches.
 
@@
 Z'_{Neel}$ is the number of parity-invariant eigenstates with no zero-momentum 
-strings in the sector with fixed particle number $M''$  (cf.~\eref{neel-fi} for 
+strings in the sector with fixed particle number $M''$  (cf.~\eref{Neel-fi} for 
 the precise expression). 
@@
 \item[\circled{4}] Calculate the N\'eel overlap $\langle\{\pm\lambda'_j\}_{j=1}^{m''}
-|N\rangle$ for the new eigenstate,  using~\eref{neel-ov}~\eref{red-G+}~\eref{red-G-} 
-and~\eref{neel-k}. Accept the new eigenstate with the quench action Metropolis 
+|N\rangle$ for the new eigenstate,  using~\eref{Neel-ov}~\eref{red-G+}~\eref{red-G-} 
+and~\eref{Neel-k}. Accept the new eigenstate with the quench action Metropolis 
 probability 
@@
 {\mathcal P}''_{\lambda\to\lambda'}=\textrm{Min}\Big\{1,\exp\Big(-
-2\Re({\mathcal E}'-{\mathcal E})\Big)\Big\}, 
-\end{equation}
-%
-where ${\mathcal E}'\equiv-\log\langle\{\pm\lambda'_j\}_{j=1}^{m''}
-|N\rangle$, ${\mathcal E}\equiv-\log\langle\{\pm\lambda_j\}_{j=1}^{m''}
-|N\rangle$, and $\Re$ denoting the real part. 
+2{\rm Re}({\mathcal E}'-{\mathcal E})\Big)\Big\}, 
+\end{equation}
+%
+where ${\mathcal E}'\equiv-\ln\langle\{\pm\lambda'_j\}_{j=1}^{m''}
+|N\rangle$, ${\mathcal E}\equiv-\ln\langle\{\pm\lambda_j\}_{j=1}^{m''}
+|N\rangle$. 
 \end{enumerate}
@@
 
-For a generic observable ${\mathcal O}$, its quench action $\langle{\mathcal O}
-\rangle$ is obtained from the Monte Carlo simulation as the arithmetic average 
+For a generic local observable ${\mathcal O}$, its quench action expectation $\langle{\mathcal O}
+\rangle$ is obtained as the arithmetic average 
 of the eigenstates expectation values $\langle\lambda|{\mathcal O}|\lambda\rangle$, 
@@
 \rangle$ (form factor) is known.
+
+Finally, it is worth stressing that although the Monte Carlo sampling is done only on the 
+zero-momentum free Hilbert subspace, the algorithm does not suffer of the reweighing problems 
+found in the exact method (see the preceding section), because the expectation values 
+\eref{qamc-obs} are automatically normalised by the factor $N_{mcs}$.
 
@@
  expected result $Q_2^{(0)}$. The dashed line is a fit to the behavior 
- $-1/2+A/L+B/L^2$, with $A,B$ fitting parameters. (b) The N\'eel sum rule 
- for the energy fluctuations $\sigma^2(Q_2)$ (cf.~\eref{sigma-sr} for 
- the definition). The horizontal line is the expected result $1/4$. 
- (c)(d) Same as in (a)(b) for the charge $Q_4$ and its fluctuations. 
+ $-1/2+A/L+B/L^2$, with $A,B$ fitting parameters.
+ (b) Same as in (a) for the charge $Q_4$ without the fit. 
 }
-\label{fig3:neel-qamc-sr}
+\label{fig3:Neel-qamc-sr}
 \end{figure}
@@
 The validity of the Monte Carlo approach outlined in~\ref{sec:6.2} is demonstrated 
-in Figure~\ref{fig3:neel-qamc-sr} (a)-(d). The Figure focuses on the N\'eel overlap 
+in Fig.~\ref{fig3:Neel-qamc-sr}. The Figure focuses on the N\'eel overlap 
 sum rules for the conserved charges densities $Q_2/L$ and $Q_4/L$ (cf. 
 subsection~\ref{sec:1.5} for the definition of the charges, and~\eref{sr-charge} 
-for the associated sum rules). Here we also consider the corresponding fluctuations 
-$\sigma^2(Q_n)$, which are defined as 
-%
-\begin{equation}
-\label{sigma-sr}
-\fl\quad\sigma^2(Q_n)\equiv\langle N|Q^2_n|N\rangle-\langle N|Q_n|N\rangle^2=
-\sum\limits_{\lambda}|\langle N|\lambda\rangle|^2Q^2_n(\lambda)-\Big(\sum_\lambda|
-\langle N|\lambda\rangle|^2Q_n(\lambda)\Big)^2.
-\end{equation}
-%
-Note that in both~\eref{sr-charge} and~\eref{sigma-sr} the sum is now over the 
+for the associated sum rules). 
+%
+Note that in~\eref{sr-charge}  the sum is now over the 
 eigenstates $|\lambda\rangle$ sampled by the Monte Carlo. 
-Panel (a) and (b) in Figure~\ref{fig3:neel-qamc-sr} plot the sum rules for 
-the energy density $Q_2/L$, and its density of fluctutations $\sigma^2(Q_2)/L$. 
-It is straightforward to derive that $\sigma(Q_2)/L=1/4$, which is shown as dash-dotted 
-line in Figure~\ref{fig3:neel-qamc-sr} (b). 
+Panel (a) in Figure~\ref{fig3:Neel-qamc-sr} reports the sum rule for 
+the energy density $Q_2/L$ (these are the same data reported in Fig. \ref{fig:rew} which 
+perfectly agree with the exact data, corroborating the accuracy of the Monte Carlo sampling). 
 The circles in the Figure are Monte Carlo data for the Heisenberg chain with $L\le 56$ 
@@
 the scaling corrections, as confirmed by the fit to $-1/2+A/L+b/L^2$ (dashed line in the Figure), 
-with $A,B$ fitting parameters. The same behavior should be expected for the energy 
-fluctuations $\sigma^2(Q_2)$ (panel (b) in the Figure), although the asymptotic  
-behvior sets in for $L\gg 56$.
-
-Similarly, panels (c) and (d) in Figure~\ref{fig3:neel-qamc-sr} plot the charge 
-density $Q_4/L$ and its fluctuations $\sigma^2(Q_4)/L$. While for $Q_4/L$ the Monte 
+with $A,B$ fitting parameters.
+
+Similarly, panel (b) in Figure~\ref{fig3:Neel-qamc-sr} reports the charge 
+density $Q_4/L$. Also in this case, the Monte 
 Carlo data for $L=48$ are already compatible with the expected result $Q_4/L=1/4$ 
-in the thermodynamic limit, $\sigma^2(Q_4)$ exhibits large scaling corrections. 
+in the thermodynamic limit. 
+The scaling corrections  are however not monotonous and it is impossible to 
+proceed to a proper extrapolation to the thermodynamic limit. 
 This could be attributed to fact that the support of $Q_n$, i.e., the number of 
@@
 (see~\cite{grabowski-1995} for the precise expression). 
+Anyhow, notice that all data deviate from the expected asymptotic value for about 1\%.
 
@@
  Carlo steps. The $y$-axis is divided by a factor $10^6$ for convenience. 
- The width of the histogram bin is $\Delta\lambda\sim 0.07$. (c) The same as 
- in (a) for the $2$-string roots. (b) The $1$-string root distribution 
+ %The width of the histogram bin is $\Delta\lambda\sim 0.07$. 
+ (c) The same as in (a) for the $2$-string roots. (b) The $1$-string root distribution 
  $\rho^*_1(\lambda)$ plotted versus $\lambda$ for two chains with $L=48$ 
@@
 }
-\label{fig4:neel-rho}
+\label{fig4:Neel-rho}
 \end{figure}
@@
 This suggests that the histogram of the $n$-strings BGT roots sampled in the Monte 
-Carlo converges in the thermdynamic limit to the saddle point root distribution 
+Carlo converges in the thermodynamic limit to the saddle point root distribution 
 $\rho^*_n(\lambda)$.
 
-This is demonstrated numerically in Figure~\ref{fig4:neel-rho} considering $\rho^*_1(\lambda)$ 
+This is demonstrated numerically in Figure~\ref{fig4:Neel-rho} considering $\rho^*_1(\lambda)$ 
 (panels (a)(b)) and $\rho^*_2(\lambda)$ (panel (c)(d)). The histograms correspond to Monte 
@@
 are smaller than the symbol size. The oscillating corrections around $|\lambda|\sim0.5$ 
-are lattice effects, which decrease with incresing the chain size 
+are lattice effects, which decrease with increasing the chain size 
 (see the data for $L=48$ in the Figure). Much larger finite-size effects are observed for 
@@
 statistics available for estimating $\rho_2^*(\lambda)$ is effectively reduced as 
-compared to $\rho_1^*(\lambda)$. Finally, we numerically checked that finite-size 
+compared to $\rho_1^*(\lambda)$. Finally, we numerically observed that finite-size 
 corrections and Monte Carlo error bars are even larger for the $3$-strings root 
-distribution $\rho^*_3(\lambda)$, which makes its numerical determination more 
-tricky.
+distribution $\rho^*_3(\lambda)$, which makes its numerical determination more difficult.
 
@@
 
-We presented a Monte Carlo implementation of the quench action method for integrable 
-spin chains. We focused on the spin-$1/2$ isotropic Heisenberg ($XXX$) chain, considering  
-the quench from the zero-momentum N\'eel state. The method is inspired by the Monte Carlo 
-approach developed in Ref.~\cite{alba-2015} to simulate the Generalized Gibbs Ensemble 
-(GGE) in integrable models. The key idea is the Monte Carlo sampling of the chain Hilbert 
-space with the quench action probability distribution given in~\eref{qa-prob}.
-
-The approach relies on the knowledge of the overlaps between the pre-quench N\'eel 
-state and the $XXX$ chain  eigenstates, which have been obtained recently~\cite{
-pozsgay-2014,brockmann-2014,brockmann-2014a,brockmann-2014b,brockmann-2014c,piroli-2014}. 
-The method is based on the detailed knowledge of the Hilbert space structure of the model 
-provided by the Bethe ansatz formalism, in particular, on the so-called string hypothesis, 
-and on the Bethe-Gaudin-Takahashi (BGT) equations. Although the approach is devised for 
-finite-size systems, thermodynamic quantities can be extracted using finite-size scaling. 
-Importantly, we restricted ourselves to a truncated Hilbert space, which is obtained by 
-excluding the chain eigenstates containing zero-momentum strings. The reason is that 
-zero-momentum strings lead to singularities in the N\'eel overlap formulas, which are 
-tricky to deal with in the framework of the string hypothesis. Note that it has been 
-argued that the physical effects of these eigenstates should be irrelevant in the 
-thermodynamic limit~\cite{brockmann-2014}.
-
-In order to understand the effect of the zero-momentum strings in {\it finite} chains 
-we first investigated the full overlap distribution function for chains up to $L=38$ sites. 
-The eigenstates having, in principle, non-zero N\'eel overlap are the so-called 
-parity-invariant eigenstates. Their total number is given in terms of the chain length 
-by a simple combinatorial formula that we provided. We also provided additional  
-formulas for the total number of eigenstates with non-zero N\'eel overlap and no 
-zero-momentum strings, in the different magnetization sectors, and for fixed eigenstate 
-``string content''. We found that for any finite chain the majority of eigenstates 
-contain zero-momentum strings. Specifically, the fraction of eigenstates with nonzero-momentum 
-strings vanishes as $L^{-1/2}$ in the thermdodynamic limit. This is dramatically reflected 
-in the N\'eel overlap sum rules for the local conserved charges of the $XXX$ chain. 
-Although for any chain size their value is fixed by the N\'eel state expectation 
-value, violations are observed. Moreover, the sum rules vanish as $L^{-1/2}$ in the 
-thermodynamic limit. This behavior reflects the vanishing of the fraction of 
-eigenstates with no zero-momentum strings, confirming that their contribution 
-cannot be trivially neglected. This behavior as $L^{-1/2}$, however, is not generic, 
-but it depends on the pre-quench initial state. This was demonstrated here by 
-considering the quench from the Majumdar-Ghosh state. We observed that the sum 
-rules vanish as $1/L$, again reflecting the vanishing as $1/L$ of the fraction of 
-eigenstates with no zero-momentum strings.
-
-Finally, we presented a Monte Carlo implementation of the quench action method. 
-We numerically demonstrated the validity of the approach focusing on the N\'eel 
-overlap sum rules for the local conserved quantities of the $XXX$ chain. Although 
-for finite chains violations of the sum rules are present, their effect decays 
-as $1/L$ upon increasing the chain size, meaning that overlap sum rules are 
-restored in the thermodynamic limit. This implies that the only effect of the 
-Hilbert space truncation is to give rise to scaling corrections. Physically, 
-this means that the remaining eigenstates after the Hilber space truncation 
-contain enough information about the post-quench thermodynamic behavior of the 
-model. Finally, following Ref.~\cite{alba-2015} we extracted from the Monte Carlo 
-the quench action BGT root distributions. Although finite-size corrections are 
-present, already for relatively small chains with $L=56$ sites, the first two 
-BGT root distributions are in impressive agreement with the analytic (quench action) 
-result in the thermodynamic limit.
+We developed a finite size implementation of the quench action method for integrable models. 
+We focused on the spin-$1/2$ isotropic Heisenberg ($XXX$) chain, 
+considering simple product states as initial states, but the approach is of general validity. 
+The main ingredient of the approach is the knowledge of the overlaps between the pre-quench
+states and the $XXX$ chain  eigenstates (that for the cases at hand have been obtained recently~\cite{
+pozsgay-2014a,brockmann-2014,brockmann-2014b,brockmann-2014c,piroli-2014}). 
+%
+For chains up to about 40 spins the (relevant part of the) Hilbert space can be fully spanned, while 
+for large systems we performed an effective Monte Carlo sampling. 
+The main outcome of the method is a precise determination of the root distributions which allow
+then the determination of local observables by standard methods. 
+Thermodynamic quantities are finally extracted using finite-size scaling. 
+The main result of this papers have been already summarised in the introductory section and 
+we limit here to some discussions about further developments.
+
+First of all, 
+the importance of the proposed method relies on the property that the only required ingredient is the (analytical or even numerical)
+knowledge of the overlaps between the initial state and the Bethe states. 
+For this reason, it can be implemented even in cases in which an analytic thermodynamic solution is not 
+available.
+
+Another interesting consequence of our work is that we can use a vanishing fraction of the eigenstates in order 
+to determine the thermodynamic behavior. It is clearly interesting to understand whether there are other clever ways 
+to further reduce the fraction of considered states (without knowing the exact solution, when we can just 
+pinpoint one representative eigenstate).
+
+Finally, it is an open interesting issue to understand how the present method can be used to describe the time evolution 
+of a finite but large system and in particular how to reconstruct the time evolution from a vanishing fraction of relevant 
+eigenstates, eventually mimicking  the strategy employed in thermodynamic limit \cite{de-nardis-2015a,de-nardis-2015}.
 
@@
 
-We are very grateful to ... for discussions. V.~A. and P.~C acknowledge 
-support by the ERC under Starting Grant 279391 EDEQS.
+We are very grateful to Fabian Essler for collaboration at the beginning of this project 
+and for very fruitful discussions. 
+We thank Maurizio Fagotti for useful discussions in the early stage of this manuscript 
+and for providing us the exact diagonalization results reported in the appendices. 
+We thank Lorenzo Piroli for useful discussions and comments. 
+All authors acknowledge support by the ERC under Starting Grant 279391 EDEQS. 
+%This work was done in part when FHL was visiting SISSA, whose hospitality is kindly acknowledged. 
+%This work was supported by the EPSRC under grants EP/I032487/1 and EP/J014885/1 (FHLE).
 
@@
 state has $S_T^z=0$. The remaining $L/2-M$ particles correspond to infinite solutions 
-of the Bethe equations (see section~\ref{sec:1.2}). It is straightforward to check that 
+of the Bethe equations (see section~\ref{sec:1.2}). It is straightforward to check that the
 total number of parity-invariant quantum number pairs ${\mathcal N}_n(L,{\mathcal S})$ 
@@
 repeated solutions of the BGT equation are discarded. Moreover, from~\eref{NnLS} one has 
-that $s_m$ is odd (even) only if this zero momentum string is (not) present. Finally, 
-the floor function $\lfloor\cdot\rfloor$ in~\eref{NLS} reflects that the quantum number 
-of zero-momentum strings is fixed.
+that $s_m$ is odd (even) only if this zero momentum string is (not) present.
 
@@
 \le M$ and fixed number of strings $1\le q\le M/2$. Note that the maximum allowed string 
-length is $M/2$ beacause of parity invariance. Note also that in determining $q$, strings 
+length is $M/2$ because of parity invariance. Note also that in determining $q$, strings 
 of different length are treated equally, i.e., $q=\sum_m s_m$. For a given fixed pair 
@@
 %
-The proof now proceeds as in~\ref{app-1}. One can define the total number of eigenstates 
+The proof now proceeds as in the previous section. One defines the total number of eigenstates 
 with nonzero N\'eel overlap in the sector with fixed $\ell$ particles and $q$ different 
-string types as $\widetilde{\mathcal N}'(L,\ell,q)$. It is straigtforward to show that 
+string types as $\widetilde{\mathcal N}'(L,\ell,q)$. It is straightforward to show that 
 $\widetilde{\mathcal N}'(L,\ell,q)$ obeys the recursive relation
@@
 %
-One can check that the solution of~\eref{NpLlq-1} is given as 
+The solution of~\eref{NpLlq-1} is given as 
 %
@@
 After summing over the allowed values of $q=2k$ with $k=1,2,\dots,\ell/2$ one obtains 
-the total number of eigenstaets with nonzero N\'eel overlap at fixed number of 
+the total number of eigenstates with nonzero N\'eel overlap at fixed number of 
 particles $\ell$ $\widetilde Z_{Neel}'(L,\ell)$ as 
@@
 \begin{equation}
-\label{neel-fi}
+\label{Neel-fi}
 \widetilde Z_{Neel}'(L,\ell)=B\Big(\frac{L}{2},\frac{\ell}{2}\Big)-
@@
 of eigenstates $\widetilde Z_{MG}$ having non-zero overlap with the Majumdar-Ghosh state 
-is obtained from~\eref{neel-fi} by replacing $\ell\to L/2$, to obtain 
+is obtained from~\eref{Neel-fi} by replacing $\ell\to L/2$, to obtain 
 %
@@
 
-In this section we provide exact diagonalization results for the overlap between the 
+In this section we provide exact diagonalization results for the overlaps between the 
 N\'eel state and the Majumdar-Ghosh (MG) state and all the eigenstates of the Heisenberg 
 spin chain with $L=12$ sites. For the eigenstates without zero-momentum strings, we 
-also provide the overlaps obtained using the string hypothesis~\eref{neel-ov}\eref{mg-ov}. 
+also provide the overlaps obtained using the string hypothesis~\eref{Neel-ov}\eref{mg-ov}. 
 This allows to check the validity of the string hypothesis when calculating overlaps. 
@@
 \subsection{N\'eel overlap}
-\label{app-neel}
+\label{app-Neel}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h]
+\begin{table}[ht]
 \scriptsize
@@
 \end{tabular}
-\caption{All Bethe states for $L=12$ having nonzero overlap with the zero-momentum N\'eel state. 
+\caption{All Bethe states for $L=12$ having nonzero overlap with the  N\'eel state. 
  The first column shows the string content of the Bethe states, including the number of infinite 
@@
  Finally, the last two columns show the exact overlap with the N\'eel state and the approximate 
- result obatained using the BGT equations. In the last column Bethe states containing zero-momentum 
+ result obtained using the BGT equations. In the last column Bethe states containing zero-momentum 
  strings are excluded. Deviations from the exact result (digits with different colors) are 
@@
 }
-\label{table:neel}
+\label{table:Neel}
 \end{table}
@@
 The overlaps between all the eigenstates of the Heisenberg spin chain and the N\'eel 
-state are reported in Table~\ref{table:neel}. The first column in the Table shows 
+state are reported in Table~\ref{table:Neel}. The first column in the Table shows 
 the string content ${\mathcal S}\equiv\{s_1,\dots,s_M\}$, with $M$ being the number 
@@
 state and the $S_z=0$ eigenstate in the sector with maximal total spin $S=L/2$ 
-(first column in Table~\ref{table:neel}), is given analytically as $2/B(L,L/2)$, 
+(first column in Table~\ref{table:Neel}), is given analytically as $2/B(L,L/2)$, 
 with $B(x,y)$ the Newton binomial.
@@
 \rangle$ are plotted against the eigenstate energy density $E/L
-\in[-\log(2),0]$. The circles are exact diagonalization results for all 
+\in[-\ln(2),0]$. The circles are exact diagonalization results for all 
 the chain eigenstates ($382$ eigenstates), whereas the crosses denote the 
-overlaps calculated using formula~\eref{neel-ov}. Note that only the 
+overlaps calculated using formula~\eref{Neel-ov}. Note that only the 
 eigenstates with no zero-momentum strings are shown ($252$ eigenstates) 
@@
 \caption{ The squared overlap $|\langle N|\lambda\rangle|^2$ between the the 
- Neel state $|N\rangle$ and the eigenstates $|\lambda\rangle$ of the $XXX$ 
+ N\'eel state $|N\rangle$ and the eigenstates $|\lambda\rangle$ of the $XXX$ 
  chain with $L=20$ sites. Only non-zero overlaps are shown. In all the panels the 
@@
  of all the non-zero overlaps. (b)(c)(d) The same overlaps as in (a) zooming in 
- the regions $[0,0.2]$, $[0,0.020]$, and $[0,4\cdot 10^{-5}]$. The discrepancies 
+ the regions $[0,0.2]$, $[0,0.020]$, and $[0,4\cdot 10^{-5}]$. The tiny differences 
  between the ED and the Bethe ansatz results are attributed to the string 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h]
+\begin{table}[ht]
 \scriptsize
@@
 \end{tabular}
-\caption{All Bethe states for $L=12$ having nonzero overlap with the zero-momentum Majumdar-Ghosh (MG) 
+\caption{All Bethe states for $L=12$ having nonzero overlap with the  Majumdar-Ghosh (MG) 
  state. The first column shows the string content of the Bethe states. The second and third column show 
@@
  In the second column only the positive BGT numbers are shown. Note that, in 
- contrast to Table~\ref{table:neel} no states with infinite rapidities are present. The fourth column 
+ contrast to Table~\ref{table:Neel} no states with infinite rapidities are present. The fourth column 
  is the Bethe state eigenenergy. Finally, the last two columns show the exact overlap with the MG state 
- and the approximate result obatained using the BGT equations. In the last column Bethe states containing 
+ and the approximate result obtained using the BGT equations. In the last column Bethe states containing 
  zero-momentum strings are excluded. Deviations from the exact result (digits with different colors) 
@@
 Table~\ref{table:mg} for the chain with $L=12$ sites. The conventions on the representation of 
-the eigenstates is the same as in Table~\ref{table:neel}. Note that in contrast with the N\'eel 
+the eigenstates is the same as in Table~\ref{table:Neel}. Note that in contrast with the N\'eel 
 state, only the eigenstates with zero total spin $S=0$ have non zero overlap, i.e., no eigenstates 
-with infinite rapidities are present, which reflect that the Majumdar-Ghosh state is unvariant 
+with infinite rapidities are present, which reflect that the Majumdar-Ghosh state is invariant 
 under $SU(2)$ rotations.
@@
 
-\bibitem{calabrese-2006}
-P.~Calabrese and J.~Cardy, Phys.\ Rev.\ Lett.\ {\bf 96}, 136801 (2006).
+\bibitem{efg-15}
+J. Eisert, M. Friesdorf, and C. Gogolin, Nature Phys. {\bf 11}, 124 (2015);\\
+C. Gogolin and J. Eisert,  arXiv:1503.07538.
+%Equilibration, thermalisation, and the emergence of statistical mechanics in closed quantum systems
+
+%%% ETH
+\bibitem{deutsch-1991} 
+J.~M.~Deutsch, Phys.\ Rev.\ A\ {\bf 43}, 2046 (1991).
+
+\bibitem{srednicki-1994}
+M.~Srednicki, Phys.\ Rev.\ E\ {\bf 50}, 888 (1994).
+
+\bibitem{tvar}
+G. Biroli, C. Kollath, and A. Laeuchli, Phys. Rev. Lett. {\bf 105}, 250401 (2010);\\
+M. C. Banuls, J. I. Cirac, and M. B. Hastings, Phys. Rev. Lett. {\bf 106}, 050405 (2011);\\
+M. Rigol and M. Fitzpatrick, Phys. Rev. A {\bf 84}, 033640 (2011);\\
+K. He and M. Rigol, Phys. Rev. A {\bf 85}, 063609 (2012);\\
+G. P. Brandino, A. De Luca, R. M. Konik, and G. Mussardo, Phys. Rev. B {\bf 85}, 214435 (2012);\\
+M. Rigol and  M. Srednicki,  Phys. Rev. Lett. {\bf 108}, 110601 (2012);\\
+J. Sirker, N.P. Konstantinidis, and N. Sedlmayr, Phys. Rev. A {\bf 89}, 042104 (2014);\\
+T. M. Wright, M. Rigol, M. J. Davis, and K. V. Kheruntsyan, Phys.\ Rev.\ Lett.\ {\bf 113},  050601 (2014);\\
+M. Rigol, ArXiv:1511.04447.
+
+\bibitem{alba-2015a}
+T.~N.~Ikeda, Y.~Watanabe, and M.~Ueda, Phys.\ Rev.\ E {\bf 87}, 012125 (2013);\\
+V.~Alba, Phys.\ Rev.\ B {\bf 91}, 155123 (2015).
 
@@
 
-\bibitem{calabrese-2007}
-P.~Calabrese and J.~Cardy, J.\ Stat.\ Mech.\ (2007) P06008.
-
-\bibitem{kollath-2007}
-C.~Kollath, A.~M.~L\"auchli, and E.~Altman, Phys.\ Rev.\ Lett.\ 
-{\bf 98}, 180601 (2007).
-
-\bibitem{manmana-2007}
-S.~R.~Manmana, S.~Wessel, R.~M.~Noack, and A.~Muramatsu, 
-Phys.\ Rev.\ Lett.\ {\bf 98}, 210405 (2007).
-
 \bibitem{rigol-2008}
@@
 
+%%%%%FREE
+
+\bibitem{calabrese-2006}
+P.~Calabrese and J.~Cardy, Phys.\ Rev.\ Lett.\ {\bf 96}, 136801 (2006);\\
+P.~Calabrese and J.~Cardy, J.\ Stat.\ Mech.\ (2007) P06008.
+
 \bibitem{cramer-2008}
-M.~Cramer, C.~M.~Dawson, J.~Eisert, and T.~J.~Osborne, Phys.\ Rev.\ 
-Lett.\ {\bf 100}, 030602 (2008).
+M.~Cramer, C.~M.~Dawson, J.~Eisert, and T.~J.~Osborne, Phys.\ Rev.\  Lett.\ {\bf 100}, 030602 (2008);\\
+M. Cramer and J. Eisert, New J. Phys. 12, 055020 (2010).
 
 \bibitem{barthel-2008}
-T.~Barthel and U.~Schollw\"ock, Phys.\ Rev.\ Lett.\ {\bf 100}, 100601 
-(2008).
-
-\bibitem{kollar-2008}
-M.~Kollar and M.~Eckstein, Phys.\ Rev.\ A {\bf 78}, 013626 (2008).
-
-\bibitem{moeckel-2008}
-M.~Moeckel and S.~Kehrein, Phys.\ Rev.\ Lett.\ {\bf 100}, 175702 (2008).
-
-\bibitem{iucci-2009}
-A.~Iucci and M.~A.~Cazalilla, Phys.\ Rev.\ A\ {\bf 80}, 063619 (2009).
+T.~Barthel and U.~Schollw\"ock, Phys.\ Rev.\ Lett.\ {\bf 100}, 100601 (2008).
 
 \bibitem{rossini-2009}
-D.~Rossini, A.~Silva, G.~Mussardo, and G.~E.~Santoro, Phys.\ Rev.\ 
-Lett.\ {\bf 102}, 127204 (2009).
-
-\bibitem{barmettler-2009}
-P.~Barmettler, M.~Punk, V.~Gritsev, E.~Demler, and E.~Altman, Phys.\ Rev.\ 
-Lett.\ {\bf 102}, 130603 (2009).
-
-\bibitem{biroli-2010}
-G.~Biroli, C.~Kollath, and A.~M.~L\"auchli, Phys.\ Rev.\ Lett.\ 
-{\bf 105}, 250401 (2010).
-
-\bibitem{rossini-2010}
-D.~Rossini, S.~Suzuki, G.~Mussardo, G.~E.~Santoro, and A.~Silva, 
-Phys.\ Rev.\ B\ {\bf 82}, 144302 (2010).
-
-\bibitem{fioretto-2010}
-D.~Fioretto and G.~Mussardo, New\ J.\ Phys.\ {\bf 12}, 
-055015 (2010).
-
-\bibitem{gogolin-2011}
-C.~Gogolin, M.~P.~Mueller, and J.~Eisert, Phys.\ Rev.\ Lett.\ 
-{\bf 106}, 040401 (2011).
-
-\bibitem{banuls-2011}
-M.~C.~Ba\~nuls, J.~I.~Cirac, and M.~B.~Hastings, Phys.\ Rev.\ Lett.\ 
-{\bf 106}, 050405 (2011).
-
-\bibitem{calabrese-2011}
-P.~Calabrese, F.~H.~L.~Essler, and M.~Fagotti, Phys.\ Rev.\ Lett.\ {\bf106}, 227203 (2011).
-
-\bibitem{rigol-2011}
-M.~Rigol and M.~Fitzpatrick, Phys.\ Rev.\ A {\bf 84}, 033640 (2011).
-
-\bibitem{calabrese-2012}
-P.~Calabrese, F.~H.~L.~Essler, and M.~Fagotti, J.\ Stat.\ Mech.\ (2012) P07016.
-
-\bibitem{caux-2012}
-J.-S.~Caux and R.~M.~Konik, Phys.\ Rev.\ Lett.\ {\bf 109}, 175301 (2012).
-
-\bibitem{essler-2012}
-F.~H.~L.~Essler, S.~Evangelisti, and M.~Fagotti, Phys.\ Rev.\ Lett.\ 
-{\bf 109}, 247206 (2012).
-
-\bibitem{cazalilla-2012}
-M.~A.~Cazalilla, A.~Iucci, and M.-C.~Chung, Phys.\ Rev.\ E {\bf 85}, 
-011133 (2012).
+D.~Rossini, A.~Silva, G.~Mussardo, and G.~E.~Santoro, Phys.\ Rev.\  Lett.\ {\bf 102}, 127204 (2009);\\
+D.~Rossini, S.~Suzuki, G.~Mussardo, G.~E.~Santoro, and A.~Silva, Phys.\ Rev.\ B\ {\bf 82}, 144302 (2010).
 
@@
 
-\bibitem{collura-2013}
-M.~Collura, S.~Sotiriadis and P.~Calabrese, Phys.\ Rev.\ Lett.\ {\bf 110}, 245301 (2013)
-
-\bibitem{mussardo-2013}
-G.~Mussardo, Phys.\ Rev.\ Lett.\ {\bf 111}, 100401 (2013).
-
-\bibitem{caux-2013}
-J.-S.~Caux and F.~H.~L.~Essler, Phys.\ Rev.\ Lett.\ {\bf 110}, 
-257203 (2013).
+\bibitem{calabrese-2011}
+P.~Calabrese, F.~H.~L.~Essler, and M.~Fagotti, Phys.\ Rev.\ Lett.\ {\bf106}, 227203 (2011);\\
+P.~Calabrese, F.~H.~L.~Essler, and M.~Fagotti, J.\ Stat.\ Mech.\ (2012) P07016;\\
+P.~Calabrese, F.~H.~L.~Essler, and M.~Fagotti, J. Stat. Mech. (2012) P07022;\\
+F.~H.~L.~Essler, S.~Evangelisti, and M.~Fagotti, Phys.\ Rev.\ Lett.\  {\bf 109}, 247206 (2012).
+
+\bibitem{cazalilla-2012}
+M. A. Cazalilla, Phys. Rev. Lett. {\bf 97}, 156403 (2006);\\
+A.~Iucci and M.~A.~Cazalilla, Phys.\ Rev.\ A\ {\bf 80}, 063619 (2009);\\
+A. Iucci and M. A. Cazalilla New J. Phys. {\bf 12}, 055019 (2010);\\
+M.~A.~Cazalilla, A.~Iucci, and M.-C.~Chung, Phys.\ Rev.\ E {\bf 85},  011133 (2012).
+
+\bibitem{se-12}
+D. Schuricht and F. H. L. Essler, J. Stat. Mech. P04017 (2012).
+
+\bibitem{kcc14}
+M.~Kormos, M.~Collura, and P.~Calabrese, Phys.\ Rev.\ A {\bf 89}, 013609  (2014).
+
+\bibitem{kcc14a}
+P.~P.~Mazza, M.\ Collura, M.\ Kormos, and P.\ Calabrese, J.\ Stat.\ Mech.\   (2014) P11016.
 
@@
 
+\bibitem{collura-2013}
+M.~Collura, S.~Sotiriadis and P.~Calabrese, Phys.\ Rev.\ Lett.\ {\bf 110}, 245301 (2013);\\
+M. Collura, S. Sotiriadis and P. Calabrese, J. Stat. Mech. P09025 (2013).
+
 \bibitem{sotiriadis-2014}
@@
 
-\bibitem{fagotti-2014}
-M.~Fagotti, M.~Collura, F.~H.~L.~Essler, and P.~Calabrese, Phys.\ Rev.\ B {\bf 89}, 
-125101 (2014).
-
-\bibitem{essler-2014}
-F.~H.~L.~Essler, S.~Kehrein, S.~R.~Manmana, and N.~J.~Robinson, Phys.\ Rev.\ B {\bf 89}, 
-165104 (2014).
-
-\bibitem{goldstein-2014}
-G.~Goldstein and N.~Andrei, arXiv:1405.4224.
-
-\bibitem{wright-2014}
-T.~M.~Wright, M.~Rigol, M.~J.~Davis, and K.~V.~Kheruntsyan, Phys.\ Rev.\ Lett.\ {\bf 113}, 
-050601 (2014).
-
-\bibitem{pozsgay-2014}
+\bibitem{bkc-14}
+M. Fagotti,  Rev. B {\bf 87}, 165106 (2013);\\
+L. Bucciantini, M. Kormos, and P. Calabrese, J. Phys. A {\bf 47}, 175002 (2014).
+
+%%%%%%
+
+\bibitem{ilievski-2015a}
+E.~Ilieveski, J.~De~Nardis, B.~Wouters, J.-S.~Caux, F.~H.~Essler, and T.~Prosen, 
+Phys. Rev. Lett. {\bf 115}, 157201 (2015).
+
+\bibitem{cardy-2015}
+J.~Cardy,  arXiv:1507.07266.
+
+\bibitem{prosen-2014}
+T.~Prosen, Nucl.\ Phys.\ B\ {\bf 886}, (2014) 1177.
+
+\bibitem{pereira-2014}
+R.~G.~Pereira, V.~Pasquier, J.~Sirker, and I.~Affleck, J.\ Stat.\ Mech.\ 
+(2014) P09037.
+
+\bibitem{ilievski-2015}
+E.~Ilievski, M.~Medejak, and T.~Prosen, Phys. Rev. Lett. {\bf 115}, 120601 (2015).
+
+\bibitem{essler-2015}
+F.~H.~L.~Essler, G.~Mussardo, and M.~Panfil, Phys.\ Rev.\ A {\bf 91}, 051602 (2015).
+
+\bibitem{caux-2013}
+J.-S.~Caux and F.~H.~L.~Essler, Phys.\ Rev.\ Lett.\ {\bf 110}, 257203 (2013).
+
+\bibitem{taka-book}
+M.~Takahashi, {\it Thermodynamics of one-dimensional solvable models}, 
+Cambridge University Press, Cambridge, 1999.
+
+\bibitem{de-nardis-2014}
+J.~De Nardis, B.~Wouters, M.~Brockmann, and J.-S.~Caux, Phys.\ Rev.\ A {\bf 89}, 033601 (2014).
+
+\bibitem{ga-15}
+G. Goldstein and N. Andrei, % Equilibration and generalized Gibbs ensemble for hard wall boundary conditions,
+Phys. Rev. B \textbf{92}, 155103 (2015).
+
+\bibitem{pce-2015}
+L. Piroli, P. Calabrese, and F. H.L. Essler,
+arXiv:1509.08234.
+
+\bibitem{b-15}
+L. Bucciantini, arXiv:1510.08125.
+
+\bibitem{pozsgay-2014A}
 B.~Pozsgay, M.~Mesty\'an, M.~A.~Werner, M.~Kormos, G.~Zar\'and, and G.~Tak\'acs,
-Phys.\ Rev.\ Lett.\ {\bf 113}, 117203 (2014).
-
-\bibitem{mestyian-2015}
-M~Mesty\'an, B.~Pozsgay, G.~Tak\'acs, and M.~A.~Werner, J.\ Stat.\ Mech.\ (2015) 
-P04001.
-
-\bibitem{kcc14}
-M.~Kormos, M.~Collura, and P.~Calabrese, Phys.\ Rev.\ A {\bf 89}, 013609 
-(2014).
-
-\bibitem{kcc14a}
-P.~P.~Mazza, M.\ Collura, M.\ Kormos, and P.\ Calabrese, J.\ Stat.\ Mech.\  
-(2014) P11016.
-
-\bibitem{mossel-2012}
-J.~Mossel and J.-S.~Caux, J.\ Phys.\ A:\ Math.\ Theor.\ {\bf 45}, 
-255001 (2012).
-
-\bibitem{pozsgay-2013}
-B.~Pozsgay, J.\ Stat.\ Mech.\ (2013) P07003.
-
-\bibitem{calabrese-2014}
-P.~Calabrese and P.~Le Doussal, J.\ Stat.\ Mech.\ (2014) P05004.
-
-\bibitem{alba-2015}
-V.~Alba, arXiv:1507.06994.
-
-\bibitem{calabrese-2007}
-P.~Calabrese and J.-S.~Caux, Phys.\ Rev.\ Lett.\ {\bf 98}, 150403 (2007).
-
-\bibitem{calabrese-2007-a}
-P.~Calabrese and J.-S.~Caux, J.\ Stat.\ Mech.\ P08032 (2007).
-
-\bibitem{de-nardis-2014}
-J.~De Nardis, B.~Wouters, M.~Brockmann, and J.-S.~Caux, Phys.\ Rev.\ A {\bf 89}, 
-033601 (2014).
-
-\bibitem{pozsgay-2014}
-B.~Pozsgay, M.~Mesty\'an, M.~A.~Werner, M.~Kormos, G.~Zar\'and, and G.~Tak\'acs,
-Phys.\ Rev.\ Lett.\ {\bf 113}, 117203 (2014).
-
-\bibitem{wouters-2014}
+Phys.\ Rev.\ Lett.\ {\bf 113}, 117203 (2014);\\
+M~Mesty\'an, B.~Pozsgay, G.~Tak\'acs, and M.~A.~Werner, J.\ Stat.\ Mech.\ (2015)  P04001.
+
+\bibitem{wouters-2014A}
 B.~Wouters, M.~Brockmann, J.~De~Nardis, D.~Fioretto, M.~Rigol, and J.-S.~Caux, 
-Phys.\ Rev.\ Lett.\ {\bf 113}, 117202 (2014).
-
-\bibitem{brockmann-2014a}
+Phys.\ Rev.\ Lett.\ {\bf 113}, 117202 (2014);\\ 
 M.~Brockmann, B.~Wouters, D.~Fioretto, J.~De Nardis, R.~Vlijm, and J.-S.~Caux, 
@@
 
-\bibitem{mazza-2015}
-P.~P.~Mazza, J.-M.~St\'ephan, E.~Canovi, V.~Alba, M.~Brockmann, and M.~Haque, 
-arXiv:1509.04666.
-
-\bibitem{fagotti-2013}
-M.~Fagotti and F.~H.~Essler, J.\ Stat.\ Mech.\ (2013) P07012.
+\bibitem{de_luca} A. De Luca, G. Martelloni, and J. Viti, %Stationary states in a free fermionic chain from the quench action method.
+ Phys. Rev. A \textbf{91}, 021603 (2015).
+
+\bibitem{bse-14}
+B. Bertini, D. Schuricht, and F. H. L. Essler, J. Stat. Mech.  P10035 (2014).
+
+%%%QA FULL DYNAMICS
+\bibitem{de-nardis-2015}
+J.~De~Nardis, L.~Piroli, and J.-S.~Caux, J. Phys. A  {\bf 48}, 43FT01 (2015).
+
+\bibitem{de-nardis-2015a}
+J.~De~Nardis and J.-S.~Caux, J.\ Stat.\ Mech.\ (2014) P12012.
 
@@
 
-\bibitem{takahashi-1971} 
-M.~Takahashi, Prog.\ Theor.\ Phys.\ {\bf 46}, 401 (1971).
-
-\bibitem{taka-book}
-M.~Takahashi, {\it Thermodynamics of one-dimensional solvable models}, 
-Cambridge University Press, Cambridge, 1999.
-
-\bibitem{gu-2005}
-S.-J.~Gu, N.~M.~R.~Peres, Y.-Q.~Li, Eur.\ Phys.\ J.\ B {\bf 48}, 157 (2005).
-
-\bibitem{faddeev-1996}
-L.~D.~Faddeev, arXiv:9605187.
-
-\bibitem{yang-1969}
-C.~N.~Yang and C.~P.~Yang, J.\ Math.\ Phys. {\bf 10}, 1115 (1969).
-
-%%%CHARGES
+%%%XXZ%
+
+\bibitem{dmcf-06}
+G. De Chiara, S. Montangero, P. Calabrese, and R. Fazio,  %Entanglement Entropy dynamics in Heisenberg chains, 
+J. Stat. Mech. P03001 (2006).
+
+\bibitem{bar-09}
+P. Barmettler, M. Punk, V. Gritsev, E. Demler, and E. Altman, 
+ Phys. Rev. Lett. {\bf 102}, 130603 (2009);\\
+P. Barmettler, M. Punk, V. Gritsev, E. Demler, and E. Altman, 
+ New J. Phys. {\bf 12} 055017 (2010).
+
+\bibitem{krs-12}
+C. Karrasch, J. Rentrop, D. Schuricht, V. Meden, Phys. Rev. Lett. {\bf 109}, 126406 (2012).
+
+\bibitem{cbp-13}
+E. Coira, F. Becca, and A. Parola, Eur. Phys. J. B {\bf 86}, 55 (2013).
+
+\bibitem{cce-15}
+M. Collura, P. Calabrese, and F. H. L. Essler, Phys. Rev. B {\bf 92}, 125131 (2015).
+
+\bibitem{fagotti-2014}
+M.~Fagotti, M.~Collura, F.~H.~L.~Essler, and P.~Calabrese, Phys.\ Rev.\ B {\bf 89}, 125101 (2014).
+
+\bibitem{pozsgay-2013}
+B.~Pozsgay, J.\ Stat.\ Mech.\ (2013) P07003.
+
+\bibitem{fagotti-2013b}
+M.~Fagotti and F.~H.~Essler, J.\ Stat.\ Mech.\ (2013) P07012.
+
+%%% OVERLAPS
+\bibitem{brockmann-2014}
+M.~Brockmann, J.~De~Nardis, B.~Wouters, and J.-S.~Caux, J.\ Phys.\ A {\bf 47}, 345003 (2014).
+
+\bibitem{brockmann-2014c}
+M.~Brockmann, J.~De~Nardis, B.~Wouters, and J.-S.~Caux, J.\ Phys.\ A {\bf 47}, 145003 (2014).
+
+\bibitem{brockmann-2014b}
+M.~Brockmann, J.\ Stat.\ Mech.\ (2014) P05006.
+
+\bibitem{pozsgay-2014a}
+B.~Pozsgay, J.\ Stat.\ Mech.\ (2014) P06011;\\ 
+B. Pozsgay, J. Stat. Mech. P10028 (2013).
+
+\bibitem{piroli-2014}
+L.~Piroli and P.~Calabrese, J.\ Phys.\ A {\bf 47}, 385003 (2014).
+
+\bibitem{mazza-2015}
+P.~P.~Mazza, J.-M.~St\'ephan, E.~Canovi, V.~Alba, M.~Brockmann, and M.~Haque,  arXiv:1509.04666.
+
+\bibitem{calabrese-2014}
+P.~Calabrese and P.~Le Doussal, J.\ Stat.\ Mech.\ (2014) P05004.
+
+%%%%%%%
+\bibitem{alba-2015}
+V.~Alba, arXiv:1507.06994.
+
 \bibitem{grabowski-1995}
@@
 
-\bibitem{prosen-2014}
-T.~Prosen, Nucl.\ Phys.\ B\ {\bf 886}, (2014) 1177.
-
-\bibitem{pereira-2014}
-R.~G.~Pereira, V.~Pasquier, J.~Sirker, and I.~Affleck, J.\ Stat.\ Mech.\ 
-(2014) P09037.
-
-\bibitem{ilievski-2015}
-E.~Ilievski, M.~Medejak, and T.~Prosen, arXiv:1506.05049.
-
-\bibitem{ilievski-2015a}
-E.~Ilieveski, J.~De~Nardis, B.~Wouters, J.-S.~Caux, F.~H.~Essler, and T.~Prosen, 
-arXiv:1507.02993.
-
-\bibitem{essler-2015}
-F.~H.~L.~Essler, G.~Mussardo, and M.~Panfil, Phys.\ Rev.\ A {\bf 91}, 051602 (2015).
-
-\bibitem{cardy-2015}
-J.~Cardy,  arXiv:1507.07266.
-
-%%%MONTE CARLO
-\bibitem{landau-binder}
-D.~P.~Landau and K.~Binder, \emph{A Guide to Monte Carlo Simulations in 
-Statistical Physics}, Cambridge University Press, Cambridge, 2000.
+\bibitem{calabrese-2007}
+P.~Calabrese and J.-S.~Caux, Phys.\ Rev.\ Lett.\ {\bf 98}, 150403 (2007).
+
+\bibitem{calabrese-2007-a}
+P.~Calabrese and J.-S.~Caux, J.\ Stat.\ Mech.\ P08032 (2007).
 
@@
 
-%%% OVERLAPS
-\bibitem{brockmann-2014}
-M.~Brockmann, J.~De~Nardis, B.~Wouters, and J.-S.~Caux, J.\ Phys.\ A:\ 
-Math.\ Theor. {\bf 47}, 345003 (2014).
-
-\bibitem{brockmann-2014c}
-M.~Brockmann, J.~De~Nardis, B.~Wouters, and J.-S.~Caux, J.\ Phys.\ A:\ 
-Math.\ Theor. {\bf 47}, 145003 (2014).
-
-\bibitem{brockmann-2014b}
-M.~Brockmann, J.\ Stat.\ Mech.\ (2014) P05006.
-
-\bibitem{pozsgay-2014a}
-B.~Pozsgay, J.\ Stat.\ Mech.\ (2014) P06011.
-
-\bibitem{piroli-2014}
-L.~Piroli and P.~Calabrese, J.\ Phys.\ A {\bf 47}, 385003 (2014).
-
-%%%ETH
-\bibitem{alba-2015a}
-V.~Alba, Phys.\ Rev.\ B {\bf 91}, 155123 (2015).
-
-\bibitem{ikeda-2013}
-T.~N.~Ikeda, Y.~Watanabe, and M.~Ueda, Phys.\ Rev.\ E {\bf 87}, 012125 (2013).
-
-%%%QA FULL DYNAMICS
-\bibitem{de-nardis-2015}
-J.~De~Nardis, L.~Piroli, and J.-S.~Caux, arXiv:1505.03080.
-
-\bibitem{de-nardis-2015a}
-J.~De~Nardis and J.-S.~Caux, J.\ Stat.\ Mech.\ (2014) P12012.
-
-%%% ETH
-\bibitem{deutsch-1991} 
-J.~M.~Deutsch, Phys.\ Rev.\ A\ {\bf 43}, 2046 (1991).
-
-\bibitem{srednicki-1994}
-M.~Srednicki, Phys.\ Rev.\ E\ {\bf 50}, 888 (1994).
+\bibitem{faddeev-1996}
+L.~D.~Faddeev, arXiv:9605187.
 

### 2015-12-05 QAMC_draft/fs_qa_v7.tex
05/12/2015

--- 2015-12-05 QAMC_draft/fs_qa_v6.tex
@@
 Consequently, restricting to this part of the Hilbert space would lead to vanishing expectation values of local observables. 
-It is, however, possible to reconstruct the asymptotic values by properly reweighing the expectations in the considered 
+It is, however, possible to reconstruct the asymptotic values by properly reweighting the expectations in the considered 
 subspace at the price of introducing finite-size corrections. 
@@
 sum rules can be recovered in the thermodynamic limit by appropriately 
-reweighing the contribution of the finite-momentum strings eigenstates.
+reweighting the contribution of the finite-momentum strings eigenstates.
 
@@
 
-Strikingly, after the reweighing, although for small chains violations of the conserved quantities 
+Strikingly, after the reweighting, although for small chains violations of the conserved quantities 
 sum rules are present, these violations vanish in the thermodynamic limit 
@@
 Subsection~\ref{sec:1.3} focuses on the string hypothesis 
-and the so-called Bethe-Gaudin-Takahashi (BGT) equations. The form of the 
-BGT equations in the thermodynamic limit is discussed in subsection~\ref{sec:1.4}. 
+and the so-called Bethe-Gaudin-Takahashi (BGT) equations. 
+The form of the BGT equations in the thermodynamic limit is discussed in subsection~\ref{sec:1.4}. 
+In subsection~\ref{app-1} we provide some combinatorial formulas for the total 
+number of the so-called parity-invariant eigenstates. The latter are the only eigenstates 
+having non-zero overlap with the N\'eel and Majumdar-Ghosh states. 
 Finally, in subsection~\ref{sec:1.5} we provide the exact formulas for the 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The thermodynamic limit}
+\subsection{The Thermodynamic Bethe Ansatz}
 \label{sec:1.4}
@@
 value of ${\mathcal O}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Counting and string content of the eigenstates with nonzero N\'eel and 
+%Majumdar-Ghosh overlap}
+\subsection{Counting and string content of parity-invariant eigenstates}
+\label{app-1}
+
+Here we provide some exact combinatorial formulas for the total number of 
+parity-invariant eigenstates of the $XXX$ chain, which are the only eigenstates 
+having, in principle, non-zero overlap with the N\'eel state and the 
+Majumdar-Ghosh state~\cite{brockmann-2014}. 
+Parity-invariant eigenstates correspond to solutions of the Bethe equations 
+containing only pairs of rapidities with opposite sign. In turn, these  
+eigenstates are in one-to-one correspondence with parity-invariant BGT quantum number 
+configurations. %In~\ref{app-1.1} we consider all possible parity-invariant 
+%eigenstates, whereas in~\ref{app-1.2} we exclude the eigenstates containing 
+%zero-momentum strings.
+
+For simplicity we restrict ourselves 
+to the situation with $L$ divisible by four. The strategy of the proof is the 
+same as that used to count the number of solutions of the Bethe-Gaudin-Takahashi 
+equations (see for instance Ref.~\cite{faddeev-1996}).  Specifically, the idea 
+is to count all the possible BGT quantum numbers configurations corresponding 
+to parity-invariant eigenstates (cf. section~\ref{sec:1.3}).
+
+We anticipate that the total number of parity-invariant eigenstates $Z_{Neel}$ 
+for a chain of length $L$ is given as 
+%
+\begin{equation}
+\label{N-count}
+Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1. 
+\end{equation}
+%
+On the other hand, after excluding the zero-momentum strings one obtains 
+%
+\begin{equation}
+\label{N-count-nz}
+\widetilde Z_{Neel}=B\Big(\frac{L}{2},\frac{L}{4}\Big). 
+\end{equation}
+%
+Note that~\eref{N-count} is only an upper bound for the number of eigenstates 
+with non-zero N\'eel overlap, while~\eref{N-count-nz} is exact. Before 
+proceeding, we should stress that the total number of particles  
+in the eigenstates having non-zero overlap with the N\'eel and Majumdar-Ghosh 
+states is fixed to $L/2$, due to the fact that for both states one has $S_T^z=0$. 
+However, since the N\'eel state is not $SU(2)$ invariant, eigenstates with 
+non-zero N\'eel overlap can contain infinity rapidities. Thus, one has to 
+consider all the possible sectors with $L/2=\ell+N_{\infty}$, and $\ell$ 
+($N_\infty$) the number of finite (infinite) rapidities. Notice that this 
+is different for the Majumdar-Ghosh state, for which only the parity-invariant 
+eigenstates in the sector with $\ell=L/2$ have to be considered (see below).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{\underline{Parity-invariant states with $\ell$ finite rapidities.}}
+\label{app-1.1}
+
+Let us first consider the eigenstate sector with fixed number of finite rapidities 
+$\ell$, the remaining $L/2-\ell$ ones being infinite (see section~\ref{sec:1.2}). 
+Let us denote the associate string content as ${\mathcal S}=\{s_1,s_2,\dots,
+s_{\ell}\}$. Here $s_n$ is the number of $n$-strings, with the constraint 
+$\sum_k ks_k=\ell$. 
+It is straightforward to check that 
+the total number of parity-invariant quantum number pairs ${\mathcal N}_n(L,{
+\mathcal S})$ in the $n$-string sector is given as 
+%
+\begin{equation}
+\label{NnLS}
+{\mathcal N}_n(L,{\mathcal S})=\Big\lfloor\frac{L}{2}-\frac{1}{2}
+\sum_{m=1}^{\ell}t_{nm}s_m\Big\rfloor,
+\end{equation}
+%
+where $t_{nm}\equiv 2\textrm{Min}(n,m)-\delta_{n,m}$. Thus, the number of parity-invariant 
+eigenstates of the $XXX$ chain ${\mathcal N}(L,{\mathcal S})$ compatible with string content 
+${\mathcal S}$ is obtained by choosing in all the possible ways the associated parity-invariant 
+quantum number pairs as     
+%
+\begin{equation}
+\label{NLS}
+{\mathcal N}(L,{\mathcal S})=\prod_{m=1}^{\ell} B\left({\mathcal N}_m,\left\lfloor
+\frac{s_m}{2}\right\rfloor\right).
+\end{equation}
+%
+Here the product is because each string sector is treated independently, while the 
+factor $1/2$ in $s_m/2$ is because since all quantum numbers are organized in pairs, 
+only half of them have to be specified. Note that in each $n$-string sector only one 
+zero momentum (i.e., zero quantum number) string is allowed, due to the fact that 
+repeated solutions of the BGT equation are discarded. Moreover, from~\eref{NnLS} one has 
+that $s_m$ is odd (even) only if this zero momentum string is (not) present.
+
+We now proceed to consider the string configurations with fixed particle number $\ell\le 
+L/2$ and fixed number of strings $1\le q\le\ell$. Note that due to parity invariance 
+$\ell$ must be even. 
+Also, in determining $q$ strings of different length are treated equally, i.e., 
+$q=\sum_m s_m$. For a given fixed pair 
+$\ell,q$ the total number of allowed quantum number configurations by definition is given 
+as 
+%
+\begin{equation}
+\label{NLlq}
+{\mathcal N}'(L,\ell,q)=\sum\limits_{\{\{s_m\}\,:\, \sum m s_m=\ell, \sum s_m=q\}}
+{\mathcal N}(L,{\mathcal S}),
+\end{equation}
+%
+where the sum is over the string content $\{s_m\}_{m=1}^\ell$ compatible with the constraints 
+$\sum_m s_m=q$ and $\sum_m m s_m=\ell$. The strategy now is to write a recursive relation 
+in both $\ell,q$ for ${\mathcal N}'(L,\ell,q)$. It is useful to consider a shifted string 
+content ${\mathcal S}'$ defined as  
+%
+\begin{equation}
+{\mathcal S}'\equiv \{s_{m+1}\}\quad\textrm{with}\, s_m\in{\mathcal S},\,\forall m.
+\end{equation}
+%
+Using the definition of $t_{ij}$, it is straightforward to derive that  
+%
+\begin{equation}
+t_{ij}=t_{i-1,j-1}+2,
+\end{equation}
+%
+which implies that ${\mathcal N}_n(L,{\mathcal S})$ (see~\eref{NnLS}) satisfies the 
+recursive equation 
+%
+\begin{equation}
+\label{inter}
+{\mathcal N}_n(L,{\mathcal S})={\mathcal N}_{n-1}(L-2q,{\mathcal S}'). 
+\end{equation}
+%
+After substituting~\eref{inter} in~\eref{NLS} one obtains 
+%
+\begin{equation}
+\label{NLSr}
+{\mathcal N}(L,{\mathcal S})=B\Big({\mathcal N}_1(L,{\mathcal S}),\Big\lfloor 
+\frac{s_1}{2}\Big\rfloor\Big){\mathcal N}(L-2q,{\mathcal S}'). 
+\end{equation}
+%
+Finally, using~\eref{NLSr} in~\eref{NLlq}, one obtains a recursive relation for 
+${\mathcal N}'(L,\ell,q)$ as 
+%
+\begin{equation}
+\label{NpLlq}
+{\mathcal N}'(L,\ell,q)=\sum_{s=0}^{q-1}B\Big(\frac{L}{2}-q+\Big\lfloor
+\frac{s}{2}\Big\rfloor,\left\lfloor\frac{s}{2}\right\rfloor\Big){\mathcal N}'
+\left(L-2q,\ell-q,q-s\right), 
+\end{equation}
+%
+with the condition that for $\ell=q$ one has 
+%
+\begin{equation}
+{\mathcal N}'(L,q,q)=B\Big(\Big\lfloor\frac{L-q}{2}\Big\rfloor,\Big\lfloor
+\frac{q}{2} \Big\rfloor\Big).
+\end{equation}
+%
+This is obtained by observing that if $\ell=q$ only $1$-strings are allowed 
+and~\eref{NnLS} gives ${\mathcal N}_n(L,{\mathcal S})=\lfloor (L-q)/2\rfloor$. 
+It is straightforward to check that for $q$ even the ansatz 
+%
+\begin{equation}
+\label{inter1}
+{\mathcal N}'(L,\ell,q)=\frac{q}{\ell}B\Big(\frac{L-\ell}{2},\frac{q}{2}\Big)
+B\Big(\frac{\ell}{2},\frac{q}{2}\Big),
+\end{equation}
+% 
+satisfies~\eref{NpLlq}. Instead, for $q$ odd the solution of~\eref{NpLlq} is 
+%
+\begin{equation}
+\label{inter2}
+{\mathcal N}'(L,\ell,q)=\frac{\ell-q+1}{\ell}B\Big(\frac{L-\ell}{2},\frac{q-1}{2}
+\Big)B\Big(\frac{\ell}{2},\frac{q-1}{2}\Big).
+\end{equation}
+%
+The number of eigenstates in the sector with $\ell$ particles having nonzero N\'eel 
+overlap $Z'_{Neel}(L,\ell)$ is obtained from~\eref{inter1} and~\eref{inter2} by 
+summing over all possible values of $q$ as 
+%
+\begin{equation}
+\label{sum1}
+Z'_{Neel}(L,\ell)=\sum\limits_{q=1}^\ell {\mathcal N}'(L,\ell,q).
+\end{equation}
+%
+It is convenient to split the summation in~\eref{sum1} considering odd and even 
+$q$ separately. For $q$ odd one obtains 
+%
+\begin{equation}
+\sum\limits_{k=0}^{\ell/2-1} {\mathcal N}'(L,\ell,2k+1)=B\Big(\frac{L}{2}-1,
+\frac{\ell}{2}-1\Big),
+\end{equation}
+%
+while for $q$ even one has 
+%
+\begin{equation}
+\sum\limits_{k=0}^{\ell/2} {\mathcal N}'(L,\ell,2k)=B\Big(\frac{L}{2}-1,
+\frac{\ell}{2}\Big). 
+\end{equation}
+%
+Putting everything together one obtains 
+%
+\begin{equation}
+\label{N-count-p}
+Z'_{Neel}(L,\ell)=B\Big(\frac{L}{2}-1,
+\frac{\ell}{2}-1\Big)+B\Big(\frac{L}{2}-1,
+\frac{\ell}{2}\Big). 
+\end{equation}
+%
+The total number of eigenstates with nonzero N\'eel overlap $Z_{Neel}(L)$ 
+(cf.~\eref{N-count}) is obtained from~\eref{N-count-p} by summing over the allowed 
+values of $\ell=2k$ with $k=0,1,\dots,L/2$. Note that the sum is over $\ell$ even 
+due to the parity invariance.
+
+Finally, it is interesting to observe that the total number $Z_{MG}$ of parity-invariant 
+eigenstates having non zero overlap with the Majumdar-Ghosh state is obtained from 
+Eq~\eref{N-count-p} by replacing $\ell=L/2$, to obtain 
+%
+\begin{equation}
+\label{p-inv-mg}
+Z_{MG}=B\Big(\frac{L}{2}-1,\frac{L}{4}-1\Big)+B\Big(\frac{L}{2}-1,\frac{L}{4}
+\Big). 
+\end{equation}
+%
+Physically, this is due to the fact that the Majumdar-Ghosh state is invariant under 
+$SU(2)$ rotations, implying that only eigenstates with zero total spin $S=0$ can have 
+non-zero overlap.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{\underline{Excluding the zero-momentum strings.}}
+\label{app-1.2}
+
+One should first observe that for the generic eigenstate of the $XXX$ chain with 
+$\ell$ finite rapidities, due to parity invariance and the exclusion of zero-momentum 
+strings, only $n$-strings with 
+length $n\le \ell/2$ are allowed. Also, the string content can be written as 
+${\mathcal S}\equiv\{s_1,\dots,s_{\ell/2}\}$, i.e., $s_m=0$ $\forall m>
+\ell/2$. Due to the parity invariance one has that $s_m$ is always even. Clearly 
+one has $\sum_{m=1}^{\ell/2}m s_m=\ell$. Finally, the total number of 
+parity-invariant quantum numbers $\widetilde{\mathcal N}_n$ in the $n$-string 
+sector is given as  
+%
+\begin{equation}
+\widetilde{\mathcal N}_n(L,{\mathcal S})=\frac{L}{2}-\frac{1}{2}
+\sum_{m=1}^{\ell/2}t_{nm} s_m.
+\end{equation}
+%
+The proof now proceeds as in the previous section. One defines the total number of eigenstates 
+with nonzero N\'eel overlap in the sector with fixed $\ell$ finite rapidities and $q$ different 
+string types as $\widetilde{\mathcal N}'(L,\ell,q)$. It is straightforward to show that 
+$\widetilde{\mathcal N}'(L,\ell,q)$ obeys the recursive relation
+%
+\begin{equation}
+\label{NpLlq-1}
+\widetilde{\mathcal N}'(L,\ell,q)=\sum_{s=0}^{q/2-1}B\Big(\frac{L}{2}-q+s,s\Big)\widetilde
+{\mathcal N}'\Big(L-2q,\frac{\ell-q}{2},\frac{q}{2}-s\Big),
+\end{equation}
+% 
+with the constraint
+%
+\begin{equation}
+\widetilde{\mathcal N}'(L,1,1)=\frac{L}{2}-1. 
+\end{equation}
+%
+The solution of~\eref{NpLlq-1} is given as 
+%
+\begin{equation}
+\widetilde{\mathcal N}'(L,\ell,q)=\frac{L-2\ell+2}{L-\ell+2}B\Big(\frac{L-\ell}{2}+1,q\Big)
+B\Big(\frac{\ell}{2}-1,\frac{q}{2}-1\Big).
+\end{equation}
+%
+After summing over the allowed values of $q=2k$ with $k=1,2,\dots,\ell/2$ one obtains 
+the total number of eigenstates with nonzero N\'eel overlap at fixed number of 
+particles $\ell$ $\widetilde Z_{Neel}'(L,\ell)$ as 
+%
+\begin{equation}
+\label{Neel-fi}
+\widetilde Z_{Neel}'(L,\ell)=B\Big(\frac{L}{2},\frac{\ell}{2}\Big)-
+B\Big(\frac{L}{2},\frac{\ell}{2}-1\Big).
+\end{equation}
+%
+by summing over $\ell$ one obtains~\eref{N-count-nz}. Similar to~\eref{p-inv-mg} the 
+total number of eigenstates $\widetilde Z_{MG}$ having non-zero overlap with the 
+Majumdar-Ghosh state is obtained from~\eref{Neel-fi} by replacing $\ell\to L/2$, to obtain 
+%
+\begin{equation}
+\label{mg-fi}
+\widetilde Z_{MG}=B\Big(\frac{L}{2},\frac{L}{4}\Big)-B\Big(\frac{L}{2},\frac{L}{4}-1
+\Big). 
+\end{equation}
+%
+Interestingly, using~\eref{p-inv-mg} and~\eref{mg-fi}, one obtains that the ratio 
+$\widetilde Z_{MG}/Z_{MG}$ is given as 
+%
+\begin{equation}
+\frac{\widetilde Z_{MG}}{Z_{MG}}=\frac{4}{4+L}. 
+\end{equation}
+%
 
@@
 
-\subsection{Quench action reweighing}
+\subsection{Quench action reweighting}
 
@@
 \caption{Energy density expectation values for a quench from N\'eel (a) and Majumdar-Ghosh state (b) obtained by means of the 
-reweighing \eref{rewe}.
+reweighting \eref{rewe}.
 For the Majumdar-Ghosh state a quadratic fit (forcing the asymptotic value $Q_2^{(0)}=-5/8$) describes perfectly the reweighed 
@@
 
-The results obtained by reweighing the data in Figs. \ref{fig1:Neel-sr} and \ref{fig2:dimer-sr}
+The results obtained by reweighting the data in Figs. \ref{fig1:Neel-sr} and \ref{fig2:dimer-sr}
 are shown in Fig. \ref{fig:rew} focusing on the conserved energy density for both the N\'eel and 
 Majumdar-Ghosh initial states. 
-It is evident that the data after reweighing approach a finite value for large $L$ in contrast with the bare vanishing values 
+It is evident that the data after reweighting approach a finite value for large $L$ in contrast with the bare vanishing values 
 (cf. Figs.  \ref{fig1:Neel-sr} and \ref{fig2:dimer-sr}). 
@@
 Finally, it is worth stressing that although the Monte Carlo sampling is done only on the 
-zero-momentum free Hilbert subspace, the algorithm does not suffer of the reweighing problems 
+zero-momentum free Hilbert subspace, the algorithm does not suffer of the reweighting problems 
 found in the exact method (see the preceding section), because the expectation values 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Counting and string content of the eigenstates with nonzero N\'eel and 
-Majumdar-Ghosh overlap}
-\label{app-1}
-
-Here we provide some exact combinatorial formulas for the total number of 
-parity-invariant eigenstates of the $XXX$ chain having non-zero overlap with 
-the N\'eel state and the Majumdar-Ghosh state. 
-%We consider both the situations  
-%with constrained and unconstrained string content and particle number (i.e., 
-%total magnetization). 
-In~\ref{app-1.1} we consider all possible parity-invariant 
-eigenstates, whereas in~\ref{app-1.2} we exclude the eigenstates containing 
-zero-momentum strings. Note that the result in~\ref{app-1.1} is only an upper 
-bound, while the counting in~\ref{app-1.2} is exact. The strategy of the proof 
-is the same as that used to count the number of solutions of the 
-Bethe-Gaudin-Takahashi equations (see for instance Ref.~\cite{faddeev-1996}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Allowing the zero-momentum strings}
-\label{app-1.1}
-
-Here we prove that the total number of parity-invariant eigenstates $Z_{Neel}$ 
-with, in principle, non-zero N\'eel overlap for a chain of length $L$ is given 
-as 
-%
-\begin{equation}
-\label{N-count}
-Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1. 
-\end{equation}
-%
-We restrict ourselves to the situation with $L$ divisible by four. The strategy to 
-prove~\eref{N-count} is to count all the possible parity-invariant BGT quantum numbers 
-configurations (cf. section~\ref{sec:1.3}). Let us consider the sector with fixed number 
-of particles $M$, and string content ${\mathcal S}=\{s_1,s_2,\dots,s_{M}\}$. Here $s_n$ is 
-the number of $n$-strings, with the constraint $\sum_k ks_k=M$. One should stress that 
-$M$ is the number of particles corresponding to {\it finite} solutions of the Bethe 
-equations. The total number of particles is $L/2$, due to the fact that the N\'eel 
-state has $S_T^z=0$. The remaining $L/2-M$ particles correspond to infinite solutions 
-of the Bethe equations (see section~\ref{sec:1.2}). It is straightforward to check that the
-total number of parity-invariant quantum number pairs ${\mathcal N}_n(L,{\mathcal S})$ 
-in the $n$-string sector is given as 
-%
-\begin{equation}
-\label{NnLS}
-{\mathcal N}_n(L,{\mathcal S})=\Big\lfloor\frac{L}{2}-\frac{1}{2}
-\sum_{m=1}^{M}t_{nm}s_m\Big\rfloor,
-\end{equation}
-%
-where $t_{nm}\equiv 2\textrm{Min}(n,m)-\delta_{n,m}$. Thus, the number of parity-invariant 
-eigenstates of the $XXX$ chain ${\mathcal N}(L,{\mathcal S})$ compatible with string content 
-${\mathcal S}$ is obtained by choosing in all the possible ways the associated parity-invariant 
-quantum number pairs as     
-%
-\begin{equation}
-\label{NLS}
-{\mathcal N}(L,{\mathcal S})=\prod_{m=1}^{M} B\left({\mathcal N}_m,\left\lfloor
-\frac{s_m}{2}\right\rfloor\right).
-\end{equation}
-%
-Here the product is because each string sector is treated independently, while the 
-factor $1/2$ in $s_m/2$ is because since all quantum numbers are organized in pairs, 
-only half of them have to be specified. Note that in each $n$-string sector only one 
-zero momentum (i.e., zero quantum number) string is allowed, due to the fact that 
-repeated solutions of the BGT equation are discarded. Moreover, from~\eref{NnLS} one has 
-that $s_m$ is odd (even) only if this zero momentum string is (not) present.
-
-We now proceed to consider the string configurations with fixed particle number $0\le\ell
-\le M$ and fixed number of strings $1\le q\le M/2$. Note that the maximum allowed string 
-length is $M/2$ because of parity invariance. Note also that in determining $q$, strings 
-of different length are treated equally, i.e., $q=\sum_m s_m$. For a given fixed pair 
-$\ell,q$ the total number of allowed quantum number configurations by definition is given 
-as 
-%
-\begin{equation}
-\label{NLlq}
-{\mathcal N}'(L,\ell,q)=\sum\limits_{\{\{s_m\}\,:\, \sum m s_m=\ell, \sum s_m=q\}}
-{\mathcal N}(L,{\mathcal S}),
-\end{equation}
-%
-where the sum is over the string content $\{s_m\}_{m=1}^M$ compatible with the constraints 
-$\sum_m s_m=q$ and $\sum_m m s_m=\ell$. The strategy now is to write a recursive relation 
-in both $\ell,q$ for ${\mathcal N}'(L,\ell,q)$. It is useful to consider a shifted string 
-content ${\mathcal S}'$ defined as  
-%
-\begin{equation}
-{\mathcal S}'\equiv \{s_{m+1}\}\quad\textrm{with}\, s_m\in{\mathcal S},\,\forall m.
-\end{equation}
-%
-Using the definition of $t_{ij}$, it is straightforward to derive that  
-%
-\begin{equation}
-t_{ij}=t_{i-1,j-1}+2,
-\end{equation}
-%
-which implies that ${\mathcal N}_n(L,{\mathcal S})$ (see~\eref{NnLS}) satisfies the 
-recursive equation 
-%
-\begin{equation}
-\label{inter}
-{\mathcal N}_n(L,{\mathcal S})={\mathcal N}_{n-1}(L-2q,{\mathcal S}'). 
-\end{equation}
-%
-After substituting~\eref{inter} in~\eref{NLS} one obtains 
-%
-\begin{equation}
-\label{NLSr}
-{\mathcal N}(L,{\mathcal S})=B\Big({\mathcal N}_1(L,{\mathcal S}),\Big\lfloor 
-\frac{s_1}{2}\Big\rfloor\Big){\mathcal N}(L-2q,{\mathcal S}'). 
-\end{equation}
-%
-Finally, using~\eref{NLSr} in~\eref{NLlq}, one obtains a recursive relation for 
-${\mathcal N}'(L,\ell,q)$ as 
-%
-\begin{equation}
-\label{NpLlq}
-{\mathcal N}'(L,\ell,q)=\sum_{s=0}^{q-1}B\Big(\frac{L}{2}-q+\Big\lfloor
-\frac{s}{2}\Big\rfloor,\left\lfloor\frac{s}{2}\right\rfloor\Big){\mathcal N}'
-\left(L-2q,\ell-q,q-s\right), 
-\end{equation}
-%
-with the condition that for $\ell=q$ one has 
-%
-\begin{equation}
-{\mathcal N}'(L,q,q)=B\Big(\Big\lfloor\frac{L-q}{2}\Big\rfloor,\Big\lfloor
-\frac{q}{2} \Big\rfloor\Big).
-\end{equation}
-%
-This is obtained by observing that if $\ell=q$ only $1$-strings are allowed 
-and~\eref{NnLS} gives ${\mathcal N}_n(L,{\mathcal S})=\lfloor (L-q)/2\rfloor$. 
-It is straightforward to check that for $q$ even the ansatz 
-%
-\begin{equation}
-\label{inter1}
-{\mathcal N}'(L,\ell,q)=\frac{q}{\ell}B\Big(\frac{L-\ell}{2},\frac{q}{2}\Big)
-B\Big(\frac{\ell}{2},\frac{q}{2}\Big),
-\end{equation}
-% 
-satisfies~\eref{NpLlq}. Instead, for $q$ odd the solution of~\eref{NpLlq} is 
-%
-\begin{equation}
-\label{inter2}
-{\mathcal N}'(L,\ell,q)=\frac{\ell-q+1}{\ell}B\Big(\frac{L-\ell}{2},\frac{q-1}{2}
-\Big)B\Big(\frac{\ell}{2},\frac{q-1}{2}\Big).
-\end{equation}
-%
-The number of eigenstates in the sector with $\ell$ particles having nonzero N\'eel 
-overlap $Z'_{Neel}(L,\ell)$ is obtained from~\eref{inter1} and~\eref{inter2} by 
-summing over all possible values of $q$ as 
-%
-\begin{equation}
-\label{sum1}
-Z'_{Neel}(L,\ell)=\sum\limits_{q=1}^\ell {\mathcal N}'(L,\ell,q).
-\end{equation}
-%
-It is convenient to split the summation in~\eref{sum1} considering odd and even 
-$q$ separately. For $q$ odd one obtains 
-%
-\begin{equation}
-\sum\limits_{k=0}^{\ell/2-1} {\mathcal N}'(L,\ell,2k+1)=B\Big(\frac{L}{2}-1,
-\frac{\ell}{2}-1\Big),
-\end{equation}
-%
-while for $q$ even one has 
-%
-\begin{equation}
-\sum\limits_{k=0}^{\ell/2} {\mathcal N}'(L,\ell,2k)=B\Big(\frac{L}{2}-1,
-\frac{\ell}{2}\Big). 
-\end{equation}
-%
-Putting everything together one obtains 
-%
-\begin{equation}
-\label{N-count-p}
-Z'_{Neel}(L,\ell)=B\Big(\frac{L}{2}-1,
-\frac{\ell}{2}-1\Big)+B\Big(\frac{L}{2}-1,
-\frac{\ell}{2}\Big). 
-\end{equation}
-%
-The total number of eigenstates with nonzero N\'eel overlap $Z_{Neel}(L)$ 
-(cf.~\eref{N-count}) is obtained from~\eref{N-count-p} by summing over the allowed 
-values of $\ell=2k$ with $k=0,1,\dots,\ell/2$. Note that the sum is over $\ell$ even 
-due to the parity invariance.
-
-Finally, it is interesting to observe that the total number $Z_{MG}$ of parity-invariant 
-eigenstates having non zero overlap with the Majumdar-Ghosh state is obtained from 
-Eq~\eref{N-count-p} by replacing $\ell=L/2$, to obtain 
-%
-\begin{equation}
-\label{p-inv-mg}
-Z_{MG}=B\Big(\frac{L}{2}-1,\frac{L}{4}-1\Big)+B\Big(\frac{L}{2}-1,\frac{L}{4}
-\Big). 
-\end{equation}
-%
-Physically, this is due to the fact that the Majumdar-Ghosh state is invariant under 
-$SU(2)$ rotations, implying that only eigenstates with zero total spin $S=0$ can have 
-non-zero overlap.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Excluding the zero-momentum strings}
-\label{app-1.2}
-
-Here we demonstrate that the total number of eigenstates $\widetilde Z_{Neel}(L)$ 
-with nonzero N\'eel overlap, after excluding the zero-momentum strings, is given as 
-%
-\begin{equation}
-\label{result}
-\widetilde Z_{Neel}(L)=B\Big(\frac{L}{2},\frac{L}{4}\Big). 
-\end{equation}
-One should first observe that in a generic $M$-particle eigenstate of the $XXX$ chain, 
-due to parity invariance, only $n$-strings with length $n\le M/2$ are allowed. Also, the 
-string content can be written as $\widetilde{\mathcal S}\equiv\{\tilde s_1,\dots,\tilde 
-s_{M/2}\}$, i.e., $\tilde s_m=0$ $\forall m>M/2$. Due to the parity invariance 
-one has that $\tilde s_m$ is always even. Clearly one has $\sum_{m=1}^{M/2}m \tilde 
-s_m=M$. Finally, the total number of parity-invariant quantum numbers $\widetilde{
-\mathcal N}_n$ in the $n$-string sector is given as  
-%
-\begin{equation}
-\widetilde{\mathcal N}_n(L,\widetilde{\mathcal S})=\frac{L}{2}-\frac{1}{2}
-\sum_{m=1}^{M/2}t_{nm}\tilde s_m.
-\end{equation}
-%
-The proof now proceeds as in the previous section. One defines the total number of eigenstates 
-with nonzero N\'eel overlap in the sector with fixed $\ell$ particles and $q$ different 
-string types as $\widetilde{\mathcal N}'(L,\ell,q)$. It is straightforward to show that 
-$\widetilde{\mathcal N}'(L,\ell,q)$ obeys the recursive relation
-%
-\begin{equation}
-\label{NpLlq-1}
-\widetilde{\mathcal N}'(L,\ell,q)=\sum_{s=0}^{q/2-1}B\Big(\frac{L}{2}-q+s,s\Big)\widetilde
-{\mathcal N}'\Big(L-2q,\frac{\ell-q}{2},\frac{q}{2}-s\Big),
-\end{equation}
-% 
-with the constraint
-%
-\begin{equation}
-\widetilde{\mathcal N}'(L,1,1)=\frac{L}{2}-1. 
-\end{equation}
-%
-The solution of~\eref{NpLlq-1} is given as 
-%
-\begin{equation}
-\widetilde{\mathcal N}'(L,\ell,q)=\frac{L-2\ell+2}{L-\ell+2}B\Big(\frac{L-\ell}{2}+1,q\Big)
-B\Big(\frac{\ell}{2}-1,\frac{q}{2}-1\Big).
-\end{equation}
-%
-After summing over the allowed values of $q=2k$ with $k=1,2,\dots,\ell/2$ one obtains 
-the total number of eigenstates with nonzero N\'eel overlap at fixed number of 
-particles $\ell$ $\widetilde Z_{Neel}'(L,\ell)$ as 
-%
-\begin{equation}
-\label{Neel-fi}
-\widetilde Z_{Neel}'(L,\ell)=B\Big(\frac{L}{2},\frac{\ell}{2}\Big)-
-B\Big(\frac{L}{2},\frac{\ell}{2}-1\Big).
-\end{equation}
-%
-Summing over $\ell$ one obtains~\eref{result}. Similar to~\eref{p-inv-mg} the total number 
-of eigenstates $\widetilde Z_{MG}$ having non-zero overlap with the Majumdar-Ghosh state 
-is obtained from~\eref{Neel-fi} by replacing $\ell\to L/2$, to obtain 
-%
-\begin{equation}
-\label{mg-fi}
-\widetilde Z_{MG}=B\Big(\frac{L}{2},\frac{L}{4}\Big)-B\Big(\frac{L}{2},\frac{L}{4}-1
-\Big). 
-\end{equation}
-%
-Interestingly, using~\eref{p-inv-mg} and~\eref{mg-fi}, one obtains that the ratio 
-$\widetilde Z_{MG}/Z_{MG}$ is given as 
-%
-\begin{equation}
-\frac{\widetilde Z_{MG}}{Z_{MG}}=\frac{4}{4+L}. 
-\end{equation}
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Exact N\'eel and Majumdar-Ghosh overlaps for a small Heisenberg chain} 
@@
 This allows to check the validity of the string hypothesis when calculating overlaps. 
-Moreover, this also provides a simple check of the counting formula~\eref{result}.
+Moreover, this also provides a simple check of the counting formula~\eref{N-count-nz}.
 

### 2015-12-05 draft/fs_qa_v7.tex
05/12/2015

--- 2015-12-05 QAMC_draft/fs_qa_v6.tex
@@
 %
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Counting and string content of the eigenstates with nonzero N\'eel and 
+%Majumdar-Ghosh overlap}
+\section{Counting and string content of parity-invariant eigenstates}
+\label{app-1}
+
+Here we provide some exact combinatorial formulas for the total number of 
+parity-invariant eigenstates of the $XXX$ chain, which are the only eigenstates 
+having, in principle, non-zero overlap with the N\'eel state and the 
+Majumdar-Ghosh state.
+
+In~\ref{app-1.1} we consider all possible parity-invariant 
+eigenstates, whereas in~\ref{app-1.2} we exclude the eigenstates containing 
+zero-momentum strings. Note that the result in~\ref{app-1.1} is only an upper 
+bound, while the counting in~\ref{app-1.2} is exact. The strategy of the proof 
+is the same as that used to count the number of solutions of the 
+Bethe-Gaudin-Takahashi equations (see for instance Ref.~\cite{faddeev-1996}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Allowing the zero-momentum strings}
+%\label{app-1.1}
+
+Here we prove that the total number of parity-invariant eigenstates $Z_{Neel}$ 
+with, in principle, non-zero N\'eel overlap for a chain of length $L$ is given 
+as 
+%
+\begin{equation}
+\label{N-count}
+Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1. 
+\end{equation}
+%
+We restrict ourselves to the situation with $L$ divisible by four. The strategy to 
+prove~\eref{N-count} is to count all the possible parity-invariant BGT quantum numbers 
+configurations (cf. section~\ref{sec:1.3}).
+
+The total number of particles in the eigenstates is fixed to $L/2$, due to the fact that 
+the N\'eel state has $S_T^z=0$. As the N\'eel state is not $SU(2)$ invariant the corresponding 
+rapidities can be finite (identifying highest-weigth states) or infinite (descendant states).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{$SU(2)$ Highest-weight eigenstates}
+
+Let us consider the eigenstate sector with fixed number of finite rapidities 
+$\ell$, the remaining $L/2-\ell$ ones being infinite (see section~\ref{sec:1.2}). 
+Let us denote the associate string content as ${\mathcal S}=\{s_1,s_2,\dots,
+s_{\ell}\}$. Here $s_n$ is the number of $n$-strings, with the constraint 
+$\sum_k ks_k=\ell$. 
+Parity-invariant eigenstates are in one-to-one correspondence with parity-invariant 
+BGT quantum number configurations. Moreover, it is straightforward to check that 
+the total number of parity-invariant quantum number pairs ${\mathcal N}_n(L,{
+\mathcal S})$ in the $n$-string sector is given as 
+%
+\begin{equation}
+\label{NnLS}
+{\mathcal N}_n(L,{\mathcal S})=\Big\lfloor\frac{L}{2}-\frac{1}{2}
+\sum_{m=1}^{\ell}t_{nm}s_m\Big\rfloor,
+\end{equation}
+%
+where $t_{nm}\equiv 2\textrm{Min}(n,m)-\delta_{n,m}$. Thus, the number of parity-invariant 
+eigenstates of the $XXX$ chain ${\mathcal N}(L,{\mathcal S})$ compatible with string content 
+${\mathcal S}$ is obtained by choosing in all the possible ways the associated parity-invariant 
+quantum number pairs as     
+%
+\begin{equation}
+\label{NLS}
+{\mathcal N}(L,{\mathcal S})=\prod_{m=1}^{\ell} B\left({\mathcal N}_m,\left\lfloor
+\frac{s_m}{2}\right\rfloor\right).
+\end{equation}
+%
+Here the product is because each string sector is treated independently, while the 
+factor $1/2$ in $s_m/2$ is because since all quantum numbers are organized in pairs, 
+only half of them have to be specified. Note that in each $n$-string sector only one 
+zero momentum (i.e., zero quantum number) string is allowed, due to the fact that 
+repeated solutions of the BGT equation are discarded. Moreover, from~\eref{NnLS} one has 
+that $s_m$ is odd (even) only if this zero momentum string is (not) present.
+
+We now proceed to consider the string configurations with fixed particle number $\ell\le 
+L/2$ and fixed number of strings $1\le q\le\ell$. Note that due to parity invariance 
+$\ell$ must be even. 
+Also, in determining $q$ strings of different length are treated equally, i.e., 
+$q=\sum_m s_m$. For a given fixed pair 
+$\ell,q$ the total number of allowed quantum number configurations by definition is given 
+as 
+%
+\begin{equation}
+\label{NLlq}
+{\mathcal N}'(L,\ell,q)=\sum\limits_{\{\{s_m\}\,:\, \sum m s_m=\ell, \sum s_m=q\}}
+{\mathcal N}(L,{\mathcal S}),
+\end{equation}
+%
+where the sum is over the string content $\{s_m\}_{m=1}^\ell$ compatible with the constraints 
+$\sum_m s_m=q$ and $\sum_m m s_m=\ell$. The strategy now is to write a recursive relation 
+in both $\ell,q$ for ${\mathcal N}'(L,\ell,q)$. It is useful to consider a shifted string 
+content ${\mathcal S}'$ defined as  
+%
+\begin{equation}
+{\mathcal S}'\equiv \{s_{m+1}\}\quad\textrm{with}\, s_m\in{\mathcal S},\,\forall m.
+\end{equation}
+%
+Using the definition of $t_{ij}$, it is straightforward to derive that  
+%
+\begin{equation}
+t_{ij}=t_{i-1,j-1}+2,
+\end{equation}
+%
+which implies that ${\mathcal N}_n(L,{\mathcal S})$ (see~\eref{NnLS}) satisfies the 
+recursive equation 
+%
+\begin{equation}
+\label{inter}
+{\mathcal N}_n(L,{\mathcal S})={\mathcal N}_{n-1}(L-2q,{\mathcal S}'). 
+\end{equation}
+%
+After substituting~\eref{inter} in~\eref{NLS} one obtains 
+%
+\begin{equation}
+\label{NLSr}
+{\mathcal N}(L,{\mathcal S})=B\Big({\mathcal N}_1(L,{\mathcal S}),\Big\lfloor 
+\frac{s_1}{2}\Big\rfloor\Big){\mathcal N}(L-2q,{\mathcal S}'). 
+\end{equation}
+%
+Finally, using~\eref{NLSr} in~\eref{NLlq}, one obtains a recursive relation for 
+${\mathcal N}'(L,\ell,q)$ as 
+%
+\begin{equation}
+\label{NpLlq}
+{\mathcal N}'(L,\ell,q)=\sum_{s=0}^{q-1}B\Big(\frac{L}{2}-q+\Big\lfloor
+\frac{s}{2}\Big\rfloor,\left\lfloor\frac{s}{2}\right\rfloor\Big){\mathcal N}'
+\left(L-2q,\ell-q,q-s\right), 
+\end{equation}
+%
+with the condition that for $\ell=q$ one has 
+%
+\begin{equation}
+{\mathcal N}'(L,q,q)=B\Big(\Big\lfloor\frac{L-q}{2}\Big\rfloor,\Big\lfloor
+\frac{q}{2} \Big\rfloor\Big).
+\end{equation}
+%
+This is obtained by observing that if $\ell=q$ only $1$-strings are allowed 
+and~\eref{NnLS} gives ${\mathcal N}_n(L,{\mathcal S})=\lfloor (L-q)/2\rfloor$. 
+It is straightforward to check that for $q$ even the ansatz 
+%
+\begin{equation}
+\label{inter1}
+{\mathcal N}'(L,\ell,q)=\frac{q}{\ell}B\Big(\frac{L-\ell}{2},\frac{q}{2}\Big)
+B\Big(\frac{\ell}{2},\frac{q}{2}\Big),
+\end{equation}
+% 
+satisfies~\eref{NpLlq}. Instead, for $q$ odd the solution of~\eref{NpLlq} is 
+%
+\begin{equation}
+\label{inter2}
+{\mathcal N}'(L,\ell,q)=\frac{\ell-q+1}{\ell}B\Big(\frac{L-\ell}{2},\frac{q-1}{2}
+\Big)B\Big(\frac{\ell}{2},\frac{q-1}{2}\Big).
+\end{equation}
+%
+The number of eigenstates in the sector with $\ell$ particles having nonzero N\'eel 
+overlap $Z'_{Neel}(L,\ell)$ is obtained from~\eref{inter1} and~\eref{inter2} by 
+summing over all possible values of $q$ as 
+%
+\begin{equation}
+\label{sum1}
+Z'_{Neel}(L,\ell)=\sum\limits_{q=1}^\ell {\mathcal N}'(L,\ell,q).
+\end{equation}
+%
+It is convenient to split the summation in~\eref{sum1} considering odd and even 
+$q$ separately. For $q$ odd one obtains 
+%
+\begin{equation}
+\sum\limits_{k=0}^{\ell/2-1} {\mathcal N}'(L,\ell,2k+1)=B\Big(\frac{L}{2}-1,
+\frac{\ell}{2}-1\Big),
+\end{equation}
+%
+while for $q$ even one has 
+%
+\begin{equation}
+\sum\limits_{k=0}^{\ell/2} {\mathcal N}'(L,\ell,2k)=B\Big(\frac{L}{2}-1,
+\frac{\ell}{2}\Big). 
+\end{equation}
+%
+Putting everything together one obtains 
+%
+\begin{equation}
+\label{N-count-p}
+Z'_{Neel}(L,\ell)=B\Big(\frac{L}{2}-1,
+\frac{\ell}{2}-1\Big)+B\Big(\frac{L}{2}-1,
+\frac{\ell}{2}\Big). 
+\end{equation}
+%
+The total number of eigenstates with nonzero N\'eel overlap $Z_{Neel}(L)$ 
+(cf.~\eref{N-count}) is obtained from~\eref{N-count-p} by summing over the allowed 
+values of $\ell=2k$ with $k=0,1,\dots,\ell/2$. Note that the sum is over $\ell$ even 
+due to the parity invariance.
+
+Finally, it is interesting to observe that the total number $Z_{MG}$ of parity-invariant 
+eigenstates having non zero overlap with the Majumdar-Ghosh state is obtained from 
+Eq~\eref{N-count-p} by replacing $\ell=L/2$, to obtain 
+%
+\begin{equation}
+\label{p-inv-mg}
+Z_{MG}=B\Big(\frac{L}{2}-1,\frac{L}{4}-1\Big)+B\Big(\frac{L}{2}-1,\frac{L}{4}
+\Big). 
+\end{equation}
+%
+Physically, this is due to the fact that the Majumdar-Ghosh state is invariant under 
+$SU(2)$ rotations, implying that only eigenstates with zero total spin $S=0$ can have 
+non-zero overlap.
 
@@
 \appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Counting and string content of the eigenstates with nonzero N\'eel and 
-Majumdar-Ghosh overlap}
-\label{app-1}
-
-Here we provide some exact combinatorial formulas for the total number of 
-parity-invariant eigenstates of the $XXX$ chain having non-zero overlap with 
-the N\'eel state and the Majumdar-Ghosh state. 
-%We consider both the situations  
-%with constrained and unconstrained string content and particle number (i.e., 
-%total magnetization). 
-In~\ref{app-1.1} we consider all possible parity-invariant 
-eigenstates, whereas in~\ref{app-1.2} we exclude the eigenstates containing 
-zero-momentum strings. Note that the result in~\ref{app-1.1} is only an upper 
-bound, while the counting in~\ref{app-1.2} is exact. The strategy of the proof 
-is the same as that used to count the number of solutions of the 
-Bethe-Gaudin-Takahashi equations (see for instance Ref.~\cite{faddeev-1996}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Allowing the zero-momentum strings}
-\label{app-1.1}
-
-Here we prove that the total number of parity-invariant eigenstates $Z_{Neel}$ 
-with, in principle, non-zero N\'eel overlap for a chain of length $L$ is given 
-as 
-%
-\begin{equation}
-\label{N-count}
-Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1. 
-\end{equation}
-%
-We restrict ourselves to the situation with $L$ divisible by four. The strategy to 
-prove~\eref{N-count} is to count all the possible parity-invariant BGT quantum numbers 
-configurations (cf. section~\ref{sec:1.3}). Let us consider the sector with fixed number 
-of particles $M$, and string content ${\mathcal S}=\{s_1,s_2,\dots,s_{M}\}$. Here $s_n$ is 
-the number of $n$-strings, with the constraint $\sum_k ks_k=M$. One should stress that 
-$M$ is the number of particles corresponding to {\it finite} solutions of the Bethe 
-equations. The total number of particles is $L/2$, due to the fact that the N\'eel 
-state has $S_T^z=0$. The remaining $L/2-M$ particles correspond to infinite solutions 
-of the Bethe equations (see section~\ref{sec:1.2}). It is straightforward to check that the
-total number of parity-invariant quantum number pairs ${\mathcal N}_n(L,{\mathcal S})$ 
-in the $n$-string sector is given as 
-%
-\begin{equation}
-\label{NnLS}
-{\mathcal N}_n(L,{\mathcal S})=\Big\lfloor\frac{L}{2}-\frac{1}{2}
-\sum_{m=1}^{M}t_{nm}s_m\Big\rfloor,
-\end{equation}
-%
-where $t_{nm}\equiv 2\textrm{Min}(n,m)-\delta_{n,m}$. Thus, the number of parity-invariant 
-eigenstates of the $XXX$ chain ${\mathcal N}(L,{\mathcal S})$ compatible with string content 
-${\mathcal S}$ is obtained by choosing in all the possible ways the associated parity-invariant 
-quantum number pairs as     
-%
-\begin{equation}
-\label{NLS}
-{\mathcal N}(L,{\mathcal S})=\prod_{m=1}^{M} B\left({\mathcal N}_m,\left\lfloor
-\frac{s_m}{2}\right\rfloor\right).
-\end{equation}
-%
-Here the product is because each string sector is treated independently, while the 
-factor $1/2$ in $s_m/2$ is because since all quantum numbers are organized in pairs, 
-only half of them have to be specified. Note that in each $n$-string sector only one 
-zero momentum (i.e., zero quantum number) string is allowed, due to the fact that 
-repeated solutions of the BGT equation are discarded. Moreover, from~\eref{NnLS} one has 
-that $s_m$ is odd (even) only if this zero momentum string is (not) present.
-
-We now proceed to consider the string configurations with fixed particle number $0\le\ell
-\le M$ and fixed number of strings $1\le q\le M/2$. Note that the maximum allowed string 
-length is $M/2$ because of parity invariance. Note also that in determining $q$, strings 
-of different length are treated equally, i.e., $q=\sum_m s_m$. For a given fixed pair 
-$\ell,q$ the total number of allowed quantum number configurations by definition is given 
-as 
-%
-\begin{equation}
-\label{NLlq}
-{\mathcal N}'(L,\ell,q)=\sum\limits_{\{\{s_m\}\,:\, \sum m s_m=\ell, \sum s_m=q\}}
-{\mathcal N}(L,{\mathcal S}),
-\end{equation}
-%
-where the sum is over the string content $\{s_m\}_{m=1}^M$ compatible with the constraints 
-$\sum_m s_m=q$ and $\sum_m m s_m=\ell$. The strategy now is to write a recursive relation 
-in both $\ell,q$ for ${\mathcal N}'(L,\ell,q)$. It is useful to consider a shifted string 
-content ${\mathcal S}'$ defined as  
-%
-\begin{equation}
-{\mathcal S}'\equiv \{s_{m+1}\}\quad\textrm{with}\, s_m\in{\mathcal S},\,\forall m.
-\end{equation}
-%
-Using the definition of $t_{ij}$, it is straightforward to derive that  
-%
-\begin{equation}
-t_{ij}=t_{i-1,j-1}+2,
-\end{equation}
-%
-which implies that ${\mathcal N}_n(L,{\mathcal S})$ (see~\eref{NnLS}) satisfies the 
-recursive equation 
-%
-\begin{equation}
-\label{inter}
-{\mathcal N}_n(L,{\mathcal S})={\mathcal N}_{n-1}(L-2q,{\mathcal S}'). 
-\end{equation}
-%
-After substituting~\eref{inter} in~\eref{NLS} one obtains 
-%
-\begin{equation}
-\label{NLSr}
-{\mathcal N}(L,{\mathcal S})=B\Big({\mathcal N}_1(L,{\mathcal S}),\Big\lfloor 
-\frac{s_1}{2}\Big\rfloor\Big){\mathcal N}(L-2q,{\mathcal S}'). 
-\end{equation}
-%
-Finally, using~\eref{NLSr} in~\eref{NLlq}, one obtains a recursive relation for 
-${\mathcal N}'(L,\ell,q)$ as 
-%
-\begin{equation}
-\label{NpLlq}
-{\mathcal N}'(L,\ell,q)=\sum_{s=0}^{q-1}B\Big(\frac{L}{2}-q+\Big\lfloor
-\frac{s}{2}\Big\rfloor,\left\lfloor\frac{s}{2}\right\rfloor\Big){\mathcal N}'
-\left(L-2q,\ell-q,q-s\right), 
-\end{equation}
-%
-with the condition that for $\ell=q$ one has 
-%
-\begin{equation}
-{\mathcal N}'(L,q,q)=B\Big(\Big\lfloor\frac{L-q}{2}\Big\rfloor,\Big\lfloor
-\frac{q}{2} \Big\rfloor\Big).
-\end{equation}
-%
-This is obtained by observing that if $\ell=q$ only $1$-strings are allowed 
-and~\eref{NnLS} gives ${\mathcal N}_n(L,{\mathcal S})=\lfloor (L-q)/2\rfloor$. 
-It is straightforward to check that for $q$ even the ansatz 
-%
-\begin{equation}
-\label{inter1}
-{\mathcal N}'(L,\ell,q)=\frac{q}{\ell}B\Big(\frac{L-\ell}{2},\frac{q}{2}\Big)
-B\Big(\frac{\ell}{2},\frac{q}{2}\Big),
-\end{equation}
-% 
-satisfies~\eref{NpLlq}. Instead, for $q$ odd the solution of~\eref{NpLlq} is 
-%
-\begin{equation}
-\label{inter2}
-{\mathcal N}'(L,\ell,q)=\frac{\ell-q+1}{\ell}B\Big(\frac{L-\ell}{2},\frac{q-1}{2}
-\Big)B\Big(\frac{\ell}{2},\frac{q-1}{2}\Big).
-\end{equation}
-%
-The number of eigenstates in the sector with $\ell$ particles having nonzero N\'eel 
-overlap $Z'_{Neel}(L,\ell)$ is obtained from~\eref{inter1} and~\eref{inter2} by 
-summing over all possible values of $q$ as 
-%
-\begin{equation}
-\label{sum1}
-Z'_{Neel}(L,\ell)=\sum\limits_{q=1}^\ell {\mathcal N}'(L,\ell,q).
-\end{equation}
-%
-It is convenient to split the summation in~\eref{sum1} considering odd and even 
-$q$ separately. For $q$ odd one obtains 
-%
-\begin{equation}
-\sum\limits_{k=0}^{\ell/2-1} {\mathcal N}'(L,\ell,2k+1)=B\Big(\frac{L}{2}-1,
-\frac{\ell}{2}-1\Big),
-\end{equation}
-%
-while for $q$ even one has 
-%
-\begin{equation}
-\sum\limits_{k=0}^{\ell/2} {\mathcal N}'(L,\ell,2k)=B\Big(\frac{L}{2}-1,
-\frac{\ell}{2}\Big). 
-\end{equation}
-%
-Putting everything together one obtains 
-%
-\begin{equation}
-\label{N-count-p}
-Z'_{Neel}(L,\ell)=B\Big(\frac{L}{2}-1,
-\frac{\ell}{2}-1\Big)+B\Big(\frac{L}{2}-1,
-\frac{\ell}{2}\Big). 
-\end{equation}
-%
-The total number of eigenstates with nonzero N\'eel overlap $Z_{Neel}(L)$ 
-(cf.~\eref{N-count}) is obtained from~\eref{N-count-p} by summing over the allowed 
-values of $\ell=2k$ with $k=0,1,\dots,\ell/2$. Note that the sum is over $\ell$ even 
-due to the parity invariance.
-
-Finally, it is interesting to observe that the total number $Z_{MG}$ of parity-invariant 
-eigenstates having non zero overlap with the Majumdar-Ghosh state is obtained from 
-Eq~\eref{N-count-p} by replacing $\ell=L/2$, to obtain 
-%
-\begin{equation}
-\label{p-inv-mg}
-Z_{MG}=B\Big(\frac{L}{2}-1,\frac{L}{4}-1\Big)+B\Big(\frac{L}{2}-1,\frac{L}{4}
-\Big). 
-\end{equation}
-%
-Physically, this is due to the fact that the Majumdar-Ghosh state is invariant under 
-$SU(2)$ rotations, implying that only eigenstates with zero total spin $S=0$ can have 
-non-zero overlap.
 

### 2015-12-05 QAMC_draft/NeelOverlap_v2.m

@@ -1,0 +1,93 @@
+(* ::Package:: *)
+
+(* ::Input:: *)
+(*SetOptions[Notebooks["NeelOverlap_v2.nb"][[1]], AutoGeneratedPackage -> Automatic]; *)
+(*incr[digs_, base_] := Module[{carry = 1, ndigs = digs, k = 1, nd}, *)
+(*    While[k <= Length[digs], {carry, nd} = QuotientRemainder[ndigs[[k]] + carry, base[[k]]]; ndigs[[k]] = nd; If[carry == 0, Break[]]; k++; ]; *)
+(*     ndigs]; *)
+(*t[i_, j_] := 2.*Min[i, j] - 1.*KroneckerDelta[i, j]; *)
+(*UpB[L_, M_, \[Alpha]_, n_] := (L - 1. - Sum[t[n, j]*\[Alpha][[j]], {j, 1., M}])/2.; *)
+(*GenString[M_] := Block[{part, part1, pair, d, j, k, m, p, check}, *)
+(*    m = M; part = Reap[While[m != 0, d = IntegerPart[RandomReal[{1., M + 1 - 1/10^12}]]; j = IntegerPart[RandomReal[{1., M + 1 - 1/10^12}]]; *)
+(*          p = RandomReal[{0, 1}]; If[p <= (d*PartitionsP[m - j*d])/(m*PartitionsP[m]), Sow[Table[d, {k, 1, j}]]; m = m - j*d; ]; ]; ]; *)
+(*     part1 = Flatten[part]; Table[Count[part1, i], {i, 1, M}]]; *)
+(*ChooString[M_, L_, strOl_] := Block[{string, mat, DDol, DDne, i, j, strNe, p, vec, vec1}, *)
+(*    string = strOl; mat = Table[t[i, j], {i, 1, M}, {j, 1, M}]; *)
+(*     DDol = Product[Binomial[L - Total[Table[mat[[i,j]]*string[[j]], {j, 1, M}]], string[[i]]], {i, 1, M}]; strNe = GenString[M]; *)
+(*     DDne = Product[Binomial[L - Total[Table[mat[[i,j]]*strNe[[j]], {j, 1, M}]], strNe[[i]]], {i, 1, M}]; p = RandomReal[{0, 1}]; *)
[…]

### 2015-12-07 QAMC_draft/fs_qa_v8.tex
arxiv

--- 2015-12-05 QAMC_draft/fs_qa_v7.tex
@@
 although the proposed approach is valid for an arbitrary integrable model. 
-We consider only those states which do not contain zero-momentum strings because the latter 
+We consider only eigenstates which do not contain zero-momentum strings because the latter 
 are affected by fictitious singularities that are very difficult to take into account. 
-We show that the fraction of eigenstates that do not contain zero-momentum strings is vanishing in the thermodynamic limit.
-Consequently, restricting to this part of the Hilbert space would lead to vanishing expectation values of local observables. 
-It is, however, possible to reconstruct the asymptotic values by properly reweighting the expectations in the considered 
-subspace at the price of introducing finite-size corrections. 
-We also develop a Monte Carlo sampling of the Hilbert space which allows us to study larger systems. 
-We accurately reconstruct the expectation values of the conserved charged and the root distributions in the stationary state, 
-which turn out to match the exact thermodynamic results. 
-The proposed method can be  implemented even in cases in which an analytic thermodynamic solution is not obtainable.
+We show that the fraction of eigenstates that do not contain zero-momentum strings is vanishing 
+in the thermodynamic limit. Consequently, restricting to this part of the Hilbert space leads to 
+vanishing expectation values of local observables. However, it is possible to reconstruct the 
+asymptotic values by properly reweighting the expectations in the considered subspace, at the 
+price of introducing finite-size corrections. We also develop a Monte Carlo sampling of the 
+Hilbert space which allows us to study larger systems. We accurately reconstruct the expectation 
+values of the conserved charged and the root distributions in the stationary state, which turn 
+out to match the exact thermodynamic results. The proposed method can be implemented even in 
+cases in which an analytic thermodynamic solution is not obtainable.
 
@@
 (ETH) implies that the diagonal ensemble~\eref{d-ensemble} becomes equivalent 
-to the usual Gibbs (thermal) ensemble (a conjecture which has been investigated in many 
-numerical studies \cite{tvar,alba-2015a}).
+to the usual Gibbs (thermal) ensemble (a conjecture which has been investigated 
+in many numerical studies \cite{tvar,alba-2015a}).
 
@@
 to be fixed by imposing that  $\langle Q_j\rangle_{GGE}=\langle\Psi_0|Q_j|\Psi_0\rangle$. 
-%Note that for the diagonal ensemble~\eref{d-ensemble}  one has trivially that $\langle
-%{\mathcal O}\rangle_{DE}=\langle\Psi_0|{\mathcal O}|\Psi_0\rangle$. 
 This also provides  useful sum rules that will be of interest in this paper. 
-The validity of the GGE has been confirmed in non-interacting theories~\cite{calabrese-2006,cramer-2008,barthel-2008,rossini-2009,calabrese-2011,cazalilla-2012,se-12,mossel-2012a,collura-2013,fagotti-2013,kcc14,kcc14a,sotiriadis-2014,bkc-14},
-whereas in interacting ones the scenario is 
-still not fully settled and some recent works~\cite{ilievski-2015a,cardy-2015} suggest that the $GGE$ 
-description of the steady state  is complete provided that the so-called quasi-local 
-charges~\cite{prosen-2014,pereira-2014,ilievski-2015,essler-2015} are included in the GGE~\eref{gge}.
+The validity of the GGE has been confirmed in non-interacting theories~\cite{calabrese-2006,
+cramer-2008,barthel-2008,rossini-2009,calabrese-2011,cazalilla-2012,se-12,mossel-2012a,
+collura-2013,fagotti-2013,kcc14,kcc14a,sotiriadis-2014,bkc-14}, whereas in interacting 
+ones the scenario is still not fully settled and some recent works~\cite{ilievski-2015a,
+cardy-2015} suggest that the $GGE$ description of the steady state  is complete provided 
+that the so-called quasi-local charges~\cite{prosen-2014,pereira-2014,ilievski-2015,essler-2015} 
+are included in the GGE~\eref{gge}.
 
@@
 for transport in spin chains \cite{de_luca}, and for some interacting field theories \cite{bse-14}.  
-The quench action approach allows in principle also to reconstruct the full relaxation dynamics to the steady state \cite{caux-2013}
-as numerically done for the 1D Bose gas~\cite{de-nardis-2015a,de-nardis-2015}.
+The quench action approach allows in principle also to reconstruct the full relaxation dynamics 
+to the steady state \cite{caux-2013} as numerically done for the 1D Bose 
+gas~\cite{de-nardis-2015a,de-nardis-2015}.
 
@@
 %
-The non-equilibrium quench dynamics of the XXZ spin chain has been investigated numerically intensively \cite{dmcf-06,bar-09,krs-12,cbp-13,cce-15,fagotti-2014},
-the GGE with all the local charges has been explicitly constructed \cite{fagotti-2014,pozsgay-2013,fagotti-2013b}, 
-and the quench action solution provided for some initial states \cite{pozsgay-2014A,wouters-2014A}.
-
-For concreteness reasons, we focus on the isotropic Heisenberg point ($XXX$), i.e. Hamiltonian \eref{xxx-ham} with $\Delta=1$, 
-but we stress that our approach applies to arbitrary $\Delta$, and  also to arbitrary integrable models. 
-We consider the quenches from the zero-momentum N\'eel 
-state $|N\rangle$ and the Majumdar-Ghosh state $|MG\rangle$, which are defined as  
+The non-equilibrium quench dynamics of the XXZ spin chain has been investigated 
+numerically intensively \cite{dmcf-06,bar-09,krs-12,cbp-13,cce-15,fagotti-2014}, the GGE with all the 
+local charges has been explicitly constructed \cite{fagotti-2014,pozsgay-2013,fagotti-2013b}, 
+and the quench action solution has been provided for some initial states~\cite{pozsgay-2014A,wouters-2014A}.
+
+For concreteness reasons, we focus on the isotropic Heisenberg point ($XXX$), i.e. 
+Hamiltonian~\eref{xxx-ham} with $\Delta=1$, but we stress that our approach applies to arbitrary 
+$\Delta$, and  also to arbitrary integrable models. We consider the quenches from the zero-momentum 
+N\'eel state $|N\rangle$ and the Majumdar-Ghosh state $|MG\rangle$, which are defined as  
 %
@@
 Bethe equations, and it can be done only in very simple cases, e.g., for small 
-chains (as explicitly done for the attractive Lieb-Liniger gas for small number of particles \cite{calabrese-2014}). 
-On the other hand, it has been argued that zero-momentum strings are irrelevant for the reconstruction of the 
-representative state in the thermodynamic limit~\cite{wouters-2014A}.
+chains (as explicitly done for the attractive Lieb-Liniger gas for small number 
+of particles \cite{calabrese-2014}). On the other hand, it has been argued that 
+zero-momentum strings are irrelevant for the reconstruction of the representative 
+state in the thermodynamic limit~\cite{wouters-2014A}.
 
@@
 
-%The key idea is to sample the eigenstates with no zero-momentum 
-%strings with the diagonal ensemble probability measure $\rho^{DE}$ (cf.~\eref{de1}). 
 We also develop a Monte Carlo scheme, which is a generalization of 
@@
 
-Strikingly, after the reweighting, although for small chains violations of the conserved quantities 
-sum rules are present, these violations vanish in the thermodynamic limit 
-and the sum rules are restored. This implies that the only effect of the 
-Hilbert space truncation is to introduce finite size scaling corrections. 
+Strikingly, after the reweighting, although for small chains violations of 
+the conserved quantities sum rules are present, these violations vanish in the 
+thermodynamic limit and the sum rules are restored. This implies that the only 
+effect of the Hilbert space truncation is to introduce finite size scaling corrections. 
 In the quench action language, this means that the eigenstates corresponding to non 
-zero-momentum strings contain enough physical information about saddle point. 
+zero-momentum strings contain enough physical information about the saddle point. 
 This is numerically confirmed by extracting the so-called saddle point 
@@
  approach these are obtained from the histograms of the Bethe ansatz 
-solutions sampled during the Monte Carlo. A part from finite size scaling 
+solutions sampled during the Monte Carlo. Apart from finite size scaling 
 corrections, we observe striking agreement with analytical results, at least 
 for the first few root distributions.
-
-%It is useful to rewrite~\eref{d-ensemble} as 
-%
-%\begin{equation}
-%\label{qa-prob}
-%\langle{\mathcal O}\rangle=\sum\limits_{\alpha}\rho^{DE}(\alpha)
-%\langle\alpha|{\mathcal O}|\alpha\rangle,\quad\textrm{with}\quad 
-%\rho^{DE}(\alpha)=\exp(-2\Re{\mathcal E}(\alpha)).
-%\end{equation}
-%
-%Here $\rho^{DE}(\alpha)$ is a diagonal ensemble density matrix, and ${\mathcal E}(\alpha)
-%\equiv-\ln\langle\alpha|\Psi_0\rangle$, with $\Re$ denoting the real part.
-
-%The N\'eel state is defined as 
-%
-%\begin{equation}
-%\label{N\'eel}
-%|N\rangle\equiv\frac{1}{\sqrt{2}}\big(|N_1\rangle
-%+|N_2\rangle\big), 
-%\end{equation}
-%
-
-%The Majumdar-Ghosh state $|MG\rangle$ is defined as 
-%
-%\begin{equation}
-%\label{mg}
-%|MG\rangle\equiv \Big(\frac{|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle}
-%{\sqrt{2}}\Big)^{\otimes L/2}. 
-%\end{equation}
-%
 
@@
 local conserved charges of the model.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{The spin-$\frac{1}{2}$ Heisenberg chain}
-%\label{sec:1.1}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Counting and string content of the eigenstates with nonzero N\'eel and 
-%Majumdar-Ghosh overlap}
-\subsection{Counting and string content of parity-invariant eigenstates}
+\subsection{Parity-invariant eigenstates with non-zero N\'eel and Majumdar-Ghosh overlap: 
+counting and string content}
 \label{app-1}
@@
 Here we provide some exact combinatorial formulas for the total number of 
-parity-invariant eigenstates of the $XXX$ chain, which are the only eigenstates 
-having, in principle, non-zero overlap with the N\'eel state and the 
-Majumdar-Ghosh state~\cite{brockmann-2014}. 
+parity-invariant eigenstates of the $XXX$ chain in the sector with $L/2$ 
+particles. These are the only eigenstates having, in principle, non-zero 
+overlap with the N\'eel state and the Majumdar-Ghosh state~\cite{brockmann-2014}. 
 Parity-invariant eigenstates correspond to solutions of the Bethe equations 
@@
 eigenstates are in one-to-one correspondence with parity-invariant BGT quantum number 
-configurations. %In~\ref{app-1.1} we consider all possible parity-invariant 
-%eigenstates, whereas in~\ref{app-1.2} we exclude the eigenstates containing 
-%zero-momentum strings.
-
-For simplicity we restrict ourselves 
-to the situation with $L$ divisible by four. The strategy of the proof is the 
-same as that used to count the number of solutions of the Bethe-Gaudin-Takahashi 
-equations (see for instance Ref.~\cite{faddeev-1996}).  Specifically, the idea 
-is to count all the possible BGT quantum numbers configurations corresponding 
-to parity-invariant eigenstates (cf. section~\ref{sec:1.3}).
+configurations.
+
+For simplicity we restrict ourselves to the situation with $L$ divisible by four. 
+The strategy of the proof is the same as that used to count the number of solutions 
+of the Bethe-Gaudin-Takahashi equations (see for instance Ref.~\cite{faddeev-1996}). 
+Specifically, the idea is to count all the possible BGT quantum numbers configurations 
+corresponding to parity-invariant eigenstates (cf. section~\ref{sec:1.3}).
 
@@
 with non-zero N\'eel overlap, while~\eref{N-count-nz} is exact. Before 
-proceeding, we should stress that the total number of particles  
-in the eigenstates having non-zero overlap with the N\'eel and Majumdar-Ghosh 
-states is fixed to $L/2$, due to the fact that for both states one has $S_T^z=0$. 
-However, since the N\'eel state is not $SU(2)$ invariant, eigenstates with 
-non-zero N\'eel overlap can contain infinity rapidities. Thus, one has to 
-consider all the possible sectors with $L/2=\ell+N_{\infty}$, and $\ell$ 
+proceeding, we should stress that since the N\'eel state is not $SU(2)$ invariant, 
+eigenstates with non-zero N\'eel overlap can contain infinite rapidities. Thus, 
+one has to consider all the possible sectors with $L/2=\ell+N_{\infty}$, and $\ell$ 
 ($N_\infty$) the number of finite (infinite) rapidities. Notice that this 
@@
 s_{\ell}\}$. Here $s_n$ is the number of $n$-strings, with the constraint 
-$\sum_k ks_k=\ell$. 
-It is straightforward to check that 
-the total number of parity-invariant quantum number pairs ${\mathcal N}_n(L,{
-\mathcal S})$ in the $n$-string sector is given as 
+$\sum_k ks_k=\ell$. It is straightforward to check that the total number of 
+parity-invariant quantum number pairs ${\mathcal N}_n(L,{\mathcal S})$ in the 
+$n$-string sector is given as 
 %
@@
 and~\eref{NnLS} gives ${\mathcal N}_n(L,{\mathcal S})=\lfloor (L-q)/2\rfloor$. 
-It is straightforward to check that for $q$ even the ansatz 
+It is straightforward to check that to satisfy~\eref{NpLlq} for $q$ even one has 
+to choose 
 %
@@
 % 
-satisfies~\eref{NpLlq}. Instead, for $q$ odd the solution of~\eref{NpLlq} is 
+Instead, for $q$ odd one has
 %
@@
 chain with the quench action probability distribution, given in~\eref{qa-d-ensemble}. 
-Importantly, we consider a truncated Hilbert space, restricting ourselves to the 
+Similar Monte Carlo techniques to sample the Hilbert space of integrable models 
+have been used in Ref.~\cite{gu-2005,buccheri-2011,faribault-2013}. 
+Importantly, here we consider a truncated Hilbert space, restricting ourselves to the 
 eigenstates corresponding to solutions of the BGT equations with no zero-momentum 
@@
 \section*{References}
+
 \begin{thebibliography}{99}
-
-%%% EXPERIMENTS
 \bibitem{bloch-2008}
@@
 
-%%% QUENCHES
 \bibitem{polkovnikov-2011}
@@
 C. Gogolin and J. Eisert,  arXiv:1503.07538.
-%Equilibration, thermalisation, and the emergence of statistical mechanics in closed quantum systems
-
-%%% ETH
+
 \bibitem{deutsch-1991} 
@@
 
-%%%%%FREE
-
 \bibitem{calabrese-2006}
@@
 D.~Rossini, S.~Suzuki, G.~Mussardo, G.~E.~Santoro, and A.~Silva, Phys.\ Rev.\ B\ {\bf 82}, 144302 (2010).
-
-\bibitem{mossel-2012a}
-J.~Mossel and J.-S.~Caux, New\ J.\ Phys.\ {\bf 14} 075006 (2012).
 
@@
 
-\bibitem{kcc14}
-M.~Kormos, M.~Collura, and P.~Calabrese, Phys.\ Rev.\ A {\bf 89}, 013609  (2014).
-
-\bibitem{kcc14a}
-P.~P.~Mazza, M.\ Collura, M.\ Kormos, and P.\ Calabrese, J.\ Stat.\ Mech.\   (2014) P11016.
-
-\bibitem{fagotti-2013}
-M.~Fagotti and F.~H.~L.~Essler, Phys.\ Rev.\ B\ {\bf87}, 245107 (2013).
+\bibitem{mossel-2012a}
+J.~Mossel and J.-S.~Caux, New\ J.\ Phys.\ {\bf 14} 075006 (2012).
 
@@
 
+\bibitem{fagotti-2013}
+M.~Fagotti and F.~H.~L.~Essler, Phys.\ Rev.\ B\ {\bf87}, 245107 (2013).
+
+\bibitem{kcc14}
+M.~Kormos, M.~Collura, and P.~Calabrese, Phys.\ Rev.\ A {\bf 89}, 013609  (2014).
+
+\bibitem{kcc14a}
+P.~P.~Mazza, M.\ Collura, M.\ Kormos, and P.\ Calabrese, J.\ Stat.\ Mech.\   (2014) P11016.
+
 \bibitem{sotiriadis-2014}
@@
 
-%%%%%%
-
 \bibitem{ilievski-2015a}
@@
 \bibitem{ga-15}
-G. Goldstein and N. Andrei, % Equilibration and generalized Gibbs ensemble for hard wall boundary conditions,
-Phys. Rev. B \textbf{92}, 155103 (2015).
+G. Goldstein and N. Andrei, Phys. Rev. B \textbf{92}, 155103 (2015).
 
@@
 
-\bibitem{de_luca} A. De Luca, G. Martelloni, and J. Viti, %Stationary states in a free fermionic chain from the quench action method.
- Phys. Rev. A \textbf{91}, 021603 (2015).
+\bibitem{de_luca} A. De Luca, G. Martelloni, and J. Viti,  Phys. Rev. A \textbf{91}, 021603 (2015).
 
@@
 
-%%%QA FULL DYNAMICS
+\bibitem{de-nardis-2015a}
+J.~De~Nardis and J.-S.~Caux, J.\ Stat.\ Mech.\ (2014) P12012.
+
 \bibitem{de-nardis-2015}
@@
 
-\bibitem{de-nardis-2015a}
-J.~De~Nardis and J.-S.~Caux, J.\ Stat.\ Mech.\ (2014) P12012.
-
-%%% BETHE ANSATZ
 \bibitem{bethe-1931}
@@
 
-%%%XXZ%
-
 \bibitem{dmcf-06}
-G. De Chiara, S. Montangero, P. Calabrese, and R. Fazio,  %Entanglement Entropy dynamics in Heisenberg chains, 
-J. Stat. Mech. P03001 (2006).
+G. De Chiara, S. Montangero, P. Calabrese, and R. Fazio,  J. Stat. Mech. P03001 (2006).
 
@@
 
-%%% OVERLAPS
 \bibitem{brockmann-2014}
@@
 
+\bibitem{brockmann-2014b}
+M.~Brockmann, J.\ Stat.\ Mech.\ (2014) P05006.
+
 \bibitem{brockmann-2014c}
 M.~Brockmann, J.~De~Nardis, B.~Wouters, and J.-S.~Caux, J.\ Phys.\ A {\bf 47}, 145003 (2014).
-
-\bibitem{brockmann-2014b}
-M.~Brockmann, J.\ Stat.\ Mech.\ (2014) P05006.
 
@@
 
-%%%%%%%
 \bibitem{alba-2015}
 V.~Alba, arXiv:1507.06994.
+
+\bibitem{faddeev-1996}
+L.~D.~Faddeev, arXiv:9605187.
 
@@
 
+\bibitem{gu-2005}
+S.-J.~Gu, N.~M.~R.~Peres, Y.-Q.~Li, Eur.\ Phys.\ J.\ B {\bf 48}, 
+157 (2005).
+
+\bibitem{buccheri-2011}
+F.~Buccheri, A.~ De Luca, and A.~Scardicchio, Phys.\ Rev.\ B {\bf 84}, 
+094203 (2011).
+
+\bibitem{faribault-2013}
+A.~Faribault and D.~Schuricht, Phys.\ Rev.\ Lett.\ {\bf 110}, 040405 
+(2013).
+
 \bibitem{quenouille-1949} 
@@
 
-\bibitem{faddeev-1996}
-L.~D.~Faddeev, arXiv:9605187.
+%%% EXPERIMENTS
+
+%%% QUENCHES
+
+%Equilibration, thermalisation, and the emergence of statistical mechanics in closed quantum systems
+
+%%% ETH
+
+%%%%%FREE
+
+%%%%%%
+
+% Equilibration and generalized Gibbs ensemble for hard wall boundary conditions,
+
+%Stationary states in a free fermionic chain from the quench action method.
+
+%%%QA FULL DYNAMICS
+
+%%% BETHE ANSATZ
+
+%%%XXZ%
+
+%Entanglement Entropy dynamics in Heisenberg chains,
+
+%%% OVERLAPS
+
+%%%%%%%
 

### 2016-01-25 QAMC_draft/referee_response/response.txt
response

Dear editor,

We are submitting a revised version of our manuscript "The quench action approach 
in finite integrable spin chains" in which we address all the points raised 
by the referee.

Sincerely,

Vincenzo Alba
Pasquale Calabrese

---------------------------------------------------------------------
RESPONSE TO THE REFEREE
---------------------------------------------------------------------

REFEREE:

This paper represents a numerical implementation of the quench action approach,
introduced in [Phys. Rev. Lett. 110, 257203 (2013)], and in particular
addresses some questions raised in [J. Stat. Mech. (2014) P05004, Phys.
Rev. Lett. 113, 117202 (2014), J. Stat. Mech. (2014) P12009], concerning
the applicability of the method to interacting integrable models (where the
scattering matrix allows for the creation of bound states). These questions
are answered in full details and the developed numerical algorithm can be
generalized to other studies of the XXZ model in- and out-of-equilibrium.

RESPONSE:

	We thank the referee for the appreciating our work and for the positive 
	evaluation.

REFEREE:

	Abstract: There is probably a typo: ”charged” should indeed be ”charges”.

RESPONSE:

	We corrected the typo in the new version of the manuscript.

REFEREE:

	After formula 2: mutually conserved charges may be replaced with
	”mutually conserved local (and quasi-local) charges” which are the only
	one relevant for the application of the GGE logic.

RESPONSE:

	We modified the sentence according to the referee suggestion.

REFEREE:

	Page 4 : ” Physically, zero-momentum strings correspond to eigenstates
	amplitudes containing multi-particle bound states which are fully delocalized
	in the chain”. All the strings in each eigenstate are fully delocalized
	being eigenstate of the momentum operator. One may say that
	the zero momentum ones correspond to bound states of spins with zero
	propagation velocity (the post-quench light-cone velocity associated to
	them is zero).

RESPONSE:

	We thank the referee for the useful suggestion. We rephrased the sentence 
	in the new version of the manuscript to meet the referee suggestion.

REFEREE:

	Page 6 : ”the string deviations, which typically, i.e., for most of the
	chain eigenstates, vanish exponentially with L in the thermodynamic
	limit”. One may add that the complications arise when this condition
	is not valid, namely for zero momentum strings, when the deviation
	decay as power laws.

RESPONSE:

	We would like to thank the referee for the useful suggestion. We now 
	mention in the manuscript that zero-momentum strings exhibit deviations 
	which decay with a power law.

REFEREE:

	Page 8 : the observable ${\mathcal O}$ in formula 20 must be local for its matrix
	elements to be described by only a set of macroscopic distributions.

RESPONSE:

	We now rephrased the sentence as

		Moreover, for all the local observables ${\mathcal O}$ (the ones considered here)
		the contribution of the ...

	to stress the importance of the locality or quasilocality of ${\mathcal O}$

REFEREE:

	Formula 21: please define B (it is indeed defined later but here
	appears for the first time).

RESPONSE:

	We now define the Newton binomial after formula 21.

REFEREE:

	Formula 57: better use the same notation as in the determinant for the 
	string centers ($\lambda_{n;j}) since j is already used for the complex 
	rapidities)

RESPONSE:

	We modified the notation as suggested by the referee in formula 57 and 
	formula 59 as well.

REFEREE:

	After formula 71: One may comment that the vanishing of the overlaps
	with zero momentum even strings is related to the conservation laws
	of quasi-local charges [Phys. Rev. Lett. 115, 157201 (2015)]

RESPONSE:

	We now added the sentence after formula 71 as

		"This is because parity-invariant eigenstates with a single zero-momentum even-length ^M
		string, which are included in~\eref{zNeel1}, have identically zero N\'eel ^M
		overlap~\cite{brockmann-2014}. This is not related to the symmetries of the N\'eel ^M
		state, but to an ``accidental'' vanishing of the prefactor in the overlap ^M
		formula~\eref{Neel-ov}. In particular, this is related to the conservation of quasi-local
		charges~\cite{ilievski-2015a}."

	to mention the relationship between vanishing of the overlaps with zero-momentum strings 
	and conservation of quasi-local charges.

REFEREE:

	section 5.2 contains repetitions and numerous overlaps with section 2.4,
	maybe a rearrangement of the content of the two sections is necessary?

RESPONSE:

	We understand the point of the referee. However, we believe that having 
	section 5.2 somehow self-contained could be useful to the readers who are 
	numerically oriented and not interested in the Bethe ansatz details 
	of the result. Therefore, we would prefer, if the referee does not have 
	further objections, to keep section 5.2 as it is.

REFEREE:

	Monte Carlo algorithm: The authors may explain why one cannot simply
	restrict to the sector with N1 = 0 and then re-weight the whole
	sum. Indeed in reference [Phys. Rev. Lett. 110, 257203 (2013)] the
	representative state was chosen to have N1 = 0, as it was for the
	amount of zero momentum strings, therefore the logic should work in
	the same way.

RESPONSE:

	We thank the referee for this useful comment. We agree with the referee 
	that it should be possible to obtain the same results restricting to 
	the sector with N1=0. However, in our work we tried to present a numerical 
	procedure that was as general as possible. In doing so we decided to 
	include in our treatment all the spin sectors, including N1\ne0. The fact 
	that only N1=0 is the only relevant one in the thermodynamic limit 
	is not a necessary ingredient of the algorithm. Moreover, restricting to 
	N1=0 should not provide a significant improvement of the method as 
	the majority of the eigenstates of the XXX chain are in the sector with 
	N1=0;

REFEREE:

	Also would be very nice to have a plot of convergence of the Monte
	Carlo as a function of the Nsteps. One would expect that for larger
	system sizes the number of steps required is smaller if the initial state
	is chosen to be very close to the representative state. How the initial
	state of the algorithm is chosen? Did the authors try to select a proper
	discretization of the thermodynamic saddle point state ? (as done for
	example in [Phys. Rev. A 89, 033605 (2014), J. Phys. A: Math. Theor.
	48, 43FT01 (2015)])

RESPONSE:

	We thank the referee for raising these very important points. First, 
	the chosen initial state is not, in principle, important for the method. 
	The eigenstates sampled at large Monte Carlo times should not be affected 
	by the choice of the initial state. Of course a careful choice of the  
	initial state could could speed up the equilibration of the Monte Carlo. 
	However, we did not perform a sistematic study of that, and for simplicity, 
	we started the Monte Carlo simulations from the ground state of the XXX 
	chain.

	Regarding the possibility of using as initial state the discretization of 
	the saddle point state, this could certainly provide a way to improve 
	the algorithm. However, in our study we preferred not to exploit this 
	possibility in order to provide an unbiased benchmark of our numerical 
	method.

	Finally, regarding the convergence of the Monte Carlo procedure as a 
	function of the number of Monte Carlo steps, the behavior is more 
	complicated than the one described by the referee. First, in our Metropolis 
	step (formula (82) in the manuscript) we chose the proposed new eigenstate 
	|\lambda_j'\rangle completely random. This implies that in general 
	one has

		Re(\epilon'-\epsilon) \sim O(L)

	In turn this implies that if an eigenstate |\lambda_j\rangle corresponds to a 
	local minimum (not the global  one) it can be ''difficult'' for 
	the algorithm to get to a different eigenstate, because the Metropolis 
	transition probability decays exponentially as the system size increases.

	The main consequence is that at fixed number of Monte Carlo steps 
	the error bar increases dramatically upon increasing chain size. This is the 
	reason why we provide only results for L\le 60.

	This problem could be solved by changing the update scheme. The key idea would 
	be to provide in the Metropolis step a proposed new eigenstate |\lambda_j'
	\rangle such that

		\epsilon'-\epsilon \sim O(1)

	This can be clearly achieved if the Bethe number configuration corresponding to 
	|\lambda'_j\rangle are obtained from that of |\lambda_j\rangle by change only 
	``few'' Bethe numbers.

	However, the non triviality of the string content of the generic eigenstates 
	of the XXX chain, makes the implementation of this tricky, and we decided no to 
	do that in the present version of the code.

REFEREE:

	Formula 84 is generically wrong since a generic observable is a more
	involved function of the different string contents of the state (i.e. a
	determinant) and not simply a sum (which is true for the local and
	quasi-local conserved quantities). The authors should then rephrase
	then this point.

RESPONSE:

	We agree with the referee about this point. Below formula 84 we now added 
	the sentence

		"We should stress again that~\eref{ref-form} is true only
		for local or quasi-local observables, while generic observables are more complicated
		functions of the rapidities."

	to stress the importance of locality (and quasi-locality).

REFEREE:

	The authors should compute the expectation values of some simple
	local operators assion for the matrix elements are
	indeed well known (for example in arXiv:1108.6224).

RESPONSE:

	We thank the referee for this very useful comment. In fact, being able to calculate  
	generic correlation functions, besides being interesting on its own, would also provide 
	a more stringent check of the validity of the numerical method. However, 
	the correlation function proposed by the referee corresponds to the local energy 
	that we already provided in the manuscript.

	In order to benchmark our results for higher spins correlation functions we 
	now include in Figure 5 Monte Carlo results for the fluctuations of the local energy 
	density Q_2. Similar to Q4 this  corresponds to a four-spin opearator.

	We could also calculate higher spin correlation functions or some long range 
	correalation functions using known results (similar to 	the one mentioned by the 
	referee). However, this would imply a considerable numerical effort and we believe 
	it goes beyond the scope of the present paper.

REFEREE:

	Once implemented this last point, the ensemble of states created by the
	Monte Carlo algorithm should be enough to reproduce the whole time
	evolution after the quench with the logic of the quench action method
	(see [Phys. Rev. Lett. 110, 257203 (2013), J. Phys. A: Math. Theor.
	48, 43FT01 (2015)]). Can the authors comment on this?

RESPONSE:

	We thank the referee for raising this interesting point. We are in fact aware 
	of the possibility of simulating the full time evolution after a quantum quench 
	starting from the saddle point result. We believe that this would represent 
	a breaktrhough and could provide valuable insights to improve for instance 
	existing numerical methods such as tDMRG. We think that this would deserve a lot 
	of attention on its own and we plan to address it in future work.

### 2016-01-25 QAMC_draft/fs_qa_v9.tex
response

--- 2015-12-07 QAMC_draft/fs_qa_v8.tex
@@
 Hilbert space which allows us to study larger systems. We accurately reconstruct the expectation 
-values of the conserved charged and the root distributions in the stationary state, which turn 
+values of the conserved charges and the root distributions in the stationary state, which turn 
 out to match the exact thermodynamic results. The proposed method can be implemented even in 
@@
 %
-Here $Q_j$ are mutually commuting conserved quantities, i.e., $[{\mathcal H},Q_j]=0\,
+Here $Q_j$ are mutually commuting conserved local (and quasi-local) charges, i.e., $[{\mathcal H},Q_j]=0\,
 \forall j$ and $[Q_j,Q_k]=0\,\forall j,k$, whereas $\beta_j$ are Lagrange multipliers 
@@
 zero-momentum strings correspond to eigenstates amplitudes containing multi-particle  
-bound states which are fully delocalized in the chain. From the Bethe ansatz perspective, 
+bound states having zero propagation velocity. From the Bethe ansatz perspective, 
 in the thermodynamic limit the presence of zero-momentum strings leads to fictitious 
@@
 deviations, which typically, i.e., for most of the chain eigenstates, vanish 
-exponentially with $L$ in the thermodynamic limit. Note that real rapidities 
+exponentially with $L$ in the thermodynamic limit. A notable execption are the 
+zero-momentum strings for which string devitions exhibit power-law decay. Note that real rapidities 
 correspond to strings of unit length ($1$-strings, i.e., $n=1$ in~\eref{str-hyp}).
@@
 densities $\pmb{\rho}$ as $\langle\pmb{\rho}|{\mathcal O}|\pmb{\rho}\rangle$. 
-Moreover, for all the local observables considered here the contribution of the 
+Moreover, for all the local observables ${\mathcal O}$ (the ones considered here) 
+the contribution of the 
 different type of strings factorize, and $\langle\pmb{\rho}|{\mathcal O}|\pmb{\rho}
@@
 \label{N-count}
-Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1. 
-\end{equation}
-%
+Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1, 
+\end{equation}
+%
+with $B(x,y)\equiv x!/(y!(x-y)!)$ the Newton binomial. 
 On the other hand, after excluding the zero-momentum strings one obtains 
@@
 \fl\quad\prod\limits_{j=1}^m\frac{\sqrt{\tilde\lambda_j^2+1}}{4\tilde\lambda_j}=
-\frac{1}{4^m}\prod\limits_{j=1}^m\prod\limits_{\ell=1}^{\tilde s_j}\left[\frac{\sqrt{j^2+
-\tilde\lambda^2_{j;\ell}}}{\tilde\lambda_{j;\ell}}
-\prod\limits_{k=0}^{\lceil j/2\rceil-1}\frac{(2k)^2+\tilde\lambda^2_{j;\ell}}{(2k+1)^2+
-\tilde\lambda^2_{j;\ell}}\right]^{(-1)^j}, 
-\end{equation}
-%
-where $\tilde s_j$ is the number of $j$-string pairs in the Bethe state.
+\frac{1}{4^m}\prod\limits_{n=1}^m\prod\limits_{\ell=1}^{\tilde s_n}\left[\frac{\sqrt{n^2+
+\tilde\lambda^2_{n;\ell}}}{\tilde\lambda_{n;\ell}}
+\prod\limits_{k=0}^{\lceil n/2\rceil-1}\frac{(2k)^2+\tilde\lambda^2_{n;\ell}}{(2k+1)^2+
+\tilde\lambda^2_{n;\ell}}\right]^{(-1)^n}, 
+\end{equation}
+%
+where $\tilde s_n$ is the number of $n$-string pairs in the Bethe state.
 
@@
 \Big(1+\frac{\tilde\lambda_j+i}{\tilde\lambda_j-i}\Big)=\\\nonumber\qquad
-2^m\prod\limits_{j=1}^m\prod\limits_{\ell=1}^{\tilde s_j}
-\tilde\lambda_{j;\ell}^{1+(-1)^j}(\tilde\lambda^2_{j;\ell}+j^2)\prod\limits_{k=0}^{
-\lfloor j/2\rfloor}\Big[\tilde\lambda_{j;\ell}^2+\Big(2k+\frac{1-(-1)^j}{2}\Big)^2
+2^m\prod\limits_{n=1}^m\prod\limits_{\ell=1}^{\tilde s_n}
+\tilde\lambda_{n;\ell}^{1+(-1)^n}(\tilde\lambda^2_{n;\ell}+n^2)\prod\limits_{k=0}^{
+\lfloor n/2\rfloor}\Big[\tilde\lambda_{n;\ell}^2+\Big(2k+\frac{1-(-1)^n}{2}\Big)^2
 \Big]^{-2}.
@@
 \includegraphics[width=.9\textwidth]{./draft_figs/Neel_overlaps}
+%\includegraphics[width=.9\textwidth]{Neel_overlaps}
 \end{center}
@@
 state, but to an ``accidental'' vanishing of the prefactor in the overlap 
-formula~\eref{Neel-ov}. Finally, after excluding the zero-momentum strings 
+formula~\eref{Neel-ov}. In particular, this is related to the conservation of quasi-local 
+charges~\cite{ilievski-2015a}. Finally, after excluding the zero-momentum strings 
 eigenstates, the total number of remaining eigenstates $\widetilde Z_{Neel}$, 
@@
 \includegraphics[width=.9\textwidth]{./draft_figs/Neel}
+%\includegraphics[width=.9\textwidth]{Neel}
 \end{center}
@@
 not depend on the length of the chain.
-%Note also that the N\'eel state, $Q_n^{(0)}$ can be 
-%calculated directly in the thermodynamic limit using~\eref{q0-th} and the root 
-%distributions $\pmb{\rho}^*$ (cf.~\eref{rho1-sp}-\eref{rho3-sp}).
 
@@
 \includegraphics[width=.9\textwidth]{./draft_figs/Dimer}
+%\includegraphics[width=.9\textwidth]{Dimer}
 \end{center}
@@
 \includegraphics[width=.95\textwidth]{./draft_figs/full_vs_mc.pdf}
+%\includegraphics[width=.95\textwidth]{full_vs_mc.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=.9\textwidth]{./draft_figs/QAMC_Obs_Neel}
+\includegraphics[width=.9\textwidth]{./draft_figs/QAMC_Obs_Neel_v2}
+%\includegraphics[width=.9\textwidth]{QAMC_Obs_Neel}
 \end{center}
@@
  expected result $Q_2^{(0)}$. The dashed line is a fit to the behavior 
- $-1/2+A/L+B/L^2$, with $A,B$ fitting parameters.
- (b) Same as in (a) for the charge $Q_4$ without the fit. 
+ $-1/2+A/L+B/L^2$, with $A,B$ fitting parameters. The standard deviation 
+ of the fluctuations of the local energy density $\sigma(Q_2)/L$. 
+ (c) Same as in (a) for the charge $Q_4$ without the fit. 
 }
@@
 \includegraphics[width=.95\textwidth]{./draft_figs/Neel_rho}
+%\includegraphics[width=.95\textwidth]{Neel_rho}
 \end{center}
@@
 \begin{equation}
+\label{ref-form}
 \langle\lambda|{\mathcal O}|\lambda\rangle=\sum\limits_{n,\gamma}{\mathcal O}_n
@@
 different $n$-strings, are the solutions of the BGT equations~\eref{bgt-eq} 
-identifying the Bethe state $|\lambda\rangle$. By comparing~\eref{qamc-obs} 
+identifying the Bethe state $|\lambda\rangle$. We should stress again that~\eref{ref-form} is true only 
+for local or quasi-local observables, while generic observables are more complicated 
+functions of the rapidities. By comparing~\eref{qamc-obs} 
 and~\eref{obs-th} one obtains that in the limit $L,N_{mcs}\to\infty$ 
@@
 \includegraphics[width=.9\textwidth]{./draft_figs/L20_BT_check}
+%\includegraphics[width=.9\textwidth]{L20_BT_check}
 \end{center}
